### 2023-08-25 accepted/COPSolver/manuscript.tex
updating

\documentclass[11pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[margin=1.5cm]{geometry}
\usepackage{titlesec}
\usepackage{tabu}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{xcolor}
\newlist{selectlist}{itemize}{2}
\setlist[selectlist]{label=$\square$,leftmargin=*,noitemsep,topsep=0pt}

\usepackage{lmodern}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\urlstyle{same}

% Set up the section label formatting
\titleformat{\section}[block]{\hspace{1em}\bfseries}{\thesection.}{0.5em}{} 
\titleformat{\subsection}[block]{\hspace{1em}}{\thesubsection}{0.5em}{}

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

%\documentclass[preprint,12pt, a4paper]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
%\usepackage{amssymb}
%\usepackage{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%\usepackage{lineno}

%\journal{Software Impacts}

\begin{document}
\noindent
\textbf{COPSolver}
\vskip0.5cm
\noindent
\textbf{Tatiana Balbi Fraga, Federal University of Pernambuco, Avenida Marielle
Franco, Bairro Nova Caruaru, Caruaru, 55014-900, PE, Brazil, tatiana.balbi@ufpe.br}\\

\noindent
\textbf{Abstract}\\
This paper presents the software COPSolver, originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area. The first version of COPSolver has an application of the Fraga's exact method for solving the multi-product batch processing time maximization problem. This paper address the application of the current version of COPSolver and the next steps that will be implemented for software development and applications.
\vskip0.5cm

\noindent
\textbf{combinatorial optimization problem; exact method; multi-product batch problem; processing time maximization.}\\
\vskip0.5cm
\newpage
\noindent
\textbf{Code metadata}\\

%\begin{table}[!h]
\noindent
\begin{tabular}{|l|p{6.5cm}|p{9.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version & COPSolver\_1.0-1 \\
\hline
C2 & Permanent link to code/repository used for this code version & \underline{$https://github.com/tbfraga/COPSolver$} \\
\hline
C3  & Permanent link to Reproducible Capsule & \underline{$https://github.com/tbfraga/COPSolver$}\\
\hline
C4 & Legal Code License   & Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 International Public License \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & c++, CodeBlocks, LINGO, Ubuntu 22.04.1, GitHub\\
\hline
C7 & Compilation requirements, operating environments \& dependencies & elementary OS (can be adapted to Ubuntu) \\
\hline
C8 & If available Link to developer documentation/manual & \underline{$http://tbfraga.github.io/COPSolver/documentation/$} \\
\hline
C9 & Support email for questions & tbfraga@proton.me\\
\hline
\end{tabular}\\
%\caption{Code metadata (mandatory)}
%\label{} 
%\end{table}
\vskip0.5cm
\noindent

A decision problem arises when we need to choose an option from a set of known options so that the chosen decision meets a set of pre-established constraints. This problem is configured as an optimization problem when the decision taken must, in addition to meeting the constraints, be the one that best contributes to the achievement of a given group of objectives.

Decision and/or optimization problems are frequent in industrial and organizational environments, as well as in our daily lives. Usually the resolution of these problems brings great benefits, such as improving the efficiency of industrial processes, reducing costs, increasing productivity, increasing the useful life of equipments, helping to make better choices, bringing better cost-effectiveness, improving customer satisfaction, etc.

Given the enormous variety of decision-making and/or optimization problems and the complexity of such problems, the scientific literature brings numerous scientific materials that deal with the various problems and propose different solution methodologies for these problems.

Fraga et al. (2023) address the problem of maximizing the processing time of batches of various products. This problem arises in production process operations where a set of products are processed simultaneously on the same machine, but with production rates that can be different for each product. There is a production limit for each product and also for the products group, as well as a limit for the batch processing time. The problem consists of defining the maximum processing time of the multi-product batch respecting the known production limits. The authors also present an exact analytical method based on the batch processing time partitioning. This method is extremely efficient, proposing solutions very quickly and with low computational cost. This method was applied using COPSolver.

The COPSolver software was (and is being) developed by Dr. Tatiana Balbi Fraga with the purpose of solving several decision and optimization problems, mainly combinatory optimization problems, in the most efficient and robust way possible.

The first version of the software, COPSolver\_1.0-1, applies the analytical solution method developed by Fraga et al. (2023) to solve the multi-product batch processing time maximization problem. COPSolver package also contains the MBPTM.lng file, which is a code written in LINGO language to solve the model proposed by Fraga et al. (2023) for the multi-product batch processing time maximization problem. When run, COPSolver automatically generates a data.ldt file to be used with this LINGO code. However, the MBPTM.lng file can only be used through the LINGO software. More details about the LINGO software are available at https://www.lindo.com.

As future works, we will be applying COPSolver to assist in planning the production of extruders, in companies of the plastic bag production sector.

We will also include new solution methods for other decision and/or optimization problems. As the multi-product batch processing time maximization problem considers the planning period of just one day, in the next solver version, we will be considering a multi-period scenario.

Professor Fraga, author of this paper, and, more generally, her research group GAMOS (Group of Analysis, Modeling and Optimization of Systems), have developed many works focused on the identification, modeling and solution/optimization of real problems in industrial/organizational environments. Therefore, the development of COPSolver will be done in conjunction with the development of these works. Our intention is that the software can, in the near future, cover a wide range of methodologies to solve real problems and standard problems found in the literature. Thus, COPsolver can be used to solve real problems, or teaching and research. Later we intend to develop a pattern identification method (possibly based on neural networks) to recognize model patterns and solve different problems automatically.

In the future, we will also be developing extension projects to train micro and small companies to use COPSolver. We hope that COPSolver can help to improve several processes and, in particular, the productive and administrative processes of micro and small companies, offering them a tool to improve their competitive potential.

\vskip0.3cm
\noindent
\textbf{Acknowledgements}\\
Huge thanks to the teams responsible for developing elementary OS, as well as google translator, gummi, CodeBlocks, LINGO, GitHub, gcc, c++, and TeXLive libraries. Without the availability of these tools, COPSolver could never have been developed. I am also very grateful to my co-workers Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique for their constant support to the projects I develop and to my dear advisees Aldênia Karla Barrêto Candido, Lays Cristiane Cavalcante de Alcântara Aguiar, Edwedja de Lima Silva and Ítalo Ruan Barbosa de Aquino, among others, for having participated so enthusiastically in the projects that gave rise to this software, in particular for having made the effort to describe real processes in such detail. I would also like to thank the company in the plastic bag sector and other companies that made the studies possible as well as the identification of the new optimization problem addressed in the first version of COPSolver. \\

\noindent
\textbf{References}\\
Fraga, T.B., Aquino, Í.R.B. and Menêzes, R.C.S. (2023). Multi-product Batch Processing Time Maximization
Problem. Manuscript submitted for publication.  \\

\noindent
\textit{\textbf{Illustrative examples}}\\
\textit{Optional. You may submit an explanatory video or screencast that will appear to the right of your published article on ScienceDirect. Only one MP4 formatted video (max. size 150MB) is possible per article and this should be uploaded as a single supplementary file with your submission. Recommended video dimensions are 640 x 480 at a maximum of 30 frames / second. %Prior to submission, please test and validate your .mp4 file at  \url{http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification}. This tool will display your video in exactly the same way as it will appear on ScienceDirect.
}

\vskip 1.5cm

\end{document}
%\endinput
%%
%% End of file `SoftwareX_article_template.tex'.

### 2023-08-25 accepted/COPSolver/software_impacts_article_template.tex
updating

\documentclass[11pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.5cm]{geometry}
\usepackage{titlesec}
\usepackage{tabu}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{xcolor}
\newlist{selectlist}{itemize}{2}
\setlist[selectlist]{label=$\square$,leftmargin=*,noitemsep,topsep=0pt}

\usepackage{lmodern}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\urlstyle{same}

% Set up the section label formatting
\titleformat{\section}[block]{\hspace{1em}\bfseries}{\thesection.}{0.5em}{} 
\titleformat{\subsection}[block]{\hspace{1em}}{\thesubsection}{0.5em}{}

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

%\documentclass[preprint,12pt, a4paper]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
%\usepackage{amssymb}
%\usepackage{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%\usepackage{lineno}

%\journal{Software Impacts}

\begin{document}
\noindent
{\Large {\textbf{\textit {Software Impacts} article template}}} \textit{Version 2 (July 2021)}
\vskip0.5cm
\noindent
\textbf{Before you complete this template}, a few important points to note:
\begin{itemize}
\item[$\bullet$]{This template is for an Original Software Publication (OSP). If you are submitting an update to a software article that has already been published in \textit{Software Impacts}, please use the \underline{software update template}.}
\item[$\bullet$]{The format of a software article is very different to a traditional research article. To help you write yours, we have created this template. \textbf{\textit{Software Impacts} will only consider articles submitted using this template.}}
\item[$\bullet$]{It is mandatory to {\bf publicly share the code/software} referred to in your software article. You’ll find information on our software sharing criteria in the \textit{Software Impacts} \href{https://www.elsevier.com/journals/software-impacts/2665-9638/guide-for-authors}{\underline{Guide for Authors}}.}  
\item[$\bullet$]{It’s important to consult the \href{https://www.elsevier.com/journals/software-impacts/2665-9638/guide-for-authors}{\underline{Guide for Authors}} when preparing your manuscript; it highlights mandatory requirements and is packed with useful advice.}
\end{itemize}
\vskip0.5cm
\noindent
\textbf{Still got questions?}
\begin{itemize}
\item[$\triangleright$]{Email our editorial team at \href{mailto:Software.Impacts@elsevier.com}{\underline{Software.Impacts@elsevier.com}}}
\end{itemize}

\noindent
Now you are ready to fill in the template below. As you complete each section, please carefully read the associated instructions. All sections are mandatory, unless marked optional.\newline
\vskip0.5cm
\begin{center}
\colorbox{yellow}{\textbf{ \textit{ Once you have completed the template, delete this line and everything above it before} }}
\colorbox{yellow}{\textbf{ \textit{ submitting your article. In addition, please delete the instructions in the template}}} 
\colorbox{yellow}{\textbf{ \textit{  (the text written in italics).}}}
\colorbox{yellow}{- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - }
\end{center}

\noindent
\textbf{\textit{Title / name of your software}}
\vskip0.5cm
\noindent
\textbf{\textit{Names of authors / main developers (incl. affiliations, addresses, email)}}\\

\noindent
\textbf{Abstract}\\
\textit{(ca. 100 words)}
\vskip0.5cm

\noindent
\textbf{Keywords}\\
\textit{(maximum of six)}
\vskip0.5cm
\newpage
\noindent
\textbf{Code metadata}\\
\textit{Please replace the italicized text in the right column with the correct information about your code/software and leave the left column untouched.}\\

%\begin{table}[!h]
\noindent
\begin{tabular}{|l|p{6.5cm}|p{9.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version & \textit{For example: v42} \\
\hline
C2 & Permanent link to code/repository used for this code version & \textit{For example: \underline{$https://github.com/mozart/mozart2$}} \\
\hline
C3  & Permanent link to Reproducible Capsule & \\
\hline
C4 & Legal Code License   & \textit{All software and code must be released under one of the pre-approved licenses listed in the \href{https://www.elsevier.com/journals/software-impacts/2665-9638/guide-for-authors}{\underline{Guide for Authors}}, such as Apache License, GNU General Public License (GPL) or MIT License. Write the name of the license you’ve chosen here.} \\
\hline
C5 & Code versioning system used & \textit{For example svn, git, mercurial, etc. (put ‘none’ if none used)} \\
\hline
C6 & Software code languages, tools, and services used & \textit{For example C++, python, r, MPI, OpenCL, etc. }\\
\hline
C7 & Compilation requirements, operating environments \& dependencies & \\
\hline
C8 & If available Link to developer documentation/manual & \textit{For example: \underline{$http://mozart.github.io/documentation/$} }\\
\hline
C9 & Support email for questions & \\
\hline
\end{tabular}\\
%\caption{Code metadata (mandatory)}
%\label{} 
%\end{table}
\vskip0.5cm
\noindent
\textit{\textbf{Body of the article} (excluding metadata, tables, figures, references)}\\
\textit{You are welcome to write up to three pages of text that describes your software. Include points such as:}
\noindent
\begin{itemize}
\item \textit{A short description of the high-level functionality and purpose of the software for a diverse, non-specialist audience}
\item \textit{An Impact overview that illustrates the purpose of your software and its achieved results. For example:}
{\it \begin{itemize}
\item[$\circ$]Any new research questions that can be pursued as a result of your software.
\item[$\circ$]In what way, and to what extent, your software improves the pursuit of existing research questions.
\item[$\circ$]Any ways in which your software has changed the daily practice of its users.
\item[$\circ$]How widespread the use of the software is within and outside the intended user group.
\item[$\circ$]How the software is being used in commercial settings and/or how it has led to the creation of spin-off companies.
\end{itemize}}
\vskip -0.7cm
\textit{\item Mentions (if applicable) any ongoing research projects using your software. }
\textit{\item Limitations and future improvements/applications of your software}
\textit{\item List of all scholarly publications enabled by your software.}
\end{itemize}
\vskip0.3cm
\textbf{Acknowledgements}\\
\textit{Optional. You can use this section to acknowledge colleagues who do not qualify as a co-author but helped you in some way. }\\

\noindent
\textbf{References}\\
\textit{If the software repository you used supplied a DOI, please add a reference for your software here.}\\

\noindent
\textit{\textbf{Illustrative examples}}\\
\textit{Optional. You may submit an explanatory video or screencast that will appear to the right of your published article on ScienceDirect. Only one MP4 formatted video (max. size 150MB) is possible per article and this should be uploaded as a single supplementary file with your submission. Recommended video dimensions are 640 x 480 at a maximum of 30 frames / second. %Prior to submission, please test and validate your .mp4 file at  \url{http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification}. This tool will display your video in exactly the same way as it will appear on ScienceDirect.
}

\vskip 1.5cm
\begin{center}
{\huge \it Reminder: Before you submit, please delete all 
the instructions in this document (the text in italics), including this paragraph.\\
Thank you!}
\end{center}

\end{document}
%\endinput
%%
%% End of file `SoftwareX_article_template.tex'.

### 2023-08-25 accepted/COPSolver/manuscript.tex
COPSover paper

@@
 The first version of COPSolver has an application of the Fraga's exact method for solving the multi-product batch processing time maximization problem.
-This paper address the application of the current version of COPSolver and the next steps that will be implemented for software development and applications.
+This paper address the COPSolver\_1.0-1 and the next steps that will be implemented for the software's applications development.
 \vskip0.5cm
@@
 Given the enormous variety of decision-making and/or optimization problems and the complexity of such problems, the scientific literature brings numerous scientific materials that deal with the various problems and propose different solution methodologies for these problems.
+However, it is rare to find software that solves such problems.
+Usually such software is closed code, developed directly to solve very specific industrial problems, and the rights of use are kept by the companies themselves.
 
-Fraga et al.
-(2023) address the problem of maximizing the processing time of batches of various products.
+COPSolver software was (and is being) developed by Dr. Tatiana Balbi Fraga with the purpose of solving several decision and optimization problems in the most efficient and robust way possible.
+
+The first version of the software, COPSolver\_1.0-1, applies the analytical solution method developed by Fraga et al.
+(2023) to solve the Multi-product Batch Processing Time Maximization (MBPTM) problem.
 This problem arises in production process operations where a set of products are processed simultaneously on the same machine, but with production rates that can be different for each product.
@@
 The problem consists of defining the maximum processing time of the multi-product batch respecting the known production limits.
-The authors also present an exact analytical method based on the batch processing time partitioning.
-This method is extremely efficient, proposing solutions very quickly and with low computational cost.
-This method was applied using COPSolver.
+The exact analytical method of Fraga et al.
+(2023) is extremely efficient, proposing solutions very quickly and with low computational cost.
 
-The COPSolver software was (and is being) developed by Dr.
-Tatiana Balbi Fraga with the purpose of solving several decision and optimization problems, mainly combinatory optimization problems, in the most efficient and robust way possible.
-
-The first version of the software, COPSolver\_1.0-1, applies the analytical solution method developed by Fraga et al.
-(2023) to solve the multi-product batch processing time maximization problem.
 COPSolver package also contains the MBPTM.lng file, which is a code written in LINGO language to solve the model proposed by Fraga et al.
@@
 
+COPSolver\_1.0-1 can serve as an important tool for inventory control for some companies.
+Also, it can be used for teaching and research.
 As future works, we will be applying COPSolver to assist in planning the production of extruders, in companies of the plastic bag production sector.
-
 We will also include new solution methods for other decision and/or optimization problems.
-As the multi-product batch processing time maximization problem considers the planning period of just one day, in the next solver version, we will be considering a multi-period scenario.
+As the MBPTM problem considers the planning period of just one day, in the next solver version, we will be considering a multi-period scenario.
 
@@
 Our intention is that the software can, in the near future, cover a wide range of methodologies to solve real problems and standard problems found in the literature.
-Thus, COPsolver can be used to solve real problems, or teaching and research.
 Later we intend to develop a pattern identification method (possibly based on neural networks) to recognize model patterns and solve different problems automatically.
-
 In the future, we will also be developing extension projects to train micro and small companies to use COPSolver.
@@
 
-\noindent
-\textit{\textbf{Illustrative examples}}\\
-\textit{Optional.
-You may submit an explanatory video or screencast that will appear to the right of your published article on ScienceDirect.
-Only one MP4 formatted video (max.
-size 150MB) is possible per article and this should be uploaded as a single supplementary file with your submission.
-Recommended video dimensions are 640 x 480 at a maximum of 30 frames / second.
-%Prior to submission, please test and validate your .mp4 file at  \url{http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification}.
-This tool will display your video in exactly the same way as it will appear on ScienceDirect.
-}
-
 \vskip 1.5cm

### 2023-08-25 accepted/COPSolver/manuscript.tex
updating paper

@@
 \textbf{Acknowledgements}\\
-Huge thanks to the teams responsible for developing elementary OS, as well as google translator, gummi, CodeBlocks, LINGO, GitHub, gcc, c++, and TeXLive libraries.
+Huge thanks to the teams responsible for developing elementary OS, as well as google translator, gummi, CodeBlocks, LINGO, git, GitHub, gcc, c++, and TeXLive libraries.
 Without the availability of these tools, COPSolver could never have been developed.

### 2023-08-25 accepted/COPSolver/manuscript.tex
updating paper

@@
 COPSolver package also contains the MBPTM.lng file, which is a code written in LINGO language to solve the model proposed by Fraga et al.
-(2023) for the multi-product batch processing time maximization problem.
+(2023) for the MBPTM problem.
 When run, COPSolver automatically generates a data.ldt file to be used with this LINGO code.
@@
 I am also very grateful to my co-workers Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique for their constant support to the projects I develop and to my dear advisees Aldênia Karla Barrêto Candido, Lays Cristiane Cavalcante de Alcântara Aguiar, Edwedja de Lima Silva and Ítalo Ruan Barbosa de Aquino, among others, for having participated so enthusiastically in the projects that gave rise to this software, in particular for having made the effort to describe real processes in such detail.
-I would also like to thank the company in the plastic bag sector and other companies that made the studies possible as well as the identification of the new optimization problem addressed in the first version of COPSolver.
+I would also like to thank the company in the plastic bag sector and other companies that made the studies possible as well as the identification of the new optimization problem addressed in COPSolver\_1.0-1.
 \\

### 2023-09-01 accepted/COPSolver/manuscript.tex
updating COPSolver paper

@@
 \usepackage{xcolor}
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric,shapes.misc,shapes.symbols,arrows.meta,graphs,fit,positioning,shadows}
+
 \newlist{selectlist}{itemize}{2}
@@
 \noindent
-\textbf{COPSolver}
+\textbf{COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multi-product batch processing time maximization problem}
 \vskip0.5cm
@@
 This paper presents the software COPSolver, originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area.
-The first version of COPSolver has an application of the Fraga's exact method for solving the multi-product batch processing time maximization problem.
+The first version of COPSolver has a application of the Fraga's exact method for solving the multi-product batch processing time maximization problem.
 This paper address the COPSolver\_1.0-1 and the next steps that will be implemented for the software's applications development.
@@
 \hline
-C3  & Permanent link to Reproducible Capsule & \underline{$https://github.com/tbfraga/COPSolver$}\\
+C3  & Permanent link to Reproducible Capsule & \underline{$https://codeocean.com/capsule/4837209$}\\
 \hline
@@
 
+\section{Motivation and significance}
+
 A decision problem arises when we need to choose an option from a set of known options so that the chosen decision meets a set of pre-established constraints.
@@
 However, it is rare to find software that solves such problems.
-Usually such software is closed code, developed directly to solve very specific industrial problems, and the rights of use are kept by the companies themselves.
+Usually such software is closed code, developed directly to solve very specific organizational problems, and the rights of use are kept by the developers and organizations involved in the software development project.
+Even when this does not occur, many pieces of software developed in research projects are simply not disclosed and end up being lost over time.
+
+For this reasons I have developed COPSolver (Combinatorial Optimization Problems Solver), to make available to everyone cientific tools that can help improve the decision management process as well as improve the efficiency of various organizational processes.
+
+\section{Software description}
 
@@
 
-COPSolver\_1.0-1 can serve as an important tool for inventory control for some companies.
-Also, it can be used for teaching and research.
+\subsection{Software architecture}
+
+COPSolver is open source software written in C++ language.
+Its architecture has been planned as follows: solver will be formed by a main.cpp file along with a library set (.h) and their respective source codes (.cpp).
+Each library will be developed to define and solve a single distinct type of problem.
+All libraries will contain two main structures called problem and solution, which will be used to define the parameters of the problem and the desired solution, respectively.
+Each library will also contain a class, called cop (for combinatorial optimization problems) or otherwise according to the nature of the problem addressed.
+Such class will basically contain functions for constructing/reading the problem, functions for solving the problem, and printing functions.
+Functions with similar purposes will be named with the same name using the functionalities of polymorphism.
+The libraries will be distinguished by a distinct namespace containing an acronym for the specific problem in the library itself.
+The definition of the problems can be done in three distinct ways: (1) through the data.txt file; (2) using solver predefined problems; and (3) generating a problem statically or randomly through pre-established functions of the solver.
+The config.txt file should be adjusted in order to inform the type of problem desired, as well as to select the method of defining the problem and the parameters that should be adjusted according to the chosen method.
+In the future, an extra library will be developed for automatic identification of the problem according to the definitions presented and for solution by the best method.
+For better suitability to the codeocean repository, the computational codes will be allocated within a folder named code, the files containing the input data (config.txt and data.txt) will be allocated within a folder named data, and the output files will be inserted into a folder named results.
+Also, files containing .h computational codes will be inserted inside a folder named lib while .cpp files (except main.cpp) will be inserted inside a folder named src.
+The lingo-language solvers developed for COPSolver validation will be available in specific folders within the folder named LINGOSolver.
+
+\begin{figure}[h]
+\begin{center}
+\begin{tikzpicture}[font=\sffamily,every label/.append style={font=\small\sffamily,align=center}]
+\tikzset{doc/.style={chamfered rectangle, draw, chamfered rectangle corners=north east, fill=blue!10,draw,thin,minimum height=1.2cm,align=center},
+pics/.cd,
+pack/.style={code={%
+\draw[fill=blue!50,opacity=0.2] (0,0) -- (0.5,-0.25) -- (0.5,0.25) -- (0,0.5) -- cycle;
+\draw[fill=blue!50,opacity=0.2] (0,0) -- (-0.5,-0.25) -- (-0.5,0.25) -- (0,0.5) -- cycle;
+\draw[fill=blue!60,opacity=0.2] (0,0) -- (-0.5,-0.25) -- (0,-0.5) -- (0.5,-0.25) -- cycle;
+\draw[fill=blue!60] (0,0) -- (0.25,0.125) -- (0,0.25) -- (-0.25,0.125) -- cycle;
+\draw[fill=blue!50] (0,0) -- (0.25,0.125) -- (0.25,-0.125) -- (0,-0.25) -- cycle;
+\draw[fill=blue!50] (0,0) -- (-0.25,0.125) -- (-0.25,-0.125) -- (0,-0.25) -- cycle;
+\draw[fill=blue!50,opacity=0.2] (0,-0.5) -- (0.5,-0.25) -- (0.5,0.25) -- (0,0) -- cycle;
+ \draw[fill=blue!50,opacity=0.2] (0,-0.5) -- (-0.5,-0.25) -- (-0.5,0.25) -- (0,0) -- cycle;
+\draw[fill=blue!60,opacity=0.2] (0,0.5) -- (-0.5,0.25) -- (0,0) -- (0.5,0.25) -- cycle;
+}}}
+\node[doc] (config) {config.txt};
+\node[below=2cm of config, doc] (data) {data.txt};
+\draw[-] (config) -- ++ (1.5,0) |- (data) coordinate[pos=0.25] (aux1);
+
+\node[draw,dashed,rounded corners,fit=(config) (data) (aux1),inner sep=10pt,label={above:{data}}](fit1){};
+
+\pic[right=2cm of fit1,local bounding box=code,scale=2] (COPSolver) {pack};
+\node[above=1mm of code,font=\small\sffamily,align=center]{COPSolver};
+
+\draw[-latex] (aux1) -- (code);
+
+\node[right=2cm of code.east,doc,fill=red!10] (datalng) {data.ldt};
+\node[above=1cm of datalng, doc, fill=red!10] (problem) {problem.txt};
+\node[below=1cm of datalng, doc, fill=red!10] (output) {output.txt};
+\node[draw,dashed,rounded corners,fit=(problem) (datalng) (output),inner sep=10pt,label={above:{results}}](fit2){};
+
+\draw[-latex] (code) -- ++ (2,0) coordinate(aux2) |- (problem);
+\draw[-latex] (aux2) |- (datalng);
+\draw[-latex] (aux2) |- (output);
+
+\node[below=3.7cm of code,doc,fill=green!10] (main) {main.cpp};
+\node[left=1cm of main,doc,fill=green!10] (mbptmh) {mbptm.h};
+\node[right=1cm of main,doc,fill=green!10] (mbptmcpp) {mbptm.cpp};
+
+\node[draw,dashed,rounded corners,fit=(mbptmh),inner sep=10pt,label={above:{lib}}](fit3){};
+\node[draw,dashed,rounded corners,fit=(mbptmcpp),inner sep=10pt,label={above:{src}}](fit4){};
+
+\node[below=0.5cm of main] (aux2) {};
+\node[above=0.5cm of main] (aux3) {};
+
+\draw[-latex] (mbptmh) -- (main);
+\draw[-latex] (fit4.south west) edge [bend left=25]  (fit3.south east);
+\draw[-latex] (main) -- (code);
+
+\node[draw,dashed,rounded corners,fit=(main) (fit3) (fit4) (aux2) (aux3),inner sep=10pt,label={above left:{code}}](fit5){};
+
+\node[above right=-0.5cm and 3cm of datalng,doc,fill=yellow!10] (lingocode) {MBPTM.lng};
+
+%\draw[-latex] (datalng.east) |- (lingocode.west);
+
+\draw[-latex] (datalng.east) -- ++ (1,0) coordinate(aux6) |- (lingocode.west);
+
+\node[draw,dashed,rounded corners,fit=(lingocode),inner sep=25pt,label={above:{MBPTM}}](fit6){};
+\node[draw,dashed,rounded corners,fit=(fit6),inner sep=20pt,label={above:{LINGOSolver}}](fit7){};
+
+\node[draw,dashed,rounded corners, white,fit= (fit1) (fit2) (fit5) (fit7),inner sep=20pt,label={above:{COPSolver}}](fit8){};
+
+\draw[dashed](fit8.north west) -- (fit8.north east);
+\draw[dashed](fit8.north west) -- (fit8.south west);
+
+\node[right=12cm of fit8.south west] (aux3) {};
+
+\draw[dashed](fit8.south west) -- (aux3.center);
+
+\node[above=4.5cm of aux3] (aux4) {};
+
+\draw[dashed](aux3.center) -- (aux4.center);
+
+\node[below=6.7cm of fit8.north east] (aux5) {};
+
+\draw[dashed](fit8.north east) -- (aux5.center);
+\draw[dashed](aux4.center) -- (aux5.center);
+
+\pic[below right=5cm and -0.5cm of fit7,local bounding box=lingo,scale=2] (LINGO) {pack};
+\node[above=1mm of lingo,font=\small\sffamily,align=center](cap){LINGO};
+
+%\draw[-latex] (lingocode) -- (cap);
+
+\draw[-latex] (lingocode.east) -| (cap);
+
+\node[above left=0.5cm and 1cm of lingo,doc,fill=orange!10] (outputlng) {MBPTM.lgr};
+
+\draw[-latex] (lingo.west) -| (outputlng.south);
+
+\draw[-latex] (outputlng) |- (output.east) node[midway,right,font=\small\sffamily,fill=white]{results validation};
+\end{tikzpicture}
+\end{center}
+\caption{Software architecture.}
+\end{figure}
+
+\section{Economic, technological, scientific and educational impact}
+
+The determination of the maximum processing time of multi-product batches is extremely important for some industries, as it is directly related to inventory management as well as to the correct fulfillment of demand.
+Therefore, COPSolver\_1.0-1 can serve as an important tool for inventory control, reducing costs and improving demand compliance.
 As future works, we will be applying COPSolver to assist in planning the production of extruders, in companies of the plastic bag production sector.
-We will also include new solution methods for other decision and/or optimization problems.
-As the MBPTM problem considers the planning period of just one day, in the next solver version, we will be considering a multi-period scenario.
+With this we hope to improve inventory management, increasing the competitive potential of these companies.
+
+COPSolver\_1.0-1 can also be used for teaching and research.
+It can be used to conduct case studies, assisting in teaching and research.
+Since COPSolver is built on the basis of libraries, it can also be reused in the development of other more complex software in research and technological projects.
+
+\section{Next steps}
 
@@
 Our intention is that the software can, in the near future, cover a wide range of methodologies to solve real problems and standard problems found in the literature.
-Later we intend to develop a pattern identification method (possibly based on neural networks) to recognize model patterns and solve different problems automatically.
+Later we intend to develop a pattern identification method to recognize problems patterns and solve different problems automatically.
 In the future, we will also be developing extension projects to train micro and small companies to use COPSolver.
@@
 \noindent
+\textbf{Declaration of competing interest}\\
+The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
+
+\vskip0.3cm
+\noindent
 \textbf{Acknowledgements}\\
-Huge thanks to the teams responsible for developing elementary OS, as well as google translator, gummi, CodeBlocks, LINGO, git, GitHub, gcc, c++, and TeXLive libraries.
+Huge thanks to the teams responsible for developing elementary OS, as well as google translator, gummi, CodeBlocks, LINGO, git, GitHub, gcc, and TeXLive libraries.
 Without the availability of these tools, COPSolver could never have been developed.

### 2023-09-04 accepted/COPSolver/manuscript.tex
updating COPSolver paper

@@
 There is a production limit for each product and also for the products group, as well as a limit for the batch processing time.
-The problem consists of defining the maximum processing time of the multi-product batch respecting the known production limits.
+The problem consists of defining the maximum processing time of the multi-product batch respecting the known restrictions.
 The exact analytical method of Fraga et al.
@@
 Functions with similar purposes will be named with the same name using the functionalities of polymorphism.
-The libraries will be distinguished by a distinct namespace containing an acronym for the specific problem in the library itself.
-The definition of the problems can be done in three distinct ways: (1) through the data.txt file; (2) using solver predefined problems; and (3) generating a problem statically or randomly through pre-established functions of the solver.
-The config.txt file should be adjusted in order to inform the type of problem desired, as well as to select the method of defining the problem and the parameters that should be adjusted according to the chosen method.
+The libraries will be distinguished by a distinct namespace containing an acronym that identifies the problem addressed in the library itself.
+The definition of the problems instances can be done in three distinct ways: 1) through the data.txt file; 2) using solver predefined problems; and 3) generating a problem statically or randomly through pre-established functions of the solver.
+The config.txt file should be adjusted in order to: 1) inform the type of problem addressed; 2) select the method of defining the problem and the parameters that should be adjusted according to the chosen method; and 3) select the method for solving the problem.
 In the future, an extra library will be developed for automatic identification of the problem according to the definitions presented and for solution by the best method.
@@
 Also, files containing .h computational codes will be inserted inside a folder named lib while .cpp files (except main.cpp) will be inserted inside a folder named src.
-The lingo-language solvers developed for COPSolver validation will be available in specific folders within the folder named LINGOSolver.
+The lingo-language solvers developed for COPSolver validation will be available in specific subfolders within the folder named LINGOSolver.
 
@@
 
-\node[below=3.7cm of code,doc,fill=green!10] (main) {main.cpp};
+\node[below left =3.7cm and -0.65cm of code.south,doc,fill=green!10] (main) {main.cpp};
 \node[left=1cm of main,doc,fill=green!10] (mbptmh) {mbptm.h};
@@
 \draw[-latex] (mbptmh) -- (main);
-\draw[-latex] (fit4.south west) edge [bend left=25]  (fit3.south east);
-\draw[-latex] (main) -- (code);
+
+\node[below=0.5cm of mbptmcpp] (aux6) {};
+
+\draw (mbptmcpp) -- (aux6.center);
+\draw[-latex] (aux6.center) -| (mbptmh);
 
@@
 
+\node[above=0.6cm of fit5, doc,regular polygon,regular polygon sides=8,fill=orange!30, scale=0.8, xscale=1.4] (compiler) {g++};
+
+\draw[-latex] (fit5) -- (compiler);
+\draw[-latex] (compiler) -- (code);
+
 \node[above right=-0.5cm and 3cm of datalng,doc,fill=yellow!10] (lingocode) {MBPTM.lng};
-
-%\draw[-latex] (datalng.east) |- (lingocode.west);
 
@@
 
-%\draw[-latex] (lingocode) -- (cap);
-
 \draw[-latex] (lingocode.east) -| (cap);
@@
 
+\node[above=0.5cm of outputlng, doc, shape=diamond, fill=black!10] (val) {validation};
+
 \draw[-latex] (lingo.west) -| (outputlng.south);
 
-\draw[-latex] (outputlng) |- (output.east) node[midway,right,font=\small\sffamily,fill=white]{results validation};
+\draw[-latex] (outputlng) -- (val);
+\draw[-latex] (output) -- (val);
+
 \end{tikzpicture}
@@
 
-COPSolver\_1.0-1 can also be used for teaching and research.
-It can be used to conduct case studies, assisting in teaching and research.
-Since COPSolver is built on the basis of libraries, it can also be reused in the development of other more complex software in research and technological projects.
+COPSolver\_1.0-1 can also be used to conduct case studies, assisting in teaching and research.
+Also, since COPSolver is built on the basis of problem-oriented libraries, it can also be reused in the development of other more complex software in research and technological projects.
 
@@
 \textbf{Acknowledgements}\\
-Huge thanks to the teams responsible for developing elementary OS, as well as google translator, gummi, CodeBlocks, LINGO, git, GitHub, gcc, and TeXLive libraries.
+Huge thanks to the teams responsible for developing elementary OS, as well as google translator, duckduckgo, gummi, CodeBlocks, LINGO, git, GitHub, gcc, and TeXLive libraries.
 Without the availability of these tools, COPSolver could never have been developed.

### 2023-09-05 accepted/COPSolver/manuscript.tex
rewriting the paper introduction

@@
 This paper presents the software COPSolver, originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area.
-The first version of COPSolver has a application of the Fraga's exact method for solving the multi-product batch processing time maximization problem.
+The first version of COPSolver has a application of Fraga's exact method for solving the multi-product batch processing time maximization problem.
 This paper address the COPSolver\_1.0-1 and the next steps that will be implemented for the software's applications development.
@@
 \hline
-C2 & Permanent link to code/repository used for this code version & \underline{$https://github.com/tbfraga/COPSolver$} \\
+C2 & Permanent link to code/repository used for this code version & $https://github.com/tbfraga/COPSolver/releases/tag$ $/v1.0\textrm{-}1$ \\
 \hline
-C3  & Permanent link to Reproducible Capsule & \underline{$https://codeocean.com/capsule/4837209$}\\
+C3  & Permanent link to Reproducible Capsule & $https://codeocean.com/capsule/4837209$\\
 \hline
@@
 
-The first version of the software, COPSolver\_1.0-1, applies the analytical solution method developed by Fraga et al.
+The first version of the software, COPSolver\_1.0-1, applies the exact solution method developed by Fraga et al.
 (2023) to solve the Multi-product Batch Processing Time Maximization (MBPTM) problem.
@@
 The problem consists of defining the maximum processing time of the multi-product batch respecting the known restrictions.
-The exact analytical method of Fraga et al.
+The exact method of Fraga et al.
 (2023) is extremely efficient, proposing solutions very quickly and with low computational cost.
@@
 
-COPSolver is open source software written in C++ language.
+COPSolver is an open source software written in C++ language.
 Its architecture has been planned as follows: solver will be formed by a main.cpp file along with a library set (.h) and their respective source codes (.cpp).

### 2023-09-05 manuscript/manuscript.tex
rewriting the paper introduction

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

\documentclass[authoryear,manuscript,12pt]{elsarticle}
\usepackage{setspace}
\doublespacing

\usepackage{algorithm}
\usepackage{algpseudocode}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

%% The `ecrc' package must be called to make the CRC functionality available
%\usepackage{ecrc}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,3p,times,authoryear]{elsarticle}
%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Computers \& Industrial Engineering}

\begin{document}

\begin{frontmatter}
%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}

\title{Multi-product Batch Processing Time Maximization Problem}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

%\author{Tatiana Balbi Fraga, Ítalo Ruan Barbosa de Aquino and Regilda da Costa e Silva Menêzes}

\author{Tatiana Balbi Fraga\corref{cor1}\fnref{label1}}
\ead{tatiana.balbi@ufpe.br}
\cortext[cor1]{corresponding author}

\author{Ítalo Ruan Barbosa de Aquino\fnref{label1}}
\ead{italo_ruan_@hotmail.com}

\author{Regilda da Costa e Silva Menêzes\fnref{label1}}
\ead{regilda.smenezes@ufpe.br}

%\affiliation[label1]{
%			 organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
%             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
%             city={Caruaru},
%             postcode={55014-900},
%             state={PE},
%             country={Brasil} }

\affiliation[label1]{
		   organization={Agreste Academic Center - Federal University of Pernambuco},%Department and Organization
           addressline={Avenida Marielle Franco, Nova Caruaru}, 
           city={Caruaru},
           postcode={55014-900}, 
           state={PE},
           country={Brazil}}

\begin{abstract}
In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates. The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch. In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MBPTM) problem. We also present a mathematical model for the MBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
\end{abstract}
%%Graphical abstract
%\begin{graphicalabstract}
%\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item brief bibliographic review on multi-product batch problems;
\item Multi-product Batch Processing Time Maximization (MBPTM) problem definition;
\item linear integer programming model for the MBPTM problem;
\item exact optimization method for solving the MBPTM problem.
\end{highlights}

\begin{keyword}
multiproduct batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep LINGO
\end{keyword}
\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
\label{sec:intro}

The term muti-product batch is usually applied to designate a type of industrial process in which the productions of different products batches share the same production facilities, but such facilities can process only a single products batch (or a limited set of products batches) at a time. The scientific literature address some different problems related to such industrial enviroment. Among these problems we have the multi-product batch plant design problem witch is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998). Another important problem is the multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product based on the known demand \citep{Eilon1985}. Since a single product (or a limited set of products) is (are) processed at a time, it is necessary that the quantity produced of each product is sufficient to meet the demand during the period in which other products batches are being processed. Also, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}. Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each products batch production, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}. Also, the cientific works consider MPBS problems within different manufacturing plants - such as single unit or serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{MendezEtAll2000, ShiEtAll2017}; and networked processes, in wich production units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}. In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each product will be processed.

In all papers presented above, each batch contains only one product type, and each machine can process only one batch (or product type) at a time. \cite{LiEtAl2022} deal with a PMPBS problem involving incompatible families with different job sizes and capacity constraints. In this problem, solutions are accepted in which two or more batches are processed simultaneously on the same machine. However, there are no production limitations for the production of each product group. The paper of \cite{LiEtAl2022} also presente an extensive literature review on production batch scheduling problems. Other important works deal with the problem of a multi-product batch plant design (MPBPD). In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).

In this work, we are concerned with determining the ideal processing time for a single batch consisting of a set of products, each product being or not different from the other products of the same batch. That is, we consider a specific case where different products are processed simultaneously on the same processor. This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils with different models of plastic bags.

As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution optmization method for solving this problem.

In the next sections, a presentation of problem is made along with an application example. Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution. Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks. In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions to this work are informed and acknowledgments are given, respectively. Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.

\section{Multi-product batch processing time maximization problem}
\label{sec:MBPTMP}

The multi-product batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch. In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product. In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set. The production quantity of each product is mainly defined according to the demand for the product. However, it is still possible to stock the products and/or send them to the outlets. In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch. Also, there is a time limit available for processing the batch. About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.

\emph{Example:} A certain machine must process a batch containing 2 different products: A and B. The production rate of A is 60 g/min while the production rate of B is 40 g/min. The factory has free stock for a maximum of 3000 g of any product, and, according to the company's inventory policy, a maximum of 3000 g of product A and 2000 g of product B can be stocked at the factory. There is a demand for 1000 g of product A and 500 g of product B. The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product. A maximum time of 100 minutes of this machine can be allocated for processing this batch. When distributing production the priority is to meet demand, then send to outlets and finily stock in factory. What is the maximum possible time for processing this batch and how production must be distributed ?

\section{Mathematical model}
\label{sec:mathModel}

Given that:

$\textrm{UD}_i$ is the demand for the product $i$;

$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch;

$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory;

$\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets;

$\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets;

$\textrm{p}_i$ is the production rate of product $i$;

$\textrm{Z}$ is the timeout for batch processing;

$P_i$ is the amount of product $i$ produced;

$D_i$ is the amount of product $i$ delivered for the demand;

$O_i$ amount of product $i$ shipped to factory outlets;

$I_i$ is the amount of product $i$ that will be stored at the factory;

$T$ is the batch processing time;

We have the problem:

\begin{equation}
\label{MBPTMP01}
max \quad T
\end{equation}

$s.t.$

\begin{equation}
P_i - \textrm{p}_i * T  = 0 \quad \forall i
\end{equation}

\begin{equation}
P_i - D_i - O_i - I_i = 0 \quad \forall i
\end{equation}

\begin{equation}
\label{MBPTMP04}
D_i \leq \textrm{UD}_i \quad \forall i
\end{equation}

\begin{equation}
O_i \leq \textrm{UO}_i \quad \forall i
\end{equation}

\begin{equation}
\sum_i{O_i} \leq \textrm{O}
\end{equation}

\begin{equation}
I_i \leq \textrm{UI}_i \quad \forall i
\end{equation}

\begin{equation}
\sum_i{I_i} \leq \textrm{I}
\end{equation}

\begin{equation}
T \leq \textrm{Z}
\end{equation}

\begin{equation}
\min \{\textrm{UD}_i - D_i, O_i + I_i\} = 0 \quad \forall i
\end{equation}

\begin{equation}
\min\{\textrm{O} - \sum_i\{ O_i\}, \textrm{UO}_i - O_i, I_i\} = 0 \quad \forall i
\end{equation}

\begin{equation}
\label{MBPTMP10}
T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
\end{equation}

where:

Constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$. Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$. Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the autlets, and the factory-stocked quantity of each product must be less than their respective known limits. Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values. The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected. Equations in (10) and (11) define the production distribution priority. And finally, the constraints in (12) inform the nature of the decision variables.

\section{Analytical solution}
\label{sec:analyticalSol}

O método proposto neste artigo para solução do MBPTM problem é composto por duas partes distintas, que são: a) cálculo do tempo máximo de processamento do lote multi-produtos; e b) cálculo e distribuição da produção entre a demanda, os outlets e o estoque em fábrica. A seguir, explicamos cada uma destas partes detalhadamente.

\noindent \emph{cálculo do tempo máximo de processamento do lote multi-produtos:}

It is possible to split the batch processing time into two time slots:

\begin{equation}
T = T' + T''
\end{equation}

\noindent where $T'$ é o tempo máximo de processamento cuja produção será utilizada exclusivamente para atendimento da demanda.

Neste caso, sendo $D_{i}^{'}$ a quantidade produzida do produto $i$ após $T'$ unidades de tempo de processamento do lote, temos que:

\begin{equation}
\label{eq:s02}
D_{i}^{'} - \textrm{p}_i * T'  = 0 \quad \forall i
\end{equation}

\begin{equation}
\label{eq:s03}
D_{i}^{'} \in Z \quad \forall i
\end{equation}

\noindent e, como $D_{i}^{'} \leq D_i$, $\forall i$, temos que:

\begin{equation}
\label{eq:s04}
D_{i}^{'} \leq \textrm{UD}_i\quad \forall i
\end{equation}

Das equações em (\ref{eq:s02}), (\ref{eq:s03}) e (\ref{eq:s04}), temos:

\begin{equation}
\label{eq:s05}
T' \leq \lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor \quad \forall i
\end{equation}

E, como desejamos máximo valor para $T'$, de (\ref{eq:s05}), temos:

\begin{equation}
\label{eq:s06}
T' = \min_i\{\lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor\}
\end{equation}

Observer que poderá haver uma sobra correspondente à demanda não atendida pela produção ocorrida na primeira parte do tempo de processamento do lote, $T'$. Esta sobra, $S_i$, será definida de acordo com as equações em (\ref{eq:s07}):

\begin{equation}
\label{eq:s07}
S_i = \textrm{UD}_i - D_{i}^{'} \quad \forall i
\end{equation}

É possível também considerar que os outlets são uma extensão do estoque da fábrica. Portanto it is possible to consider the factory stock of product $i$ and the outlets stock $i$ as single stock for the product $i$, de forma que:

\begin{equation}
\label{eq:s08}
E_i = O_i + I_i
\end{equation}

\begin{equation}
\label{eq:s09}
E_i \leq \textrm{UO}_i + \textrm{UI}_i
\end{equation}

\begin{equation}
\label{eq:s10}
\sum_i {E_i} \leq \textrm{O} + \textrm{I}
\end{equation}

\begin{equation}
\label{eq:s11}
E_i \in Z \quad \forall i
\end{equation}

\noindent where $E_i$ is the sum of factory stock and outlets stock of the product $i$.

Como o tempo $T'$ foi utilizado apenas para produção que irá atender à demanda, $T''$ será o restante do tempo de processamento, ou seja, o tempo máximo de processamento utilizado para produção que irá atender à sobra da demanda, será enviada para os outlets e estocada em fábrica. Assim temos que:

\begin{equation}
\label{eq:s12}
E_i + S_i - \textrm{p}_i * T''  = 0 \quad \forall i
\end{equation}

Portanto, das restrições em (\ref{eq:s09}) e equações em (\ref{eq:s12}), temos:

\begin{equation}
\label{eq:s13}
T''  \leq (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i \quad \forall i
\end{equation}

\noindent e, das restrições em (\ref{eq:s10}) e equações em (\ref{eq:s12}), temos:

\begin{equation}
\label{eq:s14}
 T'' \leq (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i
\end{equation}

Finalmente, como $T''$ é um valor inteiro e queremos maximizar esse valor, então:

\begin{equation}
\label{eq:s15}
 T'' = \lfloor\min\{\min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor
\end{equation}

So, the analytical method for finding maximum $T$ can be decomposed into 4 steps:

step 1: find $T'$, where:
\begin{equation}
T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
\end{equation}

step 2: calculate $S_i$ for all products.
\begin{equation}
\label{eq:unmet}
S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
\end{equation}

step 3: find $T''$, where:
\begin{equation}
T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
\end{equation}

step 4: calculate $T$, where: 
\begin{equation}
T^* = T' + T''
\end{equation}
\begin{equation}
T = \min \{T^* , \textrm{Z}\}
\end{equation}

Note that, à medida em que reduzimos o valor de $T'$, a consequente redução do valor de $D_{i}^{'}$ será atribuída diretamente à sobra $S_i$ e, portanto, there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1. Thus it is possible to use a simplification of the method presented, making $T' = 0$. In this case $S_i = \textrm{UD}_i, \forall i$. The simplified version of the method is presented below:

step 1: find $T^*$, where:
\begin{equation}
T^* = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
\end{equation}

step 2: calculate $T$, where:

\begin{equation}
T = \min \{T^* , \textrm{Z}\}
\end{equation}

Essa simplificação do método demonstra que o valor ótimo calculado para $T$ não depende da forma como a produção do produto $i$, $P_i$, é distribuída entre atendimento à demanda, $D_i$, outlets, $O_i$, e estoque de fábrica $I_i$.

We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply by seguindo the priorities for distribution. The following three algorithms can be used to find a complete solution.

The algorithm (\ref{alg:part01}) is used for finding an optimimal value fot $T$.

\begin{algorithm}
\caption{Solving MBPTM problem | Part 01 - find an optimal $T$ to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}).}\label{alg:part01}
\begin{algorithmic}
	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}$
	\State $T^* \gets \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor$
	\State $T \gets \min \{T^* , \textrm{Z}\}$
\State \textbf{Return:} $T$.
\end{algorithmic}
\end{algorithm}

Then an initial production distribution can be done by the algorithm (\ref{alg:part02}). Esta distribuição é feita sem levar em consideração as restrições definidas para o conjunto de produtos do lote. $SO$ e $SI$ representam, respectivamente, o quantidade total disponível a ser enviada para os outlets e a quantidade total disponível para estoque em fábrica após a distribuição inicial. Caso esse valores sejam negativo, isso indica que a distribuição inicial proposta não é uma distribuição viável.

\begin{algorithm}
\caption{Solving MBPTM problem | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions for the set of products of the batch.}\label{alg:part02}
\begin{algorithmic}
	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}, T$.
	\For{all i}
		\State $E_i \gets T * \textrm{p}_i$
		\State $D_i \gets \min \{\textrm{UD}_i, E_i\}$
		\State $E_i \gets E_i - D_i$
		\State $O_i \gets \min \{\textrm{UO}_i, E_i\}$
		\State $E_i = E_i - O_i$
		\State $\textrm{UO}_i = \textrm{UO}_i - O_i$
		\State $I_i = E_i$
		\State $\textrm{UI}_i = \textrm{UI}_i - I_i$
	\EndFor
	\State $SO = \textrm{O} - \sum_i{O_i}$
	\State $SI = \textrm{I} - \sum_i{I_i}$
	\State \textbf{Return:} $D_i, O_i, I_i, E_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
\end{algorithmic}
\end{algorithm}

Assim, after applying algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution. However, if $SO < 0$ or $SI <0$, solution is not yet feasible. But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements:

$if \quad SO < 0 \quad then \quad SI > 0 \quad and  \quad |SO| < SI$

$if \quad SI < 0 \quad then \quad SO > 0 \quad and  \quad |SI| < SO$

Therefore it is possible to meet the restrictions by applying the agorithm (\ref{alg:part03}). Neste algoritmo redistribuimos a produção do estoque para os outlets ou vice versa, respectivamente, em função de termos um $SI$ ou $SO$ negativo.

\begin{algorithm}
\caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch products set.}\label{alg:part03}
\begin{algorithmic}
\Require $O_i, I_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
\If{$SO < 0$}
\For{all $i$}
	\State $O_i \gets O_i - \min\{ O_i, UI_i, |SO|\}$
	\State $I_i \gets I_i + \min\{ O_i, UI_i, |SO|\}$
	\State $SO \gets SO + \min\{ O_i, UI_i, |SO|\}$
	\If{$SO = 0$}
		break looping for;
	\EndIf
\EndFor
\EndIf

\If{$SI < 0$}
\For{all $i$}
	\State $I_i \gets I_i - \min\{ I_i, UO_i, |SI|\}$
	\State $O_i \gets O_i + \min\{ I_i, UO_i, |SI|\}$
	\State $SI \gets SI + \min\{ I_i, UO_i, |SI|\}$
	\If{$SI = 0$}
		break looping for;
	\EndIf
\EndFor
\EndIf
\State \textbf{Return:} $O_i, I_i, \forall i$.
\end{algorithmic}
\end{algorithm}

\section{Tests and results}
\label{sec:results}

To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230814, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver. The tests were performed on a notebook with an Intel i7 processor. We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\

\begin{equation}
\textrm{p}_i = \textrm{rand}()\%30 + 10
\end{equation}

\begin{equation}
\textrm{UD}_i = \textrm{rand}()\%3000 + 800;
\end{equation}

\begin{equation}
 \textrm{seed1} = \textrm{rand}()\%3000 + 500;
\end{equation}

\begin{equation}
\textrm{seed2} = \textrm{rand}()\%5000 + 1000;
\end{equation}

\begin{equation}
\textrm{O} = \textrm{N}/2*\textrm{seed1};
\end{equation}

\begin{equation}
\textrm{UO}_i = \textrm{rand}()\%(\textrm{seed1}-500) + 500;
\end{equation}

\begin{equation}
\textrm{I} = \textrm{N}/2*\textrm{seed2};
\end{equation}

\begin{equation}
\textrm{UI}_i = \textrm{rand}()\%(\textrm{seed2}-1000) + 1000;
\end{equation}

\begin{equation}
\textrm{Z} = 100;
\end{equation}

\begin{table}[h]
\begin{center}
\begin{tabular}[c]{c r r r}
$i$ & 1 & 2 & total \\
\cline {1-4} \\
$\textrm{p}_i$ & 60 & 40 & \\
$\textrm{UD}_i$ & 1000 & 500 & \\
$\textrm{UO}_i$ & 600 & 600 & 1000 \\
$\textrm{UI}_i$ & 3000 & 2000 & 3000 \\
\cline {1-4} \\
& & $\textrm{Z}$ & 100 \\
\end{tabular}
\caption{Benchmark MBPTM 2}
\label{tab:MBPTMP001}
\end{center}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}[c]{c r r r r}
$i$ & 1 & 2 & 3 & total \\
\cline {1-5} \\
$\textrm{p}_i$ & 60 & 40 & 50 \\
$\textrm{UD}_i$ & 1000 & 500 & 800 \\
$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 \\
$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 3500 \\
\cline {1-5} \\
& & & $\textrm{Z}$ & 100 \\
\end{tabular}
\caption{Benchmark MBPTM 3}
\label{tab:MBPTMP002}
\end{center}
\end{table}

\begin{table}[h]
\begin{center}
\begin{small}
\begin{tabular}[c]{c r r r r r r r r r r r }
$i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
\cline {1-12} \\
$\textrm{p}_i$ & 60 & 40 & 50 & 40 & 30 & 50 & 60 & 10 & 20 & 40\\
$\textrm{UD}_i$ & 1000 & 500 & 800 & 500 & 400 & 500 & 2000 & 300 & 500 & 1000 \\
$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 & 300 & 200 & 500 & 800 & 0 & 200 & 3000 \\
$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 800 & 3000 & 1000 & 400 & 300 & 200 & 0 & 5000 \\
\cline {1-12} \\
& & & & & & & & & & $\textrm{Z}$ & 100 \\
\end{tabular}
\caption{Benchmark MBPTM 10}
\label{tab:MBPTMP003}
\end{small}
\end{center}
\end{table}

Randomly generated benchmarks were named RMBPTM $\textrm{N}$, being $\textrm{N}$ the number of products. Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value. To build the results presented in this work, we used source=0. The benchmarks used for the tests performed can be consulted at github.com/tbfraga/COPSolver.

Table \ref{tab:results} presents the results obtained by applying the analytical method (COPSolver) and the LINGO solver for the solution of the previously presented benchmarks.

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MBPTM 2 & 55 & 0.03 & 55 & $<$ 0.01 \\
MBPTM 3 & 48 & 0.03 & 48 & $<$ 0.01 \\
MBPTM 10 & 30 & 0.05 & 30 & $<$ 0.01 \\
RMBPTM 20 & 100 & 0.06 & 100 & $<$ 0.01 \\
RMBPTM 50 & 98 & 0.08 & 98 & $<$ 0.01 \\
RMBPTM 100 & 98 & 0.11 & 98 & $<$ 0.01 \\
RMBPTM 1,000 & 78 & 1.20 & 78 & $<$ 0.01 \\
RMBPTM 2,000 & 70 & 3.25 & 70 & $<$ 0.01 \\
RMBPTM 5,000 & 70 & 15.12 & 70 & $<$ 0.02 \\
RMBPTM 10,000 & 70 & 55.19 & 70 & $<$ 0.04 \\
\cline {1-5} \\
\end{tabular}
\caption{Results obtained with the LINGO solver and the analytical method}
\label{tab:results}
\end{footnotesize}
\end{center}
\end{table}

Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MBPTM 3 and 10 found by both COPSolver and LINGO solver. Files containing all results can be found at github.com/tbfraga/COPSolver.

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
product & production & delivered (s) & send to outlets & stocked in factory \\
\cline {1-5} \\
P1 & 2,880 & 1,000 & 300 & 1,580 \\
P2 & 1,920 & 500 & 600 & 820 \\
P3 & 2,400 & 800 & 600 & 1,000 \\
\cline {1-5} \\
\end{tabular}
\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 3}
\label{tab:compResultsMBPTMP2}
\end{footnotesize}
\end{center}
\end{table}

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
product & production & delivered (s) & send to outlets & stocked in factory \\
\cline {1-5} \\
P1 & 1,800 & 1,000 & 400 & 400 \\
P2 & 1,200 & 500 & 600 & 100 \\
P3 & 1,500 & 800 & 600 & 100 \\
P4 & 1,200 & 500 & 700 & 0 \\
P5 & 900 & 400 & 300 & 200 \\
P6 & 1,500 & 500 & 200 & 800 \\
P7 & 1,800 & 1800 & 0 & 0 \\
P8 & 300 & 300 & 0 & 0 \\
P9 & 600 & 500 & 0 & 100 \\
P10 & 1,200 & 1000 & 200 & 0 \\
\cline {1-5} \\
\end{tabular}
\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 10}
\label{tab:compResultsMBPTMP3}
\end{footnotesize}
\end{center}
\end{table}

It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method. As the analytical method is a polynomial time complexity method, we did not intend to compare computational costs, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.

We have considered here a one-day period problem, so in a future work we will study the complexities of solving a multi-period problem and try to propose new solution methods if needed.

\section{Conclusions and suggestions for future works}
\label{sec:conclusions}

In this paper we presented the Multi-product Batch Processing Time Maximization problem, as well as a mathematical model and an exact analytical solution method for this problem. The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO software, from LINDO Systems, and with a solver developed in C++ language. Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large problems, which demonstrates the efficiency of the proposed method. As in this paper we considered a planning period of one day, in a future work we will study the complexities that arise when considering the same problem in a multi-period scenario. We will also verify if there is the possibility of extending the proposed analytical method to solve a class of linear integer programming problems with similar characteristics to the studied problem.

\section{CRediT authorship contribution statement} 
\label{sec:contributions}

T.B. Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing. Í.R.B. Aquino: Data curation. R.C.S. Menêzes: Data curation.

\section{Acknowledgments}
\label{sec:acknowledgments}

We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects. We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process. Finally, we would like to thank Pró-reitoria de Extensão e Cultura da UFPE (PROExC) and the Research Director of Propesqi (Pró-reitoria de Pesquisa e Inovação da UFPE) for their support and recognition of our work, and dear Professors Antônio José da Silva Neto and João Flávio Vieira de Vasconcellos from IPRJ/UERJ, who contributed significantly to the formation of essential skills for the development of our projects. We also thank my co-worker Marcos Luiz Henrique, for having helped by evaluating the mathematical model and solution method proposed in this paper.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-harv} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{1}

%% \bibitem[Author(year)]{label}
%% Text of bibliographic item

\bibitem[\protect\citeauthoryear{Eilon}{1985}]{Eilon1985}
Eilon. (1985). Multi-product batch production on a single machine - A problem revisited. {\it OMEGA Int. J. of Mgmt Sci.}, Vol. 13 (5), pp. 453--468.

\bibitem[\protect\citeauthoryear{Kim \emph{et al.}}{1996}]{KimEtAl1996}
Kim, M., Jung, J. H. and Lee, I. (1996). Intelligent scheduling and monitoring for multi-product networked batch processes. {\it  Computers chem. Engn}, Vol. 20 (Suppl.), pp. 1149--1154.

\bibitem[\protect\citeauthoryear{Li et al.}{2022}]{LiEtAl2022}
Li, C., Wang, F., Gupta, J.N.D., Chung, T. (2022). Scheduling identical parallel batch processing machines involving incompatible families with different job sizes and capacity constraints. {\it Computers \& Industrial Engineering}, Vol. 169, pp. 108115.

\bibitem[\protect\citeauthoryear{Liu \emph{et al.}}{2020}]{LiuEtAl2020}
Liu, G., Li, F., Yang, X., and Qiu. S. (2020). The multi-stage multi-product batch-sizing problem in the steel industry. {\it  Applied Mathematics and Computation}, Vol. 369, 124830.

\bibitem[\protect\citeauthoryear{Méndez \emph{et al.}}{2000}]{MendezEtAll2000}
Méndez, C.A., Henning, G.P., Cerdá, J. (2000). Optimal scheduling of batch plants satisfying multiple product
orders with different due-dates. {\it Computers and Chemical Engineering}, Vol. 24, pp. 2223--2245.

\bibitem[\protect\citeauthoryear{Omega Journal}{1993}]{Omega1993}
OMEGA Journal. (1993). Single Machine Multi-product Batch Scheduling: Testing Several Solution Methods. {\it  OMEGA Int. J. of Mgmt Sci.}, Vol. 21 (6), pp. 709--711.

\bibitem[\protect\citeauthoryear{Ravemark and Rippin}{1998}]{RavemarkAndRippin1998}
Ravemark, D. E., and Rippin, D. W. T. (1998). Optimal design of a multi-product batch plant. {\it Computers chem. Engng}, Vol. 22 (1-2), pp. 177--183.

\bibitem[\protect\citeauthoryear{Shi \emph{et al.}}{2017}]{ShiEtAll2017}
Shi, B., Qian, X., Sun, S., Yan, L. (2017). Rule-based scheduling of multi-stage multi-product batch plants with parallel units. {\it Chinese Journal of Chemical Engineering}, in press.

\end{thebibliography}
\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

### 2023-09-06 manuscript/manuscript.tex
rewriting the introduction

@@
 \usepackage{algpseudocode}
+\usepackage{rotating}
+\usepackage{multirow}
 \newtheorem{theorem}{Theorem}
@@
 
-The term muti-product batch is usually applied to designate a type of industrial process in which the productions of different products batches share the same production facilities, but such facilities can process only a single products batch (or a limited set of products batches) at a time.
+The term muti-product batch is usually applied to designate an intermittent production system in which different products batches are processed sharing the same production facilities, but in a way that such facilities process only one batch at a time.
 The scientific literature address some different problems related to such industrial enviroment.
-Among these problems we have the multi-product batch plant design problem witch is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
-Another important problem is the multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product based on the known demand \citep{Eilon1985}.
-Since a single product (or a limited set of products) is (are) processed at a time, it is necessary that the quantity produced of each product is sufficient to meet the demand during the period in which other products batches are being processed.
-Also, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
+Among these problems we have the multi-product batch plant design witch is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
+The less complex multi-product batch problem is the batches sizing.
+Since a single products batch is processed at a time, it is necessary that the batches are dimensioned in such a way that the quantity produced of each product is sufficient to meet the demand during the period in which other products batches are being processed.
+Another important problem, however a little more complex, is the multi-product batch scheduling (MPBS), in which it is necessary to determine the ideal batch size for each product and also the production sequence of the products batches based on the known demand \citep{Eilon1985}.
+Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
 Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each products batch production, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
@@
 In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each product will be processed.
+
+\begin{sidewaystable}[h]
+\begin{center}
+\begin{small}
+\begin{tabular}[c]{|c|c|c|c|c|c|c|c|c|}
+reference & problem & period & stage & units & int. stor. & constraints & objectives & method \\
+\hline
+\multirow{2}{*}{\cite{Eilon1985}} & \multirow{2}{*}{scheduling} & \multirow{2}{*}{single} & \multirow{2}{*}{single} & \multirow{2}{*}{single} & & & minimize total setup;  \\
+ & & & & & & & minimize daily holding cost;  \\
+\multirow{3}{*}{\cite{ShiEtAll2017}} & \multirow{3}{*}{scheduling} & \multirow{3}{*}{single} & non-identical & \multirow{3}{*}{unlimited} & release time \\
+ & & & & parallel & & due date \\
+ & & & & & \\
+ & & & & \\
+\end{tabular}
+\label{tab:MBPTax}
+\caption{Multi-product batch problems taxonomy}
+\end{small}
+\end{center}
+\end{sidewaystable}
 

### 2023-09-11 manuscript/manuscript.tex
improving the introduction

@@
 
-The term muti-product batch is usually applied to designate an intermittent production system in which different products batches are processed sharing the same production facilities, but in a way that such facilities process only one batch at a time.
-The scientific literature address some different problems related to such industrial enviroment.
-Among these problems we have the multi-product batch plant design witch is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
-The less complex multi-product batch problem is the batches sizing.
-Since a single products batch is processed at a time, it is necessary that the batches are dimensioned in such a way that the quantity produced of each product is sufficient to meet the demand during the period in which other products batches are being processed.
-Another important problem, however a little more complex, is the multi-product batch scheduling (MPBS), in which it is necessary to determine the ideal batch size for each product and also the production sequence of the products batches based on the known demand \citep{Eilon1985}.
+The term multi-product batch production is usually applied to designate an intermittent production system in which batches of different products and sizes are processed one at a time, sharing the same production facilities.
+A multi-product batch plant basically consists of one or more units, grouped into one or more stages, and intermediate storage locations.
+At each stage some distinct operations are performed and the batches are processed sequentially over the stages.
+However, the plant layout can take on different formats, such as: single unit; serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{MendezEtAll2000, ShiEtAll2017}; and networked processes, in which production units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
+
+The scientific literature address many different problems related to such industrial enviroment, including the design, sizing and scheduling problems.
+The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
+The configuration of the plant basically consists of defining how many stages, how many units at each stage, and what capacity for intermediate storages will be necessary, as well as the best factory layout.
+
+Since a single products batch is processed at a time, it is also necessary that the batches are dimensioned in such a way that the quantity produced of each product is sufficient to meet the demand during the period in which other products batches are being processed.
+This problem is named multi-product batch sizing.
+
+We also have the multi-product batch scheduling (MPBS) problems, in which it is necessary to determine the ideal batch size for each product and also the production sequence of the products batches based on the known demand \citep{Eilon1985}.
 Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
 Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each products batch production, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
-Also, the cientific works consider MPBS problems within different manufacturing plants - such as single unit or serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{MendezEtAll2000, ShiEtAll2017}; and networked processes, in wich production units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
-In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each product will be processed.
+Also, the cientific works consider MPBS problems within different layouts.
+In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
 

### 2023-09-11 manuscript/manuscript.tex
multi-product balancing problem definition

@@
 The term multi-product batch production is usually applied to designate an intermittent production system in which batches of different products and sizes are processed one at a time, sharing the same production facilities.
-A multi-product batch plant basically consists of one or more units, grouped into one or more stages, and intermediate storage locations.
+A multi-product batch plant basically consists of one or more units, grouped into one or more stages, and possibly, intermediate storage locations.
 At each stage some distinct operations are performed and the batches are processed sequentially over the stages.
@@
 
-The scientific literature address many different problems related to such industrial enviroment, including the design, sizing and scheduling problems.
+The scientific literature address many different problems related to such industrial enviroment, including the design, sizing, scheduling and balancing problems.
 The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
@@
 Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each products batch production, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
-Also, the cientific works consider MPBS problems within different layouts.
+Also, some cientific works consider MPBS problems within different layouts and multiperiod scenario.
 In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
+
+It is importante to note that some production units are capable of processing multiple jobs at the same time.
+In such a case batches of different products and sizes can be grouped and processed by these units as a single batch.
+It is therefore necessary to determine the set of "batches" that each new grouped batch will contain.
+The multi-product balancing problem consists of determining these groupings, seeking to minimize the makespan.
+\cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.
+
+\cite{LiEtAl2022} deal with a PMPBS problem involving incompatible families with different job sizes and capacity constraints.
+In this problem, solutions are accepted in which two or more batches are processed simultaneously on the same machine.
+However, there are no production limitations for the production of each product group.
+The paper of \cite{LiEtAl2022} also presente an extensive literature review on production batch scheduling problems.
+Other important works deal with the problem of a multi-product batch plant design (MPBPD).
+In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
 
@@
 
-In all papers presented above, each batch contains only one product type, and each machine can process only one batch (or product type) at a time.
-\cite{LiEtAl2022} deal with a PMPBS problem involving incompatible families with different job sizes and capacity constraints.
-In this problem, solutions are accepted in which two or more batches are processed simultaneously on the same machine.
-However, there are no production limitations for the production of each product group.
-The paper of \cite{LiEtAl2022} also presente an extensive literature review on production batch scheduling problems.
-Other important works deal with the problem of a multi-product batch plant design (MPBPD).
-In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
+About the solution method many papers propose mathmatical models which are solved using IBM ILOG CPLEX or another constraint programming solver.
+
+Another not very common definition for multi-product batch production is a type of process in which several products are processed simultaneously in the same production unit.
 
@@
 
+\bibitem[\protect\citeauthoryear{Kashan and Ozturk}{2022}]{KashanOzturk2022}
+Kashan, A.
+H., and Ozturk, O.
+(2022).
+Improved MILP formulation equipped with valid inequalities for scheduling a batch processing machine with non-identical job sizes.
+{\it  Omega}, Vol.
+112, pp.
+102673.
+
 \bibitem[\protect\citeauthoryear{Kim \emph{et al.}}{1996}]{KimEtAl1996}

### 2023-09-11 manuscript/manuscript.tex
mixed multi-product batch problems

@@
 It is therefore necessary to determine the set of "batches" that each new grouped batch will contain.
-The multi-product balancing problem consists of determining these groupings, seeking to minimize the makespan.
+The multi-product balancing problem consists of determining these groupings, seeking to minimize the overall makespan.
 \cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.
+
+As normally, in a real production environment, some of these problems arise in a connected way, many authors work with mixed multi-product batch problems.
 

### 2023-09-13 manuscript/manuscript.tex
updating paper

@@
 \newtheorem{lemma}[theorem]{Lemma}
+
+\usepackage{xcolor}
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric,shapes.misc,shapes.symbols,arrows.meta,graphs,fit,positioning,shadows}
 
@@
 A multi-product batch plant basically consists of one or more units, grouped into one or more stages, and possibly, intermediate storage locations.
-At each stage some distinct operations are performed and the batches are processed sequentially over the stages.
-However, the plant layout can take on different formats, such as: single unit; serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{MendezEtAll2000, ShiEtAll2017}; and networked processes, in which production units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
+At each stage some distinct operations are performed and the batches are processed sequentially over the stages (serial batching).
+As stated by \cite{PetkovMaranas1998} the batch plant can operate under a single-product campaign (SPC) production mode, where all the batches of a given product are manufactured before production of the next product begins, or under mixed-product campaign (MPC) production modes where more batches are produced per unit time at the expense of increased changeover times and cleanup costs.
+Also the plant layout can take on different formats, such as: single unit, where all batches are processed at a single stage; serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{MendezEtAll2000, ShiEtAll2017}; and networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
 
-The scientific literature address many different problems related to such industrial enviroment, including the design, sizing, scheduling and balancing problems.
+The scientific literature address many different problems related to such industrial enviroment, including the design, planning, sizing, scheduling and balancing problems.
 The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
-The configuration of the plant basically consists of defining how many stages, how many units at each stage, and what capacity for intermediate storages will be necessary, as well as the best factory layout.
+The configuration of the plant basically consists of defining the number of stages, the number of units and their capacity per stage, and the capacity for intermediate storages, as well as the best factory layout.
 
-Since a single products batch is processed at a time, it is also necessary that the batches are dimensioned in such a way that the quantity produced of each product is sufficient to meet the demand during the period in which other products batches are being processed.
+The multi-product batch planning problem is basically determining the needs of materials and resources based on known demands and demand forecasts.
+
+Since a single batch is processed at a time, it is necessary that the batches are dimensioned in such a way that the quantity produced of each product is sufficient to meet the demand during the period in which other batches are being processed \citep{Eilon1985}.
 This problem is named multi-product batch sizing.
+\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production and \cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product s-batch sizing problem in a networked plant of a steel industry (Fig.
+\ref{fig:networkdPlantSteelIndustry}).
 
-We also have the multi-product batch scheduling (MPBS) problems, in which it is necessary to determine the ideal batch size for each product and also the production sequence of the products batches based on the known demand \citep{Eilon1985}.
+\begin{figure}[h]
+\label{fig:networkdPlantSteelIndustry}
+\begin{center}
+\begin{tikzpicture}[font=\sffamily,every label/.append style={font=\small\sffamily,align=center}]
+
+\node[cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP00){};
+\node[rectangle, draw, right=0.5cm of WIP00, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit00){};
+\node[draw,dashed,rounded corners,fit=(WIP00) (unit00),inner sep=25pt,label={above:{stage (0,0)}}](stage00){};
+
+\node[above right=2cm and 4cm of WIP00, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP11){};
+\node[rectangle, draw, right=0.5cm of WIP11, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit11){};
+\node[draw,dashed,rounded corners,fit=(WIP11) (unit11),inner sep=25pt,label={above:{stage (1,1)}}](stage11){};
+
+\draw[-latex] (stage00.east) -- (stage11.west);
+
+\node[right=2.5cm of stage00, minimum width=1cm, minimum height=1.4cm](WIP1){.....};
+
+\node[right=0.3cm of WIP1, minimum width=1cm, minimum height=1.4cm](WIP1a){};
+
+\draw[-latex] (stage00.east) -- (WIP1.west);
+
+\node[below right=2cm and 4cm of WIP00, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIPp1){};
+\node[rectangle, draw, right=0.5cm of WIPp1, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unitp1){};
+\node[draw,dashed,rounded corners,fit=(WIPp1) (unitp1),inner sep=25pt,label={above:{stage (p,1)}}](stagep1){};
+
+\draw[-latex] (stage00.east) -- (stagep1.west);
+
+\node[right=4cm of WIP11, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP1m){};
+\node[rectangle, draw, right=0.5cm of WIP1m, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit1m){};
+\node[draw,dashed,rounded corners,fit=(WIP1m) (unit1m),inner sep=25pt,label={above:{stage (1,m$_1$)}}](stage1m){};
+
+\draw[-latex] (stage11.east) -- (stage1m.west);
+
+\node[right=4cm of WIPp1, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIPpm){};
+\node[rectangle, draw, right=0.5cm of WIPpm, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unitpm){};
+\node[draw,dashed,rounded corners,fit=(WIPpm) (unitpm),inner sep=25pt,label={above:{stage (p,m$_p$)}}](stagepm){};
+
+\draw[-latex] (stagep1.east) -- (stagepm.west);
+
+\node[right=3.5cm of WIP1, minimum width=1cm, minimum height=1.4cm](WIPm){.....};
+
+\node[left=0.5cm of WIPm, minimum width=1cm, minimum height=1.4cm](WIPma){};
+
+\draw[-latex] (WIP1a.east) -- (WIPma.west);
+
+\end{tikzpicture}
+\end{center}
+\caption{Multi-product s-batch networked plant of a steel industry. Source: adapted from \cite{LiuEtAl2020} * stage $(i, j)$ means stage $j$ of production line $i$.}
+\end{figure}
+
+In multi-product batch scheduling (MPBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the products batches based on the known demand.
 Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
@@
 
-As normally, in a real production environment, some of these problems arise in a connected way, many authors work with mixed multi-product batch problems.
+In a real production environment, some of these problems arise in a connected way, so many cientific works adress mixed multi-product batch problems.
+\cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.
 
@@
 
-Another not very common definition for multi-product batch production is a type of process in which several products are processed simultaneously in the same production unit.
+In this work we are interested in a sub problem of the \emph{p-batch} scheduling problem described by \cite{KashanOzturk2022}, named multi-product batch processing time maximization (MBPTM) problem.
+When appliyng some local search heuristic for solving the \emph{p-batch} scheduling problem it is necessary to solve the MBPTM problem on each iteration, so it has a direct impact on the overall efficiency of any local search heuristc for solving the \emph{p-batch} scheduling problem.
+As scientific contributions, in this paper we present a mathematical model and a polynomial time complexity optmization method for solving this problem.
 
-In this work, we are concerned with determining the ideal processing time for a single batch consisting of a set of products, each product being or not different from the other products of the same batch.
-That is, we consider a specific case where different products are processed simultaneously on the same processor.
-This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils with different models of plastic bags.
-
-As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution optmization method for solving this problem.
-
+The rest of the paper is organized as follows.
 In the next sections, a presentation of problem is made along with an application example.
@@
 
+\bibitem[\protect\citeauthoryear{Fumero \emph{et al.}}{2016}]{FumeroEtAl2016}
+Fumero Y., Moreno M.
+S., Corsano, G., Montagna, J.
+M.
+(2016).
+A multiproduct batch plant design model incorporating production planning and scheduling decisions under a multiperiod scenario.
+{\it Applied Mathematical Modelling}, Vol.
+40, pp.
+3498--3515.
+
 \bibitem[\protect\citeauthoryear{Kashan and Ozturk}{2022}]{KashanOzturk2022}
@@
 
+\bibitem[\protect\citeauthoryear{Petkov and Maranas}{1998}]{PetkovMaranas1998}
+Petkov, S. B., and Maranas, C. D. (1998). Design of Single-Product Campaign Batch Plants under Demand Uncertainty. {\it  AIChE Journal}, Vol. 44 (4), pp. 896--911.
+
 \bibitem[\protect\citeauthoryear{Ravemark and Rippin}{1998}]{RavemarkAndRippin1998}

### 2023-09-15 manuscript/manuscript.tex
updating introduction

@@
 As stated by \cite{PetkovMaranas1998} the batch plant can operate under a single-product campaign (SPC) production mode, where all the batches of a given product are manufactured before production of the next product begins, or under mixed-product campaign (MPC) production modes where more batches are produced per unit time at the expense of increased changeover times and cleanup costs.
-Also the plant layout can take on different formats, such as: single unit, where all batches are processed at a single stage; serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{MendezEtAll2000, ShiEtAll2017}; and networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
+Also the plant layout can take on different formats, such as: single unit, where all batches are processed at a single stage; serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{ShiEtAll2017}; and networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
 
@@
 This problem is named multi-product batch sizing.
-\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production and \cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product s-batch sizing problem in a networked plant of a steel industry (Fig.
+\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production.
+\cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product s-batch sizing problem in a networked plant of a steel industry (Fig.
 \ref{fig:networkdPlantSteelIndustry}).
@@
 Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each products batch production, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
-Also, some cientific works consider MPBS problems within different layouts and multiperiod scenario.
+Also, some cientific works consider MPBS problems within different layouts as well as dinamic and multiperiod scenarios.
 In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
+Many cientifc works propose mixed-integer linear programming (MILP) formulations to solve MPBS problems.
+As example, we can mention the work of \cite{MendezEtAll2000} that presents a MILP continuous-time model and a two-step systematic methodology for a single-stage multi-product batch scheduling problem with different due-dates.
+Later, \cite{MendezCerda2003} also proposed another MILP formulation for reactive scheduling.
+As observerd by \cite{HeHui2008}, with the problem size increasing, the computational effort of MILP increases greatly so it is very difﬁcult for MILP to obtain acceptable solutions to large-size problems within reasonable time.
+Citing some works, \cite {KimEtAl1996} propose a Gantt chart mapping method and a modified genetic algorithm for solving a networked flowshop multi-product batch scheduling problem as well as a rule-based reactive rescheduling scheme for dinamicaly overcoming in-process deviation from the initial optimized schedule.
+\cite{HeHui2008} present a rule-based genetic algorithm for the scheduling of single-stage multi-product batch plants with parallel units.
 
@@
 \cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.
+However, in the best of our knowledge, few works consider p-patch multi-product batch problems.
+One exception is the work of \cite{LiEtAl2022} which deal with a multi-product s-batch p-batch problem involving incompatible families with different job sizes and capacity constraints.
 
@@
 \cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.
-
-\cite{LiEtAl2022} deal with a PMPBS problem involving incompatible families with different job sizes and capacity constraints.
-In this problem, solutions are accepted in which two or more batches are processed simultaneously on the same machine.
-However, there are no production limitations for the production of each product group.
-The paper of \cite{LiEtAl2022} also presente an extensive literature review on production batch scheduling problems.
-Other important works deal with the problem of a multi-product batch plant design (MPBPD).
-In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
 
@@
 \end{sidewaystable}
-
-About the solution method many papers propose mathmatical models which are solved using IBM ILOG CPLEX or another constraint programming solver.
 
@@
 
+\bibitem[\protect\citeauthoryear{He and Hui}{2008}]{HeHui2008}
+He, Y., Hui, C-W.
+(2008).
+A rule-based genetic algorithm for the scheduling of single-stage multi-product batch plants with parallel units.
+{\it  Computers and Chemical Engineering}, Vol.
+32, pp.
+3067--3083.
+
 \bibitem[\protect\citeauthoryear{Kashan and Ozturk}{2022}]{KashanOzturk2022}
@@
 
+\bibitem[\protect\citeauthoryear{Méndez and Cerdá}{2003}]{MendezCerda2003}
+Méndez, C.A., Cerdá, J. (2003). Dynamic scheduling in multiproduct batch plants. {\it Computers and Chemical Engineering}, Vol. 27, pp. 1247--1259.
+
 \bibitem[\protect\citeauthoryear{Omega Journal}{1993}]{Omega1993}

### 2023-09-20 manuscript/manuscript.tex
updating paper - introduction
almost finished

@@
 The term multi-product batch production is usually applied to designate an intermittent production system in which batches of different products and sizes are processed one at a time, sharing the same production facilities.
-A multi-product batch plant basically consists of one or more units, grouped into one or more stages, and possibly, intermediate storage locations.
+A multi-product batch plant basically consists of one or more production units, grouped into one or more stages, and possibly, intermediate storage locations.
 At each stage some distinct operations are performed and the batches are processed sequentially over the stages (serial batching).
@@
 Also the plant layout can take on different formats, such as: single unit, where all batches are processed at a single stage; serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{ShiEtAll2017}; and networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
+Also networked plant can be divergent, convergent or both.
 
@@
 This problem is named multi-product batch sizing.
-\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production.
-\cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product s-batch sizing problem in a networked plant of a steel industry (Fig.
+\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production, and \cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product serial batching sizing problem in a divergent networked plant of a steel industry (Fig.
 \ref{fig:networkdPlantSteelIndustry}).
@@
 \end{center}
-\caption{Multi-product s-batch networked plant of a steel industry. Source: adapted from \cite{LiuEtAl2020} * stage $(i, j)$ means stage $j$ of production line $i$.}
+\caption{Multi-product serial batching divergent networked plant of a steel industry. Source: adapted from \cite{LiuEtAl2020} * stage $(i, j)$ means stage $j$ of production line $i$.}
 \end{figure}
 
-In multi-product batch scheduling (MPBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the products batches based on the known demand.
+In multi-product batch scheduling (MPBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the batches based on the known demand.
 Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
-Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each products batch production, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
+Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each batch, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
 Also, some cientific works consider MPBS problems within different layouts as well as dinamic and multiperiod scenarios.
@@
 As observerd by \cite{HeHui2008}, with the problem size increasing, the computational effort of MILP increases greatly so it is very difﬁcult for MILP to obtain acceptable solutions to large-size problems within reasonable time.
-Citing some works, \cite {KimEtAl1996} propose a Gantt chart mapping method and a modified genetic algorithm for solving a networked flowshop multi-product batch scheduling problem as well as a rule-based reactive rescheduling scheme for dinamicaly overcoming in-process deviation from the initial optimized schedule.
-\cite{HeHui2008} present a rule-based genetic algorithm for the scheduling of single-stage multi-product batch plants with parallel units.
+Citing some works that use other approaches, \cite {KimEtAl1996} propose a Gantt chart mapping method and a modified genetic algorithm for solving a networked flowshop multi-product batch scheduling problem as well as a rule-based reactive rescheduling scheme for dinamicaly overcoming in-process deviation from the initial optimized schedule and \cite{HeHui2008} present a rule-based genetic algorithm for the scheduling of single-stage multi-product batch plants with parallel units.
 
@@
 However, in the best of our knowledge, few works consider p-patch multi-product batch problems.
-One exception is the work of \cite{LiEtAl2022} which deal with a multi-product s-batch p-batch problem involving incompatible families with different job sizes and capacity constraints.
+One exception is the work of \cite{LiEtAl2022} which deal with a multi-product \emph{p-batch} \emph{s-batch} problem involving incompatible families with different job sizes and capacity constraints.
 
 In a real production environment, some of these problems arise in a connected way, so many cientific works adress mixed multi-product batch problems.
-\cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.
+As example, \cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.
 
-\begin{sidewaystable}[h]
-\begin{center}
-\begin{small}
-\begin{tabular}[c]{|c|c|c|c|c|c|c|c|c|}
-reference & problem & period & stage & units & int. stor. & constraints & objectives & method \\
-\hline
-\multirow{2}{*}{\cite{Eilon1985}} & \multirow{2}{*}{scheduling} & \multirow{2}{*}{single} & \multirow{2}{*}{single} & \multirow{2}{*}{single} & & & minimize total setup;  \\
- & & & & & & & minimize daily holding cost;  \\
-\multirow{3}{*}{\cite{ShiEtAll2017}} & \multirow{3}{*}{scheduling} & \multirow{3}{*}{single} & non-identical & \multirow{3}{*}{unlimited} & release time \\
- & & & & parallel & & due date \\
- & & & & & \\
- & & & & \\
-\end{tabular}
-\label{tab:MBPTax}
-\caption{Multi-product batch problems taxonomy}
-\end{small}
-\end{center}
-\end{sidewaystable}
+In this work we are interested in the multiperiod multi-product batch scheduling problem in a networked plant that arises in a plastic bag industry.
+The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020}, however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
+Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}.
+Thus, part of the problem solving process consists of solving a multi-product p-batch problem into extruders.
+Also, in the problem we study, in addition to demand, we must consider the factory and outlets' storage capacity, which is individually defined for products, but also for the set of products.
 
-In this work we are interested in a sub problem of the \emph{p-batch} scheduling problem described by \cite{KashanOzturk2022}, named multi-product batch processing time maximization (MBPTM) problem.
-When appliyng some local search heuristic for solving the \emph{p-batch} scheduling problem it is necessary to solve the MBPTM problem on each iteration, so it has a direct impact on the overall efficiency of any local search heuristc for solving the \emph{p-batch} scheduling problem.
-As scientific contributions, in this paper we present a mathematical model and a polynomial time complexity optmization method for solving this problem.
+When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
+We named this problem multi-product p-batch processing time maximization (MPBPTM) problem.
+
+It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied.
+In a future work, we intend to present the mathematical model and solution algorithm we are developing for this last problem.
+As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPBPTM problem.
 

### 2023-09-27 accepted/COPSolver/manuscript.tex
updating paper - revisions

@@
 \noindent
-\textbf{COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multi-product batch processing time maximization problem}
+\textbf{COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multi-product p-batch processing time maximization problem}
 \vskip0.5cm
@@
 \textbf{Abstract}\\
-This paper presents the software COPSolver, originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area.
-The first version of COPSolver has a application of Fraga's exact method for solving the multi-product batch processing time maximization problem.
-This paper address the COPSolver\_1.0-1 and the next steps that will be implemented for the software's applications development.
+COPSolver is an open source software originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area.
+The first version of COPSolver has a application of Fraga's exact method for solving the multi-product p-batch processing time maximization problem.
+Such application can have significant impacts on software development for efficiently solving p-batch problems as well as contributing to better inventory control in some industries.
+Also it can be applied to conduct case studies, contributing to teaching and research.
+This paper address the first version of COPSolver as well as some important aspects of this software and the next steps that will be implemented for it's applications development.
 \vskip0.5cm
@@
 
-Given the enormous variety of decision-making and/or optimization problems and the complexity of such problems, the scientific literature brings numerous scientific materials that deal with the various problems and propose different solution methodologies for these problems.
+Given the enormous variety of decision-making and/or optimization problems and the complexity of such problems, the literature brings numerous scientific materials that deal with the various problems and propose different solution methodologies for these problems.
 However, it is rare to find software that solves such problems.
@@
 The first version of the software, COPSolver\_1.0-1, applies the exact solution method developed by Fraga et al.
-(2023) to solve the Multi-product Batch Processing Time Maximization (MBPTM) problem.
+(2023) to solve the multi-product p-batch processing time maximization (MBPTM) problem.
 This problem arises in production process operations where a set of products are processed simultaneously on the same machine, but with production rates that can be different for each product.
@@
 For better suitability to the codeocean repository, the computational codes will be allocated within a folder named code, the files containing the input data (config.txt and data.txt) will be allocated within a folder named data, and the output files will be inserted into a folder named results.
-Also, files containing .h computational codes will be inserted inside a folder named lib while .cpp files (except main.cpp) will be inserted inside a folder named src.
+Also, files containing .h computational codes will be inserted inside a subfolder named lib while .cpp files (except main.cpp) will be inserted inside a subfolder named src.
 The lingo-language solvers developed for COPSolver validation will be available in specific subfolders within the folder named LINGOSolver.
@@
 
-\section{Economic, technological, scientific and educational impact}
+\section{Impacts}
 
-The determination of the maximum processing time of multi-product batches is extremely important for some industries, as it is directly related to inventory management as well as to the correct fulfillment of demand.
+Some industrial equipment process a set of jobs (batches) simultaneously.
+For production scheduling in these equipment, in addition to the sequencing and determination of the batches sizes, it is also necessary to define the set of batches that will be processed simultaneously in each time interval.
+These compound batches are called p-batch (parallel batching).
+Since most of p-batch problems are NP-Hard, many scientific works propose different local search heuristics for solving these problems (Fowler and Mönch, 2022).
+When applying some local search heuristics for solving a p-batch problem, it becomes necessary to determine the maximum p-batch processing time at each iteration.
+So, the method applied to solve this sub-problem can have a strong impact on the computational cost of the local search algorithm proposed for solving p-batch problems.
+As reported earlier, COPSolver's library for solving the multi-product p-batch processing time maximization problem has an application of the Fraga's method to solve this sub-problem, which has very low computational cost.
+Therefore, this library can be used to implement local search heuristics-based algorithms developed for solving p-batch problems, generating a high impact on the efficiency of these algorithms.
+An article has been submitted for publication, which present the exact method proposed for solving multi-product p-batch processing time maximization problems as well as an extensive study on the computational efficiency of the COPSolver\_1.0-1 (Fraga \emph{et al.}, 2023).
+In order to make this software available to the rest of the world, all the necessary files that is required to compile and run the software successfully have been published to the codeocean project (Fraga, 2023).
+
+It is important to note that the determination of the maximum processing time of multi-product p-batches itself is extremely important for some industries, as it is directly related to inventory management as well as to the correct fulfillment of demand.
 Therefore, COPSolver\_1.0-1 can serve as an important tool for inventory control, reducing costs and improving demand compliance.
-As future works, we will be applying COPSolver to assist in planning the production of extruders, in companies of the plastic bag production sector.
+As future works, we will be applying COPSolver to assist in planning and scheduling the production of extruders, in companies of the plastic bag production sector.
 With this we hope to improve inventory management, increasing the competitive potential of these companies.
-
-COPSolver\_1.0-1 can also be used to conduct case studies, assisting in teaching and research.
-Also, since COPSolver is built on the basis of problem-oriented libraries, it can also be reused in the development of other more complex software in research and technological projects.
+These works will be case studies, conducted to assist in teaching and research, so it can also generate an important impact in these aspects.
 
@@
 \textbf{References}\\
-Fraga, T.B., Aquino, Í.R.B. and Menêzes, R.C.S. (2023). Multi-product Batch Processing Time Maximization
-Problem. Manuscript submitted for publication.  \\
+
+Fraga, T.B., Aquino, Í.R.B. and Menêzes, R.C.S. (2023). Exact method for solving the multi-product p-batch processing time maximization problem. Manuscript submitted for publication.  \\
+
+Fraga, T.B.
+(2023).
+COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multi-product batch processing time maximization problem.
+Published Version 1.0.
+codeocean.
+Available at: https://codeocean.com/capsule/4837209/tree/v1.
+\\
+
+Fowler, J.W. and Mönch, L. (2022). A survey of scheduling with parallel batch (p-batch) processing. European Journal of Operational Research, v. 298, pp. 1–24. \\
 

### 2023-09-27 accepted/COPSolver/manuscript.tex
updating paper

@@
 \noindent
-\textbf{combinatorial optimization problem; exact method; multi-product batch problem; processing time maximization.}\\
+\textbf{combinatorial optimization problem; exact method; p-batch problem; processing time maximization.}\\
 \vskip0.5cm
@@
 When applying some local search heuristics for solving a p-batch problem, it becomes necessary to determine the maximum p-batch processing time at each iteration.
-So, the method applied to solve this sub-problem can have a strong impact on the computational cost of the local search algorithm proposed for solving p-batch problems.
-As reported earlier, COPSolver's library for solving the multi-product p-batch processing time maximization problem has an application of the Fraga's method to solve this sub-problem, which has very low computational cost.
+So, the method applied to solve this subproblem can have a strong impact on the computational cost of the local search algorithm proposed for solving p-batch problems.
+As reported earlier, COPSolver's library for solving the multi-product p-batch processing time maximization problem has an application of the Fraga's method to solve this subproblem, which has very low computational cost.
 Therefore, this library can be used to implement local search heuristics-based algorithms developed for solving p-batch problems, generating a high impact on the efficiency of these algorithms.

### 2023-09-27 accepted/COPSolver/manuscript.tex
updating files

@@
 Also it can be applied to conduct case studies, contributing to teaching and research.
-This paper address the first version of COPSolver as well as some important aspects of this software and the next steps that will be implemented for it's applications development.
+This paper address some important aspects of COPSolver and the next steps that will be implemented for it's applications development.
 \vskip0.5cm

### 2023-10-05 manuscript/manuscript.tex
updating paper

@@
 
-\title{Multi-product Batch Processing Time Maximization Problem}
+\title{Exact method for the multi-product p-batch processing time maximization problem}
 
@@
 \cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.
-However, in the best of our knowledge, few works consider p-patch multi-product batch problems.
-One exception is the work of \cite{LiEtAl2022} which deal with a multi-product \emph{p-batch} \emph{s-batch} problem involving incompatible families with different job sizes and capacity constraints.
+\cite{FowlerMonch2022} present a taxonomy and an extensive literature review for the p-batch problems.
+Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product \emph{p-batch} \emph{s-batch} problem involving incompatible families with different job sizes and capacity constraints.
 
@@
 In this work we are interested in the multiperiod multi-product batch scheduling problem in a networked plant that arises in a plastic bag industry.
-The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020}, however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
+The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020} (Fig.
+\ref{fig:networkdPlantSteelIndustry}), however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
 Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}.
@@
 
-\section{Multi-product batch processing time maximization problem}
+\section{Multi-product p-batch processing time maximization problem}
 \label{sec:MBPTMP}
 
-The multi-product batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
+The multi-product p-batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
 In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product.
@@
 
-O método proposto neste artigo para solução do MBPTM problem é composto por duas partes distintas, que são: a) cálculo do tempo máximo de processamento do lote multi-produtos; e b) cálculo e distribuição da produção entre a demanda, os outlets e o estoque em fábrica.
-A seguir, explicamos cada uma destas partes detalhadamente.
+The method proposed in this paper for solution of the MPBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the production to meet demand, the production sent to outlets and the production stocked in factory.
+Next, we explain each of these parts in detail.
+\\
 
-\noindent \emph{cálculo do tempo máximo de processamento do lote multi-produtos:}
+\noindent \emph{Calculation of maximum p-batch processing time:} \\
 
@@
 
-\noindent where $T'$ é o tempo máximo de processamento cuja produção será utilizada exclusivamente para atendimento da demanda.
+\noindent where $T'$ is the maximum processing time whose production will be used exclusively to meet the demand.
 
-Neste caso, sendo $D_{i}^{'}$ a quantidade produzida do produto $i$ após $T'$ unidades de tempo de processamento do lote, temos que:
+Then, being $D_{i}^{'}$ the quantity produced of the product $i$ after $T'$ units of processing time, we have:
 
@@
 
-\noindent e, como $D_{i}^{'} \leq D_i$, $\forall i$, temos que:
+\noindent and, as $D_{i}^{'} \leq D_i$, $\forall i$, we have:
 
@@
 
-Das equações em (\ref{eq:s02}), (\ref{eq:s03}) e (\ref{eq:s04}), temos:
+From the equations in (\ref{eq:s02}) and the restrictions in (\ref{eq:s03}) and (\ref{eq:s04}), we have:
 
@@
 
-E, como desejamos máximo valor para $T'$, de (\ref{eq:s05}), temos:
+And, as we wish maximum value to $T'$, from (\ref{eq:s05}) we have:
 
@@
 
-Observer que poderá haver uma sobra correspondente à demanda não atendida pela produção ocorrida na primeira parte do tempo de processamento do lote, $T'$.
-Esta sobra, $S_i$, será definida de acordo com as equações em (\ref{eq:s07}):
+Observe that there may be a leftover corresponding to the demand not met by the production in the first part of the processing time, $T'$.
+This leftover, $S_i$, will be defined according to the equations in (\ref{eq:s07}):
 
@@
 
-É possível também considerar que os outlets são uma extensão do estoque da fábrica.
-Portanto it is possible to consider the factory stock of product $i$ and the outlets stock $i$ as single stock for the product $i$, de forma que:
+It is also possible to consider that outlets are extensions of the factory stock.
+Therefore, it is possible to consider the factory stock of product $i$ and the outlets stock $i$ as single stock for the product $i$, $E_i$, so that:
 
@@
 
-\noindent where $E_i$ is the sum of factory stock and outlets stock of the product $i$.
-
-Como o tempo $T'$ foi utilizado apenas para produção que irá atender à demanda, $T''$ será o restante do tempo de processamento, ou seja, o tempo máximo de processamento utilizado para produção que irá atender à sobra da demanda, será enviada para os outlets e estocada em fábrica.
-Assim temos que:
+As the time $T'$ was used only for production that will meet the demand, $T''$  will be the remaining processing time, \emph{i.e.} the maximum processing time used for production that will meet the leftover of demand, sent to the outlets and stored in factory.
+So we have:
 
@@
 
-Portanto, das restrições em (\ref{eq:s09}) e equações em (\ref{eq:s12}), temos:
+\noindent Thus, after replacing (\ref{eq:s12}) in (\ref{eq:s09}) and applying some algebra, we have:
 
@@
 
-\noindent e, das restrições em (\ref{eq:s10}) e equações em (\ref{eq:s12}), temos:
+\noindent And, after replacing (\ref{eq:s12}) in (\ref{eq:s10}) and applying some algebra, we have:
 
@@
 
-Finalmente, como $T''$ é um valor inteiro e queremos maximizar esse valor, então:
+Finally, as $T$  is an integer value and we want to maximize this value, then:
 
@@
 
-Note that, à medida em que reduzimos o valor de $T'$, a consequente redução do valor de $D_{i}^{'}$ será atribuída diretamente à sobra $S_i$ e, portanto, there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1.
+Note that, as we reduce the value of $T'$, the consequent reduction of $D_{i}^{'}$ will be directly attributed to the leftover of demand $S_i$ and, therefore, there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1.
 Thus it is possible to use a simplification of the method presented, making $T' = 0$.
@@
 
-Essa simplificação do método demonstra que o valor ótimo calculado para $T$ não depende da forma como a produção do produto $i$, $P_i$, é distribuída entre atendimento à demanda, $D_i$, outlets, $O_i$, e estoque de fábrica $I_i$.
+This simplification of the method demonstrates that the great value calculated to $T$ does not depend on the way the production of the product $i$, $P_i$, is distributed between service to demand, $D_i$, outlets, $O_i$, and  factory's stock $I_i$.
 
-We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply by seguindo the priorities for distribution. The following three algorithms can be used to find a complete solution.
+We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply attending the priorities for distribution. The following three algorithms can be used to find a complete solution.
 
-The algorithm (\ref{alg:part01}) is used for finding an optimimal value fot $T$.
+The Algorithm (\ref{alg:part01}) is used for finding an optimimal value for $T$.
 
@@
 
-Then an initial production distribution can be done by the algorithm (\ref{alg:part02}).
-Esta distribuição é feita sem levar em consideração as restrições definidas para o conjunto de produtos do lote.
-$SO$ e $SI$ representam, respectivamente, o quantidade total disponível a ser enviada para os outlets e a quantidade total disponível para estoque em fábrica após a distribuição inicial.
-Caso esse valores sejam negativo, isso indica que a distribuição inicial proposta não é uma distribuição viável.
+Then an initial production distribution can be done by the Algorithm (\ref{alg:part02}).
+This distribution is made without considering the restrictions defined for the set of products.
+$SO$ and $SI$ represent, respectively, the total amount available to be sent to the outlets and the total amount available for factory inventory after the initial distribution.
+If this values are negative, this indicates that the proposed initial distribution is not a feasible distribution.
 
@@
 
-Assim, after applying algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
+Assim, after applying Algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
 However, if $SO < 0$ or $SI <0$, solution is not yet feasible.
@@
 
-Therefore it is possible to meet the restrictions by applying the agorithm (\ref{alg:part03}).
-Neste algoritmo redistribuimos a produção do estoque para os outlets ou vice versa, respectivamente, em função de termos um $SI$ ou $SO$ negativo.
+Therefore it is possible to meet the restrictions by applying the Agorithm (\ref{alg:part03}).
+In this algorithm we redistributed the production of factory's stock to the outlets or vice versa, respectively, due to having a $SI$ or $SO$ negative.
 
 \begin{algorithm}
-\caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch products set.}\label{alg:part03}
+\caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch set.}\label{alg:part03}
 \begin{algorithmic}
@@
 
+\bibitem[\protect\citeauthoryear{Fowler and Mönch}{2022}]{FowlerMonch2022}
+Fowler, J.W. and Mönch, L. (2022). A survey of scheduling with parallel batch (p-batch) processing. {\it European Journal of Operational Research}, Vol. 298, pp. 1--24.
+
+\bibitem[\protect\citeauthoryear{Fowler and Mönch}{2022}]{FowlerMonch2022}
+Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision prob-
+lems - library for solving the multi-product p-batch processing time maximization problem {\it Software Impacts}, invited paper, in press.
+
 \bibitem[\protect\citeauthoryear{Fumero \emph{et al.}}{2016}]{FumeroEtAl2016}

### 2023-10-05 manuscript/manuscript.tex
updating paper

@@
 
+Summarized, it is possible to propose the following taxonomy for the multi-product batch problems: 1) layout: flowshop, parallel or networked (coonvergent and /or divergent); 2) number of stages: single stage or multistage; 3) planning horizon: single period or multiperiod; 4) scenario: static or dynamic; 5) production mode: single-product campaing, mixed-product campaign, s-batch and/or p-batch; and 6) problem: design, planning, sizing, scheduling and/or balancing.
+
 In this work we are interested in the multiperiod multi-product batch scheduling problem in a networked plant that arises in a plastic bag industry.
@@
 When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
-We named this problem multi-product p-batch processing time maximization (MPBPTM) problem.
+We named this problem multi-product p-batch processing time maximization (MBPTM) problem.
 
-It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied.
+It is important to note that, since the MBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied.
 In a future work, we intend to present the mathematical model and solution algorithm we are developing for this last problem.
-As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPBPTM problem.
+As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MBPTM problem.
 
@@
 
-The method proposed in this paper for solution of the MPBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the production to meet demand, the production sent to outlets and the production stocked in factory.
+The method proposed in this paper for solution of the MBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the production to meet demand, the production sent to outlets and the production stocked in factory.
 Next, we explain each of these parts in detail.
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230814, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver.
+To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230814, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver \citep{Fraga2023}.
 The tests were performed on a notebook with an Intel i7 processor.
@@
 
-\bibitem[\protect\citeauthoryear{Fowler and Mönch}{2022}]{FowlerMonch2022}
+\bibitem[\protect\citeauthoryear{Fraga}{2023}]{Fraga2023}
 Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision prob-

### 2023-10-09 manuscript/manuscript.tex
updating paper - taxonomy design

@@
 \doublespacing
-
 \usepackage{algorithm}
@@
 As stated by \cite{PetkovMaranas1998} the batch plant can operate under a single-product campaign (SPC) production mode, where all the batches of a given product are manufactured before production of the next product begins, or under mixed-product campaign (MPC) production modes where more batches are produced per unit time at the expense of increased changeover times and cleanup costs.
-Also the plant layout can take on different formats, such as: single unit, where all batches are processed at a single stage; serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{ShiEtAll2017}; and networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
+Also the plant layout can take on different formats, such as: single unit, where all operations needed to process the batches are performed by a single processor; serial flowshop plant, in which all products follow the same linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{ShiEtAll2017}; and networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
 Also networked plant can be divergent, convergent or both.
@@
 The configuration of the plant basically consists of defining the number of stages, the number of units and their capacity per stage, and the capacity for intermediate storages, as well as the best factory layout.
-
 The multi-product batch planning problem is basically determining the needs of materials and resources based on known demands and demand forecasts.
@@
 \cite{FowlerMonch2022} present a taxonomy and an extensive literature review for the p-batch problems.
-Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product \emph{p-batch} \emph{s-batch} problem involving incompatible families with different job sizes and capacity constraints.
+According to the authors, a p-batch problem can be classified as compatible setting - where there is no restriction on which jobs can be used to form a batch - and incompatible family case - where only jobs belonging to the same family can be used to form a batch.
+Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product \emph{s-batch} problem involving incompatible families with different job sizes and capacity constraints.
 
@@
 
-Summarized, it is possible to propose the following taxonomy for the multi-product batch problems: 1) layout: flowshop, parallel or networked (coonvergent and /or divergent); 2) number of stages: single stage or multistage; 3) planning horizon: single period or multiperiod; 4) scenario: static or dynamic; 5) production mode: single-product campaing, mixed-product campaign, s-batch and/or p-batch; and 6) problem: design, planning, sizing, scheduling and/or balancing.
+Fig. \label{fig:taxonomy} presents a taxonomy for the multi-product batch problems cited in this paper
+
+Summarized, it is possible to propose the following taxonomy for the multi-product batch problems: 1) layout: single unit, flowshop, parallel or networked (coonvergent and /or divergent); 2) number of stages: single stage or multistage; 3) planning horizon: single period or multiperiod; 4) scenario: static or dynamic; 5) production mode: single-product campaing, mixed-product campaign, s-batch and/or p-batch; 6) problem: design, planning, sizing, scheduling and/or balancing (with compatible or incompatible jobs); 7) restrictions: ; and 8) performance measure: makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness ($TT$), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and multiple criteria.
+
+\begin{figure}[h]
+\label{fig:taxonomy}
+\begin{center}
+\begin{tikzpicture}[font=\sffamily,every label/.append style={font=\small\sffamily,align=center}]
+
+\node[draw](SS){single stage};
+\node[right=0.3cm of SS, draw](MS){multi-stage};
+\node[draw,dashed,rounded corners,fit=(SS) (MS),inner sep=12pt,label={above:{number of stages}}](stages){};
+
+\node[right=1.2cm of MS, draw](SP){single period};
+\node[right=0.3cm of SP, draw](MP){multi-period};
+\node[right=0.3cm of MP, draw](CP){cyclic};
+\node[draw,dashed,rounded corners,fit=(SP) (MP) (CP),inner sep=12pt,label={above:{periods}}](periods){};
+
+\node[below left=1.5cm and -1.2cm of stages.south east, draw](L2){flowshop};
+\node[left=0.5cm of L2, draw](L1){single unit};
+\node[right=0.5cm of L2, draw](L3){parallel};
+\node[right=0.5cm of L3, draw](L4){networked};
+\node[draw,dashed,rounded corners,fit=(L1) (L2) (L3) (L4),inner sep=15pt,label={west:\rotatebox{90}{layout}}](layout){};
+
+\node[below left=1.5cm and 0cm of layout.south, draw](P3){sizing};
+\node[left=0.5cm of P3, draw](P2){planning};
+\node[left=0.5cm of P2, draw](P1){design};
+\node[right=0.5cm of P3, draw](P4){scheduling};
+\node[right=0.5cm of P4, draw](P5){balancing};
+\node[draw,dashed,rounded corners,fit=(P1) (P2) (P3) (P4) (P5),inner sep=15pt,label={west:\rotatebox{90}{problem}}](problem){};
+
+\node[below left=1.5cm and 0cm of problem.south, draw](O1){s-batch};
+\node[right=0.5cm of O1, draw](O2){p-batch};
+\node[draw,dashed,rounded corners,fit=(O1) (O2),inner sep=15pt,label={west:\rotatebox{90}{mode}}](mode){};
+
+\node[below left=3.5cm and 6cm of mode.south, draw, rotate=90](M1){makespan};
+\node[right=1cm of M1.south west, draw, rotate=90](M2){setup/holding cost};
+\node[right=1cm of M2.south west, draw, rotate=90](M3){customer satisfaction};
+\node[right=1cm of M3.south west, draw, rotate=90](M4){plant performance};
+\node[draw,dashed,rounded corners,fit=(M1) (M2) (M3) (M4),inner sep=15pt,label={west:\rotatebox{90}{performance measure}}](measure){};
+
+\node[right=2.5cm of M4.south west, draw, rotate=90](R1){family incompatibility};
+\node[right=1cm of R1.south west, draw, rotate=90](R2){capacity constrained};
+\node[right=1cm of R2.south west, draw, rotate=90](R3){color incompatibility};
+\node[right=1cm of R3.south west, draw, rotate=90](R4){work-in-process storage};
+\node[draw,dashed,rounded corners,fit=(R1) (R2) (R3) (R4),inner sep=15pt,label={west:\rotatebox{90}{restriction}}](restriction){};
+
+\node[below right =1cm and 0cm of measure.south west](N1){};
+\node[right =1cm of N1](N2){};
+\draw[blue, very thick] (N1.east) -- (N2.west);
+
+\node[right =0cm of N2](A1){\cite{Eilon1985}};
+\draw[blue, very thick] (SS.south) -- (L1.north);
+\draw[blue, very thick] (CP.south) -- (L1.north);
+\draw[blue, very thick] (L1.south) -- (P4.north);
+\draw[blue, very thick] (P4.south) -- (O1.north);
+\draw[blue, very thick] (O1.south) -- (M2.east);
+
+\node[right=4cm of N1](N3){};
+\node[right =1cm of N3](N4){};
+\draw[red, very thick] (N3.east) -- (N4.west);
+
+\node[right =0cm of N4](A2){\cite{LiuEtAl2020}};
+\draw[red, very thick] (MS.south) -- (L4.north);
+\draw[red, very thick] (MP.south) -- (L4.north);
+\draw[red, very thick] (L4.south) -- (P3.north);
+\draw[red, very thick] (P3.south) -- (O1.north);
+
+\node[below right =-2.5mm and 1mm of O1.south](N5){};
+\node[above right =-2.5mm and -1.5mm of M2.east](N6){};
+
+\draw[red, very thick] (N5) -- (N6);
+\draw[red, very thick] (O1.south) -- (R2.east);
+\draw[red, very thick] (O1.south) -- (R4.east);
+
+\end{tikzpicture}
+\end{center}
+\caption{Taxonomy of multi-product batch problems cited in this paper.}
+\end{figure}
 
@@
 About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.
-
-\emph{Example:} A certain machine must process a batch containing 2 different products: A and B.
-The production rate of A is 60 g/min while the production rate of B is 40 g/min.
-The factory has free stock for a maximum of 3000 g of any product, and, according to the company's inventory policy, a maximum of 3000 g of product A and 2000 g of product B can be stocked at the factory.
-There is a demand for 1000 g of product A and 500 g of product B.
-The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product.
-A maximum time of 100 minutes of this machine can be allocated for processing this batch.
-When distributing production the priority is to meet demand, then send to outlets and finily stock in factory.
-What is the maximum possible time for processing this batch and how production must be distributed ?
 
@@
 
-This simplification of the method demonstrates that the great value calculated to $T$ does not depend on the way the production of the product $i$, $P_i$, is distributed between service to demand, $D_i$, outlets, $O_i$, and  factory's stock $I_i$.
+This simplification of the method demonstrates that the value calculated to $T$ does not depend on the way the production of the product $i$, $P_i$, is distributed between service to demand, $D_i$, outlets, $O_i$, and  factory's stock $I_i$.
+
+\noindent \emph{Full solution:}
 
@@
 
-Assim, after applying Algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
+So, after applying Algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
 However, if $SO < 0$ or $SI <0$, solution is not yet feasible.
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230814, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver \citep{Fraga2023}.
+To test the developed model and analytical solution method, we created a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem and also a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver \citep{Fraga2023}.
 The tests were performed on a notebook with an Intel i7 processor.

### 2023-10-10 manuscript/manuscript.tex
updating papers - reply letter

@@
 \node[right=0.5cm of O1, draw](O2){p-batch};
-\node[draw,dashed,rounded corners,fit=(O1) (O2),inner sep=15pt,label={west:\rotatebox{90}{mode}}](mode){};
+\node[left=0.5cm of O1, draw](O3){MPC};
+\node[draw,dashed,rounded corners,fit=(O1) (O2) (O3),inner sep=15pt,label={west:\rotatebox{90}{mode}}](mode){};
 
 \node[below left=3.5cm and 6cm of mode.south, draw, rotate=90](M1){makespan};
-\node[right=1cm of M1.south west, draw, rotate=90](M2){setup/holding cost};
-\node[right=1cm of M2.south west, draw, rotate=90](M3){customer satisfaction};
-\node[right=1cm of M3.south west, draw, rotate=90](M4){plant performance};
-\node[draw,dashed,rounded corners,fit=(M1) (M2) (M3) (M4),inner sep=15pt,label={west:\rotatebox{90}{performance measure}}](measure){};
-
-\node[right=2.5cm of M4.south west, draw, rotate=90](R1){family incompatibility};
-\node[right=1cm of R1.south west, draw, rotate=90](R2){capacity constrained};
-\node[right=1cm of R2.south west, draw, rotate=90](R3){color incompatibility};
-\node[right=1cm of R3.south west, draw, rotate=90](R4){work-in-process storage};
-\node[draw,dashed,rounded corners,fit=(R1) (R2) (R3) (R4),inner sep=15pt,label={west:\rotatebox{90}{restriction}}](restriction){};
-
-\node[below right =1cm and 0cm of measure.south west](N1){};
-\node[right =1cm of N1](N2){};
+\node[right=0.7cm of M1.south west, draw, rotate=90](M2){setup/holding cost};
+\node[right=0.7cm of M2.south west, draw, rotate=90](M3){customer satisfaction};
+\node[right=0.7cm of M3.south west, draw, rotate=90](M4){plant performance};
+\node[right=0.7cm of M4.south west, draw, rotate=90](M5){net profit};
+\node[draw,dashed,rounded corners,fit=(M1) (M2) (M3) (M4) (M5),inner sep=15pt,label={west:\rotatebox{90}{performance measure}}](measure){};
+
+\node[right=3.5cm of M4.south west, draw, rotate=90](R1){family incompatibility};
+\node[right=0.7cm of R1.south west, draw, rotate=90](R2){capacity constrained};
+\node[right=0.7cm of R2.south west, draw, rotate=90](R3){color incompatibility};
+\node[right=0.7cm of R3.south west, draw, rotate=90](R4){work-in-process storage};
+\node[right=0.7cm of R4.south west, draw, rotate=90](R5){product storage capacity};
+\node[draw,dashed,rounded corners,fit=(R1) (R2) (R3) (R4) (R5),inner sep=15pt,label={west:\rotatebox{90}{restriction}}](restriction){};
+
+\node[below right =1cm and -0.7cm of measure.south west](N1){};
+\node[right =0.5cm of N1](N2){};
 \draw[blue, very thick] (N1.east) -- (N2.west);
@@
 
-\node[right=4cm of N1](N3){};
-\node[right =1cm of N3](N4){};
-\draw[red, very thick] (N3.east) -- (N4.west);
-
-\node[right =0cm of N4](A2){\cite{LiuEtAl2020}};
+\node[right=3.5cm of N1](N3){};
+\node[right =0.5cm of N3](N4){};
+\draw[green, very thick] (N3.east) -- (N4.west);
+
+\node[right =0cm of N4](A1){\cite{FumeroEtAl2016}};
+\draw[green, very thick] (MS.south) -- (L3.north);
+\draw[green, very thick] (CP.south) -- (L3.north);
+\draw[green, very thick] (L3.south) -- (P1.north);
+\draw[green, very thick] (L3.south) -- (P2.north);
+\draw[green, very thick] (L3.south) -- (P4.north);
+\draw[green, very thick] (P1.south) -- (O3.north);
+\draw[green, very thick] (P2.south) -- (O3.north);
+\draw[green, very thick] (P4.south) -- (O3.north);
+\draw[green, very thick] (O3.south) -- (M5.east);
+\draw[green, very thick] (O3.south) -- (R5.east);
+
+\node[right=5cm of N3](N5){};
+\node[right =0.5cm of N5](N6){};
+\draw[red, very thick] (N5.east) -- (N6.west);
+
+\node[right =0cm of N6](A2){\cite{LiuEtAl2020}};
 \draw[red, very thick] (MS.south) -- (L4.north);
@@
 
-\node[below right =-2.5mm and 1mm of O1.south](N5){};
-\node[above right =-2.5mm and -1.5mm of M2.east](N6){};
-
-\draw[red, very thick] (N5) -- (N6);
+\node[below right =-2.5mm and 1mm of O1.south](N7){};
+\node[above right =-2.5mm and -1.5mm of M2.east](N8){};
+
+\draw[red, very thick] (N7) -- (N8);
 \draw[red, very thick] (O1.south) -- (R2.east);

### 2023-10-10 manuscript/manuscript.tex
updating paper

--- 2023-10-09 manuscript/manuscript.tex
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\usepackage{enumitem}
 
@@
 
-\title{Exact method for the multi-product p-batch processing time maximization problem}
+\title{An exact method for the multi-product p-batch processing time maximization problem}
 
@@
 
-Summarized, it is possible to propose the following taxonomy for the multi-product batch problems: 1) layout: single unit, flowshop, parallel or networked (coonvergent and /or divergent); 2) number of stages: single stage or multistage; 3) planning horizon: single period or multiperiod; 4) scenario: static or dynamic; 5) production mode: single-product campaing, mixed-product campaign, s-batch and/or p-batch; 6) problem: design, planning, sizing, scheduling and/or balancing (with compatible or incompatible jobs); 7) restrictions: ; and 8) performance measure: makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness ($TT$), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and multiple criteria.
+\subsection{Taxonomy and notation}
 
-\begin{figure}[h]
-\label{fig:taxonomy}
-\begin{center}
-\begin{tikzpicture}[font=\sffamily,every label/.append style={font=\small\sffamily,align=center}]
+In short, based on the bibliographic survey conducted for the preparation of this paper, we identify that the multi-product batch problems can differentiate with the following aspects:
 
-\node[draw](SS){single stage};
-\node[right=0.3cm of SS, draw](MS){multi-stage};
-\node[draw,dashed,rounded corners,fit=(SS) (MS),inner sep=12pt,label={above:{number of stages}}](stages){};
+\begin{enumerate}[label=\arabic*)]
+\item \textbf{number of stages ($\sigma$)}: single stage (SS) or multistage (MS);
+\item \textbf{layout($\lambda$)}: single unit (SU), flowshop (Fl), parallel (Pl), or networked (Nt) (convergent (CN) and /or divergent (DN));
+\item \textbf{production mode ($\mu$)}: single-product campaing (SPC), mixed-product campaign (MPC), serial batching (s-batch) and/or parallel batching (p-batch);
+\item \textbf{problem:($\pi$)}  : design (D), planning (P), sizing (Sz), scheduling (Sc) and/or balancing (B); 
+\item \textbf{planning horizon ($\eta$)}: single period (SP) or multiperiod (MP);
+\item \textbf{scenario ($\gamma$)}: static (St) or dynamic (Dn);
+\item \textbf{input ($\iota$)}: deterministic (Dt) and/or stochastic (St);
+\item \textbf{performance measure ($\delta$)}: capital cost ($C$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness ($TT$), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$) and/or weighted $E/T$ ($wE/T$);
+\item \textbf{restrictions ($\rho$)}: incompatible jobs (IJ).
+\end{enumerate}
 
-\node[right=1.2cm of MS, draw](SP){single period};
-\node[right=0.3cm of SP, draw](MP){multi-period};
-\node[right=0.3cm of MP, draw](CP){cyclic};
-\node[draw,dashed,rounded corners,fit=(SP) (MP) (CP),inner sep=12pt,label={above:{periods}}](periods){};
+So, to describe a speciﬁc multi-product batch problem, we propose the notation $\sigma|\lambda|\mu|\pi|\eta|\gamma|\iota|\delta|\rho$.
+The multi-product batch problems and solution approaches discussed in the references cited in this paper are summarized in Tab.
+.
 
-\node[below left=1.5cm and -1.2cm of stages.south east, draw](L2){flowshop};
-\node[left=0.5cm of L2, draw](L1){single unit};
-\node[right=0.5cm of L2, draw](L3){parallel};
-\node[right=0.5cm of L3, draw](L4){networked};
-\node[draw,dashed,rounded corners,fit=(L1) (L2) (L3) (L4),inner sep=15pt,label={west:\rotatebox{90}{layout}}](layout){};
-
-\node[below left=1.5cm and 0cm of layout.south, draw](P3){sizing};
-\node[left=0.5cm of P3, draw](P2){planning};
-\node[left=0.5cm of P2, draw](P1){design};
-\node[right=0.5cm of P3, draw](P4){scheduling};
-\node[right=0.5cm of P4, draw](P5){balancing};
-\node[draw,dashed,rounded corners,fit=(P1) (P2) (P3) (P4) (P5),inner sep=15pt,label={west:\rotatebox{90}{problem}}](problem){};
-
-\node[below left=1.5cm and 0cm of problem.south, draw](O1){s-batch};
-\node[right=0.5cm of O1, draw](O2){p-batch};
-\node[draw,dashed,rounded corners,fit=(O1) (O2),inner sep=15pt,label={west:\rotatebox{90}{mode}}](mode){};
-
-\node[below left=3.5cm and 6cm of mode.south, draw, rotate=90](M1){makespan};
-\node[right=1cm of M1.south west, draw, rotate=90](M2){setup/holding cost};
-\node[right=1cm of M2.south west, draw, rotate=90](M3){customer satisfaction};
-\node[right=1cm of M3.south west, draw, rotate=90](M4){plant performance};
-\node[draw,dashed,rounded corners,fit=(M1) (M2) (M3) (M4),inner sep=15pt,label={west:\rotatebox{90}{performance measure}}](measure){};
-
-\node[right=2.5cm of M4.south west, draw, rotate=90](R1){family incompatibility};
-\node[right=1cm of R1.south west, draw, rotate=90](R2){capacity constrained};
-\node[right=1cm of R2.south west, draw, rotate=90](R3){color incompatibility};
-\node[right=1cm of R3.south west, draw, rotate=90](R4){work-in-process storage};
-\node[draw,dashed,rounded corners,fit=(R1) (R2) (R3) (R4),inner sep=15pt,label={west:\rotatebox{90}{restriction}}](restriction){};
-
-\node[below right =1cm and 0cm of measure.south west](N1){};
-\node[right =1cm of N1](N2){};
-\draw[blue, very thick] (N1.east) -- (N2.west);
-
-\node[right =0cm of N2](A1){\cite{Eilon1985}};
-\draw[blue, very thick] (SS.south) -- (L1.north);
-\draw[blue, very thick] (CP.south) -- (L1.north);
-\draw[blue, very thick] (L1.south) -- (P4.north);
-\draw[blue, very thick] (P4.south) -- (O1.north);
-\draw[blue, very thick] (O1.south) -- (M2.east);
-
-\node[right=4cm of N1](N3){};
-\node[right =1cm of N3](N4){};
-\draw[red, very thick] (N3.east) -- (N4.west);
-
-\node[right =0cm of N4](A2){\cite{LiuEtAl2020}};
-\draw[red, very thick] (MS.south) -- (L4.north);
-\draw[red, very thick] (MP.south) -- (L4.north);
-\draw[red, very thick] (L4.south) -- (P3.north);
-\draw[red, very thick] (P3.south) -- (O1.north);
-
-\node[below right =-2.5mm and 1mm of O1.south](N5){};
-\node[above right =-2.5mm and -1.5mm of M2.east](N6){};
-
-\draw[red, very thick] (N5) -- (N6);
-\draw[red, very thick] (O1.south) -- (R2.east);
-\draw[red, very thick] (O1.south) -- (R4.east);
-
-\end{tikzpicture}
-\end{center}
-\caption{Taxonomy of multi-product batch problems cited in this paper.}
-\end{figure}
+\subsection{Contributions of this paper}
 

### 2023-10-11 manuscript/manuscript.tex
updating manuscript - taxonomy

@@
 \usepackage{enumitem}
+
+\usepackage{array, makecell}
 
@@
 \begin{highlights}
-\item brief bibliographic review on multi-product batch problems;
-\item Multi-product Batch Processing Time Maximization (MBPTM) problem definition;
+\item taxonomy and notation for the multi-product batch problems;
+\item multi-product p-batch processing time maximization (MBPTM) problem definition;
 \item linear integer programming model for the MBPTM problem;
@@
 The configuration of the plant basically consists of defining the number of stages, the number of units and their capacity per stage, and the capacity for intermediate storages, as well as the best factory layout.
-The multi-product batch planning problem is basically determining the needs of materials and resources based on known demands and demand forecasts.
+The multi-product batch planning problem is basically determining the quantities to be produced, the number of batches and their sizes, the needs of materials and the total sales during each time period \citep{FumeroEtAl2016}.
 
@@
 
-Fig. \label{fig:taxonomy} presents a taxonomy for the multi-product batch problems cited in this paper
-
 \subsection{Taxonomy and notation}
@@
 \item \textbf{number of stages ($\sigma$)}: single stage (SS) or multistage (MS);
-\item \textbf{layout($\lambda$)}: single unit (SU), flowshop (Fl), parallel (Pl), or networked (Nt) (convergent (CN) and /or divergent (DN));
+\item \textbf{layout($\lambda$)}: single unit (SU), flowshop (Fl), parallel (Pl), or networked (Nt) (convergent (CNt) and /or divergent (DNt));
 \item \textbf{production mode ($\mu$)}: single-product campaing (SPC), mixed-product campaign (MPC), serial batching (s-batch) and/or parallel batching (p-batch);
 \item \textbf{problem:($\pi$)}  : design (D), planning (P), sizing (Sz), scheduling (Sc) and/or balancing (B); 
-\item \textbf{planning horizon ($\eta$)}: single period (SP) or multiperiod (MP);
+\item \textbf{time horizon ($\eta$)}: single period (SP) or multiperiod (MP), cyclic (Cc);
 \item \textbf{scenario ($\gamma$)}: static (St) or dynamic (Dn);
 \item \textbf{input ($\iota$)}: deterministic (Dt) and/or stochastic (St);
-\item \textbf{performance measure ($\delta$)}: capital cost ($C$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness ($TT$), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$) and/or weighted $E/T$ ($wE/T$);
-\item \textbf{restrictions ($\rho$)}: incompatible jobs (IJ).
+\item \textbf{performance measure ($\delta$)}: capital cost (C), setup cost (SC), holding cost (HC), work-in-process cost (WIPC), net profit (NP), makespan (C$_{\textrm{max}}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$) and/or weighted $E/T$ ($wE/T$);
+\item \textbf{others ($\rho$)}: capacited (UC), storage capacity (SC), work-in-process storage (WIP), due dates (DD), incompatible jobs (IJ). $\textrm{Z}$ 
 \end{enumerate}
@@
 The multi-product batch problems and solution approaches discussed in the references cited in this paper are summarized in Tab.
-.
+\ref{tab:review}.
+
+\begin{table}[thb]
+\begin{center}
+\begin{small}
+\begin{tabular}[c]{l l l}
+reference & problem & contributions  \\
+\cline {1-3} \\
+\cite{Eilon1985} & $SS|SU|s\textrm{-}batch|Sc|SP$ &  analysis of the effect\\
+& $St|Dt|SC, HC|-$  & of splitting batches \\
+\cline {1-3} \\
+Ravemark and & $MS|Pl|SPC|D|Cc|$ & convex mixed-integer\\
+Rippin (1998) & $St|Dt|C|WIP$ & linear programming \\
+& & model solved with \\
+& & DICOPT++ \\
+\cline {1-3} \\
+Petkov and & $MS|Pl|SPC|D|Cc|$ & exact method\\
+Maranas (1998)  & $St|St|NP|-$ & \\
+\cline {1-3} \\
+\cite{HeHui2008} & $SS|Pl|MPC|Sc|SP|$ & rule-based genetic \\
+& $St|Dt|C_{\textrm{max}}, TT|UC, DD$ & algorithm \\
+\cline {1-3} \\
+\cite{FumeroEtAl2016} & $MS|Pl|MPC|D,P,Sc|Cc|$ & mixed-integer linear  \\
+& $St|Dt|NP|UC,SC$ & programming model \\
+& & solved with CPLEX \\
+\cline {1-3} \\
+\cite{LiuEtAl2020} & $MS|DNt|s\textrm{-}batch|Sz|MP$ & mixed-integer quadratic \\
+& $|St|Dt|SC,WIPC|UC,WIP$ & programming model  \\
+& & and exact algorithm \\
+\cline {1-3} \\
+\end{tabular}
+\caption{Some contributions on the multi-product batch problems}
+\label{tab:review}
+\end{small}
+\end{center}
+\end{table}
 

### 2023-10-16 manuscript/manuscript.tex
updating paper - Improving the introduction

@@
 According to the authors, a p-batch problem can be classified as compatible setting - where there is no restriction on which jobs can be used to form a batch - and incompatible family case - where only jobs belonging to the same family can be used to form a batch.
-Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product \emph{s-batch} problem involving incompatible families with different job sizes and capacity constraints.
+Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product p-batch problem involving identical parallel units, capacity constraints, and incompatible families with different job sizes.
 
@@
 As example, \cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.
+Also, de work of \cite{MendezEtAll2000}, previously mentioned, considers planning as an integrated part of solution in real-world multi-product batch plant scheduling and therefore includes the product batching problem in its proposed MILP continuous-time models and two-step systematic methodology.
 
@@
 \item \textbf{input ($\iota$)}: deterministic (Dt) and/or stochastic (St);
-\item \textbf{performance measure ($\delta$)}: capital cost (C), setup cost (SC), holding cost (HC), work-in-process cost (WIPC), net profit (NP), makespan (C$_{\textrm{max}}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$) and/or weighted $E/T$ ($wE/T$);
-\item \textbf{others ($\rho$)}: capacited (UC), storage capacity (SC), work-in-process storage (WIP), due dates (DD), incompatible jobs (IJ). $\textrm{Z}$ 
+\item \textbf{performance measure ($\delta$)}: capital cost (C), setup cost (SC), holding cost (HC), work-in-process cost (WIPC), net profit (NP), makespan (C$_{\textrm{max}}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and processing time (PT);
+\item \textbf{others ($\rho$)}: limited capacity units (LCU), storage capacity by product (PSC), storage capacity (SC), work-in-process storage (WIP), release time (RT), due dates (DD), incompatible families (IF), different processing rates (DPR).
 \end{enumerate}
@@
 
-\begin{table}[thb]
+\begin{table}[h!]
 \begin{center}
@@
 \cline {1-3} \\
+\cite{MendezEtAll2000} & $SS|\lambda|p,s\textrm{-}batch|P,Sc|\eta|\gamma|$ & two-step systematic \\
+& $Dt|WIPC|RT, DD$& methodology \\
+\cline {1-3} \\
 \cite{HeHui2008} & $SS|Pl|MPC|Sc|SP|$ & rule-based genetic \\
-& $St|Dt|C_{\textrm{max}}, TT|UC, DD$ & algorithm \\
+& $St|Dt|C_{max}, TT|LCU, DD$ & algorithm \\
 \cline {1-3} \\
 \cite{FumeroEtAl2016} & $MS|Pl|MPC|D,P,Sc|Cc|$ & mixed-integer linear  \\
-& $St|Dt|NP|UC,SC$ & programming model \\
+& $St|Dt|NP|LCU,USC$ & programming model \\
 & & solved with CPLEX \\
 \cline {1-3} \\
-\cite{LiuEtAl2020} & $MS|DNt|s\textrm{-}batch|Sz|MP$ & mixed-integer quadratic \\
-& $|St|Dt|SC,WIPC|UC,WIP$ & programming model  \\
+\cite{LiuEtAl2020} & $MS|DNt|s\textrm{-}batch|Sz|MP|St|$ & mixed-integer quadratic \\
+& $Dt|SC,WIPC|LCU,WIP$ & programming model  \\
 & & and exact algorithm \\
+\cline {1-3} \\
+\cite{LiEtAl2022} & $SS|Pl|p\textrm{-}batch|Sc,B|SP|$ & mixed-
+integer linear \\
+& $St|Dt|C_{max}|LCU, RT, IF$ & programming and \\
+ & & a constraint-guided \\
+ & & artificial immune \\
+ & & system based algorithm \\ 
 \cline {1-3} \\
@@
 When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
-We named this problem multi-product p-batch processing time maximization (MBPTM) problem.
+This problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ batch problem.
+For simplification purposes, we named this problem multi-product p-batch processing time maximization (MBPTM) problem.
 

### 2023-10-16 manuscript/manuscript.tex
updating paper - changing abstract

@@
 \begin{abstract} 
+The multi-product batch (MPB) problems have been widely studied by the researchers.
+Among the most complex MPB problems are the multi-product p-batch scheduling (MPPBS) problems, where jobs must be scheduled on parallel batch processing machines.
+When applying some local search heuristics to solve a MPPBS problem, it can be necessary to determine, in each iteration, the maximum processing time for batches of compound products considering that the products that make up the batches have different processing rates, and that there are limitations for the amount produced for each product, as well as for the set of products of the compound  batch.
+Using the denominations present in the literature, this sub-problem can be simply referred as a single stage multi-product p-batch sizing problem.
+
 In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates.
 The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch.
-In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MBPTM) problem.
+In this paper we present the multi-product batch processing time maximization (MBPTM) problem.
 We also present a mathematical model for the MBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
@@
 \item \textbf{input ($\iota$)}: deterministic (Dt) and/or stochastic (St);
-\item \textbf{performance measure ($\delta$)}: capital cost (C), setup cost (SC), holding cost (HC), work-in-process cost (WIPC), net profit (NP), makespan (C$_{\textrm{max}}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), the total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and processing time (PT);
-\item \textbf{others ($\rho$)}: limited capacity units (LCU), storage capacity by product (PSC), storage capacity (SC), work-in-process storage (WIP), release time (RT), due dates (DD), incompatible families (IF), different processing rates (DPR).
+\item \textbf{performance measure ($\delta$)}: capital cost (C), setup cost (SC), holding cost (HC), work-in-process cost (WIPC), net profit (NP), makespan (C$_{\textrm{max}}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), the total weighted earliness (TWE), total weighted tardiness (TWT), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and processing time (PT);
+\item \textbf{others ($\rho$)}: limited capacity units (LCU), storage capacity by product (PSC), storage capacity (SC), work-in-process storage (WIP), release time (RT), due dates (DD), incompatible families (IF), different processing rates (DPR), sequence-dependent setup times (SDST).
 \end{enumerate}
@@
 So, to describe a speciﬁc multi-product batch problem, we propose the notation $\sigma|\lambda|\mu|\pi|\eta|\gamma|\iota|\delta|\rho$.
-The multi-product batch problems and solution approaches discussed in the references cited in this paper are summarized in Tab.
+Some of the multi-product batch problems and solution approaches discussed in the references cited in this paper are summarized in Tab.
 \ref{tab:review}.
@@
 \cline {1-3} \\
-Ravemark and & $MS|Pl|SPC|D|Cc|$ & convex mixed-integer\\
-Rippin (1998) & $St|Dt|C|WIP$ & linear programming \\
-& & model solved with \\
-& & DICOPT++ \\
+Ravemark and & $MS|Pl|SPC|D|Cc|$ & convex MILP model \\
+Rippin (1998) & $St|Dt|C|WIP$ & solved with DICOPT++ \\
 \cline {1-3} \\
@@
 \cline {1-3} \\
-\cite{MendezEtAll2000} & $SS|\lambda|p,s\textrm{-}batch|P,Sc|\eta|\gamma|$ & two-step systematic \\
-& $Dt|WIPC|RT, DD$& methodology \\
+\cite{MendezEtAll2000} & $SS|Pl|MPC|P,Sc|SP|St|$ & MILP continuous-time  \\
+& $Dt|WIPC|RT, DD$ & model and a two-step  \\
+& & systematic methodology \\
+\cline {1-3} \\
+Méndez and & $SS|Pl|MPC|Sc|SP|Dn|Dt|$ & MIPL model and \\
+Cerdá (2003) &$TWE, TWT|RT, DD, SDST$ & a rescheduling algorithm\\
 \cline {1-3} \\
@@
 \cline {1-3} \\
-\cite{FumeroEtAl2016} & $MS|Pl|MPC|D,P,Sc|Cc|$ & mixed-integer linear  \\
-& $St|Dt|NP|LCU,USC$ & programming model \\
-& & solved with CPLEX \\
+\cite{FumeroEtAl2016} & $MS|Pl|MPC|D,P,Sc|Cc|$ & MILP model \\
+& $St|Dt|NP|LCU,USC$ & solved with CPLEX \\
 \cline {1-3} \\
@@
 \cline {1-3} \\
-\cite{LiEtAl2022} & $SS|Pl|p\textrm{-}batch|Sc,B|SP|$ & mixed-
-integer linear \\
-& $St|Dt|C_{max}|LCU, RT, IF$ & programming and \\
- & & a constraint-guided \\
+\cite{LiEtAl2022} & $SS|Pl|p\textrm{-}batch|Sc,B|SP|$ & MILP model \\
+& $St|Dt|C_{max}|LCU, RT, IF$ & and a constraint-guided \\
  & & artificial immune \\

### 2023-10-16 manuscript/manuscript.tex
updating paper - abstract

@@
 Among the most complex MPB problems are the multi-product p-batch scheduling (MPPBS) problems, where jobs must be scheduled on parallel batch processing machines.
-When applying some local search heuristics to solve a MPPBS problem, it can be necessary to determine, in each iteration, the maximum processing time for batches of compound products considering that the products that make up the batches have different processing rates, and that there are limitations for the amount produced for each product, as well as for the set of products of the compound  batch.
-Using the denominations present in the literature, this sub-problem can be simply referred as a single stage multi-product p-batch sizing problem.
-
-In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates.
-The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch.
-In this paper we present the multi-product batch processing time maximization (MBPTM) problem.
-We also present a mathematical model for the MBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
+When applying some local search heuristics to solve a MPPBS problem, it can be necessary to determine, in each iteration, the maximum processing time for batches of compound jobs considering that the jobs that make up the batches have different processing rates, and that there are limitations for the amount produced for each product, as well as for the set of products of the compound  batch.
+Using the denominations present in the literature, this sub-problem can be simply referred as a single stage multi-product p-batch sizing (SSMPPBS) problem .
+Once a SSMPPBS problem needs to be solved in each iteration, the efficiency of the method developed for solving a SSMPPBS problem has a huge impact on the computational cost of the local search algorithm.
+In addition, for some industries, efficiently solving an SSMPPBS problem can have a significant impact on storage costs and customer satisfaction.
+In this paper we presente a mathematical model and an exact method with polynomial time complexity for the SSMPPBS problem.
+We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method.
+We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small and very large.
+As result, we find that the exact method can obtain optimal solutions in a very short time (just few seconds), even when solving very large instances.
 \end{abstract}

### 2023-10-17 manuscript/manuscript.tex
updating paper - small changes

@@
 \begin{abstract} 
-The multi-product batch (MPB) problems have been widely studied by the researchers.
-Among the most complex MPB problems are the multi-product p-batch scheduling (MPPBS) problems, where jobs must be scheduled on parallel batch processing machines.
-When applying some local search heuristics to solve a MPPBS problem, it can be necessary to determine, in each iteration, the maximum processing time for batches of compound jobs considering that the jobs that make up the batches have different processing rates, and that there are limitations for the amount produced for each product, as well as for the set of products of the compound  batch.
-Using the denominations present in the literature, this sub-problem can be simply referred as a single stage multi-product p-batch sizing (SSMPPBS) problem .
-Once a SSMPPBS problem needs to be solved in each iteration, the efficiency of the method developed for solving a SSMPPBS problem has a huge impact on the computational cost of the local search algorithm.
-In addition, for some industries, efficiently solving an SSMPPBS problem can have a significant impact on storage costs and customer satisfaction.
-In this paper we presente a mathematical model and an exact method with polynomial time complexity for the SSMPPBS problem.
+Among the most complex multi-product batch problems are the multi-product p-batch scheduling (MPPBS) problems, where jobs must be scheduled on parallel batch processing machines.
+When applying some local search heuristics to solve a MPPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products.
+In this paper we name this problem multi-product p-batch processing time maximization (MPBPTM) problem.
+Once a MPBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPPBS problems.
+In addition, for some industries, efficiently solving a MPBPTM problem can have a significant impact on storage costs and customer satisfaction.
+In this paper we presente a mathematical model and an exact method with polynomial time complexity for the MPBPTM problem.
 We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method.
@@
 \begin{keyword}
-multiproduct batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep LINGO
+multi-product batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep LINGO
 \end{keyword}
@@
 \begin{enumerate}[label=\arabic*)]
-\item \textbf{number of stages ($\sigma$)}: single stage (SS) or multistage (MS);
-\item \textbf{layout($\lambda$)}: single unit (SU), flowshop (Fl), parallel (Pl), or networked (Nt) (convergent (CNt) and /or divergent (DNt));
-\item \textbf{production mode ($\mu$)}: single-product campaing (SPC), mixed-product campaign (MPC), serial batching (s-batch) and/or parallel batching (p-batch);
-\item \textbf{problem:($\pi$)}  : design (D), planning (P), sizing (Sz), scheduling (Sc) and/or balancing (B); 
-\item \textbf{time horizon ($\eta$)}: single period (SP) or multiperiod (MP), cyclic (Cc);
-\item \textbf{scenario ($\gamma$)}: static (St) or dynamic (Dn);
-\item \textbf{input ($\iota$)}: deterministic (Dt) and/or stochastic (St);
-\item \textbf{performance measure ($\delta$)}: capital cost (C), setup cost (SC), holding cost (HC), work-in-process cost (WIPC), net profit (NP), makespan (C$_{\textrm{max}}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), the total weighted earliness (TWE), total weighted tardiness (TWT), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and processing time (PT);
-\item \textbf{others ($\rho$)}: limited capacity units (LCU), storage capacity by product (PSC), storage capacity (SC), work-in-process storage (WIP), release time (RT), due dates (DD), incompatible families (IF), different processing rates (DPR), sequence-dependent setup times (SDST).
+\item \textbf{number of stages ($\sigma$)}: single stage ($SS$) or multistage ($MS$);
+\item \textbf{layout($\lambda$)}: single unit ($SU$), flowshop ($Fl$), parallel ($Pl$), or networked ($Nt$) (convergent ($CNt$) and /or divergent ($DNt$));
+\item \textbf{production mode ($\mu$)}: single-product campaing ($SPC$), mixed-product campaign ($MPC$), serial batching ($s\textrm{-}batch$) and/or parallel batching ($p\textrm{-}batch$);
+\item \textbf{problem:($\pi$)}  : design ($D$), planning ($P$), sizing ($Sz$), scheduling ($Sc$) and/or balancing ($B$); 
+\item \textbf{time horizon ($\eta$)}: single period ($SP$), multiperiod ($MP$) or cyclic ($Cc$);
+\item \textbf{scenario ($\gamma$)}: static ($St$) or dynamic ($Dn$);
+\item \textbf{input ($\iota$)}: deterministic ($Dt$) and/or stochastic ($St$);
+\item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and processing time ($PT$);
+\item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$).
 \end{enumerate}
@@
 Méndez and & $SS|Pl|MPC|Sc|SP|Dn|Dt|$ & MIPL model and \\
-Cerdá (2003) &$TWE, TWT|RT, DD, SDST$ & a rescheduling algorithm\\
+Cerdá (2003) &$wE/T|RT, DD, SDST$ & a rescheduling algorithm\\
 \cline {1-3} \\

### 2023-10-17 manuscript/manuscript.tex
small correction

@@
 
-In this work we are interested in the multiperiod multi-product batch scheduling problem in a networked plant that arises in a plastic bag industry.
+In this work we are interested in the multiperiod multi-product batch scheduling problem that arises in a networked plant of a plastic bag industry.
 The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020} (Fig.
@@
 Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}.
-Thus, part of the problem solving process consists of solving a multi-product p-batch problem into extruders.
+Thus, part of the problem solving process consists of solving a multi-product p-batch scheduling problem into extruders.
 Also, in the problem we study, in addition to demand, we must consider the factory and outlets' storage capacity, which is individually defined for products, but also for the set of products.
@@
 When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
-This problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ batch problem.
-For simplification purposes, we named this problem multi-product p-batch processing time maximization (MBPTM) problem.
+Using the notation presented before, this problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ batch problem.
+For simplification purposes, we named this problem multi-product p-batch processing time maximization (MPBPTM) problem.
 
-It is important to note that, since the MBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied.
+It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied.
 In a future work, we intend to present the mathematical model and solution algorithm we are developing for this last problem.
-As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MBPTM problem.
+As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPBPTM problem.
 

### 2023-10-19 manuscript/FCPCOM/manuscript.tex
updating paper - AHP consistency

--- 2023-10-17 manuscript/manuscript.tex
@@
 
-\title{An exact method for the multi-product p-batch processing time maximization problem}
+\title{Analytic Hierarchy Process: how to force consistency of pairwise comparisons matrix}
 
@@
 \begin{abstract} 
-Among the most complex multi-product batch problems are the multi-product p-batch scheduling (MPPBS) problems, where jobs must be scheduled on parallel batch processing machines.
-When applying some local search heuristics to solve a MPPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products.
-In this paper we name this problem multi-product p-batch processing time maximization (MPBPTM) problem.
-Once a MPBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPPBS problems.
-In addition, for some industries, efficiently solving a MPBPTM problem can have a significant impact on storage costs and customer satisfaction.
-In this paper we presente a mathematical model and an exact method with polynomial time complexity for the MPBPTM problem.
-We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method.
-We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small and very large.
-As result, we find that the exact method can obtain optimal solutions in a very short time (just few seconds), even when solving very large instances.
+Saaty's Analytic Hierarchy Process is an important method for assigning weight to multiple criteria.
+The logic of this method is not complicated.
+First a pairwise comparisons matrix is generated for the multiple criteria, and the normalized eigenvector of this pairwise matrix is used as the weight of the criteria.
+Despite this method represents an important inovation, its logic is not complicated at all.
+First a pairwise comparisons matrix is generated for the multiple criteria, and the normalized eigenvector of this matrix is used as the weight of criteria.
+But, since pairwise matrixes are usually generated manually and based only on some employee knowhow, there is a huge complexity on generating a consistent pairwise matrix.
+Especially when many criteria are used.
+This paper presents two algorithms that can be used to adjust inconsistent matrices, forcing such matrices to have a better consistency rate.
+The first method is a constructive method that uses the data inserted in the matrix to build a new improved one.
+The second method iteratively identifies inconsistencies, making minor changes in order to improve the matrix consistency rate.
 \end{abstract}
@@
 \begin{highlights}
-\item taxonomy and notation for the multi-product batch problems;
-\item multi-product p-batch processing time maximization (MBPTM) problem definition;
-\item linear integer programming model for the MBPTM problem;
-\item exact optimization method for solving the MBPTM problem.
+\item generative method for forcing consistenc ;
+\item multi-product p-batch processing time maximization (MPBPTM) problem definition;
+\item linear integer programming model for the MPBPTM problem;
+\item exact optimization method for solving the MPBPTM problem.
 \end{highlights}
@@
 
-The term multi-product batch production is usually applied to designate an intermittent production system in which batches of different products and sizes are processed one at a time, sharing the same production facilities.
-A multi-product batch plant basically consists of one or more production units, grouped into one or more stages, and possibly, intermediate storage locations.
-At each stage some distinct operations are performed and the batches are processed sequentially over the stages (serial batching).
-As stated by \cite{PetkovMaranas1998} the batch plant can operate under a single-product campaign (SPC) production mode, where all the batches of a given product are manufactured before production of the next product begins, or under mixed-product campaign (MPC) production modes where more batches are produced per unit time at the expense of increased changeover times and cleanup costs.
-Also the plant layout can take on different formats, such as: single unit, where all operations needed to process the batches are performed by a single processor; serial flowshop plant, in which all products follow the same linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{ShiEtAll2017}; and networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
-Also networked plant can be divergent, convergent or both.
-
-The scientific literature address many different problems related to such industrial enviroment, including the design, planning, sizing, scheduling and balancing problems.
-The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
-The configuration of the plant basically consists of defining the number of stages, the number of units and their capacity per stage, and the capacity for intermediate storages, as well as the best factory layout.
-The multi-product batch planning problem is basically determining the quantities to be produced, the number of batches and their sizes, the needs of materials and the total sales during each time period \citep{FumeroEtAl2016}.
-
-Since a single batch is processed at a time, it is necessary that the batches are dimensioned in such a way that the quantity produced of each product is sufficient to meet the demand during the period in which other batches are being processed \citep{Eilon1985}.
-This problem is named multi-product batch sizing.
-\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production, and \cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product serial batching sizing problem in a divergent networked plant of a steel industry (Fig.
-\ref{fig:networkdPlantSteelIndustry}).
-
-\begin{figure}[h]
-\label{fig:networkdPlantSteelIndustry}
-\begin{center}
-\begin{tikzpicture}[font=\sffamily,every label/.append style={font=\small\sffamily,align=center}]
-
-\node[cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP00){};
-\node[rectangle, draw, right=0.5cm of WIP00, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit00){};
-\node[draw,dashed,rounded corners,fit=(WIP00) (unit00),inner sep=25pt,label={above:{stage (0,0)}}](stage00){};
-
-\node[above right=2cm and 4cm of WIP00, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP11){};
-\node[rectangle, draw, right=0.5cm of WIP11, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit11){};
-\node[draw,dashed,rounded corners,fit=(WIP11) (unit11),inner sep=25pt,label={above:{stage (1,1)}}](stage11){};
-
-\draw[-latex] (stage00.east) -- (stage11.west);
-
-\node[right=2.5cm of stage00, minimum width=1cm, minimum height=1.4cm](WIP1){.....};
-
-\node[right=0.3cm of WIP1, minimum width=1cm, minimum height=1.4cm](WIP1a){};
-
-\draw[-latex] (stage00.east) -- (WIP1.west);
-
-\node[below right=2cm and 4cm of WIP00, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIPp1){};
-\node[rectangle, draw, right=0.5cm of WIPp1, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unitp1){};
-\node[draw,dashed,rounded corners,fit=(WIPp1) (unitp1),inner sep=25pt,label={above:{stage (p,1)}}](stagep1){};
-
-\draw[-latex] (stage00.east) -- (stagep1.west);
-
-\node[right=4cm of WIP11, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP1m){};
-\node[rectangle, draw, right=0.5cm of WIP1m, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit1m){};
-\node[draw,dashed,rounded corners,fit=(WIP1m) (unit1m),inner sep=25pt,label={above:{stage (1,m$_1$)}}](stage1m){};
-
-\draw[-latex] (stage11.east) -- (stage1m.west);
-
-\node[right=4cm of WIPp1, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIPpm){};
-\node[rectangle, draw, right=0.5cm of WIPpm, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unitpm){};
-\node[draw,dashed,rounded corners,fit=(WIPpm) (unitpm),inner sep=25pt,label={above:{stage (p,m$_p$)}}](stagepm){};
-
-\draw[-latex] (stagep1.east) -- (stagepm.west);
-
-\node[right=3.5cm of WIP1, minimum width=1cm, minimum height=1.4cm](WIPm){.....};
-
-\node[left=0.5cm of WIPm, minimum width=1cm, minimum height=1.4cm](WIPma){};
-
-\draw[-latex] (WIP1a.east) -- (WIPma.west);
-
-\end{tikzpicture}
-\end{center}
-\caption{Multi-product serial batching divergent networked plant of a steel industry. Source: adapted from \cite{LiuEtAl2020} * stage $(i, j)$ means stage $j$ of production line $i$.}
-\end{figure}
-
-In multi-product batch scheduling (MPBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the batches based on the known demand.
-Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
-Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each batch, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
-Also, some cientific works consider MPBS problems within different layouts as well as dinamic and multiperiod scenarios.
-In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
-Many cientifc works propose mixed-integer linear programming (MILP) formulations to solve MPBS problems.
-As example, we can mention the work of \cite{MendezEtAll2000} that presents a MILP continuous-time model and a two-step systematic methodology for a single-stage multi-product batch scheduling problem with different due-dates.
-Later, \cite{MendezCerda2003} also proposed another MILP formulation for reactive scheduling.
-As observerd by \cite{HeHui2008}, with the problem size increasing, the computational effort of MILP increases greatly so it is very difﬁcult for MILP to obtain acceptable solutions to large-size problems within reasonable time.
-Citing some works that use other approaches, \cite {KimEtAl1996} propose a Gantt chart mapping method and a modified genetic algorithm for solving a networked flowshop multi-product batch scheduling problem as well as a rule-based reactive rescheduling scheme for dinamicaly overcoming in-process deviation from the initial optimized schedule and \cite{HeHui2008} present a rule-based genetic algorithm for the scheduling of single-stage multi-product batch plants with parallel units.
-
-It is importante to note that some production units are capable of processing multiple jobs at the same time.
-In such a case batches of different products and sizes can be grouped and processed by these units as a single batch.
-It is therefore necessary to determine the set of "batches" that each new grouped batch will contain.
-The multi-product balancing problem consists of determining these groupings, seeking to minimize the overall makespan.
-\cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.
-\cite{FowlerMonch2022} present a taxonomy and an extensive literature review for the p-batch problems.
-According to the authors, a p-batch problem can be classified as compatible setting - where there is no restriction on which jobs can be used to form a batch - and incompatible family case - where only jobs belonging to the same family can be used to form a batch.
-Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product p-batch problem involving identical parallel units, capacity constraints, and incompatible families with different job sizes.
-
-In a real production environment, some of these problems arise in a connected way, so many cientific works adress mixed multi-product batch problems.
-As example, \cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.
-Also, de work of \cite{MendezEtAll2000}, previously mentioned, considers planning as an integrated part of solution in real-world multi-product batch plant scheduling and therefore includes the product batching problem in its proposed MILP continuous-time models and two-step systematic methodology.
-
-\subsection{Taxonomy and notation}
-
-In short, based on the bibliographic survey conducted for the preparation of this paper, we identify that the multi-product batch problems can differentiate with the following aspects:
-
-\begin{enumerate}[label=\arabic*)]
-\item \textbf{number of stages ($\sigma$)}: single stage ($SS$) or multistage ($MS$);
-\item \textbf{layout($\lambda$)}: single unit ($SU$), flowshop ($Fl$), parallel ($Pl$), or networked ($Nt$) (convergent ($CNt$) and /or divergent ($DNt$));
-\item \textbf{production mode ($\mu$)}: single-product campaing ($SPC$), mixed-product campaign ($MPC$), serial batching ($s\textrm{-}batch$) and/or parallel batching ($p\textrm{-}batch$);
-\item \textbf{problem:($\pi$)}  : design ($D$), planning ($P$), sizing ($Sz$), scheduling ($Sc$) and/or balancing ($B$); 
-\item \textbf{time horizon ($\eta$)}: single period ($SP$), multiperiod ($MP$) or cyclic ($Cc$);
-\item \textbf{scenario ($\gamma$)}: static ($St$) or dynamic ($Dn$);
-\item \textbf{input ($\iota$)}: deterministic ($Dt$) and/or stochastic ($St$);
-\item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and processing time ($PT$);
-\item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$).
-\end{enumerate}
-
-So, to describe a speciﬁc multi-product batch problem, we propose the notation $\sigma|\lambda|\mu|\pi|\eta|\gamma|\iota|\delta|\rho$.
-Some of the multi-product batch problems and solution approaches discussed in the references cited in this paper are summarized in Tab.
-\ref{tab:review}.
-
-\begin{table}[h!]
-\begin{center}
-\begin{small}
-\begin{tabular}[c]{l l l}
-reference & problem & contributions  \\
-\cline {1-3} \\
-\cite{Eilon1985} & $SS|SU|s\textrm{-}batch|Sc|SP$ &  analysis of the effect\\
-& $St|Dt|SC, HC|-$  & of splitting batches \\
-\cline {1-3} \\
-Ravemark and & $MS|Pl|SPC|D|Cc|$ & convex MILP model \\
-Rippin (1998) & $St|Dt|C|WIP$ & solved with DICOPT++ \\
-\cline {1-3} \\
-Petkov and & $MS|Pl|SPC|D|Cc|$ & exact method\\
-Maranas (1998)  & $St|St|NP|-$ & \\
-\cline {1-3} \\
-\cite{MendezEtAll2000} & $SS|Pl|MPC|P,Sc|SP|St|$ & MILP continuous-time  \\
-& $Dt|WIPC|RT, DD$ & model and a two-step  \\
-& & systematic methodology \\
-\cline {1-3} \\
-Méndez and & $SS|Pl|MPC|Sc|SP|Dn|Dt|$ & MIPL model and \\
-Cerdá (2003) &$wE/T|RT, DD, SDST$ & a rescheduling algorithm\\
-\cline {1-3} \\
-\cite{HeHui2008} & $SS|Pl|MPC|Sc|SP|$ & rule-based genetic \\
-& $St|Dt|C_{max}, TT|LCU, DD$ & algorithm \\
-\cline {1-3} \\
-\cite{FumeroEtAl2016} & $MS|Pl|MPC|D,P,Sc|Cc|$ & MILP model \\
-& $St|Dt|NP|LCU,USC$ & solved with CPLEX \\
-\cline {1-3} \\
-\cite{LiuEtAl2020} & $MS|DNt|s\textrm{-}batch|Sz|MP|St|$ & mixed-integer quadratic \\
-& $Dt|SC,WIPC|LCU,WIP$ & programming model  \\
-& & and exact algorithm \\
-\cline {1-3} \\
-\cite{LiEtAl2022} & $SS|Pl|p\textrm{-}batch|Sc,B|SP|$ & MILP model \\
-& $St|Dt|C_{max}|LCU, RT, IF$ & and a constraint-guided \\
- & & artificial immune \\
- & & system based algorithm \\ 
-\cline {1-3} \\
-\end{tabular}
-\caption{Some contributions on the multi-product batch problems}
-\label{tab:review}
-\end{small}
-\end{center}
-\end{table}
-
-\subsection{Contributions of this paper}
-
-In this work we are interested in the multiperiod multi-product batch scheduling problem in a networked plant that arises in a plastic bag industry.
-The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020} (Fig.
-\ref{fig:networkdPlantSteelIndustry}), however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
-Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}.
-Thus, part of the problem solving process consists of solving a multi-product p-batch problem into extruders.
-Also, in the problem we study, in addition to demand, we must consider the factory and outlets' storage capacity, which is individually defined for products, but also for the set of products.
-
-When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
-This problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ batch problem.
-For simplification purposes, we named this problem multi-product p-batch processing time maximization (MBPTM) problem.
-
-It is important to note that, since the MBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied.
-In a future work, we intend to present the mathematical model and solution algorithm we are developing for this last problem.
-As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MBPTM problem.
-
-The rest of the paper is organized as follows.
-In the next sections, a presentation of problem is made along with an application example.
-Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution.
-Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
-In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions to this work are informed and acknowledgments are given, respectively.
-Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.
-
-\section{Multi-product p-batch processing time maximization problem}
-\label{sec:MBPTMP}
-
-The multi-product p-batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
-In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product.
-In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set.
-The production quantity of each product is mainly defined according to the demand for the product.
-However, it is still possible to stock the products and/or send them to the outlets.
-In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch.
-Also, there is a time limit available for processing the batch.
-About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.
-
-\section{Mathematical model}
-\label{sec:mathModel}
-
-Given that:
-
-$\textrm{UD}_i$ is the demand for the product $i$;
-
-$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch;
-
-$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory;
-
-$\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets;
-
-$\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets;
-
-$\textrm{p}_i$ is the production rate of product $i$;
-
-$\textrm{Z}$ is the timeout for batch processing;
-
-$P_i$ is the amount of product $i$ produced;
-
-$D_i$ is the amount of product $i$ delivered for the demand;
-
-$O_i$ amount of product $i$ shipped to factory outlets;
-
-$I_i$ is the amount of product $i$ that will be stored at the factory;
-
-$T$ is the batch processing time;
-
-We have the problem:
-
-\begin{equation}
-\label{MBPTMP01}
-max \quad T
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-P_i - \textrm{p}_i * T  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-P_i - D_i - O_i - I_i = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-\label{MBPTMP04}
-D_i \leq \textrm{UD}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-O_i \leq \textrm{UO}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i{O_i} \leq \textrm{O}
-\end{equation}
-
-\begin{equation}
-I_i \leq \textrm{UI}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i{I_i} \leq \textrm{I}
-\end{equation}
-
-\begin{equation}
-T \leq \textrm{Z}
-\end{equation}
-
-\begin{equation}
-\min \{\textrm{UD}_i - D_i, O_i + I_i\} = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-\min\{\textrm{O} - \sum_i\{ O_i\}, \textrm{UO}_i - O_i, I_i\} = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-\label{MBPTMP10}
-T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-where:
-
-Constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$.
-Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$.
-Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the autlets, and the factory-stocked quantity of each product must be less than their respective known limits.
-Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values.
-The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
-Equations in (10) and (11) define the production distribution priority.
-And finally, the constraints in (12) inform the nature of the decision variables.
-
-\section{Analytical solution}
-\label{sec:analyticalSol}
-
-The method proposed in this paper for solution of the MBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the production to meet demand, the production sent to outlets and the production stocked in factory.
-Next, we explain each of these parts in detail.
-\\
-
-\noindent \emph{Calculation of maximum p-batch processing time:} \\
-
-It is possible to split the batch processing time into two time slots:
-
-\begin{equation}
-T = T' + T''
-\end{equation}
-
-\noindent where $T'$ is the maximum processing time whose production will be used exclusively to meet the demand.
-
-Then, being $D_{i}^{'}$ the quantity produced of the product $i$ after $T'$ units of processing time, we have:
-
-\begin{equation}
-\label{eq:s02}
-D_{i}^{'} - \textrm{p}_i * T'  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-\label{eq:s03}
-D_{i}^{'} \in Z \quad \forall i
-\end{equation}
-
-\noindent and, as $D_{i}^{'} \leq D_i$, $\forall i$, we have:
-
-\begin{equation}
-\label{eq:s04}
-D_{i}^{'} \leq \textrm{UD}_i\quad \forall i
-\end{equation}
-
-From the equations in (\ref{eq:s02}) and the restrictions in (\ref{eq:s03}) and (\ref{eq:s04}), we have:
-
-\begin{equation}
-\label{eq:s05}
-T' \leq \lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor \quad \forall i
-\end{equation}
-
-And, as we wish maximum value to $T'$, from (\ref{eq:s05}) we have:
-
-\begin{equation}
-\label{eq:s06}
-T' = \min_i\{\lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor\}
-\end{equation}
-
-Observe that there may be a leftover corresponding to the demand not met by the production in the first part of the processing time, $T'$.
-This leftover, $S_i$, will be defined according to the equations in (\ref{eq:s07}):
-
-\begin{equation}
-\label{eq:s07}
-S_i = \textrm{UD}_i - D_{i}^{'} \quad \forall i
-\end{equation}
-
-It is also possible to consider that outlets are extensions of the factory stock.
-Therefore, it is possible to consider the factory stock of product $i$ and the outlets stock $i$ as single stock for the product $i$, $E_i$, so that:
-
-\begin{equation}
-\label{eq:s08}
-E_i = O_i + I_i
-\end{equation}
-
-\begin{equation}
-\label{eq:s09}
-E_i \leq \textrm{UO}_i + \textrm{UI}_i
-\end{equation}
-
-\begin{equation}
-\label{eq:s10}
-\sum_i {E_i} \leq \textrm{O} + \textrm{I}
-\end{equation}
-
-\begin{equation}
-\label{eq:s11}
-E_i \in Z \quad \forall i
-\end{equation}
-
-As the time $T'$ was used only for production that will meet the demand, $T''$  will be the remaining processing time, \emph{i.e.} the maximum processing time used for production that will meet the leftover of demand, sent to the outlets and stored in factory.
-So we have:
-
-\begin{equation}
-\label{eq:s12}
-E_i + S_i - \textrm{p}_i * T''  = 0 \quad \forall i
-\end{equation}
-
-\noindent Thus, after replacing (\ref{eq:s12}) in (\ref{eq:s09}) and applying some algebra, we have:
-
-\begin{equation}
-\label{eq:s13}
-T''  \leq (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i \quad \forall i
-\end{equation}
-
-\noindent And, after replacing (\ref{eq:s12}) in (\ref{eq:s10}) and applying some algebra, we have:
-
-\begin{equation}
-\label{eq:s14}
- T'' \leq (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i
-\end{equation}
-
-Finally, as $T$  is an integer value and we want to maximize this value, then:
-
-\begin{equation}
-\label{eq:s15}
- T'' = \lfloor\min\{\min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor
-\end{equation}
-
-So, the analytical method for finding maximum $T$ can be decomposed into 4 steps:
-
-step 1: find $T'$, where:
-\begin{equation}
-T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
-\end{equation}
-
-step 2: calculate $S_i$ for all products.
-\begin{equation}
-\label{eq:unmet}
-S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
-\end{equation}
-
-step 3: find $T''$, where:
-\begin{equation}
-T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
-\end{equation}
-
-step 4: calculate $T$, where: 
-\begin{equation}
-T^* = T' + T''
-\end{equation}
-\begin{equation}
-T = \min \{T^* , \textrm{Z}\}
-\end{equation}
-
-Note that, as we reduce the value of $T'$, the consequent reduction of $D_{i}^{'}$ will be directly attributed to the leftover of demand $S_i$ and, therefore, there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1.
-Thus it is possible to use a simplification of the method presented, making $T' = 0$.
-In this case $S_i = \textrm{UD}_i, \forall i$.
-The simplified version of the method is presented below:
-
-step 1: find $T^*$, where:
-\begin{equation}
-T^* = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
-\end{equation}
-
-step 2: calculate $T$, where:
-
-\begin{equation}
-T = \min \{T^* , \textrm{Z}\}
-\end{equation}
-
-This simplification of the method demonstrates that the value calculated to $T$ does not depend on the way the production of the product $i$, $P_i$, is distributed between service to demand, $D_i$, outlets, $O_i$, and  factory's stock $I_i$.
-
-\noindent \emph{Full solution:}
-
-We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply attending the priorities for distribution. The following three algorithms can be used to find a complete solution.
-
-The Algorithm (\ref{alg:part01}) is used for finding an optimimal value for $T$.
-
-\begin{algorithm}
-\caption{Solving MBPTM problem | Part 01 - find an optimal $T$ to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}).}\label{alg:part01}
-\begin{algorithmic}
-	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}$
-	\State $T^* \gets \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor$
-	\State $T \gets \min \{T^* , \textrm{Z}\}$
-\State \textbf{Return:} $T$.
-\end{algorithmic}
-\end{algorithm}
-
-Then an initial production distribution can be done by the Algorithm (\ref{alg:part02}).
-This distribution is made without considering the restrictions defined for the set of products.
-$SO$ and $SI$ represent, respectively, the total amount available to be sent to the outlets and the total amount available for factory inventory after the initial distribution.
-If this values are negative, this indicates that the proposed initial distribution is not a feasible distribution.
-
-\begin{algorithm}
-\caption{Solving MBPTM problem | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions for the set of products of the batch.}\label{alg:part02}
-\begin{algorithmic}
-	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}, T$.
-	\For{all i}
-		\State $E_i \gets T * \textrm{p}_i$
-		\State $D_i \gets \min \{\textrm{UD}_i, E_i\}$
-		\State $E_i \gets E_i - D_i$
-		\State $O_i \gets \min \{\textrm{UO}_i, E_i\}$
-		\State $E_i = E_i - O_i$
-		\State $\textrm{UO}_i = \textrm{UO}_i - O_i$
-		\State $I_i = E_i$
-		\State $\textrm{UI}_i = \textrm{UI}_i - I_i$
-	\EndFor
-	\State $SO = \textrm{O} - \sum_i{O_i}$
-	\State $SI = \textrm{I} - \sum_i{I_i}$
-	\State \textbf{Return:} $D_i, O_i, I_i, E_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
-\end{algorithmic}
-\end{algorithm}
-
-So, after applying Algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
-However, if $SO < 0$ or $SI <0$, solution is not yet feasible.
-But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements:
-
-$if \quad SO < 0 \quad then \quad SI > 0 \quad and  \quad |SO| < SI$
-
-$if \quad SI < 0 \quad then \quad SO > 0 \quad and  \quad |SI| < SO$
-
-Therefore it is possible to meet the restrictions by applying the Agorithm (\ref{alg:part03}).
-In this algorithm we redistributed the production of factory's stock to the outlets or vice versa, respectively, due to having a $SI$ or $SO$ negative.
-
-\begin{algorithm}
-\caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch set.}\label{alg:part03}
-\begin{algorithmic}
-\Require $O_i, I_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
-\If{$SO < 0$}
-\For{all $i$}
-	\State $O_i \gets O_i - \min\{ O_i, UI_i, |SO|\}$
-	\State $I_i \gets I_i + \min\{ O_i, UI_i, |SO|\}$
-	\State $SO \gets SO + \min\{ O_i, UI_i, |SO|\}$
-	\If{$SO = 0$}
-		break looping for;
-	\EndIf
-\EndFor
-\EndIf
-
-\If{$SI < 0$}
-\For{all $i$}
-	\State $I_i \gets I_i - \min\{ I_i, UO_i, |SI|\}$
-	\State $O_i \gets O_i + \min\{ I_i, UO_i, |SI|\}$
-	\State $SI \gets SI + \min\{ I_i, UO_i, |SI|\}$
-	\If{$SI = 0$}
-		break looping for;
-	\EndIf
-\EndFor
-\EndIf
-\State \textbf{Return:} $O_i, I_i, \forall i$.
-\end{algorithmic}
-\end{algorithm}
-
 \section{Tests and results}
 \label{sec:results}
-
-To test the developed model and analytical solution method, we created a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem and also a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver \citep{Fraga2023}.
-The tests were performed on a notebook with an Intel i7 processor.
-We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\
-
-\begin{equation}
-\textrm{p}_i = \textrm{rand}()\%30 + 10
-\end{equation}
-
-\begin{equation}
-\textrm{UD}_i = \textrm{rand}()\%3000 + 800;
-\end{equation}
-
-\begin{equation}
- \textrm{seed1} = \textrm{rand}()\%3000 + 500;
-\end{equation}
-
-\begin{equation}
-\textrm{seed2} = \textrm{rand}()\%5000 + 1000;
-\end{equation}
-
-\begin{equation}
-\textrm{O} = \textrm{N}/2*\textrm{seed1};
-\end{equation}
-
-\begin{equation}
-\textrm{UO}_i = \textrm{rand}()\%(\textrm{seed1}-500) + 500;
-\end{equation}
-
-\begin{equation}
-\textrm{I} = \textrm{N}/2*\textrm{seed2};
-\end{equation}
-
-\begin{equation}
-\textrm{UI}_i = \textrm{rand}()\%(\textrm{seed2}-1000) + 1000;
-\end{equation}
-
-\begin{equation}
-\textrm{Z} = 100;
-\end{equation}
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}[c]{c r r r}
-$i$ & 1 & 2 & total \\
-\cline {1-4} \\
-$\textrm{p}_i$ & 60 & 40 & \\
-$\textrm{UD}_i$ & 1000 & 500 & \\
-$\textrm{UO}_i$ & 600 & 600 & 1000 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 3000 \\
-\cline {1-4} \\
-& & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\caption{Benchmark MBPTM 2}
-\label{tab:MBPTMP001}
-\end{center}
-\end{table}
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}[c]{c r r r r}
-$i$ & 1 & 2 & 3 & total \\
-\cline {1-5} \\
-$\textrm{p}_i$ & 60 & 40 & 50 \\
-$\textrm{UD}_i$ & 1000 & 500 & 800 \\
-$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 3500 \\
-\cline {1-5} \\
-& & & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\caption{Benchmark MBPTM 3}
-\label{tab:MBPTMP002}
-\end{center}
-\end{table}
-
-\begin{table}[h]
-\begin{center}
-\begin{small}
-\begin{tabular}[c]{c r r r r r r r r r r r }
-$i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
-\cline {1-12} \\
-$\textrm{p}_i$ & 60 & 40 & 50 & 40 & 30 & 50 & 60 & 10 & 20 & 40\\
-$\textrm{UD}_i$ & 1000 & 500 & 800 & 500 & 400 & 500 & 2000 & 300 & 500 & 1000 \\
-$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 & 300 & 200 & 500 & 800 & 0 & 200 & 3000 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 800 & 3000 & 1000 & 400 & 300 & 200 & 0 & 5000 \\
-\cline {1-12} \\
-& & & & & & & & & & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\caption{Benchmark MBPTM 10}
-\label{tab:MBPTMP003}
-\end{small}
-\end{center}
-\end{table}
-
-Randomly generated benchmarks were named RMBPTM $\textrm{N}$, being $\textrm{N}$ the number of products.
-Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
-To build the results presented in this work, we used source=0.
-The benchmarks used for the tests performed can be consulted at github.com/tbfraga/COPSolver.
-
-Table \ref{tab:results} presents the results obtained by applying the analytical method (COPSolver) and the LINGO solver for the solution of the previously presented benchmarks.
-
-\begin{table}[h]
-\begin{center}
-\begin{footnotesize}
-\begin{tabular}[c]{l r r r r}
-problem & LINGO solver & time (s) & analytical method & time (s) \\
-\cline {1-5} \\
-MBPTM 2 & 55 & 0.03 & 55 & $<$ 0.01 \\
-MBPTM 3 & 48 & 0.03 & 48 & $<$ 0.01 \\
-MBPTM 10 & 30 & 0.05 & 30 & $<$ 0.01 \\
-RMBPTM 20 & 100 & 0.06 & 100 & $<$ 0.01 \\
-RMBPTM 50 & 98 & 0.08 & 98 & $<$ 0.01 \\
-RMBPTM 100 & 98 & 0.11 & 98 & $<$ 0.01 \\
-RMBPTM 1,000 & 78 & 1.20 & 78 & $<$ 0.01 \\
-RMBPTM 2,000 & 70 & 3.25 & 70 & $<$ 0.01 \\
-RMBPTM 5,000 & 70 & 15.12 & 70 & $<$ 0.02 \\
-RMBPTM 10,000 & 70 & 55.19 & 70 & $<$ 0.04 \\
-\cline {1-5} \\
-\end{tabular}
-\caption{Results obtained with the LINGO solver and the analytical method}
-\label{tab:results}
-\end{footnotesize}
-\end{center}
-\end{table}
-
-Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MBPTM 3 and 10 found by both COPSolver and LINGO solver.
-Files containing all results can be found at github.com/tbfraga/COPSolver.
-
-\begin{table}[h]
-\begin{center}
-\begin{footnotesize}
-\begin{tabular}[c]{l r r r r}
-product & production & delivered (s) & send to outlets & stocked in factory \\
-\cline {1-5} \\
-P1 & 2,880 & 1,000 & 300 & 1,580 \\
-P2 & 1,920 & 500 & 600 & 820 \\
-P3 & 2,400 & 800 & 600 & 1,000 \\
-\cline {1-5} \\
-\end{tabular}
-\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 3}
-\label{tab:compResultsMBPTMP2}
-\end{footnotesize}
-\end{center}
-\end{table}
-
-\begin{table}[h]
-\begin{center}
-\begin{footnotesize}
-\begin{tabular}[c]{l r r r r}
-product & production & delivered (s) & send to outlets & stocked in factory \\
-\cline {1-5} \\
-P1 & 1,800 & 1,000 & 400 & 400 \\
-P2 & 1,200 & 500 & 600 & 100 \\
-P3 & 1,500 & 800 & 600 & 100 \\
-P4 & 1,200 & 500 & 700 & 0 \\
-P5 & 900 & 400 & 300 & 200 \\
-P6 & 1,500 & 500 & 200 & 800 \\
-P7 & 1,800 & 1800 & 0 & 0 \\
-P8 & 300 & 300 & 0 & 0 \\
-P9 & 600 & 500 & 0 & 100 \\
-P10 & 1,200 & 1000 & 200 & 0 \\
-\cline {1-5} \\
-\end{tabular}
-\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 10}
-\label{tab:compResultsMBPTMP3}
-\end{footnotesize}
-\end{center}
-\end{table}
-
-It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
-As the analytical method is a polynomial time complexity method, we did not intend to compare computational costs, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
-
-We have considered here a one-day period problem, so in a future work we will study the complexities of solving a multi-period problem and try to propose new solution methods if needed.
 
@@
 
-In this paper we presented the Multi-product Batch Processing Time Maximization problem, as well as a mathematical model and an exact analytical solution method for this problem.
-The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO software, from LINDO Systems, and with a solver developed in C++ language.
-Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large problems, which demonstrates the efficiency of the proposed method.
-As in this paper we considered a planning period of one day, in a future work we will study the complexities that arise when considering the same problem in a multi-period scenario.
-We will also verify if there is the possibility of extending the proposed analytical method to solve a class of linear integer programming problems with similar characteristics to the studied problem.
+In this paper we presented ...
 

### 2023-10-19 manuscript/MBPTMP/manuscript.tex
updating paper - AHP consistency

--- 2023-10-17 manuscript/manuscript.tex
@@
 \item taxonomy and notation for the multi-product batch problems;
-\item multi-product p-batch processing time maximization (MBPTM) problem definition;
-\item linear integer programming model for the MBPTM problem;
-\item exact optimization method for solving the MBPTM problem.
+\item multi-product p-batch processing time maximization (MPBPTM) problem definition;
+\item linear integer programming model for the MPBPTM problem;
+\item exact optimization method for solving the MPBPTM problem.
 \end{highlights}
@@
 As stated by \cite{PetkovMaranas1998} the batch plant can operate under a single-product campaign (SPC) production mode, where all the batches of a given product are manufactured before production of the next product begins, or under mixed-product campaign (MPC) production modes where more batches are produced per unit time at the expense of increased changeover times and cleanup costs.
-Also the plant layout can take on different formats, such as: single unit, where all operations needed to process the batches are performed by a single processor; serial flowshop plant, in which all products follow the same linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{ShiEtAll2017}; and networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
-Also networked plant can be divergent, convergent or both.
+Also the plant layout can take on different formats, such as: single unit, where all operations needed to process the batches are performed by a single processor; serial flowshop plant, in which all products follow the same linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{ShiEtAll2017}; and convergent and/or divergent networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
 
@@
 Many cientifc works propose mixed-integer linear programming (MILP) formulations to solve MPBS problems.
-As example, we can mention the work of \cite{MendezEtAll2000} that presents a MILP continuous-time model and a two-step systematic methodology for a single-stage multi-product batch scheduling problem with different due-dates.
+As example, we can mention the work of \cite{MendezEtAll2000} that presents a MILP continuous-time model and a two-step systematic methodology for a single stage multi-product batch scheduling problem with different due-dates.
 Later, \cite{MendezCerda2003} also proposed another MILP formulation for reactive scheduling.
 As observerd by \cite{HeHui2008}, with the problem size increasing, the computational effort of MILP increases greatly so it is very difﬁcult for MILP to obtain acceptable solutions to large-size problems within reasonable time.
-Citing some works that use other approaches, \cite {KimEtAl1996} propose a Gantt chart mapping method and a modified genetic algorithm for solving a networked flowshop multi-product batch scheduling problem as well as a rule-based reactive rescheduling scheme for dinamicaly overcoming in-process deviation from the initial optimized schedule and \cite{HeHui2008} present a rule-based genetic algorithm for the scheduling of single-stage multi-product batch plants with parallel units.
+Citing some works that use other approaches, \cite {KimEtAl1996} propose a Gantt chart mapping method and a modified genetic algorithm for solving a networked flowshop multi-product batch scheduling problem as well as a rule-based reactive rescheduling scheme for dinamicaly overcoming in-process deviation from the initial optimized schedule and \cite{HeHui2008} present a rule-based genetic algorithm for the scheduling of single stage multi-product batch plants with parallel units.
 
@@
 When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
-Using the notation presented before, this problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ batch problem.
+Using the notation presented before, this problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ problem.
 For simplification purposes, we named this problem multi-product p-batch processing time maximization (MPBPTM) problem.
@@
 It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied.
-In a future work, we intend to present the mathematical model and solution algorithm we are developing for this last problem.
+In a future work, we intend to present the mathematical model and a Particle Collison based solution algorithm we are developing for this last problem.
 As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPBPTM problem.
@@
 The rest of the paper is organized as follows.
-In the next sections, a presentation of problem is made along with an application example.
+In the next sections, the MPBPTM problem is presented.
 Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution.

### 2023-10-23 manuscript/MBPTMP/manuscript.tex
updating papers

@@
 \begin{abstract} 
-Among the most complex multi-product batch problems are the multi-product p-batch scheduling (MPPBS) problems, where jobs must be scheduled on parallel batch processing machines.
-When applying some local search heuristics to solve a MPPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products.
-In this paper we name this problem multi-product p-batch processing time maximization (MPBPTM) problem.
-Once a MPBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPPBS problems.
-In addition, for some industries, efficiently solving a MPBPTM problem can have a significant impact on storage costs and customer satisfaction.
-In this paper we presente a mathematical model and an exact method with polynomial time complexity for the MPBPTM problem.
+Among the most complex multi-product batch problems are the multi-product p-batch scheduling (MPBS) problems, where jobs must be scheduled on parallel batch processing machines.
+When applying some local search heuristics to solve a MPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products.
+In this paper we name this problem multi-product p-batch processing time maximization (MBPTM) problem.
+Once a MBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPPBS problems.
+In addition, for some industries, efficiently solving a MBPTM problem can have a significant impact on storage costs and customer satisfaction.
+In this paper we presente a mathematical model and an exact method with polynomial time complexity for the MBPTM problem.
 We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method.
@@
 \item taxonomy and notation for the multi-product batch problems;
-\item multi-product p-batch processing time maximization (MPBPTM) problem definition;
-\item linear integer programming model for the MPBPTM problem;
-\item exact optimization method for solving the MPBPTM problem.
+\item multi-product p-batch processing time maximization (MBPTM) problem definition;
+\item linear integer programming model for the MBPTM problem;
+\item exact optimization method for solving the MBPTM problem.
 \end{highlights}
@@
 \begin{keyword}
-multi-product batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep LINGO
+multi-product p-batch \sep processing time maximization \sep mathematical model \sep exact method \sep LINGO
 \end{keyword}
@@
 
-In multi-product batch scheduling (MPBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the batches based on the known demand.
+In multi-product batch scheduling (MBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the batches based on the known demand.
 Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
-Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each batch, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
-Also, some cientific works consider MPBS problems within different layouts as well as dinamic and multiperiod scenarios.
-In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
-Many cientifc works propose mixed-integer linear programming (MILP) formulations to solve MPBS problems.
+Some cientific works impose additional constraints on the MBS problem - such as release times and due dates for each batch, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
+Also, some cientific works consider MBS problems within different layouts as well as dinamic and multiperiod scenarios.
+In parallel MBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
+Many cientifc works propose mixed-integer linear programming (MILP) formulations to solve MBS problems.
 As example, we can mention the work of \cite{MendezEtAll2000} that presents a MILP continuous-time model and a two-step systematic methodology for a single stage multi-product batch scheduling problem with different due-dates.
@@
 In such a case batches of different products and sizes can be grouped and processed by these units as a single batch.
-It is therefore necessary to determine the set of "batches" that each new grouped batch will contain.
+It is therefore necessary to determine the set of "batches" that each new compounded batch will contain.
 The multi-product balancing problem consists of determining these groupings, seeking to minimize the overall makespan.
@@
 As example, \cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.
-Also, de work of \cite{MendezEtAll2000}, previously mentioned, considers planning as an integrated part of solution in real-world multi-product batch plant scheduling and therefore includes the product batching problem in its proposed MILP continuous-time models and two-step systematic methodology.
+Also, the work of \cite{MendezEtAll2000}, previously mentioned, considers planning as an integrated part of solution in real-world multi-product batch plant scheduling and therefore includes the product batching problem in its proposed MILP continuous-time models and two-step systematic methodology.
 
@@
 \item \textbf{input ($\iota$)}: deterministic ($Dt$) and/or stochastic ($St$);
-\item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and processing time ($PT$);
+\item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), customer satisfaction($CS$), plant performance ($PP$) and/or processing time ($PT$);
 \item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$).
@@
 
-When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
+When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product p-batches, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
 Using the notation presented before, this problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ problem.
-For simplification purposes, we named this problem multi-product p-batch processing time maximization (MPBPTM) problem.
+For simplification purposes, we named this problem multi-product p-batch processing time maximization (MBPTM) problem.
 
-It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied.
+It is important to note that, since the MBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product p-batch s-batch problem in the plastic bag networked plant of the industry studied.
 In a future work, we intend to present the mathematical model and a Particle Collison based solution algorithm we are developing for this last problem.
-As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPBPTM problem.
+As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MBPTM problem.
 
 The rest of the paper is organized as follows.
-In the next sections, the MPBPTM problem is presented.
-Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution.
+In the next sections, the MBPTM problem is presented.
+Section \ref{sec:mathModel} presents an interger mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution.
 Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
-In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions to this work are informed and acknowledgments are given, respectively.
-Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.
+Section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.
+Finally, in sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions to this work are informed and acknowledgments are given, respectively.
 
@@
 Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$.
-Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the autlets, and the factory-stocked quantity of each product must be less than their respective known limits.
-Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values.
+Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the outlets, and the factory-stocked quantity of each product must be less than their respective known limits.
+Constraints (6) and (8) state that both the sum of product quantities sent to the outlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values.
 The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
@@
 
-The method proposed in this paper for solution of the MBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the production to meet demand, the production sent to outlets and the production stocked in factory.
+The method proposed in this paper for solution of the MBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the part of the production used to meet demand, the part of the production sent to outlets and the part of the production stocked in factory.
 Next, we explain each of these parts in detail.
@@
 
-Finally, as $T$  is an integer value and we want to maximize this value, then:
+Finally, as $T''$  is an integer value and we want to maximize this value, then:
 
@@
 \begin{equation}
-T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
+T' = \lfloor{\min_{i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
 \end{equation}
@@
 \begin{equation}
-T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
+T'' = \lfloor{\min \{\min_{i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
 \end{equation}
@@
 \begin{equation}
-T^* = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
+T^* = \lfloor{\min \{\min_{i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
 \end{equation}
@@
 
-This simplification of the method demonstrates that the value calculated to $T$ does not depend on the way the production of the product $i$, $P_i$, is distributed between service to demand, $D_i$, outlets, $O_i$, and  factory's stock $I_i$.
+This simplification of the method demonstrates that the value calculated to $T$ does not depend on the way the production of the product $i$, $P_i$, is distributed between service to demand, $D_i$, outlets, $O_i$, and  factory's stock, $I_i$.
 
@@
 	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}$
-	\State $T^* \gets \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor$
+	\State $T^* \gets \lfloor{\min \{\min_{i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor$
 	\State $T \gets \min \{T^* , \textrm{Z}\}$
@@
 This distribution is made without considering the restrictions defined for the set of products.
-$SO$ and $SI$ represent, respectively, the total amount available to be sent to the outlets and the total amount available for factory inventory after the initial distribution.
+$SO$ and $SI$ represent, respectively, the total amount that can be sent to the outlets and the total amount that can be stocked in factory after the initial distribution.
 If this values are negative, this indicates that the proposed initial distribution is not a feasible distribution.
@@
 Therefore it is possible to meet the restrictions by applying the Agorithm (\ref{alg:part03}).
-In this algorithm we redistributed the production of factory's stock to the outlets or vice versa, respectively, due to having a $SI$ or $SO$ negative.
+This algorithm redistributes the production of factory's stock to the outlets or vice versa, respectively, due to having a $SI$ or $SO$ negative.
 
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem and also a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver \citep{Fraga2023}.
+To test the developed model and analytical solution method, we created a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem and also a solver in LINGO named MBPTM.lng both available at codeocean and GitHub \citep{COPSolver2023}.
+A brief explanation of the software can be found in the paper of \cite{Fraga2023}.
 The tests were performed on a notebook with an Intel i7 processor.
@@
 
-We have considered here a one-day period problem, so in a future work we will study the complexities of solving a multi-period problem and try to propose new solution methods if needed.
+We have considered here a static problem, so in a future work we will study the complexities of solving the problem dynamically and try to propose new solution methods if needed.
 
@@
 
-In this paper we presented the Multi-product Batch Processing Time Maximization problem, as well as a mathematical model and an exact analytical solution method for this problem.
+In this paper we presented the multi-product p-batch processing time maximization problem, as well as a mathematical model and an exact analytical solution method for this problem.
 The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO software, from LINDO Systems, and with a solver developed in C++ language.
 Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large problems, which demonstrates the efficiency of the proposed method.
-As in this paper we considered a planning period of one day, in a future work we will study the complexities that arise when considering the same problem in a multi-period scenario.
-We will also verify if there is the possibility of extending the proposed analytical method to solve a class of linear integer programming problems with similar characteristics to the studied problem.
+As in this paper we considered a static problem, in a future work we will study the complexities that arise when considering the same problem in a dinamic scenario.
+We will also verify if there is the possibility of extending the proposed analytical method to solve a class of integer programming problems with similar characteristics to the studied problem.
 
@@
 %% Text of bibliographic item
+
+\bibitem[\protect\citeauthoryear{COPSolver}{2023}]{COPSolver2023}
+COPSolver (2023).
+COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multi-product batch processing time maximization problem.
+{\it codeocean and GitHub}, codeocean.com/capsule/4837209/tree/v1, github.com/tbfraga/COPSolver/releases/tag/v1.0-1.
 

### 2023-10-23 manuscript/FCPCOM/manuscript.tex
updating
updating papers
forcing consistency

@@
 \usepackage{algpseudocode}
+%\usepackage{algorithm2e}
 \usepackage{rotating}
@@
 Saaty's Analytic Hierarchy Process is an important method for assigning weight to multiple criteria.
-The logic of this method is not complicated.
-First a pairwise comparisons matrix is generated for the multiple criteria, and the normalized eigenvector of this pairwise matrix is used as the weight of the criteria.
 Despite this method represents an important inovation, its logic is not complicated at all.
@@
 \label{sec:intro}
+
+\section{Algorithms for forcing matrix consistency}
+\begin{algorithm}
+\caption{function $consistencyRate()$}\label{alg:CA}
+\begin{algorithmic}
+\Require $[a_{ij}]_{i,j=1}^{n}, RI[x]_{x=1}^{10}$
+\State{$\lambda_{max} = mainEigenvalue([a_{ij}]_{i,j=1}^{n})$ \footnote{main eigenvalue can be found using "Eigen/Eigenvalues library.}}
+\State{$CI = (\lambda_{max} - n) / (n-1)$}
+\State{$CR \gets CI/RI[n]$}
+\State{\Return {$CR$}}	
+\end{algorithmic}
+\end{algorithm}
+
+\subsection{Constructive algorithm}
+
+\begin{algorithm}
+\caption{function $constructivelyForceConsistency([a_{ij}]_{i,j=1}^{n})$}\label{alg:CA}
+\begin{algorithmic}
+\Require $[a_{ij}]_{i,j=1}^{n}$
+\Ensure $consistencyRate([a_{ij}]_{i,j=1}^{n}) \leq 0.1$
+\State{$CR = consistencyRate([a_{ij}]_{i,j=1}^{n})$}
+\If {$CR \leq 0.1 $}
+	\State{\Return {$[a_{ij}]_{i,j=1}^{n}$}}
+\Else
+	\For{$ 3 \leq k \leq n $}
+		\State{$([a_{ij}]_{i,j=1}^{k}, CR) \gets forceConsistency([a_{ij}]_{i,j=1}^{k})$}
+		\If{$CR \leq 0.1$}
+			\State{\textbf{break for}}
+		\EndIf
+	\EndFor
+\EndIf
+\State{\Return {$([a_{ij}]_{i,j=1}^{n}, CR)$}}
+
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{function $forceConsistency([a_{ij}]_{i,j=1}^{k})$}\label{alg:CA}
+\begin{algorithmic}
+\Require $[a_{ij}]_{i,j=1}^{n} \quad | \quad consistencyRate([a_{ij}]_{i,j=1}^{n-1}) \leq 0.1 $
+\Ensure $consistencyRate([a_{ij}]_{i,j=1}^{n}) \leq 0.1$
+\State{$CR \gets consistencyRate([a_{ij}]_{i,j=1}^{n})$}
+\For{$j \leq n-2$}
+	\For{$j+1 \leq k \leq n-1 $}
+			\State{$g \gets 0$}
+			\State{$s \gets 0$}
+		\If{$a_{nj} > a_{nk} \textrm{ and } a_{jk} \leq 1 $}
+			\State{$g \gets j$}
+			\State{$s \gets k$}
+		\ElsIf{$a_{nj} < a_{nk} \textrm{ and } a_{jk} \geq 1 $}
+			\State{$g \gets k$}
+			\State{$s \gets j$}
+		\EndIf
+		\If{$g \neq 0$}
+			\State{$([a_{ij}]_{i,j=1}^{n} , CR) \gets reduce([a_{ij}]_{i,j=1}^{n}, g, s)$}
+			\If{$CR \geq 0.1$}
+				\State{$([a_{ij}]_{i,j=1}^{n} , CR) \gets encrease([a_{ij}]_{i,j=1}^{n}, g, s)$}
+			\EndIf
+		\EndIf
+		\If{$CR \leq 0.1$}
+			\State{\textbf{break for}}
+		\EndIf
+	\EndFor
+	\If{$CR \leq 0.1$}
+		\State{\textbf{break for}}
+	\EndIf
+\EndFor
+\State{\Return {$([a_{ij}]_{i,j=1}^{n}, CR)$}}
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{function $reduce([a_{ij}]_{i,j=1}^{n}, g, s)$}\label{alg:CA}
+\begin{algorithmic}
+\Require $g,s < n; [a_{ij}]_{i,j=1}^{n}$
+\While{$a_{ng} > a_{ns}$}
+	\State{$a_{ng} \gets a_{ng}^{--}$}
+	\State{$a_{gn} \gets a_{gn}^{++}$}
+	\State{$aux_{CR} = consistencyRate([a_{ij}]_{i,j=1}^{n})$}
+	\If{$aux_{CR} < CR$}
+		\State{$CR = aux_{CR}$}
+		\If{$CR \leq 0.1$}
+			\State{\textbf{break}}
+		\EndIf
+	\Else
+		\State{$a_{ng} \gets a_{ng}^{++}$}
+		\State{$a_{gn} \gets a_{gn}^{--}$}
+		\State{\textbf{break}}
+	\EndIf
+\EndWhile
+\State{\Return {$([a_{ij}]_{i,j=1}^{n}, CR)$}}
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{function $encrease([a_{ij}]_{i,j=1}^{n}, g, s)$}\label{alg:CA}
+\begin{algorithmic}
+\Require $g,s < n; [a_{ij}]_{i,j=1}^{n}$
+\While{$a_{ng} > a_{ns}$}
+	\State{$a_{ns} \gets a_{ns}^{++}$}
+	\State{$a_{sn} \gets a_{sn}^{--}$}
+	\State{$aux_{CR} = consistencyRate([a_{ij}]_{i,j=1}^{n})$}
+	\If{$aux_{CR} < CR$}
+		\State{$CR = aux_{CR}$}
+		\If{$CR \leq 0.1$}
+			\State{\textbf{break}}
+		\EndIf
+	\Else
+		\State{$a_{ns} \gets a_{ns}^{--}$}
+		\State{$a_{sn} \gets a_{sn}^{++}$}
+		\State{\textbf{break}}
+	\EndIf
+\EndWhile
+\State{\Return {$([b_{ij}]_{i,j=1}^{n}, CR)$}}
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{function $a_{ij}^{++}$}\label{alg:CA}
+\begin{algorithmic}
+\Require $a_{ij} \quad | \quad a_{ij} \in \{1/9, 1/7, 1/5, 1/3, 1, 3, 5, 7, 9\}$
+	\If{$a_{ij} \geq 1 \textrm{ and } a_{ij} \neq 9 $}
+		\State {$a_{ij} \gets a_{ij} + 2$}
+	\ElsIf{$a_{ij} < 1$}
+		\State {$a_{ij} \gets 1/(1/a_{ij} - 2)$}
+	\EndIf
+\State{\Return {$a_{ij}$}}
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{function $a_{ij}^{--}$}\label{alg:CA}
+\begin{algorithmic}
+\Require $a_{ij} \quad | \quad a_{ij} \in \{1/9, 1/7, 1/5, 1/3, 1, 3, 5, 7, 9\}$
+	\If{$a_{ij} \geq 3  $}
+		\State {$a_{ij} \gets b_{ij} - 2$}
+	\ElsIf{$a_{ij} \leq 1 \textrm{ and } a_{ij} \neq 1/9$}
+		\State {$a_{ij} \gets 1/(1/a_{ij} + 2)$}
+	\EndIf
+\State{\Return {$a_{ij}$}}
+\end{algorithmic}
+\end{algorithm}
+
+\subsection{Iterative algorithm}
+
+\begin{algorithm}
+\caption{function iterativelyForcingConsistency()}\label{alg:CA}
+\begin{algorithmic}
+\Require $\textrm{M}[a_{ij}]_{i,j=1}^{n}$
+\Ensure $consistencyRate([b_{ij}]_{i,j=1}^{n}) \leq 0.1$
+
+\State{\Return {$\textrm{M}[b_{ij}]_{i,j=1}^{n}$}}
+\end{algorithmic}
+\end{algorithm}
 

### 2023-11-06 manuscript/FCPCOM/manuscript.tex
updating files and cleaning

@@
 
-\title{Analytic Hierarchy Process: how to force consistency of pairwise comparisons matrix}
+\title{ABC multi-criteria classification with analytical hierarchy process: how to force consistency of pairwise comparisons matrix}
 
@@
 \begin{abstract} 
-Saaty's Analytic Hierarchy Process is an important method for assigning weight to multiple criteria.
-Despite this method represents an important inovation, its logic is not complicated at all.
-First a pairwise comparisons matrix is generated for the multiple criteria, and the normalized eigenvector of this matrix is used as the weight of criteria.
-But, since pairwise matrixes are usually generated manually and based only on some employee knowhow, there is a huge complexity on generating a consistent pairwise matrix.
+Multicriteria classification is usualy very important to the decision-making in manufacturing management process.
+For such classification, the attribution of weights to the criteria strongly influences the coherence of the results found.
+Saaty's Analytic Hierarchy Process (AHP) is an important method for assigning weights to multiple criteria.
+AHP's logic is not complicated at all but, since matrices of pairwise comparisons of criteria  are usually generated manually and based only on some employee know-how, there is a huge complexity on generating a consistent pairwise matrix.
 Especially when many criteria are used.
-This paper presents two algorithms that can be used to adjust inconsistent matrices, forcing such matrices to have a better consistency rate.
-The first method is a constructive method that uses the data inserted in the matrix to build a new improved one.
-The second method iteratively identifies inconsistencies, making minor changes in order to improve the matrix consistency rate.
+This paper presents a constructive algorithm that can be used to adjust inconsistent matrices, forcing such matrices to have a better consistency rate.
+We tested this algorithm by applying the AHP method, for ABC multicriteria classification, to companies in two sectors.
+As a result we observed that the algorithm can adjust the pairwise matrices in just a few seconds, avoiding the manual work that would be done in weeks, therefore showing that it is an important resource for applying the AHP method.
 \end{abstract}
@@
 \begin{keyword}
-multi-product batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep LINGO
+multi-product batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep COPSolver \sep LINGO
 \end{keyword}

### 2023-11-06 manuscript/MBPTMP/title_page.tex
updating files and cleaning

--- 2023-10-19 manuscript/MBPTMP/manuscript.tex
@@
            country={Brazil}}
-
-\begin{abstract} 
-Among the most complex multi-product batch problems are the multi-product p-batch scheduling (MPPBS) problems, where jobs must be scheduled on parallel batch processing machines.
-When applying some local search heuristics to solve a MPPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products.
-In this paper we name this problem multi-product p-batch processing time maximization (MPBPTM) problem.
-Once a MPBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPPBS problems.
-In addition, for some industries, efficiently solving a MPBPTM problem can have a significant impact on storage costs and customer satisfaction.
-In this paper we presente a mathematical model and an exact method with polynomial time complexity for the MPBPTM problem.
-We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method.
-We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small and very large.
-As result, we find that the exact method can obtain optimal solutions in a very short time (just few seconds), even when solving very large instances.
-\end{abstract}
 %%Graphical abstract
@@
 %%Research highlights
-\begin{highlights}
-\item taxonomy and notation for the multi-product batch problems;
-\item multi-product p-batch processing time maximization (MPBPTM) problem definition;
-\item linear integer programming model for the MPBPTM problem;
-\item exact optimization method for solving the MPBPTM problem.
-\end{highlights}
-
-\begin{keyword}
-multi-product batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep LINGO
-\end{keyword}
 \end{frontmatter}
-
-%% \linenumbers
-
-%% main text
-\section{Introduction}
-\label{sec:intro}
-
-The term multi-product batch production is usually applied to designate an intermittent production system in which batches of different products and sizes are processed one at a time, sharing the same production facilities.
-A multi-product batch plant basically consists of one or more production units, grouped into one or more stages, and possibly, intermediate storage locations.
-At each stage some distinct operations are performed and the batches are processed sequentially over the stages (serial batching).
-As stated by \cite{PetkovMaranas1998} the batch plant can operate under a single-product campaign (SPC) production mode, where all the batches of a given product are manufactured before production of the next product begins, or under mixed-product campaign (MPC) production modes where more batches are produced per unit time at the expense of increased changeover times and cleanup costs.
-Also the plant layout can take on different formats, such as: single unit, where all operations needed to process the batches are performed by a single processor; serial flowshop plant, in which all products follow the same linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{ShiEtAll2017}; and convergent and/or divergent networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
-
-The scientific literature address many different problems related to such industrial enviroment, including the design, planning, sizing, scheduling and balancing problems.
-The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
-The configuration of the plant basically consists of defining the number of stages, the number of units and their capacity per stage, and the capacity for intermediate storages, as well as the best factory layout.
-The multi-product batch planning problem is basically determining the quantities to be produced, the number of batches and their sizes, the needs of materials and the total sales during each time period \citep{FumeroEtAl2016}.
-
-Since a single batch is processed at a time, it is necessary that the batches are dimensioned in such a way that the quantity produced of each product is sufficient to meet the demand during the period in which other batches are being processed \citep{Eilon1985}.
-This problem is named multi-product batch sizing.
-\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production, and \cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product serial batching sizing problem in a divergent networked plant of a steel industry (Fig.
-\ref{fig:networkdPlantSteelIndustry}).
-
-\begin{figure}[h]
-\label{fig:networkdPlantSteelIndustry}
-\begin{center}
-\begin{tikzpicture}[font=\sffamily,every label/.append style={font=\small\sffamily,align=center}]
-
-\node[cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP00){};
-\node[rectangle, draw, right=0.5cm of WIP00, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit00){};
-\node[draw,dashed,rounded corners,fit=(WIP00) (unit00),inner sep=25pt,label={above:{stage (0,0)}}](stage00){};
-
-\node[above right=2cm and 4cm of WIP00, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP11){};
-\node[rectangle, draw, right=0.5cm of WIP11, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit11){};
-\node[draw,dashed,rounded corners,fit=(WIP11) (unit11),inner sep=25pt,label={above:{stage (1,1)}}](stage11){};
-
-\draw[-latex] (stage00.east) -- (stage11.west);
-
-\node[right=2.5cm of stage00, minimum width=1cm, minimum height=1.4cm](WIP1){.....};
-
-\node[right=0.3cm of WIP1, minimum width=1cm, minimum height=1.4cm](WIP1a){};
-
-\draw[-latex] (stage00.east) -- (WIP1.west);
-
-\node[below right=2cm and 4cm of WIP00, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIPp1){};
-\node[rectangle, draw, right=0.5cm of WIPp1, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unitp1){};
-\node[draw,dashed,rounded corners,fit=(WIPp1) (unitp1),inner sep=25pt,label={above:{stage (p,1)}}](stagep1){};
-
-\draw[-latex] (stage00.east) -- (stagep1.west);
-
-\node[right=4cm of WIP11, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP1m){};
-\node[rectangle, draw, right=0.5cm of WIP1m, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit1m){};
-\node[draw,dashed,rounded corners,fit=(WIP1m) (unit1m),inner sep=25pt,label={above:{stage (1,m$_1$)}}](stage1m){};
-
-\draw[-latex] (stage11.east) -- (stage1m.west);
-
-\node[right=4cm of WIPp1, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIPpm){};
-\node[rectangle, draw, right=0.5cm of WIPpm, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unitpm){};
-\node[draw,dashed,rounded corners,fit=(WIPpm) (unitpm),inner sep=25pt,label={above:{stage (p,m$_p$)}}](stagepm){};
-
-\draw[-latex] (stagep1.east) -- (stagepm.west);
-
-\node[right=3.5cm of WIP1, minimum width=1cm, minimum height=1.4cm](WIPm){.....};
-
-\node[left=0.5cm of WIPm, minimum width=1cm, minimum height=1.4cm](WIPma){};
-
-\draw[-latex] (WIP1a.east) -- (WIPma.west);
-
-\end{tikzpicture}
-\end{center}
-\caption{Multi-product serial batching divergent networked plant of a steel industry. Source: adapted from \cite{LiuEtAl2020} * stage $(i, j)$ means stage $j$ of production line $i$.}
-\end{figure}
-
-In multi-product batch scheduling (MPBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the batches based on the known demand.
-Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
-Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each batch, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
-Also, some cientific works consider MPBS problems within different layouts as well as dinamic and multiperiod scenarios.
-In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
-Many cientifc works propose mixed-integer linear programming (MILP) formulations to solve MPBS problems.
-As example, we can mention the work of \cite{MendezEtAll2000} that presents a MILP continuous-time model and a two-step systematic methodology for a single stage multi-product batch scheduling problem with different due-dates.
-Later, \cite{MendezCerda2003} also proposed another MILP formulation for reactive scheduling.
-As observerd by \cite{HeHui2008}, with the problem size increasing, the computational effort of MILP increases greatly so it is very difﬁcult for MILP to obtain acceptable solutions to large-size problems within reasonable time.
-Citing some works that use other approaches, \cite {KimEtAl1996} propose a Gantt chart mapping method and a modified genetic algorithm for solving a networked flowshop multi-product batch scheduling problem as well as a rule-based reactive rescheduling scheme for dinamicaly overcoming in-process deviation from the initial optimized schedule and \cite{HeHui2008} present a rule-based genetic algorithm for the scheduling of single stage multi-product batch plants with parallel units.
-
-It is importante to note that some production units are capable of processing multiple jobs at the same time.
-In such a case batches of different products and sizes can be grouped and processed by these units as a single batch.
-It is therefore necessary to determine the set of "batches" that each new grouped batch will contain.
-The multi-product balancing problem consists of determining these groupings, seeking to minimize the overall makespan.
-\cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.
-\cite{FowlerMonch2022} present a taxonomy and an extensive literature review for the p-batch problems.
-According to the authors, a p-batch problem can be classified as compatible setting - where there is no restriction on which jobs can be used to form a batch - and incompatible family case - where only jobs belonging to the same family can be used to form a batch.
-Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product p-batch problem involving identical parallel units, capacity constraints, and incompatible families with different job sizes.
-
-In a real production environment, some of these problems arise in a connected way, so many cientific works adress mixed multi-product batch problems.
-As example, \cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.
-Also, de work of \cite{MendezEtAll2000}, previously mentioned, considers planning as an integrated part of solution in real-world multi-product batch plant scheduling and therefore includes the product batching problem in its proposed MILP continuous-time models and two-step systematic methodology.
-
-\subsection{Taxonomy and notation}
-
-In short, based on the bibliographic survey conducted for the preparation of this paper, we identify that the multi-product batch problems can differentiate with the following aspects:
-
-\begin{enumerate}[label=\arabic*)]
-\item \textbf{number of stages ($\sigma$)}: single stage ($SS$) or multistage ($MS$);
-\item \textbf{layout($\lambda$)}: single unit ($SU$), flowshop ($Fl$), parallel ($Pl$), or networked ($Nt$) (convergent ($CNt$) and /or divergent ($DNt$));
-\item \textbf{production mode ($\mu$)}: single-product campaing ($SPC$), mixed-product campaign ($MPC$), serial batching ($s\textrm{-}batch$) and/or parallel batching ($p\textrm{-}batch$);
-\item \textbf{problem:($\pi$)}  : design ($D$), planning ($P$), sizing ($Sz$), scheduling ($Sc$) and/or balancing ($B$); 
-\item \textbf{time horizon ($\eta$)}: single period ($SP$), multiperiod ($MP$) or cyclic ($Cc$);
-\item \textbf{scenario ($\gamma$)}: static ($St$) or dynamic ($Dn$);
-\item \textbf{input ($\iota$)}: deterministic ($Dt$) and/or stochastic ($St$);
-\item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), and processing time ($PT$);
-\item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$).
-\end{enumerate}
-
-So, to describe a speciﬁc multi-product batch problem, we propose the notation $\sigma|\lambda|\mu|\pi|\eta|\gamma|\iota|\delta|\rho$.
-Some of the multi-product batch problems and solution approaches discussed in the references cited in this paper are summarized in Tab.
-\ref{tab:review}.
-
-\begin{table}[h!]
-\begin{center}
-\begin{small}
-\begin{tabular}[c]{l l l}
-reference & problem & contributions  \\
-\cline {1-3} \\
-\cite{Eilon1985} & $SS|SU|s\textrm{-}batch|Sc|SP$ &  analysis of the effect\\
-& $St|Dt|SC, HC|-$  & of splitting batches \\
-\cline {1-3} \\
-Ravemark and & $MS|Pl|SPC|D|Cc|$ & convex MILP model \\
-Rippin (1998) & $St|Dt|C|WIP$ & solved with DICOPT++ \\
-\cline {1-3} \\
-Petkov and & $MS|Pl|SPC|D|Cc|$ & exact method\\
-Maranas (1998)  & $St|St|NP|-$ & \\
-\cline {1-3} \\
-\cite{MendezEtAll2000} & $SS|Pl|MPC|P,Sc|SP|St|$ & MILP continuous-time  \\
-& $Dt|WIPC|RT, DD$ & model and a two-step  \\
-& & systematic methodology \\
-\cline {1-3} \\
-Méndez and & $SS|Pl|MPC|Sc|SP|Dn|Dt|$ & MIPL model and \\
-Cerdá (2003) &$wE/T|RT, DD, SDST$ & a rescheduling algorithm\\
-\cline {1-3} \\
-\cite{HeHui2008} & $SS|Pl|MPC|Sc|SP|$ & rule-based genetic \\
-& $St|Dt|C_{max}, TT|LCU, DD$ & algorithm \\
-\cline {1-3} \\
-\cite{FumeroEtAl2016} & $MS|Pl|MPC|D,P,Sc|Cc|$ & MILP model \\
-& $St|Dt|NP|LCU,USC$ & solved with CPLEX \\
-\cline {1-3} \\
-\cite{LiuEtAl2020} & $MS|DNt|s\textrm{-}batch|Sz|MP|St|$ & mixed-integer quadratic \\
-& $Dt|SC,WIPC|LCU,WIP$ & programming model  \\
-& & and exact algorithm \\
-\cline {1-3} \\
-\cite{LiEtAl2022} & $SS|Pl|p\textrm{-}batch|Sc,B|SP|$ & MILP model \\
-& $St|Dt|C_{max}|LCU, RT, IF$ & and a constraint-guided \\
- & & artificial immune \\
- & & system based algorithm \\ 
-\cline {1-3} \\
-\end{tabular}
-\caption{Some contributions on the multi-product batch problems}
-\label{tab:review}
-\end{small}
-\end{center}
-\end{table}
-
-\subsection{Contributions of this paper}
-
-In this work we are interested in the multiperiod multi-product batch scheduling problem that arises in a networked plant of a plastic bag industry.
-The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020} (Fig.
-\ref{fig:networkdPlantSteelIndustry}), however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
-Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}.
-Thus, part of the problem solving process consists of solving a multi-product p-batch scheduling problem into extruders.
-Also, in the problem we study, in addition to demand, we must consider the factory and outlets' storage capacity, which is individually defined for products, but also for the set of products.
-
-When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product \emph{p-batches}, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
-Using the notation presented before, this problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ problem.
-For simplification purposes, we named this problem multi-product p-batch processing time maximization (MPBPTM) problem.
-
-It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product \emph{p-batch} \emph{s-batch} problem in the plastic bag networked plant of the industry studied.
-In a future work, we intend to present the mathematical model and a Particle Collison based solution algorithm we are developing for this last problem.
-As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPBPTM problem.
-
-The rest of the paper is organized as follows.
-In the next sections, the MPBPTM problem is presented.
-Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution.
-Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
-In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions to this work are informed and acknowledgments are given, respectively.
-Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.
-
-\section{Multi-product p-batch processing time maximization problem}
-\label{sec:MBPTMP}
-
-The multi-product p-batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
-In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product.
-In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set.
-The production quantity of each product is mainly defined according to the demand for the product.
-However, it is still possible to stock the products and/or send them to the outlets.
-In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch.
-Also, there is a time limit available for processing the batch.
-About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.
-
-\section{Mathematical model}
-\label{sec:mathModel}
-
-Given that:
-
-$\textrm{UD}_i$ is the demand for the product $i$;
-
-$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch;
-
-$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory;
-
-$\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets;
-
-$\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets;
-
-$\textrm{p}_i$ is the production rate of product $i$;
-
-$\textrm{Z}$ is the timeout for batch processing;
-
-$P_i$ is the amount of product $i$ produced;
-
-$D_i$ is the amount of product $i$ delivered for the demand;
-
-$O_i$ amount of product $i$ shipped to factory outlets;
-
-$I_i$ is the amount of product $i$ that will be stored at the factory;
-
-$T$ is the batch processing time;
-
-We have the problem:
-
-\begin{equation}
-\label{MBPTMP01}
-max \quad T
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-P_i - \textrm{p}_i * T  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-P_i - D_i - O_i - I_i = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-\label{MBPTMP04}
-D_i \leq \textrm{UD}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-O_i \leq \textrm{UO}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i{O_i} \leq \textrm{O}
-\end{equation}
-
-\begin{equation}
-I_i \leq \textrm{UI}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i{I_i} \leq \textrm{I}
-\end{equation}
-
-\begin{equation}
-T \leq \textrm{Z}
-\end{equation}
-
-\begin{equation}
-\min \{\textrm{UD}_i - D_i, O_i + I_i\} = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-\min\{\textrm{O} - \sum_i\{ O_i\}, \textrm{UO}_i - O_i, I_i\} = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-\label{MBPTMP10}
-T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-where:
-
-Constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$.
-Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$.
-Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the autlets, and the factory-stocked quantity of each product must be less than their respective known limits.
-Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values.
-The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
-Equations in (10) and (11) define the production distribution priority.
-And finally, the constraints in (12) inform the nature of the decision variables.
-
-\section{Analytical solution}
-\label{sec:analyticalSol}
-
-The method proposed in this paper for solution of the MBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the production to meet demand, the production sent to outlets and the production stocked in factory.
-Next, we explain each of these parts in detail.
-\\
-
-\noindent \emph{Calculation of maximum p-batch processing time:} \\
-
-It is possible to split the batch processing time into two time slots:
-
-\begin{equation}
-T = T' + T''
-\end{equation}
-
-\noindent where $T'$ is the maximum processing time whose production will be used exclusively to meet the demand.
-
-Then, being $D_{i}^{'}$ the quantity produced of the product $i$ after $T'$ units of processing time, we have:
-
-\begin{equation}
-\label{eq:s02}
-D_{i}^{'} - \textrm{p}_i * T'  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-\label{eq:s03}
-D_{i}^{'} \in Z \quad \forall i
-\end{equation}
-
-\noindent and, as $D_{i}^{'} \leq D_i$, $\forall i$, we have:
-
-\begin{equation}
-\label{eq:s04}
-D_{i}^{'} \leq \textrm{UD}_i\quad \forall i
-\end{equation}
-
-From the equations in (\ref{eq:s02}) and the restrictions in (\ref{eq:s03}) and (\ref{eq:s04}), we have:
-
-\begin{equation}
-\label{eq:s05}
-T' \leq \lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor \quad \forall i
-\end{equation}
-
-And, as we wish maximum value to $T'$, from (\ref{eq:s05}) we have:
-
-\begin{equation}
-\label{eq:s06}
-T' = \min_i\{\lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor\}
-\end{equation}
-
-Observe that there may be a leftover corresponding to the demand not met by the production in the first part of the processing time, $T'$.
-This leftover, $S_i$, will be defined according to the equations in (\ref{eq:s07}):
-
-\begin{equation}
-\label{eq:s07}
-S_i = \textrm{UD}_i - D_{i}^{'} \quad \forall i
-\end{equation}
-
-It is also possible to consider that outlets are extensions of the factory stock.
-Therefore, it is possible to consider the factory stock of product $i$ and the outlets stock $i$ as single stock for the product $i$, $E_i$, so that:
-
-\begin{equation}
-\label{eq:s08}
-E_i = O_i + I_i
-\end{equation}
-
-\begin{equation}
-\label{eq:s09}
-E_i \leq \textrm{UO}_i + \textrm{UI}_i
-\end{equation}
-
-\begin{equation}
-\label{eq:s10}
-\sum_i {E_i} \leq \textrm{O} + \textrm{I}
-\end{equation}
-
-\begin{equation}
-\label{eq:s11}
-E_i \in Z \quad \forall i
-\end{equation}
-
-As the time $T'$ was used only for production that will meet the demand, $T''$  will be the remaining processing time, \emph{i.e.} the maximum processing time used for production that will meet the leftover of demand, sent to the outlets and stored in factory.
-So we have:
-
-\begin{equation}
-\label{eq:s12}
-E_i + S_i - \textrm{p}_i * T''  = 0 \quad \forall i
-\end{equation}
-
-\noindent Thus, after replacing (\ref{eq:s12}) in (\ref{eq:s09}) and applying some algebra, we have:
-
-\begin{equation}
-\label{eq:s13}
-T''  \leq (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i \quad \forall i
-\end{equation}
-
-\noindent And, after replacing (\ref{eq:s12}) in (\ref{eq:s10}) and applying some algebra, we have:
-
-\begin{equation}
-\label{eq:s14}
- T'' \leq (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i
-\end{equation}
-
-Finally, as $T$  is an integer value and we want to maximize this value, then:
-
-\begin{equation}
-\label{eq:s15}
- T'' = \lfloor\min\{\min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor
-\end{equation}
-
-So, the analytical method for finding maximum $T$ can be decomposed into 4 steps:
-
-step 1: find $T'$, where:
-\begin{equation}
-T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
-\end{equation}
-
-step 2: calculate $S_i$ for all products.
-\begin{equation}
-\label{eq:unmet}
-S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
-\end{equation}
-
-step 3: find $T''$, where:
-\begin{equation}
-T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
-\end{equation}
-
-step 4: calculate $T$, where: 
-\begin{equation}
-T^* = T' + T''
-\end{equation}
-\begin{equation}
-T = \min \{T^* , \textrm{Z}\}
-\end{equation}
-
-Note that, as we reduce the value of $T'$, the consequent reduction of $D_{i}^{'}$ will be directly attributed to the leftover of demand $S_i$ and, therefore, there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1.
-Thus it is possible to use a simplification of the method presented, making $T' = 0$.
-In this case $S_i = \textrm{UD}_i, \forall i$.
-The simplified version of the method is presented below:
-
-step 1: find $T^*$, where:
-\begin{equation}
-T^* = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
-\end{equation}
-
-step 2: calculate $T$, where:
-
-\begin{equation}
-T = \min \{T^* , \textrm{Z}\}
-\end{equation}
-
-This simplification of the method demonstrates that the value calculated to $T$ does not depend on the way the production of the product $i$, $P_i$, is distributed between service to demand, $D_i$, outlets, $O_i$, and  factory's stock $I_i$.
-
-\noindent \emph{Full solution:}
-
-We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply attending the priorities for distribution. The following three algorithms can be used to find a complete solution.
-
-The Algorithm (\ref{alg:part01}) is used for finding an optimimal value for $T$.
-
-\begin{algorithm}
-\caption{Solving MBPTM problem | Part 01 - find an optimal $T$ to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}).}\label{alg:part01}
-\begin{algorithmic}
-	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}$
-	\State $T^* \gets \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor$
-	\State $T \gets \min \{T^* , \textrm{Z}\}$
-\State \textbf{Return:} $T$.
-\end{algorithmic}
-\end{algorithm}
-
-Then an initial production distribution can be done by the Algorithm (\ref{alg:part02}).
-This distribution is made without considering the restrictions defined for the set of products.
-$SO$ and $SI$ represent, respectively, the total amount available to be sent to the outlets and the total amount available for factory inventory after the initial distribution.
-If this values are negative, this indicates that the proposed initial distribution is not a feasible distribution.
-
-\begin{algorithm}
-\caption{Solving MBPTM problem | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions for the set of products of the batch.}\label{alg:part02}
-\begin{algorithmic}
-	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}, T$.
-	\For{all i}
-		\State $E_i \gets T * \textrm{p}_i$
-		\State $D_i \gets \min \{\textrm{UD}_i, E_i\}$
-		\State $E_i \gets E_i - D_i$
-		\State $O_i \gets \min \{\textrm{UO}_i, E_i\}$
-		\State $E_i = E_i - O_i$
-		\State $\textrm{UO}_i = \textrm{UO}_i - O_i$
-		\State $I_i = E_i$
-		\State $\textrm{UI}_i = \textrm{UI}_i - I_i$
-	\EndFor
-	\State $SO = \textrm{O} - \sum_i{O_i}$
-	\State $SI = \textrm{I} - \sum_i{I_i}$
-	\State \textbf{Return:} $D_i, O_i, I_i, E_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
-\end{algorithmic}
-\end{algorithm}
-
-So, after applying Algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
-However, if $SO < 0$ or $SI <0$, solution is not yet feasible.
-But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements:
-
-$if \quad SO < 0 \quad then \quad SI > 0 \quad and  \quad |SO| < SI$
-
-$if \quad SI < 0 \quad then \quad SO > 0 \quad and  \quad |SI| < SO$
-
-Therefore it is possible to meet the restrictions by applying the Agorithm (\ref{alg:part03}).
-In this algorithm we redistributed the production of factory's stock to the outlets or vice versa, respectively, due to having a $SI$ or $SO$ negative.
-
-\begin{algorithm}
-\caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch set.}\label{alg:part03}
-\begin{algorithmic}
-\Require $O_i, I_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
-\If{$SO < 0$}
-\For{all $i$}
-	\State $O_i \gets O_i - \min\{ O_i, UI_i, |SO|\}$
-	\State $I_i \gets I_i + \min\{ O_i, UI_i, |SO|\}$
-	\State $SO \gets SO + \min\{ O_i, UI_i, |SO|\}$
-	\If{$SO = 0$}
-		break looping for;
-	\EndIf
-\EndFor
-\EndIf
-
-\If{$SI < 0$}
-\For{all $i$}
-	\State $I_i \gets I_i - \min\{ I_i, UO_i, |SI|\}$
-	\State $O_i \gets O_i + \min\{ I_i, UO_i, |SI|\}$
-	\State $SI \gets SI + \min\{ I_i, UO_i, |SI|\}$
-	\If{$SI = 0$}
-		break looping for;
-	\EndIf
-\EndFor
-\EndIf
-\State \textbf{Return:} $O_i, I_i, \forall i$.
-\end{algorithmic}
-\end{algorithm}
-
-\section{Tests and results}
-\label{sec:results}
-
-To test the developed model and analytical solution method, we created a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem and also a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver \citep{Fraga2023}.
-The tests were performed on a notebook with an Intel i7 processor.
-We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\
-
-\begin{equation}
-\textrm{p}_i = \textrm{rand}()\%30 + 10
-\end{equation}
-
-\begin{equation}
-\textrm{UD}_i = \textrm{rand}()\%3000 + 800;
-\end{equation}
-
-\begin{equation}
- \textrm{seed1} = \textrm{rand}()\%3000 + 500;
-\end{equation}
-
-\begin{equation}
-\textrm{seed2} = \textrm{rand}()\%5000 + 1000;
-\end{equation}
-
-\begin{equation}
-\textrm{O} = \textrm{N}/2*\textrm{seed1};
-\end{equation}
-
-\begin{equation}
-\textrm{UO}_i = \textrm{rand}()\%(\textrm{seed1}-500) + 500;
-\end{equation}
-
-\begin{equation}
-\textrm{I} = \textrm{N}/2*\textrm{seed2};
-\end{equation}
-
-\begin{equation}
-\textrm{UI}_i = \textrm{rand}()\%(\textrm{seed2}-1000) + 1000;
-\end{equation}
-
-\begin{equation}
-\textrm{Z} = 100;
-\end{equation}
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}[c]{c r r r}
-$i$ & 1 & 2 & total \\
-\cline {1-4} \\
-$\textrm{p}_i$ & 60 & 40 & \\
-$\textrm{UD}_i$ & 1000 & 500 & \\
-$\textrm{UO}_i$ & 600 & 600 & 1000 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 3000 \\
-\cline {1-4} \\
-& & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\caption{Benchmark MBPTM 2}
-\label{tab:MBPTMP001}
-\end{center}
-\end{table}
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}[c]{c r r r r}
-$i$ & 1 & 2 & 3 & total \\
-\cline {1-5} \\
-$\textrm{p}_i$ & 60 & 40 & 50 \\
-$\textrm{UD}_i$ & 1000 & 500 & 800 \\
-$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 3500 \\
-\cline {1-5} \\
-& & & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\caption{Benchmark MBPTM 3}
-\label{tab:MBPTMP002}
-\end{center}
-\end{table}
-
-\begin{table}[h]
-\begin{center}
-\begin{small}
-\begin{tabular}[c]{c r r r r r r r r r r r }
-$i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
-\cline {1-12} \\
-$\textrm{p}_i$ & 60 & 40 & 50 & 40 & 30 & 50 & 60 & 10 & 20 & 40\\
-$\textrm{UD}_i$ & 1000 & 500 & 800 & 500 & 400 & 500 & 2000 & 300 & 500 & 1000 \\
-$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 & 300 & 200 & 500 & 800 & 0 & 200 & 3000 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 800 & 3000 & 1000 & 400 & 300 & 200 & 0 & 5000 \\
-\cline {1-12} \\
-& & & & & & & & & & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\caption{Benchmark MBPTM 10}
-\label{tab:MBPTMP003}
-\end{small}
-\end{center}
-\end{table}
-
-Randomly generated benchmarks were named RMBPTM $\textrm{N}$, being $\textrm{N}$ the number of products.
-Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
-To build the results presented in this work, we used source=0.
-The benchmarks used for the tests performed can be consulted at github.com/tbfraga/COPSolver.
-
-Table \ref{tab:results} presents the results obtained by applying the analytical method (COPSolver) and the LINGO solver for the solution of the previously presented benchmarks.
-
-\begin{table}[h]
-\begin{center}
-\begin{footnotesize}
-\begin{tabular}[c]{l r r r r}
-problem & LINGO solver & time (s) & analytical method & time (s) \\
-\cline {1-5} \\
-MBPTM 2 & 55 & 0.03 & 55 & $<$ 0.01 \\
-MBPTM 3 & 48 & 0.03 & 48 & $<$ 0.01 \\
-MBPTM 10 & 30 & 0.05 & 30 & $<$ 0.01 \\
-RMBPTM 20 & 100 & 0.06 & 100 & $<$ 0.01 \\
-RMBPTM 50 & 98 & 0.08 & 98 & $<$ 0.01 \\
-RMBPTM 100 & 98 & 0.11 & 98 & $<$ 0.01 \\
-RMBPTM 1,000 & 78 & 1.20 & 78 & $<$ 0.01 \\
-RMBPTM 2,000 & 70 & 3.25 & 70 & $<$ 0.01 \\
-RMBPTM 5,000 & 70 & 15.12 & 70 & $<$ 0.02 \\
-RMBPTM 10,000 & 70 & 55.19 & 70 & $<$ 0.04 \\
-\cline {1-5} \\
-\end{tabular}
-\caption{Results obtained with the LINGO solver and the analytical method}
-\label{tab:results}
-\end{footnotesize}
-\end{center}
-\end{table}
-
-Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MBPTM 3 and 10 found by both COPSolver and LINGO solver.
-Files containing all results can be found at github.com/tbfraga/COPSolver.
-
-\begin{table}[h]
-\begin{center}
-\begin{footnotesize}
-\begin{tabular}[c]{l r r r r}
-product & production & delivered (s) & send to outlets & stocked in factory \\
-\cline {1-5} \\
-P1 & 2,880 & 1,000 & 300 & 1,580 \\
-P2 & 1,920 & 500 & 600 & 820 \\
-P3 & 2,400 & 800 & 600 & 1,000 \\
-\cline {1-5} \\
-\end{tabular}
-\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 3}
-\label{tab:compResultsMBPTMP2}
-\end{footnotesize}
-\end{center}
-\end{table}
-
-\begin{table}[h]
-\begin{center}
-\begin{footnotesize}
-\begin{tabular}[c]{l r r r r}
-product & production & delivered (s) & send to outlets & stocked in factory \\
-\cline {1-5} \\
-P1 & 1,800 & 1,000 & 400 & 400 \\
-P2 & 1,200 & 500 & 600 & 100 \\
-P3 & 1,500 & 800 & 600 & 100 \\
-P4 & 1,200 & 500 & 700 & 0 \\
-P5 & 900 & 400 & 300 & 200 \\
-P6 & 1,500 & 500 & 200 & 800 \\
-P7 & 1,800 & 1800 & 0 & 0 \\
-P8 & 300 & 300 & 0 & 0 \\
-P9 & 600 & 500 & 0 & 100 \\
-P10 & 1,200 & 1000 & 200 & 0 \\
-\cline {1-5} \\
-\end{tabular}
-\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 10}
-\label{tab:compResultsMBPTMP3}
-\end{footnotesize}
-\end{center}
-\end{table}
-
-It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
-As the analytical method is a polynomial time complexity method, we did not intend to compare computational costs, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
-
-We have considered here a one-day period problem, so in a future work we will study the complexities of solving a multi-period problem and try to propose new solution methods if needed.
-
-\section{Conclusions and suggestions for future works}
-\label{sec:conclusions}
-
-In this paper we presented the Multi-product Batch Processing Time Maximization problem, as well as a mathematical model and an exact analytical solution method for this problem.
-The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO software, from LINDO Systems, and with a solver developed in C++ language.
-Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large problems, which demonstrates the efficiency of the proposed method.
-As in this paper we considered a planning period of one day, in a future work we will study the complexities that arise when considering the same problem in a multi-period scenario.
-We will also verify if there is the possibility of extending the proposed analytical method to solve a class of linear integer programming problems with similar characteristics to the studied problem.
 
@@
 T.B.
-Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing.
+Fraga: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing – original draft, Writing – review \& editing, Supervision, Project administration.
 Í.R.B.
-Aquino: Data curation.
+Aquino: Investigation.
 R.C.S.
-Menêzes: Data curation.
+Menêzes: Investigation.
 
@@
 %% TeX file.
-
-\begin{thebibliography}{1}
-
-%% \bibitem[Author(year)]{label}
-%% Text of bibliographic item
-
-\bibitem[\protect\citeauthoryear{Eilon}{1985}]{Eilon1985}
-Eilon. (1985). Multi-product batch production on a single machine - A problem revisited. {\it OMEGA Int. J. of Mgmt Sci.}, Vol. 13 (5), pp. 453--468.
-
-\bibitem[\protect\citeauthoryear{Fowler and Mönch}{2022}]{FowlerMonch2022}
-Fowler, J.W. and Mönch, L. (2022). A survey of scheduling with parallel batch (p-batch) processing. {\it European Journal of Operational Research}, Vol. 298, pp. 1--24.
-
-\bibitem[\protect\citeauthoryear{Fraga}{2023}]{Fraga2023}
-Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision prob-
-lems - library for solving the multi-product p-batch processing time maximization problem {\it Software Impacts}, invited paper, in press.
-
-\bibitem[\protect\citeauthoryear{Fumero \emph{et al.}}{2016}]{FumeroEtAl2016}
-Fumero Y., Moreno M.
-S., Corsano, G., Montagna, J.
-M.
-(2016).
-A multiproduct batch plant design model incorporating production planning and scheduling decisions under a multiperiod scenario.
-{\it Applied Mathematical Modelling}, Vol.
-40, pp.
-3498--3515.
-
-\bibitem[\protect\citeauthoryear{He and Hui}{2008}]{HeHui2008}
-He, Y., Hui, C-W.
-(2008).
-A rule-based genetic algorithm for the scheduling of single-stage multi-product batch plants with parallel units.
-{\it  Computers and Chemical Engineering}, Vol.
-32, pp.
-3067--3083.
-
-\bibitem[\protect\citeauthoryear{Kashan and Ozturk}{2022}]{KashanOzturk2022}
-Kashan, A.
-H., and Ozturk, O.
-(2022).
-Improved MILP formulation equipped with valid inequalities for scheduling a batch processing machine with non-identical job sizes.
-{\it  Omega}, Vol.
-112, pp.
-102673.
-
-\bibitem[\protect\citeauthoryear{Kim \emph{et al.}}{1996}]{KimEtAl1996}
-Kim, M., Jung, J. H. and Lee, I. (1996). Intelligent scheduling and monitoring for multi-product networked batch processes. {\it  Computers chem. Engn}, Vol. 20 (Suppl.), pp. 1149--1154.
-
-\bibitem[\protect\citeauthoryear{Li et al.}{2022}]{LiEtAl2022}
-Li, C., Wang, F., Gupta, J.N.D., Chung, T.
-(2022).
-Scheduling identical parallel batch processing machines involving incompatible families with different job sizes and capacity constraints.
-{\it Computers \& Industrial Engineering}, Vol.
-169, pp.
-108115.
-
-\bibitem[\protect\citeauthoryear{Liu \emph{et al.}}{2020}]{LiuEtAl2020}
-Liu, G., Li, F., Yang, X., and Qiu. S. (2020). The multi-stage multi-product batch-sizing problem in the steel industry. {\it  Applied Mathematics and Computation}, Vol. 369, 124830.
-
-\bibitem[\protect\citeauthoryear{Méndez \emph{et al.}}{2000}]{MendezEtAll2000}
-Méndez, C.A., Henning, G.P., Cerdá, J. (2000). Optimal scheduling of batch plants satisfying multiple product
-orders with different due-dates. {\it Computers and Chemical Engineering}, Vol. 24, pp. 2223--2245.
-
-\bibitem[\protect\citeauthoryear{Méndez and Cerdá}{2003}]{MendezCerda2003}
-Méndez, C.A., Cerdá, J. (2003). Dynamic scheduling in multiproduct batch plants. {\it Computers and Chemical Engineering}, Vol. 27, pp. 1247--1259.
-
-\bibitem[\protect\citeauthoryear{Omega Journal}{1993}]{Omega1993}
-OMEGA Journal. (1993). Single Machine Multi-product Batch Scheduling: Testing Several Solution Methods. {\it  OMEGA Int. J. of Mgmt Sci.}, Vol. 21 (6), pp. 709--711.
-
-\bibitem[\protect\citeauthoryear{Petkov and Maranas}{1998}]{PetkovMaranas1998}
-Petkov, S. B., and Maranas, C. D. (1998). Design of Single-Product Campaign Batch Plants under Demand Uncertainty. {\it  AIChE Journal}, Vol. 44 (4), pp. 896--911.
-
-\bibitem[\protect\citeauthoryear{Ravemark and Rippin}{1998}]{RavemarkAndRippin1998}
-Ravemark, D. E., and Rippin, D. W. T. (1998). Optimal design of a multi-product batch plant. {\it Computers chem. Engng}, Vol. 22 (1-2), pp. 177--183.
-
-\bibitem[\protect\citeauthoryear{Shi \emph{et al.}}{2017}]{ShiEtAll2017}
-Shi, B., Qian, X., Sun, S., Yan, L. (2017). Rule-based scheduling of multi-stage multi-product batch plants with parallel units. {\it Chinese Journal of Chemical Engineering}, in press.
-
-\end{thebibliography}
 \end{document}

### 2023-12-13 manuscript/FCPCOM/manuscript.tex
A study on multicriteria ABC classification with analytical hierarchy process

@@
 
-\title{ABC multi-criteria classification with analytical hierarchy process: how to force consistency of pairwise comparisons matrix}
+\title{A study on multicriteria ABC classification with analytical hierarchy process}
 
@@
 This paper presents a constructive algorithm that can be used to adjust inconsistent matrices, forcing such matrices to have a better consistency rate.
-We tested this algorithm by applying the AHP method, for ABC multicriteria classification, to companies in two sectors.
+We tested this algorithm by applying the AHP method, for multicriteria ABC classification, to companies in two sectors.
 As a result we observed that the algorithm can adjust the pairwise matrices in just a few seconds, avoiding the manual work that would be done in weeks, therefore showing that it is an important resource for applying the AHP method.
+We also present in this paper an analysis of the importance of the attribution of the weights to the criteria and show how the multicriteria classification may influence the decision on the choice of the appropriate forecasting method.
 \end{abstract}
@@
 \begin{highlights}
-\item generative method for forcing consistenc ;
-\item multi-product p-batch processing time maximization (MPBPTM) problem definition;
-\item linear integer programming model for the MPBPTM problem;
-\item exact optimization method for solving the MPBPTM problem.
+\item generative method for force consistency of pairwise comparisons matrix;
+\item importance of the correct balance of weights assigned to the criteria;
+\item evidence of the importance of ABC multicriteria clssf for forecasting.
 \end{highlights}
@@
 
-\section{Algorithms for forcing matrix consistency}
+\section{Algorithm for forcing pairwise matrix consistency}
+
+The algorithm is not represented correctly.
+
+Changes will be made during the preparation of the article according to the module of software COPSolver: library for solving classification problems.
+
 \begin{algorithm}
@@
 
-\subsection{Iterative algorithm}
-
-\begin{algorithm}
-\caption{function iterativelyForcingConsistency()}\label{alg:CA}
-\begin{algorithmic}
-\Require $\textrm{M}[a_{ij}]_{i,j=1}^{n}$
-\Ensure $consistencyRate([b_{ij}]_{i,j=1}^{n}) \leq 0.1$
-
-\State{\Return {$\textrm{M}[b_{ij}]_{i,j=1}^{n}$}}
-\end{algorithmic}
-\end{algorithm}
-
 \section{Tests and results}
@@
 
-T.B.
-Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing.
-Í.R.B.
-Aquino: Data curation.
-R.C.S.
-Menêzes: Data curation.
+T.B. Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing.
 
@@
 \label{sec:acknowledgments}
-
-We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects.
-We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process.
-Finally, we would like to thank Pró-reitoria de Extensão e Cultura da UFPE (PROExC) and the Research Director of Propesqi (Pró-reitoria de Pesquisa e Inovação da UFPE) for their support and recognition of our work, and dear Professors Antônio José da Silva Neto and João Flávio Vieira de Vasconcellos from IPRJ/UERJ, who contributed significantly to the formation of essential skills for the development of our projects.
-We also thank my co-worker Marcos Luiz Henrique, for having helped by evaluating the mathematical model and solution method proposed in this paper.
 

### 2023-12-13 manuscript/FCPCOM/manuscript.tex
A study on multicriteria ABC classification with analytical hierarchy process

@@
 
-\author{Ítalo Ruan Barbosa de Aquino\fnref{label1}}
-\ead{italo_ruan_@hotmail.com}
+\author{Beatriz Marinho Cavalcanti\fnref{label1}}
+\ead{<beatriz.marinhocavalcanti@ufpe.br}
 
-\author{Regilda da Costa e Silva Menêzes\fnref{label1}}
-\ead{regilda.smenezes@ufpe.br}
+\author{Alexia Maria Duque Silva\fnref{label1}}
+\ead{alexia.duque@ufpe.br}
+
+\author{Erika Leticia Rodrigues Silva\fnref{label1}}
+\ead{erika.leticias@ufpe.br}
 
@@
 \begin{highlights}
-\item generative method for force consistency of pairwise comparisons matrix;
-\item importance of the correct balance of weights assigned to the criteria;
-\item evidence of the importance of ABC multicriteria clssf for forecasting.
+\item generative method to force consistency of pairwise comparisons matrix;
+\item importance of the correct balance of product criteria weights assigning;
+\item importance of ABC multicriteria classification for forecasting.
 \end{highlights}
@@
 \begin{keyword}
-multi-product batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep COPSolver \sep LINGO
+multicriteria classification \sep ABC classification \sep analytic hierarchy process \sep pairwise matrix consistency \sep COPSolver
 \end{keyword}
@@
 
-\bibitem[\protect\citeauthoryear{Eilon}{1985}]{Eilon1985}
-Eilon. (1985). Multi-product batch production on a single machine - A problem revisited. {\it OMEGA Int. J. of Mgmt Sci.}, Vol. 13 (5), pp. 453--468.
-
-\bibitem[\protect\citeauthoryear{Fowler and Mönch}{2022}]{FowlerMonch2022}
-Fowler, J.W. and Mönch, L. (2022). A survey of scheduling with parallel batch (p-batch) processing. {\it European Journal of Operational Research}, Vol. 298, pp. 1--24.
+\bibitem[\protect\citeauthoryear{Flores and Whybark}{1987}]{FloresWhybark1987}
+Flores, B. E., Whybark, D. C. (1987). Implementing Multiple Criteria ABC Analysis. {\it Journal of Operations Management}, Vol. 7 (1,2), pp. 79--85.
 
 \bibitem[\protect\citeauthoryear{Fraga}{2023}]{Fraga2023}
-Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision prob-
-lems - library for solving the multi-product p-batch processing time maximization problem {\it Software Impacts}, invited paper, in press.
-
-\bibitem[\protect\citeauthoryear{Fumero \emph{et al.}}{2016}]{FumeroEtAl2016}
-Fumero Y., Moreno M.
-S., Corsano, G., Montagna, J.
-M.
-(2016).
-A multiproduct batch plant design model incorporating production planning and scheduling decisions under a multiperiod scenario.
-{\it Applied Mathematical Modelling}, Vol.
-40, pp.
-3498--3515.
-
-\bibitem[\protect\citeauthoryear{He and Hui}{2008}]{HeHui2008}
-He, Y., Hui, C-W.
-(2008).
-A rule-based genetic algorithm for the scheduling of single-stage multi-product batch plants with parallel units.
-{\it  Computers and Chemical Engineering}, Vol.
-32, pp.
-3067--3083.
-
-\bibitem[\protect\citeauthoryear{Kashan and Ozturk}{2022}]{KashanOzturk2022}
-Kashan, A.
-H., and Ozturk, O.
-(2022).
-Improved MILP formulation equipped with valid inequalities for scheduling a batch processing machine with non-identical job sizes.
-{\it  Omega}, Vol.
-112, pp.
-102673.
-
-\bibitem[\protect\citeauthoryear{Kim \emph{et al.}}{1996}]{KimEtAl1996}
-Kim, M., Jung, J. H. and Lee, I. (1996). Intelligent scheduling and monitoring for multi-product networked batch processes. {\it  Computers chem. Engn}, Vol. 20 (Suppl.), pp. 1149--1154.
-
-\bibitem[\protect\citeauthoryear{Li et al.}{2022}]{LiEtAl2022}
-Li, C., Wang, F., Gupta, J.N.D., Chung, T.
-(2022).
-Scheduling identical parallel batch processing machines involving incompatible families with different job sizes and capacity constraints.
-{\it Computers \& Industrial Engineering}, Vol.
-169, pp.
-108115.
-
-\bibitem[\protect\citeauthoryear{Liu \emph{et al.}}{2020}]{LiuEtAl2020}
-Liu, G., Li, F., Yang, X., and Qiu. S. (2020). The multi-stage multi-product batch-sizing problem in the steel industry. {\it  Applied Mathematics and Computation}, Vol. 369, 124830.
-
-\bibitem[\protect\citeauthoryear{Méndez \emph{et al.}}{2000}]{MendezEtAll2000}
-Méndez, C.A., Henning, G.P., Cerdá, J. (2000). Optimal scheduling of batch plants satisfying multiple product
-orders with different due-dates. {\it Computers and Chemical Engineering}, Vol. 24, pp. 2223--2245.
-
-\bibitem[\protect\citeauthoryear{Méndez and Cerdá}{2003}]{MendezCerda2003}
-Méndez, C.A., Cerdá, J. (2003). Dynamic scheduling in multiproduct batch plants. {\it Computers and Chemical Engineering}, Vol. 27, pp. 1247--1259.
-
-\bibitem[\protect\citeauthoryear{Omega Journal}{1993}]{Omega1993}
-OMEGA Journal. (1993). Single Machine Multi-product Batch Scheduling: Testing Several Solution Methods. {\it  OMEGA Int. J. of Mgmt Sci.}, Vol. 21 (6), pp. 709--711.
-
-\bibitem[\protect\citeauthoryear{Petkov and Maranas}{1998}]{PetkovMaranas1998}
-Petkov, S. B., and Maranas, C. D. (1998). Design of Single-Product Campaign Batch Plants under Demand Uncertainty. {\it  AIChE Journal}, Vol. 44 (4), pp. 896--911.
-
-\bibitem[\protect\citeauthoryear{Ravemark and Rippin}{1998}]{RavemarkAndRippin1998}
-Ravemark, D. E., and Rippin, D. W. T. (1998). Optimal design of a multi-product batch plant. {\it Computers chem. Engng}, Vol. 22 (1-2), pp. 177--183.
-
-\bibitem[\protect\citeauthoryear{Shi \emph{et al.}}{2017}]{ShiEtAll2017}
-Shi, B., Qian, X., Sun, S., Yan, L. (2017). Rule-based scheduling of multi-stage multi-product batch plants with parallel units. {\it Chinese Journal of Chemical Engineering}, in press.
+Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multicriteria classification problem, in press.
 

### 2023-12-26 manuscript/FCPCOM/manuscript.tex
A study on multicriteria ABC and demand pattern classifications

@@
 
-\title{A study on multicriteria ABC classification with analytical hierarchy process}
+\title{How demand pattern identification and multicriteria ABC classification can guide management decisions}
 
@@
 As a result we observed that the algorithm can adjust the pairwise matrices in just a few seconds, avoiding the manual work that would be done in weeks, therefore showing that it is an important resource for applying the AHP method.
-We also present in this paper an analysis of the importance of the attribution of the weights to the criteria and show how the multicriteria classification may influence the decision on the choice of the appropriate forecasting method.
+We also present in this paper an analysis of the importance of the attribution of the weights to the criteria and show how the multicriteria and demand pattern classifications may influence the decision on the choice of the appropriate forecasting method.
 \end{abstract}
@@
 \begin{highlights}
+\item literature review about multicriteria classification;
+\item literature review about demand pattern classification;
 \item generative method to force consistency of pairwise comparisons matrix;
 \item importance of the correct balance of product criteria weights assigning;
-\item importance of ABC multicriteria classification for forecasting.
+\item importance of ABC multicriteria and demand pattern classifications for forecasting;
+\item brief description of COPSolver: library for solving the multicriteria classification problem;
+\item brief description of COPSolver: library for solving the demand pattern classification problem.
 \end{highlights}
@@
 \begin{keyword}
-multicriteria classification \sep ABC classification \sep analytic hierarchy process \sep pairwise matrix consistency \sep COPSolver
+demand pattern identitification \sep multicriteria ABC classification \sep analytic hierarchy process \sep pairwise matrix consistency \sep COPSolver
 \end{keyword}
@@
 
-The algorithm is not represented correctly.
-
-Changes will be made during the preparation of the article according to the module of software COPSolver: library for solving classification problems.
-
-\begin{algorithm}
-\caption{function $consistencyRate()$}\label{alg:CA}
-\begin{algorithmic}
-\Require $[a_{ij}]_{i,j=1}^{n}, RI[x]_{x=1}^{10}$
-\State{$\lambda_{max} = mainEigenvalue([a_{ij}]_{i,j=1}^{n})$ \footnote{main eigenvalue can be found using "Eigen/Eigenvalues library.}}
-\State{$CI = (\lambda_{max} - n) / (n-1)$}
-\State{$CR \gets CI/RI[n]$}
-\State{\Return {$CR$}}	
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Constructive algorithm}
-
-\begin{algorithm}
-\caption{function $constructivelyForceConsistency([a_{ij}]_{i,j=1}^{n})$}\label{alg:CA}
-\begin{algorithmic}
-\Require $[a_{ij}]_{i,j=1}^{n}$
-\Ensure $consistencyRate([a_{ij}]_{i,j=1}^{n}) \leq 0.1$
-\State{$CR = consistencyRate([a_{ij}]_{i,j=1}^{n})$}
-\If {$CR \leq 0.1 $}
-	\State{\Return {$[a_{ij}]_{i,j=1}^{n}$}}
-\Else
-	\For{$ 3 \leq k \leq n $}
-		\State{$([a_{ij}]_{i,j=1}^{k}, CR) \gets forceConsistency([a_{ij}]_{i,j=1}^{k})$}
-		\If{$CR \leq 0.1$}
-			\State{\textbf{break for}}
-		\EndIf
-	\EndFor
-\EndIf
-\State{\Return {$([a_{ij}]_{i,j=1}^{n}, CR)$}}
-
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{function $forceConsistency([a_{ij}]_{i,j=1}^{k})$}\label{alg:CA}
-\begin{algorithmic}
-\Require $[a_{ij}]_{i,j=1}^{n} \quad | \quad consistencyRate([a_{ij}]_{i,j=1}^{n-1}) \leq 0.1 $
-\Ensure $consistencyRate([a_{ij}]_{i,j=1}^{n}) \leq 0.1$
-\State{$CR \gets consistencyRate([a_{ij}]_{i,j=1}^{n})$}
-\For{$j \leq n-2$}
-	\For{$j+1 \leq k \leq n-1 $}
-			\State{$g \gets 0$}
-			\State{$s \gets 0$}
-		\If{$a_{nj} > a_{nk} \textrm{ and } a_{jk} \leq 1 $}
-			\State{$g \gets j$}
-			\State{$s \gets k$}
-		\ElsIf{$a_{nj} < a_{nk} \textrm{ and } a_{jk} \geq 1 $}
-			\State{$g \gets k$}
-			\State{$s \gets j$}
-		\EndIf
-		\If{$g \neq 0$}
-			\State{$([a_{ij}]_{i,j=1}^{n} , CR) \gets reduce([a_{ij}]_{i,j=1}^{n}, g, s)$}
-			\If{$CR \geq 0.1$}
-				\State{$([a_{ij}]_{i,j=1}^{n} , CR) \gets encrease([a_{ij}]_{i,j=1}^{n}, g, s)$}
-			\EndIf
-		\EndIf
-		\If{$CR \leq 0.1$}
-			\State{\textbf{break for}}
-		\EndIf
-	\EndFor
-	\If{$CR \leq 0.1$}
-		\State{\textbf{break for}}
-	\EndIf
-\EndFor
-\State{\Return {$([a_{ij}]_{i,j=1}^{n}, CR)$}}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{function $reduce([a_{ij}]_{i,j=1}^{n}, g, s)$}\label{alg:CA}
-\begin{algorithmic}
-\Require $g,s < n; [a_{ij}]_{i,j=1}^{n}$
-\While{$a_{ng} > a_{ns}$}
-	\State{$a_{ng} \gets a_{ng}^{--}$}
-	\State{$a_{gn} \gets a_{gn}^{++}$}
-	\State{$aux_{CR} = consistencyRate([a_{ij}]_{i,j=1}^{n})$}
-	\If{$aux_{CR} < CR$}
-		\State{$CR = aux_{CR}$}
-		\If{$CR \leq 0.1$}
-			\State{\textbf{break}}
-		\EndIf
-	\Else
-		\State{$a_{ng} \gets a_{ng}^{++}$}
-		\State{$a_{gn} \gets a_{gn}^{--}$}
-		\State{\textbf{break}}
-	\EndIf
-\EndWhile
-\State{\Return {$([a_{ij}]_{i,j=1}^{n}, CR)$}}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{function $encrease([a_{ij}]_{i,j=1}^{n}, g, s)$}\label{alg:CA}
-\begin{algorithmic}
-\Require $g,s < n; [a_{ij}]_{i,j=1}^{n}$
-\While{$a_{ng} > a_{ns}$}
-	\State{$a_{ns} \gets a_{ns}^{++}$}
-	\State{$a_{sn} \gets a_{sn}^{--}$}
-	\State{$aux_{CR} = consistencyRate([a_{ij}]_{i,j=1}^{n})$}
-	\If{$aux_{CR} < CR$}
-		\State{$CR = aux_{CR}$}
-		\If{$CR \leq 0.1$}
-			\State{\textbf{break}}
-		\EndIf
-	\Else
-		\State{$a_{ns} \gets a_{ns}^{--}$}
-		\State{$a_{sn} \gets a_{sn}^{++}$}
-		\State{\textbf{break}}
-	\EndIf
-\EndWhile
-\State{\Return {$([b_{ij}]_{i,j=1}^{n}, CR)$}}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{function $a_{ij}^{++}$}\label{alg:CA}
-\begin{algorithmic}
-\Require $a_{ij} \quad | \quad a_{ij} \in \{1/9, 1/7, 1/5, 1/3, 1, 3, 5, 7, 9\}$
-	\If{$a_{ij} \geq 1 \textrm{ and } a_{ij} \neq 9 $}
-		\State {$a_{ij} \gets a_{ij} + 2$}
-	\ElsIf{$a_{ij} < 1$}
-		\State {$a_{ij} \gets 1/(1/a_{ij} - 2)$}
-	\EndIf
-\State{\Return {$a_{ij}$}}
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{function $a_{ij}^{--}$}\label{alg:CA}
-\begin{algorithmic}
-\Require $a_{ij} \quad | \quad a_{ij} \in \{1/9, 1/7, 1/5, 1/3, 1, 3, 5, 7, 9\}$
-	\If{$a_{ij} \geq 3  $}
-		\State {$a_{ij} \gets b_{ij} - 2$}
-	\ElsIf{$a_{ij} \leq 1 \textrm{ and } a_{ij} \neq 1/9$}
-		\State {$a_{ij} \gets 1/(1/a_{ij} + 2)$}
-	\EndIf
-\State{\Return {$a_{ij}$}}
-\end{algorithmic}
-\end{algorithm}
-
 \section{Tests and results}
 \label{sec:results}
+
+To test the two developed COPSolver libraries (COPSolver: library for solving the multi-criteria classification problem and COPSolver: library for solving the demand pattern classification problem), we used data from three companies in three different sectors (plastic packaging manufacturers, furniture retailers and car mechanics).
+In the case of the company in the car mechanics sector, only the data relating to truck repairs was used; in the case of the other two companies, all the data obtained from all the products sold over the last 5 years was used.
+The files containing the formatted data used for all the tests can be found at tbfraga.github.io/COPSolver/benchmarks.
 

### 2023-12-26 manuscript/FCPCOM/manuscript.tex
A study on multicriteria ABC and demand pattern classifications

@@
 
-To test the two developed COPSolver libraries (COPSolver: library for solving the multi-criteria classification problem and COPSolver: library for solving the demand pattern classification problem), we used data from three companies in three different sectors (plastic packaging manufacturers, furniture retailers and car mechanics).
+To test the two developed COPSolver libraries (COPSolver: library for solving the multi-criteria classification problem and COPSolver: library for solving the demand pattern classification problem), we used data from three companies in three different sectors (plastic packaging manufacturers, furniture trades and car mechanics).
 In the case of the company in the car mechanics sector, only the data relating to truck repairs was used; in the case of the other two companies, all the data obtained from all the products sold over the last 5 years was used.
-The files containing the formatted data used for all the tests can be found at tbfraga.github.io/COPSolver/benchmarks.
+The files containing the formatted data used for all the tests and the results can be found at tbfraga.github.io/COPSolver/benchmarks.
+\\
+
+\begin{table}[h!]
+\begin{center}
+\begin{small}
+\begin{tabular}[c]{l r r | l r r r r}
+ \multicolumn{8}{l}{plastic packaging manufacturing company} \\
+\cline {1-8} \\
+\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern}\\
+\multicolumn{3}{l |}{} &\\
+& & & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
+A &  26 & 10.24 \% & smooth & 31.98 \% &  73.08 \% & 30.38 \% & 25.35 \%\\
+B &  80 & 31.50 \% & slow-moving & 18.22 \% & 19.23 \% & 34.18 \% & 9.15 \%\\
+C & 148 & 58.27 \% & sporadic & 49.80 \% & 7.69 \% & 35.44 \% & 65.49 \% \\
+\cline {1-8} \\
+\multicolumn{8}{l}{furniture trades company} \\
+\cline {1-8} \\
+\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern}\\
+\multicolumn{3}{l |}{} &\\
+& & & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
+A &  26 & 10.24 \% & smooth & 31.98 \% &  73.08 \% & 30.38 \% & 25.35 \%\\
+B &  80 & 31.50 \% & slow-moving & 18.22 \% & 19.23 \% & 34.18 \% & 9.15 \%\\
+C & 148 & 58.27 \% & sporadic & 49.80 \% & 7.69 \% & 35.44 \% & 65.49 \% \\
+\cline {1-8} \\
+\multicolumn{8}{l}{car mechanics company} \\
+\cline {1-8} \\
+\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern}\\
+\multicolumn{3}{l |}{} &\\
+& & & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
+A &  26 & 10.24 \% & smooth & 31.98 \% &  73.08 \% & 30.38 \% & 25.35 \%\\
+B &  80 & 31.50 \% & slow-moving & 18.22 \% & 19.23 \% & 34.18 \% & 9.15 \%\\
+C & 148 & 58.27 \% & sporadic & 49.80 \% & 7.69 \% & 35.44 \% & 65.49 \% \\
+\end{tabular}
+\caption{Multicriteria ABC and demand pattern classifications for three companies (results found by COPSolver)}
+\label{tab:results}
+\end{small}
+\end{center}
+\end{table}
 

### 2023-12-26 manuscript/FCPCOM/manuscript.tex
updating paper

@@
 
-To test the two developed COPSolver libraries (COPSolver: library for solving the multi-criteria classification problem and COPSolver: library for solving the demand pattern classification problem), we used data from three companies in three different sectors (plastic packaging manufacturers, furniture trades and car mechanics).
+To test the two developed COPSolver libraries (COPSolver: library for solving the multicriteria classification problem and COPSolver: library for solving the demand pattern classification problem), we used data from three companies in three different sectors (plastic packaging manufacturering, furniture trades and car mechanics).
 In the case of the company in the car mechanics sector, only the data relating to truck repairs was used; in the case of the other two companies, all the data obtained from all the products sold over the last 5 years was used.
+One year's data (last 12 months prior to the data collection date) was used for the ABC multicriteria classification.
 The files containing the formatted data used for all the tests and the results can be found at tbfraga.github.io/COPSolver/benchmarks.
@@
 \cline {1-8} \\
-\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern}\\
+\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
 \multicolumn{3}{l |}{} &\\

### 2024-01-02 manuscript/FCPCOM/manuscript.tex
tests and results - pairwise comparisons matrix and consistency rate

@@
 
-\usepackage{xcolor}
+\usepackage[table]{xcolor}
 \usepackage{tikz}
@@
 
+\section{COPSolver}
+
+\section{Data collected}
+\label{sec:data}
+
+To test the two developed COPSolver libraries (COPSolver: library for solving the multicriteria classification problem and COPSolver: library for solving the demand pattern classification problem), we used data from three companies from three different sectors (plastic packaging manufacturing, furniture trades and car mechanics).
+In the case of the company from the car mechanics sector, only the data relating to truck repairs was used; in the case of the other two companies, all the data obtained from all the products sold over 5 years (last 60 months prior to the data collection date) was used.
+One year's data (last 12 months prior to the data collection date) was used for the ABC multicriteria classification.
+The files containing the formatted data used for all the tests and the results can be found at tbfraga.github.io/COPSolver/benchmarks.
+
 \section{Tests and results}
@@
 
-To test the two developed COPSolver libraries (COPSolver: library for solving the multicriteria classification problem and COPSolver: library for solving the demand pattern classification problem), we used data from three companies in three different sectors (plastic packaging manufacturering, furniture trades and car mechanics).
-In the case of the company in the car mechanics sector, only the data relating to truck repairs was used; in the case of the other two companies, all the data obtained from all the products sold over the last 5 years was used.
-One year's data (last 12 months prior to the data collection date) was used for the ABC multicriteria classification.
-The files containing the formatted data used for all the tests and the results can be found at tbfraga.github.io/COPSolver/benchmarks.
-\\
+\subsection{Pairwise comparisons matrix and consistency rate}
+
+Table \ref{tab:pairwiseMatrix} presents the modifications made by the software 'COPSolver: library for solving the multicriteria classification problem' in the pairwise comparisons matrix and the consequent change in the consistency rate (CR) for the data colected from the three companies selected for this study.
+
+\begin{table}[h!]
+\begin{center}
+\begin{small}
+\begin{tabular}[l]{p{0.4cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
+ \multicolumn{1}{l}{} & \multicolumn{14}{l}{car mechanics company} \\
+\cline {2-15} \\
+ & \multicolumn{7}{c | }{CR = 0.216}  & \multicolumn{7}{c}{CR = 0.085} \\
+   & sb & lt & rp & cr & ob & np & cm & sb & lt & rp & cr & ob & co & cm \\
+sb & 1.00 & 3.00 & 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 7.00 & 9.00 & 9.00 & 1.00 & 3.00 & 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 7.00 & 9.00 & 9.00 \\
+lt & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 7.00 & 9.00 & 9.00 & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 9.00 & 9.00 \\
+rp & 0.33 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 9.00 & \cellcolor[HTML]{ACE600} 9.00 & 9.00 & 0.33 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 9.00 \\
+cr & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 9.00 & 9.00 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 9.00 \\
+ob & 0.14 & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & \cellcolor[HTML]{ACE600} 5.00 & 9.00 & 0.14 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 \\
+np & 0.11 & 0.11 & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & 9.00 & 0.11 & 0.11 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & 9.00 \\
+cm & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 1.00 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 1.00 \\
+\cline {2-15} \\
+ & \multicolumn{14}{l}{furniture trades company} \\
+\cline {2-15} \\
+   & \multicolumn{7}{c | }{CR = 0.151}  & \multicolumn{7}{c}{CR = 0.096} \\
+   & lt & sb & rp & cr & cm & np & ob & lt & sb & rp & cr & cm & np & ob \\
+lt & 1.00 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.20 & 7.00 & \cellcolor[HTML]{ACE600} 0.11 & 5.00 & 1.00 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 7.00 & \cellcolor[HTML]{ACE600} 0.20 & 5.00 \\
+sb & 5.00 & 1.00 & 0.33 & \cellcolor[HTML]{ACE600} 0.33 & 5.00 &\cellcolor[HTML]{ACE600}  0.14 & 7.00 & 5.00 & 1.00 & 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 5.00 & \cellcolor[HTML]{ACE600} 0.33 & 7.00 \\
+rp & 7.00 & 3.00 & 1.00 & \cellcolor[HTML]{ACE600} 0.33 & 5.00 & \cellcolor[HTML]{ACE600} 0.14 & 3.00 & 7.00 & 3.00 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 7.00 & \cellcolor[HTML]{ACE600} 1.00 & 3.00 \\
+cr & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 1.00 & \cellcolor[HTML]{ACE600} 9.00 & \cellcolor[HTML]{ACE600} 0.33 & 9.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 \\
+cm & 0.14 & 0.20 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.11 & 1.00 & 0.11 & 1.00 & 0.14 & 0.20 & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 0.14 & 1.00 & 0.11 & 1.00 \\
+np & \cellcolor[HTML]{ACE600} 9.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 3.00 & 9.00 & 1.00 & 9.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 & 1.00 & 9.00 \\
+ob & 0.20 & 0.14 & 0.33 & 0.11 & 1.00 & 0.11 & 1.00 & 0.20 & 0.14 & 0.33 & 0.11 & 1.00 & 0.11 & 1.00 \\
+\cline {2-15} \\
+ & \multicolumn{14}{l}{plastic packaging manufacturing company} \\
+\cline {2-15} \\
+   & \multicolumn{7}{c | }{CR = 0.625}  & \multicolumn{7}{c}{CR = 0.085} \\
+   & np & cr & lt & ob & sb & rp & & np & cr & lt & ob & sb & rp & \\
+np & 1.00 & 3.00 & 7.00 & \cellcolor[HTML]{ACE600} 7.00 & 5.00 & \cellcolor[HTML]{ACE600} 5.00 & & 1.00 & 3.00 & 7.00 & \cellcolor[HTML]{ACE600} 9.00 & 5.00 & \cellcolor[HTML]{ACE600} 9.00 \\
+cr & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.20 & & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 5.00 \\
+lt & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 7.00 & 7.00 & & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 7.00 \\
+ob & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & \cellcolor[HTML]{ACE600} 0.33 & 3.00 & & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 3.00 \\
+sb & 0.20 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 3.00 & 1.00 & 3.00 & & 0.20 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & 3.00 \\
+rp & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 5.00 & 0.14 & 0.33 & 0.33 & 1.00 & & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.20 & 0.14 & 0.33 & 0.33 & 1.00
+\end{tabular}
+\caption{Pairwise comparisons matrix and consistency rate changes for three companies (results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; np = net-profit; cm = commonality;}
+\label{tab:pairwiseMatrix}
+\end{small}
+\end{center}
+\end{table}
+
+As we can see in this table, the pairwise comparison weights are adjusted primarily according to the  weights assigned to the first three criteria.
+Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria will be preserved.
+The change will be made in the weights of the other criteria in order to force the consistency of the pairwise comparisons matrix.
+Another important point to note in the method is that the algorithm stops when the desired consistency rate is reached.
+So, it is more likely that there will be significant changes in the fourth criterion and the next ones.
+Therefore, it is important that the criteria are ordered in such a way that the three most relevant criteria for the company are among the first.
+Then the next most relevant criteria can be ordered from last to fourth position.
+
+\subsection{Analysis of the ABC multicriterio classification}
+
+\subsection{Analysis of the demand pattern classification}
 
@@
 \begin{tabular}[c]{l r r | l r r r r}
- \multicolumn{8}{l}{plastic packaging manufacturing company} \\
+\multicolumn{8}{l}{car mechanics company} \\
 \cline {1-8} \\
 \multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
-\multicolumn{3}{l |}{} &\\
-& & & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
-A &  26 & 10.24 \% & smooth & 31.98 \% &  73.08 \% & 30.38 \% & 25.35 \%\\
-B &  80 & 31.50 \% & slow-moving & 18.22 \% & 19.23 \% & 34.18 \% & 9.15 \%\\
-C & 148 & 58.27 \% & sporadic & 49.80 \% & 7.69 \% & 35.44 \% & 65.49 \% \\
+\multicolumn{3}{c |}{cutoff}  & \multicolumn{5}{c}{75 sales between October 2020 and July 2023} \\
+\multicolumn{3}{c |}{0.35 \%; 0.70 \%} & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
+A &  10 & 23.81 \% & smooth & 18.75 \% &  20.00 \% & 16.67 \% & 0 \%\\
+B &  15 & 35.71 \% & slow-moving & 6.25 \% & 10.00 \% & 0.00 \% & 0 \%\\
+C &  17 & 40.48 \% & sporadic & 75.00 \% & 70.00 \% & 83.33 \% & 0 \% \\
 \cline {1-8} \\
@@
 \multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
-\multicolumn{3}{l |}{} &\\
-& & & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
-A &  26 & 10.24 \% & smooth & 31.98 \% &  73.08 \% & 30.38 \% & 25.35 \%\\
-B &  80 & 31.50 \% & slow-moving & 18.22 \% & 19.23 \% & 34.18 \% & 9.15 \%\\
-C & 148 & 58.27 \% & sporadic & 49.80 \% & 7.69 \% & 35.44 \% & 65.49 \% \\
+\multicolumn{3}{c |}{cutoff:} &\\
+\multicolumn{3}{c |}{0.35 \%; 0.70 \%}& & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
+A &  26 & 10.24 \% & smooth & 31.58 \% &  73.08 \% & 30.00 \% & 24.82 \%\\
+B &  80 & 31.50 \% & slow-moving & 18.62 \% & 19.23 \% & 33.75 \% & 9.93 \%\\
+C & 148 & 58.27 \% & sporadic & 49.80 \% & 7.69 \% & 36.25 \% & 65.25 \% \\
 \cline {1-8} \\
-\multicolumn{8}{l}{car mechanics company} \\
+ \multicolumn{8}{l}{plastic packaging manufacturing company}\\
 \cline {1-8} \\
 \multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
-\multicolumn{3}{l |}{} &\\
-& & & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
-A &  26 & 10.24 \% & smooth & 31.98 \% &  73.08 \% & 30.38 \% & 25.35 \%\\
-B &  80 & 31.50 \% & slow-moving & 18.22 \% & 19.23 \% & 34.18 \% & 9.15 \%\\
-C & 148 & 58.27 \% & sporadic & 49.80 \% & 7.69 \% & 35.44 \% & 65.49 \% \\
+\multicolumn{3}{c |}{cutoff:} & \multicolumn{5}{c}{5,967 sales between November 2019 and February 2023}\\
+\multicolumn{3}{c |}{0.35 \%; 0.70 \%} & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
+A &   128 &  5.49 \% & smooth & 15.31 \% & 22.66 \% & 23.97 \% & 10.42 \%\\
+B &   726 & 31.12 \% & slow-moving & 5.53 \% & 1.56 \% & 8.68 \% & 4.33 \%\\
+C & 1,479 & 63.39 \% & sporadic & 79.16 \% & 75.78 \% & 67.36 \% & 85.25 \% \\
+\cline {1-8} \\
+
 \end{tabular}

### 2024-01-02 manuscript/FCPCOM/manuscript.tex
small changes

@@
 \begin{small}
-\begin{tabular}[l]{p{0.4cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
- \multicolumn{1}{l}{} & \multicolumn{14}{l}{car mechanics company} \\
-\cline {2-15} \\
+\begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
+\multicolumn{14}{l}{car mechanics company} \\
+\cline {1-15} \\
  & \multicolumn{7}{c | }{CR = 0.216}  & \multicolumn{7}{c}{CR = 0.085} \\
@@
 cm & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 1.00 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 1.00 \\
-\cline {2-15} \\
- & \multicolumn{14}{l}{furniture trades company} \\
-\cline {2-15} \\
+\cline {1-15} \\
+\multicolumn{14}{l}{furniture trades company} \\
+\cline {1-15} \\
    & \multicolumn{7}{c | }{CR = 0.151}  & \multicolumn{7}{c}{CR = 0.096} \\
@@
 ob & 0.20 & 0.14 & 0.33 & 0.11 & 1.00 & 0.11 & 1.00 & 0.20 & 0.14 & 0.33 & 0.11 & 1.00 & 0.11 & 1.00 \\
-\cline {2-15} \\
- & \multicolumn{14}{l}{plastic packaging manufacturing company} \\
-\cline {2-15} \\
+\cline {1-15} \\
+\multicolumn{14}{l}{plastic packaging manufacturing company} \\
+\cline {1-15} \\
    & \multicolumn{7}{c | }{CR = 0.625}  & \multicolumn{7}{c}{CR = 0.085} \\
@@
 The change will be made in the weights of the other criteria in order to force the consistency of the pairwise comparisons matrix.
-Another important point to note in the method is that the algorithm stops when the desired consistency rate is reached.
+Another important point to note is that the algorithm stops when the desired consistency rate is reached.
 So, it is more likely that there will be significant changes in the fourth criterion and the next ones.
@@
 
-\subsection{Analysis of the ABC multicriterio classification}
+\subsection{Analysis of the ABC multicriteria classification}
 
@@
 \end{tabular}
-\caption{Multicriteria ABC and demand pattern classifications for three companies (results found by COPSolver)}
+\caption{ABC multicriteria and demand pattern classifications for three companies (results found by COPSolver)}
 \label{tab:results}

### 2024-01-09 manuscript/FCPCOM/manuscript.tex
getting started building the introduction section

@@
 \begin{abstract}
+
 Multicriteria classification is usualy very important to the decision-making in manufacturing management process.
@@
 We also present in this paper an analysis of the importance of the attribution of the weights to the criteria and show how the multicriteria and demand pattern classifications may influence the decision on the choice of the appropriate forecasting method.
+
 \end{abstract}
@@
 \label{sec:intro}
+
+Decades of experience in applying the philosophy of lean production eventually popularized the famous saying: "stock is a necessary evil" \citep{Younkin2021}.
+Apresentar desvantagens e vantagens (citar livro produção enxuta).
+Briefly, it is safe to say that stock is unavoidable and must be kept up with in suitable amount \citep{Nirmala2022}.
+
+Apresentar definição de contole de estoque.
+
+As stated by \citep{Nirmala2022}, inventory control means well-organized management of raw materials and supplies, semi-finished goods and finished goods.
+
+Falar sobre técnicas de controle de estoque (classificação ABC (multicriterio) e identificação de padrão de demanda).
+
+Referências sobre classificação ABC multicriteŕio.
+(revisões da literatura).
+Dar enfoque ao ABC multicritério com AHP.
+\cite{FloresEtAl1992} suggest the use of Analytic Hierarchy Process (AHP) to integrate the use of several criteria and rank inventory items.
+Dezde então, diversos trabalhos tem utilizado esta técnica.
+Falar sobre o artigo que compara AHP e algoritmos genéticos.
+
+Referências sobre identificação de padrão de demanda. (revisão da literatura). Dar enfoque ao método de Willians.
+
+Apresentar as contribuições científicas deste artigo.
 
@@
 
+\bibitem[\protect\citeauthoryear{Flores et al.}{1992}]{FloresEtAl1992}
+Flores, B. E., Olson, D. L., Dorai V. K. (1992). Management of multicriteria inventory classification. {\it Mathematical and Computer Modelling}, Vol. 16 (12), pp. 71--82.
+
 \bibitem[\protect\citeauthoryear{Flores and Whybark}{1987}]{FloresWhybark1987}
@@
 Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multicriteria classification problem, in press.
+
+\bibitem[\protect\citeauthoryear{Younkin}{2021}]{Younkin2021}
+Younkin, K.
+(2021).
+The Effect of Lean Inventory and Policies during COVID-19.
+{\it linkedin}, https://www.linkedin.com/pulse/effect-lean-inventory-policies-during-covid-19-kyle-younkin (last accessed on 09/01/2024).
+
+\bibitem[\protect\citeauthoryear{Nirmala}{2022}]{Nirmala2022}
+Nirmala, D.
+A.
+R., Kannan, V., Thanalakshmi, M., Gnanaraj, S.
+J.
+P., Appadurai, M.
+(2022).
+Inventory management and control system using ABC and VED analysis.
+{\it Materials Today: Proceedings}, Vol.
+60 (2), pp.
+922--925.
 

### 2024-01-17 manuscript/FCPCOM/manuscript.tex
updating abstract

@@
 
-Multicriteria classification is usualy very important to the decision-making in manufacturing management process.
-For such classification, the attribution of weights to the criteria strongly influences the coherence of the results found.
-Saaty's Analytic Hierarchy Process (AHP) is an important method for assigning weights to multiple criteria.
-AHP's logic is not complicated at all but, since matrices of pairwise comparisons of criteria  are usually generated manually and based only on some employee know-how, there is a huge complexity on generating a consistent pairwise matrix.
-Especially when many criteria are used.
-This paper presents a constructive algorithm that can be used to adjust inconsistent matrices, forcing such matrices to have a better consistency rate.
-We tested this algorithm by applying the AHP method, for multicriteria ABC classification, to companies in two sectors.
-As a result we observed that the algorithm can adjust the pairwise matrices in just a few seconds, avoiding the manual work that would be done in weeks, therefore showing that it is an important resource for applying the AHP method.
-We also present in this paper an analysis of the importance of the attribution of the weights to the criteria and show how the multicriteria and demand pattern classifications may influence the decision on the choice of the appropriate forecasting method.
+Multicriteria classification and demand pattern identification are two very important techniques that can be used for decision-making in manufacturing management process.
+Although there are many studies that address different multicriteria techniques, few publications associate the use of multicriteria classification with the identification of demand patterns.
+They are complementary techniques, which however are rarely addressed together.
+In this article we present a case study in which we designed product portfolios applying the ABC / Saaty's Analytic Hierarchy Process (AHP) multicriteria classification, in conjunction with the Willians demand pattern identification method, to support the inventory control process and sales strategy in three small and medium-sized companies, from three different sectors.
+Based on the results found, we present an analysis of the impact of the identified patterns on production and inventory planning, and present inventory management decisions and sales strategies that can be taken based on the portfolio built to mitigate the impact of product demand behavior on production efficiency and lead times.
+In carrying out this work, the matrices of pairwise comparisons of criteria were generated manually and based only on employees know-how, so we identified a strong difficulty in the construction of consistent matrices, so we also present a constructive algorithm that can be used to adjust inconsistent matrices when applying AHP, forcing such matrices to have a better consistency rate.
+As a result we observed that this algorithm could adjust the pairwise matrices in just a few seconds, avoiding the manual work that would be done in weeks, showing, therefore, that it is an important resource when applying the AHP method.
 
@@
 Apresentar as contribuições científicas deste artigo.
+
+Also, in multicriteria ABC classification, the attribution of weights to the criteria strongly influences the coherence of the results found.
+Saaty's Analytic Hierarchy Process (AHP) is an important method for assigning weights to multiple criteria.
+AHP's logic is not complicated at all but, since matrices of pairwise comparisons of criteria  are usually generated manually and based only on some employee know-how, there is a huge complexity on generating a consistent pairwise matrix.
+Especially when many criteria are used.
+This paper presents a constructive algorithm that can be used to adjust inconsistent matrices, forcing such matrices to have a better consistency rate.
+We tested this algorithm by applying the AHP method, for multicriteria ABC classification, to companies in two sectors.
+As a result we observed that the algorithm can adjust the pairwise matrices in just a few seconds, avoiding the manual work that would be done in weeks, therefore showing that it is an important resource for applying the AHP method.
+We also present in this paper an analysis of the importance of the attribution of the weights to the criteria and show how the multicriteria and demand pattern classifications may influence the decision on the choice of the appropriate forecasting method.
 

### 2024-01-17 manuscript/FCPCOM/manuscript.tex
updating introduction

@@
 Decades of experience in applying the philosophy of lean production eventually popularized the famous saying: "stock is a necessary evil" \citep{Younkin2021}.
-Apresentar desvantagens e vantagens (citar livro produção enxuta).
-Briefly, it is safe to say that stock is unavoidable and must be kept up with in suitable amount \citep{Nirmala2022}.
-
-Apresentar definição de contole de estoque.
-
-As stated by \citep{Nirmala2022}, inventory control means well-organized management of raw materials and supplies, semi-finished goods and finished goods.
+On the one hand the stock of raw materil, and finished and semi-finished goods serves to reduce the delivery time for the customer and ensure that possible failures in the process do not generate greater influence on production efficiency as well as delays in deliveries, on the other hand the stock usually represents a high cost, allocation of spaces that could be used for other purposes, possibilities of loss and depreciation, in addition to hiding process failures \citep{Shingo1996}.
+Briefly, it is safe to say that stock is unavoidable and must be kept up with in suitable amount, and the well-organized management of raw materials and supplies, semi-finished goods and finished goods is nominated Inventory Control \citep{Nirmala2022}.
 
@@
 
+\bibitem[\protect\citeauthoryear{Shingo}{1996}]{Shingo1996}
+Shingo, S. (1996). {\it O Sistema Toyota de Produção do ponto de vista da Engenharia de Produção}, tradução Eduardo Schaan, Ed. 2, Porto Alegre: Bookman.
+
 \end{thebibliography}

### 2024-01-17 manuscript/FCPCOM/manuscript.tex
updating introduction

@@
 Decades of experience in applying the philosophy of lean production eventually popularized the famous saying: "stock is a necessary evil" \citep{Younkin2021}.
-On the one hand the stock of raw materil, and finished and semi-finished goods serves to reduce the delivery time for the customer and ensure that possible failures in the process do not generate greater influence on production efficiency as well as delays in deliveries, on the other hand the stock usually represents a high cost, allocation of spaces that could be used for other purposes, possibilities of loss and depreciation, in addition to hiding process failures \citep{Shingo1996}.
+On the one hand the stock of raw material, and finished and semi-finished goods serves to reduce the delivery time for the customer and ensure that possible failures in the process do not generate greater influence on production efficiency as well as delays in deliveries, on the other hand the stock usually represents a high cost, allocation of spaces that could be used for other purposes, possibilities of loss and depreciation, in addition to hiding process failures \citep{Shingo1996}.
 Briefly, it is safe to say that stock is unavoidable and must be kept up with in suitable amount, and the well-organized management of raw materials and supplies, semi-finished goods and finished goods is nominated Inventory Control \citep{Nirmala2022}.
+
+As this topic is of utmost importance for companies, the scientific literature presents a large number of works proposing different techniques for Inventory Control (\emph{e.g.} incluir referências sobre trabalhos propondo novas técnicas de controle de inventário) and it is a unanimous conclusion that a multicriteria classification is an essential technique when inventory control involves a high quantity of different goods (incluir referências que dão suporte à frase), which is usually what happens in practice.
 

### 2024-01-17 manuscript/FCPCOM/manuscript.tex
including section portfolio of patterns.

@@
 
+\section{Portfolio of patterns, management decisions and sales strategies}
+
+Contruir um portifólio gráfico para os diferentes casos possíveis e identificados de acordo com Tabela \ref{tab:results}.
+Apresntar sugestões para decisões de controle de inventário e de estratégias de vendas para os casos identificados.
+
 \section{Data collected}

### 2024-01-23 accepted/CONEM2024/MBPTMP/CONEM2024.tex
CONEM2024

% MODELO CONEM 2022 - Obs. Adequado para o CONEM 2024.
%
% Date: January 12, 2024
%
\documentclass[10pt,fleqn,a4paper,twoside]{article}
\usepackage{abcm}
\def\shortauthor{P. Autor, S. Autor e T. Autor \textcolor[rgb]{0.98,0.00,0.00}{(Atualize o cabeçalho de acordo)}}
\def\shorttitle{Versão Reduzida do Título do Artigo \textcolor[rgb]{0.98,0.00,0.00}{(Letras Iniciais em Caixa Alta, certifique que não ultrapasse uma linha)}}

\begin{document}

    % CABEÇALHO
    \thispagestyle{empty}
    \begin{figure}[h]
        \begin{center}
            \includegraphics[angle=0, width=\textwidth]{Logo_template.png}
        \end{center}
    \end{figure}
    \vspace{-.5cm}
    \hspace{-.8cm}
    \begin{tabular}{||p{\textwidth}}
    \begin{center}
    \vspace{-.6cm}
    %
    % Digitar o título
    \title{CONEM2024-XXXX \\ AN EXACT METHOD FOR THE MULTI-PRODUCT P-BATCH PROCESSING TIME MAXIMIZATION PROBLEM}
    %
    \end{center}
	%
	% Digitar os nomes dos autores/instituição
    \authors{Tatiana Balbi Fraga, tatiana.balbi@ufpe.br$^1$} \\
    \authors{Ítalo Ruan Barbosa de Aquino, italo\_ruan\_@hotmail.com$^1$} \\
    \authors{Regilda da Costa e Silva Menêzes, regilda.smenezes@ufpe.br$^1$} \\\\
    \institution{$^1$Centro Acadêmico do Agreste, Universidade Federal de Pernambuco, Avenida Marielle Franco, Bairro Nova Caruaru, Caruaru - PE, CEP: 55014-900} \\
    \\
    %
    % Digitar o resumo
    \abstract{\textbf{Resumo:} Among the most complex multi-product batch problems are the multi-product p-batch scheduling (MPBS) problems, where jobs must be scheduled on parallel batch processing machines. When applying some local search heuristics to solve a MPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products. In this paper we name this problem multi-product p-batch processing time maximization (MPBPTM) problem. Once a MPBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPBS problems. In addition, for some industries, efficiently solving a MPBPTM problem can have a significant impact on storage costs and customer satisfaction. In this paper we present a mathematical model and an exact method with polynomial time complexity for the MBPTM problem. We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method. We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small and very large. As result, we find that the exact method can obtain optimal solutions in a very short time (just few seconds), even when solving very large instances.}\\
    %
    % Digitar as palavras-chave
   \\
    \keywords{\textbf{Palavras-chave:} palavra 1, palavra 2, palavra 3 (até 5 palavras, separadas  por vírgulas) }\\
    %
    \end{tabular}

    \section{INTRODUÇÃO}

        O objetivo destas instruções é servir de guia para a formatação dos trabalhos a serem publicados nos anais. Os anais do XII CONEM serão publicados no formato Adobe$^{\small{TM}}$ PDF.

        Os artigos \textcolor{red}{\underline{\textbf{DEVEM}}} ser formatados de acordo com estas instruções. O presente arquivo pode ser usado como modelo por usuários do \LaTeX. Além disso, pode ser usado como um guia de formatação para usuários de outros processadores de texto.

        Os trabalhos (\textit{draft} e \textit{final paper}) estão limitados a no mínimo \textcolor{red}{\underline{\textbf{6 páginas}}} e no máximo \textcolor{red}{\underline{\textbf{10 páginas}}}, incluindo tabelas e figuras. O arquivo final em formato PDF não deve exceder 2 MB.

        A língua oficial do congresso é o português; entretanto serão aceitos manuscritos em espanhol ou em inglês. Se o trabalho não for escrito em inglês, o autor deverá incluir o título, os nomes dos autores e afiliações, o resumo e as palavras-chave, traduzidos para o inglês, após a lista de referências, no fim do artigo.

    \section{FORMATO DO TEXTO}

        O artigo deve ser digitado no \textit{template} ``CONEM2024.tex'' e as principais configurações (ex.: formato do papel, tipo e tamanho da fonte do título/Seção/Subseção, espaços, margens, alinhamentos, indentação, etc.) já estão previamente configuradas no arquivo ``abcm.sty''. Título, nomes dos autores, instituição, endereço, resumo e palavras-chave devem ser recuados 0,1 cm da margem esquerda e marcados por uma linha preta na borda esquerda com largura de 2$\frac{1}{4}$ pontos.

        Informações suficientes devem ser fornecidas diretamente no texto, ou por referência a trabalhos publicados disponíveis. Notas de rodapé devem ser evitadas.

        Todos os símbolos e notações devem ser definidos no texto. As grandezas físicas devem ser expressas no Sistema Internacional de Unidades. Os símbolos matemáticos que aparecem no texto devem ser digitados em itálico. As unidades devem ser digitadas no estilo romano (ex.: kg, m, MJ, kW/m$^2$, em vez de $kg$, $m$, $MJ$, $kW/m^2$).

        As referências bibliográficas devem ser citadas no texto dando o sobrenome do(s) autor(es) e o ano de publicação, conforme os seguintes exemplos: ``... conforme apresentado \citep{MinwooShamim13}.'' ou ``Recentemente, \citet{MinwooShamim13} demonstraram que …''. No caso de três ou mais autores, deve ser utilizada a expressão ``\textit{et al.}'', como segue: ``... conforme já relatado \citep{Bordalo89}'' e ``Recentemente, \citet{Bordalo89} demonstraram que …''. Duas ou mais referências com os mesmos autores e ano de publicação devem ser distinguidas acrescentando ``a'', ``b'', etc., ao ano de publicação. No caso da necessidade de citar vários trabalhos em uma mesma chamada, o seguinte formato pode ser utilizado: ``...já se encontra consolidado na literatura (\citeauthor{Coimbra78}, \citeyear{Coimbra78}; \citeauthor{Clark86}, \citeyear{Clark86} e \citeauthor{Sparrow80},  \citeyear{Sparrow80})''.

        As referências devem ser listadas no final do manuscrito de acordo com as instruções fornecidas na Seção 4.

        \textbf{\textcolor[rgb]{0.98,0.00,0.00}{\underline{NÃO NUMERAR AS PÁGINAS.}}}

    \subsection{Títulos e Subtítulos das Seções }

        Os títulos das seções são com letras maiúsculas (Exemplo: \textbf{MODELO MATEMÁTICO}), enquanto os subtítulos só têm as primeiras letras maiúsculas de cada palavra (Exemplo: \textbf{Modelo Matemático}). Eles devem ser numerados, usando numerais arábicos separados por pontos, até o máximo de 3 subníveis. Uma linha em branco de espaçamento simples deve ser incluída acima e abaixo de cada título ou subtítulo.

    \subsection{Corpo do Texto}

        Conforme já se encontra definido no arquivo ``abcm.sty'', o corpo do texto é justificado e com espaçamento simples. A primeira linha de cada parágrafo tem recuo de 0,5 cm a partir da margem esquerda.

        As equações matemáticas são alinhadas à esquerda com recuo de 0,5 cm.  Elas são referidas como ``Eq. (\ref{eq:equation1})'' no meio de uma frase, ou ``Equação (\ref{eq:equation1})'' quando usada no início de uma sentença. Os números das equações são numerais arábicos colocados entre parênteses, e alinhados à direita, como mostrado na Eq. (\ref{eq:equation1}). Os símbolos usados nas equações devem ser definidos imediatamente antes ou depois de sua primeira ocorrência no texto.

        O tamanho da fonte usado nas equações deve ser compatível com o utilizado no texto. Todas as grandezas físicas devem ter suas unidades expressas no Sistema Internacional de Unidades, como já mencionado.

        \begin{equation}
        \sigma = E \cdot \epsilon. \label{eq:equation1}
        \end{equation}

    	\noindent
    	onde: $\sigma$ é a tensão, $E$ é o módulo de elasticidade longitudinal (ou Módulo de Young) e $\epsilon$ é a deformação longitudinal.

        As figuras e tabelas devem ser colocadas no texto o mais próximo possível do ponto em que foram mencionadas pela primeira vez e devem ser numeradas consecutivamente em algarismos arábicos. As tabelas devem ser centralizadas e referidas por ``Tab. \ref{tab:tabexemplo}'' no meio de uma frase, ou por ``Tabela \ref{tab:tabexemplo}'' quando usada no início de uma sentença. Uma linha em branco, em espaço simples, deve ser introduzida entre a tabela e o texto subsequente.

        Anotações e valores numéricos incluídos na tabela devem ter tamanhos compatíveis com a fonte usada no texto do trabalho e todas as unidades devem ser expressas no Sistema Internacional de Unidades. As unidades são incluídas apenas na primeira linha ou primeira coluna de cada tabela, conforme for apropriado. O estilo de borda é livre. As explicações, se houver, devem ser fornecidas ao pé das tabelas e não dentro das mesmas.

        \begin{table}[ht]
            \begin{center}
                \caption{\textbf{Exemplo de tabela.}}
                    \begin{tabular}{c|c|c}
                    \hline
                    Propriedades do compósito       & CFRC-TWILL        & CFRC-4HS         \\
                    \hline
                    Resistência à Flexão  (MPa)     & 209.0 $\pm$ 10.0       & 180.0 $\pm$  15.0    \\
                    \hline
                    Módulo de Flexão  (GPa)         & 57.0 $\pm$ 2.8    & 18.0 $\pm$  1.3  \\
                    \hline
                    \end{tabular} \label{tab:tabexemplo}
            \end{center}
        \end{table}

        As figuras devem ser centralizadas. Elas são referenciadas por ``Fig. \ref{fig:figexemplo}'' no meio de uma frase ou por ``Figura \ref{fig:figexemplo}'' quando usada no início de uma sentença. Sua legenda deve ser centralizada e localizada imediatamente abaixo da figura. As anotações e numerações devem ter tamanhos compatíveis com a fonte usada no texto e todas as unidades devem ser expressas no Sistema Internacional de Unidades. As figuras devem ser colocadas o mais próximo possível de sua primeira citação no texto. Deve ser deixada uma linha em branco, de espaçamento simples, entre a figura e o texto subsequente.

        \begin{figure}[h]
            \begin{center}
                \includegraphics[angle=0, scale=.8]{figura.png}
            \end{center}
            \caption{\textbf{Exemplo de figura.}}
            \label{fig:figexemplo}
        \end{figure}

        Figuras coloridas e fotografias de alta qualidade podem ser incluídas no trabalho. Para reduzir o tamanho do arquivo e preservar a resolução gráfica, os arquivos das imagens podem ser convertidos para o formato GIF (para figuras com até 16 cores) ou para o formato JPEG (alta densidade de cores), antes de serem inseridos no trabalho.

    \section{AGRADECIMENTOS}

        Se houver, esta seção deve ser colocada antes da lista de referências.

    % REFERÊNCIAS
    \section{REFERÊNCIAS}

         %   \citet{key} ==>>                Jones et al. (1990)
         %   \citet*{key} ==>>               Jones, Baker, and Smith (1990)
         %   \citep{key} ==>>                (Jones et al., 1990)
         %   \citep*{key} ==>>               (Jones, Baker, and Smith, 1990)
         %   \citep[chap. 2]{key} ==>>       (Jones et al., 1990, chap. 2)
         %   \citep[e.g.][]{key} ==>>        (e.g. Jones et al., 1990)
         %   \citep[e.g.][p. 32]{key} ==>>   (e.g. Jones et al., p. 32)
         %   \citeauthor{key} ==>>           Jones et al.
         %   \citeauthor*{key} ==>>          Jones, Baker, and Smith
         %   \citeyear{key} ==>>             1990

        Referências aceitas incluem: artigos de periódicos, dissertações, teses, artigos publicados em anais de congressos, livros, comunicações privadas e artigos submetidos e aceitos (com fonte identificada) e citações a páginas da internet.

        A lista de referências deve ser uma seção específica denominada Referências, localizada no fim do artigo.

        A primeira linha de cada referência deve ser alinhada à esquerda, sendo que as demais terão recuo já configurado a partir da margem esquerda. Todas as referências incluídas na lista devem aparecer como citações no texto do trabalho.

        As referências devem ser postas em ordem alfabética, usando o último nome do primeiro autor, seguida do ano da publicação. Exemplo da lista de referências é apresentado abaixo.

        \bibliographystyle{abcm}
        \bibliography{bibliografia}

    \section{RESPONSABILIDADE AUTORAIS}

        Os trabalhos escritos em português ou espanhol devem incluir (após direitos autorais) título, os nomes dos autores e afiliações, o resumo e as palavras-chave, traduzidos para o inglês e a declaração a seguir, devidamente adaptada para o número de autores.

        O(s) autor(es) é(são) o(s) único(s) responsável(is) pelo conteúdo deste trabalho.

 % RESUMO EM INGLES

\noindent{
   \\ 
    \begin{tabular}{||p{\textwidth}}
    \begin{center}
    \vspace{-.6cm}
    \title{AFTER FULL PAPER IN PORTUGUESE OR SPANISH, IT IS NECESSARY THE ABSTRACT IN ENGLISH}
    \end{center}
    \authors{First Author’s Name, e-mail1$^1$} \\
    \authors{Second Author’s Name, e-mail$^2$} \\
    \authors{Third Author’s Name, e-mail$^2$} \\\\
    \institution{$^1$Institution and address for first author} \\
    \institution{$^2$Institution and address for second and third authors} \\
    \\
    \authors{\textcolor[rgb]{0.98,0.00,0.00}{Same format for other authors and institutions, if any. (\textit{This guidance should be removed from the final paper.})}} \\
    \\
    \abstract{\textbf{Abstract:} The purpose of these instructions is to serve as a guide for formatting papers to be published in the Proceedings of the XII CONEM. The abstract must describe the objectives, methodology and main conclusions of the article, containing between 300 and 400 words in a single paragraph.  It should not contain either formulae or bibliographic references. The full paper will be published in the proceedings of the event.}\\
    \\
    \keywords{\textbf{Keywords:} keyword 1, keyword 2, keyword 3 (up to 5 keywords) }\\
    \end{tabular}
}

\end{document}

### 2024-01-23 accepted/CONEM2024/MBPTMP/MBPTMP/manuscript.tex
CONEM2024

--- 2023-10-23 manuscript/MBPTMP/manuscript.tex
@@
 
-\author{Tatiana Balbi Fraga\corref{cor1}\fnref{label1}}
-\ead{tatiana.balbi@ufpe.br}
-\cortext[cor1]{corresponding author}
-
-\author{Ítalo Ruan Barbosa de Aquino\fnref{label1}}
-\ead{italo_ruan_@hotmail.com}
-
-\author{Regilda da Costa e Silva Menêzes\fnref{label1}}
-\ead{regilda.smenezes@ufpe.br}
+%\author{Tatiana Balbi Fraga\corref{cor1}\fnref{label1}}
+%\ead{tatiana.balbi@ufpe.br}
+%\cortext[cor1]{corresponding author}
+
+%\author{Ítalo Ruan Barbosa de Aquino\fnref{label1}}
+%\ead{italo_ruan_@hotmail.com}
+
+%\author{Regilda da Costa e Silva Menêzes\fnref{label1}}
+%\ead{regilda.smenezes@ufpe.br}
 
@@
 
-\affiliation[label1]{
-		   organization={Agreste Academic Center - Federal University of Pernambuco},%Department and Organization
-           addressline={Avenida Marielle Franco, Nova Caruaru}, 
-           city={Caruaru},
-           postcode={55014-900}, 
-           state={PE},
-           country={Brazil}}
+%\affiliation[label1]{
+%		   organization={Agreste Academic Center - Federal University of Pernambuco},%Department and Organization
+%           addressline={Avenida Marielle Franco, Nova Caruaru}, 
+%           city={Caruaru},
+%           postcode={55014-900}, 
+%           state={PE},
+%           country={Brazil}}
 
@@
 In addition, for some industries, efficiently solving a MBPTM problem can have a significant impact on storage costs and customer satisfaction.
-In this paper we presente a mathematical model and an exact method with polynomial time complexity for the MBPTM problem.
+In this paper we present a mathematical model and an exact method with polynomial time complexity for the MBPTM problem.
 We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method.
@@
 \item multi-product p-batch processing time maximization (MBPTM) problem definition;
-\item linear integer programming model for the MBPTM problem;
-\item exact optimization method for solving the MBPTM problem.
+\item integer programming model for the MBPTM problem;
+\item exact optimization method for solving the MBPTM problem;
+\item important inventory control support for some industries.
 \end{highlights}
@@
 \begin{keyword}
-multi-product p-batch \sep processing time maximization \sep mathematical model \sep exact method \sep LINGO
+multi-product batch problem\sep p-batch problem \sep processing time maximization \sep integer programming model \sep analytical solution \sep LINGO
 \end{keyword}
@@
 \item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), customer satisfaction($CS$), plant performance ($PP$) and/or processing time ($PT$);
-\item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$).
+\item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$), sequencing constraints($SqC$).
 \end{enumerate}
@@
 
-T.B.
-Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing.
+Blinded.
+
+%T.B.
+Fraga: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing – original draft, Writing – review \& editing, Supervision, Project administration.
 Í.R.B.
-Aquino: Data curation.
+Aquino: Investigation.
 R.C.S.
-Menêzes: Data curation.
+Menêzes: Investigation.
 
@@
 
-We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects.
+Blinded.
+
+%We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects.
 We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process.
@@
 \bibitem[\protect\citeauthoryear{COPSolver}{2023}]{COPSolver2023}
-COPSolver (2023).
-COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multi-product batch processing time maximization problem.
+Blinded.
+
+%\bibitem[\protect\citeauthoryear{COPSolver}{2023}]{COPSolver2023}
+%COPSolver (2023).
+COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multi-product p-batch processing time maximization problem.
 {\it codeocean and GitHub}, codeocean.com/capsule/4837209/tree/v1, github.com/tbfraga/COPSolver/releases/tag/v1.0-1.
@@
 \bibitem[\protect\citeauthoryear{Fraga}{2023}]{Fraga2023}
-Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision prob-
-lems - library for solving the multi-product p-batch processing time maximization problem {\it Software Impacts}, invited paper, in press.
+Fraga, T.B.
+(2023).
+COPSolver: Open source software for solving combinatorial optimization and other decision problems — Library for solving the multi-product p-batch processing time maximization problem {\it Software Impacts}, invited paper, Vol.
+18, pp.
+100592.
 

### 2024-01-31 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating

--- 2024-01-23 accepted/CONEM2024/MBPTMP/CONEM2024.tex
@@
 \usepackage{abcm}
-\def\shortauthor{P. Autor, S. Autor e T. Autor \textcolor[rgb]{0.98,0.00,0.00}{(Atualize o cabeçalho de acordo)}}
-\def\shorttitle{Versão Reduzida do Título do Artigo \textcolor[rgb]{0.98,0.00,0.00}{(Letras Iniciais em Caixa Alta, certifique que não ultrapasse uma linha)}}
+\def\shortauthor{T. B. Fraga, B. M. Cavalcanti, A. M. D. Silva e E. L. R. Silva \textcolor[rgb]{0.98,0.00,0.00}}
+\def\shorttitle{ABC Multicriteria Classification with Analytical Hierarchy Process: How to Force Consistency of Paiwise Comparisons Matrix \textcolor[rgb]{0.98,0.00,0.00}}
+
+\usepackage{array, makecell}
+
+\usepackage[table]{xcolor}
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric,shapes.misc,shapes.symbols,arrows.meta,graphs,fit,positioning,shadows}
 
@@
     % Digitar o título
-    \title{CONEM2024-XXXX \\ AN EXACT METHOD FOR THE MULTI-PRODUCT P-BATCH PROCESSING TIME MAXIMIZATION PROBLEM}
+    \title{CONEM2024-0025\\ ABC  MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX} 
     %
@@
     \authors{Tatiana Balbi Fraga, tatiana.balbi@ufpe.br$^1$} \\
-    \authors{Ítalo Ruan Barbosa de Aquino, italo\_ruan\_@hotmail.com$^1$} \\
-    \authors{Regilda da Costa e Silva Menêzes, regilda.smenezes@ufpe.br$^1$} \\\\
-    \institution{$^1$Centro Acadêmico do Agreste, Universidade Federal de Pernambuco, Avenida Marielle Franco, Bairro Nova Caruaru, Caruaru - PE, CEP: 55014-900} \\
+    \authors{Beatriz Marinho Cavacanti, beatriz.marinhocavalcanti@ufpe.br$^1$} \\
+    \authors{Alexia Maria Duque Silva, alexia.duque@ufpe.br$^1$} \\
+    \authors{Erika Leticia Rodrigues Silva, erika.leticias@ufpe.br$^1$} \\\\
+    \institution{$^1$Nome da instituição, endereço para correspondência (institucional, se houver)} \\
     \\
@@
     % Digitar o resumo
-    \abstract{\textbf{Resumo:} Among the most complex multi-product batch problems are the multi-product p-batch scheduling (MPBS) problems, where jobs must be scheduled on parallel batch processing machines.
-When applying some local search heuristics to solve a MPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products.
-In this paper we name this problem multi-product p-batch processing time maximization (MPBPTM) problem.
-Once a MPBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPBS problems.
-In addition, for some industries, efficiently solving a MPBPTM problem can have a significant impact on storage costs and customer satisfaction.
-In this paper we present a mathematical model and an exact method with polynomial time complexity for the MBPTM problem.
-We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method.
-We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small and very large.
-As result, we find that the exact method can obtain optimal solutions in a very short time (just few seconds), even when solving very large instances.}\\
+    \abstract{\textbf{Resumo:} Multicriteria classification is usually a crucial step in the decision-making in the manufacturing management process.
+For such classification, the attribution of weights to the criteria strongly influences the coherence of the categorization.
+Saaty's Analytic Hierarchy Process (AHP) is an eminent method for assigning weights to multiple criteria.
+AHP's logic is not complicated at all.
+However, since criteria's pairwise comparison matrices are usually generated manually and based only on some employee know-how, there is high complexity in elaborating a consistent pairwise matrix, especially when comparing several criteria.
+This paper presents a constructive algorithm that can adjust inconsistent matrices, forcing such matrices to have a better consistency rate.
+We tested this algorithm by applying the AHP method for ABC multicriteria classification to companies in three sectors.
+As a result, we observed that the algorithm adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours, then showing that it is an essential resource for applying the AHP method.}\\
     %
@@
    \\
-    \keywords{\textbf{Palavras-chave:} palavra 1, palavra 2, palavra 3 (até 5 palavras, separadas  por vírgulas) }\\
+    \keywords{\textbf{Palavras-chave:} ABC multicriteria classification, analytic hierarchy process, consistency rate,  constructive algorithm, COPSolver library}\\
     %
     \end{tabular}
+
+    \section{INTRODUCTION}
+
+    \subsection{Pairwise Comparisons Matrix and Consistency Rate}
+
+    \section{RESULTS AND DISCUSSIONS}
+
+    \subsection{Algorithm for forcing low consistency rate}
+
+    Table \ref{tab:pairwiseMatrix} presents the modifications made by the software 'COPSolver: library for solving the multicriteria classification problem' in the pairwise comparisons matrix and the consequent changes in the consistency rate (CR) for the data colected from the three companies selected for this study.
+
+	\begin{table}[ht]
+            \begin{center}
+                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; np = net-profit; cm = commonality.}}
+                    \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
+						\multicolumn{14}{l}{car mechanics company} \\
+						\cline {1-15} \\
+						& \multicolumn{7}{c | }{CR = 0.216}  & \multicolumn{7}{c}{CR = 0.085} \\
+   						& sb & lt & rp & cr & ob & np & cm & sb & lt & rp & cr & ob & co & cm \\
+						sb & 1.00 & 3.00 & 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 7.00 & 9.00 & 9.00 & 1.00 & 3.00 								& 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 7.00 & 9.00 & 9.00 \\
+						lt & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 7.00 & 9.00 & 9.00 & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 9.00 & 9.00 \\
+						rp & 0.33 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 9.00 & \cellcolor[HTML]{ACE600} 9.00 & 9.00 & 0.33 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 9.00 \\
+						cr & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 9.00 & 9.00 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 9.00 \\
+						ob & 0.14 & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & \cellcolor[HTML]{ACE600} 5.00 & 9.00 & 0.14 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 \\
+						np & 0.11 & 0.11 & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & 9.00 & 0.11 & 0.11 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & 9.00 \\
+						cm & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 1.00 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 1.00 \\
+						\cline {1-15} \\
+						\multicolumn{14}{l}{furniture trades company} \\
+						\cline {1-15} \\
+  						& \multicolumn{7}{c | }{CR = 0.151}  & \multicolumn{7}{c}{CR = 0.096} \\
+   						& lt & sb & rp & cr & cm & np & ob & lt & sb & rp & cr & cm & np & ob \\
+						lt & 1.00 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.20 & 7.00 & \cellcolor[HTML]{ACE600} 0.11 & 5.00 & 1.00 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 7.00 & \cellcolor[HTML]{ACE600} 0.20 & 5.00 \\
+						sb & 5.00 & 1.00 & 0.33 & \cellcolor[HTML]{ACE600} 0.33 & 5.00 &\cellcolor[HTML]{ACE600}  0.14 & 7.00 & 5.00 & 1.00 & 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 5.00 & \cellcolor[HTML]{ACE600} 0.33 & 7.00 \\
+						rp & 7.00 & 3.00 & 1.00 & \cellcolor[HTML]{ACE600} 0.33 & 5.00 & \cellcolor[HTML]{ACE600} 0.14 & 3.00 & 7.00 & 3.00 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 7.00 & \cellcolor[HTML]{ACE600} 1.00 & 3.00 \\
+						cr & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]		{ACE600} 3.00 & 1.00 & \cellcolor[HTML]{ACE600} 9.00 & \cellcolor[HTML]{ACE600} 0.33 & 9.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 \\
+						cm & 0.14 & 0.20 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.11 & 1.00 & 0.11 & 1.00 & 0.14 & 0.20 & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 0.14 & 1.00 & 0.11 & 1.00 \\
+						np & \cellcolor[HTML]{ACE600} 9.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 3.00 & 9.00 & 1.00 & 9.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 & 1.00 & 9.00 \\
+						ob & 0.20 & 0.14 & 0.33 & 0.11 & 1.00 & 0.11 & 1.00 & 0.20 & 0.14 & 0.33 & 0.11 & 1.00 & 0.11 & 1.00 \\
+						\cline {1-15} \\
+						\multicolumn{14}{l}{plastic packaging manufacturing company} \\
+						\cline {1-15} \\
+   						& \multicolumn{7}{c | }{CR = 0.625}  & \multicolumn{7}{c}{CR = 0.085} \\
+   						& np & cr & lt & ob & sb & rp & & np & cr & lt & ob & sb & rp & \\
+						np & 1.00 & 3.00 & 7.00 & \cellcolor[HTML]{ACE600} 7.00 & 5.00 & \cellcolor[HTML]{ACE600} 5.00 & & 1.00 & 3.00 & 7.00 & \cellcolor[HTML]{ACE600} 9.00 & 5.00 & \cellcolor[HTML]{ACE600} 9.00 \\
+						cr & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.20 & & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 5.00 \\
+						lt & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 7.00 & 7.00 & & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 7.00 \\
+						ob & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & \cellcolor[HTML]{ACE600} 0.33 & 3.00 & & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 3.00 \\
+						sb & 0.20 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 3.00 & 1.00 & 3.00 & & 0.20 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & 3.00 \\
+						rp & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 5.00 & 0.14 & 0.33 & 0.33 & 1.00 & & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.20 & 0.14 & 0.33 & 0.33 & 1.00
+				\end{tabular} \label{tab:pairwiseMatrix}
+            \end{center}
+	\end{table}
+
+As we can see in this table, the pairwise comparison weights are adjusted primarily according to the  weights assigned to the first three criteria.
+Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria will be preserved.
+The change will be made in the weights of the other criteria in order to force the consistency of the pairwise comparisons matrix.
+Another important point to note is that the algorithm stops when the desired consistency rate is reached.
+So, it is more likely that there will be significant changes in the fourth criterion and the next ones.
+Therefore, it is important that the criteria are ordered in such a way that the three most relevant criteria for the company are among the first.
+Then the next most relevant criteria can be ordered from last to fourth position.
+
+Initially there was no concern in the construction of the files with the input data, with the correct ordering of the criteria.
+Based on the results and observations previously presented, the students were asked to order the criteria in descending order according to their importance.
+Based on this ordering, the input files were readjusted.
+The following table presents the modifications made after the correct ordering of the criteria.
 

### 2024-02-02 accepted/CONEM2024/FCPCOM/CONEM2024.tex
Results - analysis on fits of inconsistencies.

@@
 
-    Table \ref{tab:pairwiseMatrix} presents the modifications made by the software 'COPSolver: library for solving the multicriteria classification problem' in the pairwise comparisons matrix and the consequent changes in the consistency rate (CR) for the data colected from the three companies selected for this study.
+    Table \ref{tab:pairwiseMatrix} presents the modifications made by the software 'COPSolver: library for solving the multicriteria classification problem' in the pairwise comparisons matrix and the consequent changes in the consistency rate (CR) for the data collected from the three companies selected for this study.
 
@@
             \begin{center}
-                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; np = net-profit; cm = commonality.}}
+                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; np = net-profit; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
                     \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
@@
 						& \multicolumn{7}{c | }{CR = 0.216}  & \multicolumn{7}{c}{CR = 0.085} \\
+						& \multicolumn{7}{c | }{$w=(0.35, 0.26, 0.18, 0.11, 0.05, 0.03, 0.01)$}  & \multicolumn{7}{c}{$w = (0.37, 0.26, 0.12, 0.12, 0.06, 0.05, 0.02)$} \\
    						& sb & lt & rp & cr & ob & np & cm & sb & lt & rp & cr & ob & co & cm \\
@@
   						& \multicolumn{7}{c | }{CR = 0.151}  & \multicolumn{7}{c}{CR = 0.096} \\
+  						& \multicolumn{7}{c | }{$w=(0.05, 0.10, 0.14, 0.21, 0.02, 0.45, 0.02\underline{})$}  & \multicolumn{7}{c}{$w = (0.07, 0.16, 0.25, 0.20, 0.02, 0.26, 0.03)$} \\
    						& lt & sb & rp & cr & cm & np & ob & lt & sb & rp & cr & cm & np & ob \\
@@
    						& \multicolumn{7}{c | }{CR = 0.625}  & \multicolumn{7}{c}{CR = 0.085} \\
+   						& \multicolumn{7}{c | }{$w=(0.39, 0.10, 0.22, 0.09, 0.12, 0.07)$}  & \multicolumn{7}{c}{$w = (0.50, 0.18, 0.14, 0.06, 0.09, 0.03)$} \\
    						& np & cr & lt & ob & sb & rp & & np & cr & lt & ob & sb & rp & \\
@@
 As we can see in this table, the pairwise comparison weights are adjusted primarily according to the weights assigned to the first three criteria.
-Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria will be preserved.
-The change will be made in the weights of the other criteria in order to force the consistency of the pairwise comparisons matrix.
-Another important point to note is that the algorithm stops when the desired consistency rate is reached.
-So, it is more likely that there will be significant changes in the fourth criterion and the next ones.
-Therefore, it is important that the criteria are ordered in such a way that the three most relevant criteria for the company are among the first.
-Then the next most relevant criteria can be ordered from last to fourth position.
+Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria are preserved.
+The algorithm will change the weights of the other criteria to force the consistency of the pairwise comparisons matrix.
+Another significant observation is that the algorithm stops when it reaches the desired consistency rate.
+So, it is more likely that the algorithm changes the weights related to the fourth criterion and the next ones.
+Therefore, the ordering of criteria in the matrix must follow the following rules:
 
-Initially there was no concern in the construction of the files with the input data, with the correct ordering of the criteria.
-Based on the results and observations previously presented, the students were asked to order the criteria in descending order according to their importance.
-Based on this ordering, the input files were readjusted.
-The following table presents the modifications made after the correct ordering of the criteria.
+\begin{itemize}
+\item the three most relevant criteria for the company are among the first;
+\item the other criteria are ordered from the last to fourth position, in descending order of relevance.
+\end{itemize}
+
+For the data presented in Table 1, there was no concern with the correct ordering of the criteria.
+Based on the results and previous observations,  we requested the criteria classification according to its relevance to each company.
+Table 2 presents the modification of results after altering the criteria ordination on the input data.
+
+Speaking about the CR, Tab. 1 clearly shows the inconsistencies before the modification and how the weight modifications made by the algorithm reflect the adjustments
+of these inconsistencies.
+For example, in the case of the plastic bag manufacturing company, the net profit criterion is more important than the criticality criterion and much more valuable than the lead time criterion.
+Also, the criticality criterion is more important than the lead time criterion.
+These statements are coherent.
+However, the vector of the weights of this matrix clearly shows that the criticality criterion is less relevant than the lead time criterion, which is inconsistent with the two first statements.
+The assignment of the other weights related to criteria criticality and lead time causes this inconsistency.
+We can see from the input data matrix that the obsolescence, replaceability, and repairability criteria are more important than the criticality criterion but less valuable than the lead-time criterion.
+According to the initial statement (that criticality is more relevant than lead time), this new statement generates the inconsistency of the pairwise comparisons matrix.
+As we can see in the adjusted matrix, the algorithm quickly corrects these inconsistencies and then the weight vector.
 

### 2024-02-02 accepted/CONEM2024/FCPCOM/CONEM2024.tex
comparative weights

@@
 
+    \section{ALGORITHM FOR FORCING LOW CONSISTENCY RATE}
+
     \section{RESULTS AND DISCUSSIONS}
 
-    \subsection{Algorithm for forcing low consistency rate}
+    \subsection{Analysis on the Algorithm for Adjusting Inconsistencies}
 
@@
 As we can see in the adjusted matrix, the algorithm quickly corrects these inconsistencies and then the weight vector.
+
+\subsection{Reflections on the Correct Application of the Multicriteria Classification}
+
+In our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification.
+
+When we built the input data file, we considered two types of criteria for ABC analysis, cumulative sum (for the net profit and lead time criteria) and qualitative criteria measured by weights (0 and 1, in the case of the criticality criterion, and 1, 2, 3, in the case of the other criteria).
+As a result, we had a bias in the multicriteria classification.
+The criterion with the top percentage difference (turnover) was dominant.
+
+In the case of the criticality criterion, the choice of a binary parameter results in a distribution of the probability among the criteria that are critical.
+This seems to be consistent with the desired goal.
+However, in the case of the other criteria, the consistency is no longer so clear.
+For example, in the company, the product with the highest turnover (242,280.00 reais) has a turnover corresponding to 12\% of the total turnover.
+A product with a longer lead time (30 days) represents 0.46\% of the total lead time, that is, a percentage 0.25\% higher than products with a lead time of 20 days (0.31\%) and 0.35\% higher than products with a lead time of 7 days (0.11\%).
+
+The question is: is the difference between the importance of a product with a 30-day lead time and a product with a 7-day lead time really only 0.35\%.
+This importance can only really be appreciated when put in comparison with the difference in importance of 12\% between the product with the highest turnover and the product with the lowest turnover.
+
+Analyzing these values, we come to the conclusion that it seems coherent to adopt as a measure for the weights not gross values, but comparative values.
+This conclusion gave rise to the idea of assigning comparative weights.
 

### 2024-02-02 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating

@@
 
-The question is: is the difference between the importance of a product with a 30-day lead time and a product with a 7-day lead time really only 0.35\%.
-This importance can only really be appreciated when put in comparison with the difference in importance of 12\% between the product with the highest turnover and the product with the lowest turnover.
+The question is: is the difference between the importance of a product with a 30-day lead time and a product with a 7-day lead time only 0.35\%?
+This value can only be appreciated when compared with the difference in importance of 12\% between the product with the highest turnover and the product with the lowest turnover.
+It is like creating an average of the annual sales of vehicles and bananas, hoping that this average will have some meaning.
+For there to be real meaning in the weighted average found by the multicriteria method, it is necessary to apply some procedure to normalize the weights assigned to each criterion.
 
-Analyzing these values, we come to the conclusion that it seems coherent to adopt as a measure for the weights not gross values, but comparative values.
-This conclusion gave rise to the idea of assigning comparative weights.
+	\citet{Odu2019} cites CRITIC as one of the methods applied for weight assignment in multicriteria classification. This method starts with normalizing the weights using the following equations:
+
+	The problem with this normalization method is that the largest values of the different criteria will have the same importance.
+In the case of the companies studied, this may not correspond to the assessment of experts.
+However, it is possible to make a comparative analysis of amounts using different criteria.
+And use this analysis for normalization.
+For this purpose, we propose the following procedure:
+
+\begin{itemize}
+\item classification of products in descending order according to a first criterion;
+\item identification of the product with the highest weight, according to a second criterion;
+\item peer-to-peer comparison with the products ordered according to the first criterion, answering the following question: the degree of importance of this product according to the second criterion is equivalent to what degree of importance of the other product evaluated according to the first criterion?
+\end{itemize}
+
+Using this procedure, we can identify, for example, that the lead time weight of a product that has a lead time of 30 days is equivalent to the annual turnover weight of a product with an annual turnover of 68,380.00 reais.
+
+    \section{REFERENCES}
 

### 2024-02-02 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating

@@
 
-	The problem with this normalization method is that the largest values of the different criteria will have the same importance.
+	The problem with this normalization method is that the largest values of the different criteria will have the same weight.
 In the case of the companies studied, this may not correspond to the assessment of experts.
@@
 \item identification of the product with the highest weight, according to a second criterion;
-\item peer-to-peer comparison with the products ordered according to the first criterion, answering the following question: the degree of importance of this product according to the second criterion is equivalent to what degree of importance of the other product evaluated according to the first criterion?
+\item peer-to-peer comparison with the products ordered according to the first criterion, answering the following question: the degree of importance of this product according to the second criterion is equivalent to what degree of importance of the other product evaluated according to the first criterion?;
+\item use of the first criterion normalized weight of correspondent product for normalization.
 \end{itemize}

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
On Multicriteria ABC Classification

--- 2024-02-02 accepted/CONEM2024/FCPCOM/CONEM2024.tex
@@
 
-\subsection{Reflections on the Correct Application of the Multicriteria Classification}
+\subsection{On Multicriteria ABC Classification}
 
@@
 
-When we built the input data file, we considered two types of criteria for ABC analysis, cumulative sum (for the net profit and lead time criteria) and qualitative criteria measured by weights (0 and 1, in the case of the criticality criterion, and 1, 2, 3, in the case of the other criteria).
-As a result, we had a bias in the multicriteria classification.
-The criterion with the top percentage difference (turnover) was dominant.
+When we built the input data file, we considered three types of criteria for ABC analysis, cumulative sum (for billing and lead time criteria), qualitative, and binary criteria.
+While we were testing the solver, we noticed that an incorrect assignment of the weights can generate a strong bias in the multicriteria classification, since the criterion with the top percentage difference will always be dominant.
 
-In the case of the criticality criterion, the choice of a binary parameter results in a distribution of the probability among the criteria that are critical.
+Therefore, to assign the weights, three procedures were adopted, according to the different nature of each type of criterion used.
+
+In the case of the binary criteria, the choice of a binary parameters (0 and 1) results in a distribution of the percentage among the criteria that are critical.
 This seems to be consistent with the desired goal.
 However, in the case of the other criteria, the consistency is no longer so clear.
-For example, in the company, the product with the highest turnover (242,280.00 reais) has a turnover corresponding to 12\% of the total turnover.
-A product with a longer lead time (30 days) represents 0.46\% of the total lead time, that is, a percentage 0.25\% higher than products with a lead time of 20 days (0.31\%) and 0.35\% higher than products with a lead time of 7 days (0.11\%).
 
-The question is: is the difference between the importance of a product with a 30-day lead time and a product with a 7-day lead time really only 0.35\%.
-This importance can only really be appreciated when put in comparison with the difference in importance of 12\% between the product with the highest turnover and the product with the lowest turnover.
+We can verify this inconsistency through a brief analysis of the two criteria classified according to the cumulative sum.
+For the data collected from the furniture trades company, the product with the highest billing (242,280.00 reais) has a turnover corresponding to 12\% of the total turnover; and a product with a longer lead time (30 days) represents 0.46\% of the total lead time, that is, a percentage 0.25\% higher than products with a lead time of 20 days (0.31\%) and 0.35\% higher than products with a lead time of 7 days (0.11\%).
 
-Analyzing these values, we come to the conclusion that it seems coherent to adopt as a measure for the weights not gross values, but comparative values.
-This conclusion gave rise to the idea of assigning comparative weights.
+The question is: is the difference between the importance of a product with a 30-day lead time and a product with a 7-day lead time only 0.35\%?
+This value can only be appreciated when compared with the difference in importance of 12\% between the product with the highest and the product with the lowest billing.
+
+Make a multicriteria classification for the billing and lead time criteria based only on the accumulated sum is like calculate a weighted average of the annual sales of vehicles and bananas, hoping that this average will have some meaning.
+For there to be real meaning in the weighted average found by the multicriteria method, it is necessary to apply some procedure to balance the weights assigned to each criterion.
+
+	\citet{Odu2019} cites CRITIC as one of the methods applied for weight assignment in multicriteria classification. This method starts with normalizing the weights using the following equations:
+
+	\begin{equation}
+		\rho_{ij} = \frac{w_{ij} - w_{j}^{\min}}{w_{j}^{\max} - w_{j}^{\min}} \qquad i=1,...,m; j = 1, ..., n \qquad \textrm{for benefit criteria}
+	\end{equation}
+
+	\begin{equation}
+		\rho_{ij} = \frac{w_{j}^{\max} - w_{ij}}{w_{j}^{\max} - w_{j}^{\min}} \qquad i=1,...,m; j = 1, ..., n \qquad \textrm{for cost criteria}
+	\end{equation}
+
+	Where $w_{j}^{\min}$ and $w_{j}^{\max}$ are, respectively, the lowest and highest weights assigned to criterion $j$, $w_{ij}$ is the weight and $\rho_{ij}$ is the normalized weight of criteria $j$ for product $i$.
+
+	The problem with this normalization method is that the largest values of the different criteria will have exactly the same weight.
+In the case of the companies studied, this may not correspond to the assessment of experts.
+
+	The solution that we adopted this work for multicriteria classification with lead time and billing criteria, was based on the work of Willians.
+A single measure was adopted for these two criteria (billing per lead time) dividing the billing by the lead time.
+
+In the case of qualitative criteria (substitutability, obsolescence and commonality), the initial ABC classification was made using three weights, one weight assigned to products A, pa, a second weight assigned to products B, pb, and a third weight assigned to products C, pc, where pa > pb > pc.
+For qualitative criteria, pa, pb and pc must be assigned using the following steps:
+
+\begin{itemize}
+\item order the products, in descending order, according to their respective values for lead time billing;
+\item classify products into three groups, A, B and C, for each qualitative criterion;
+\item do pc = 0 for all group C products, for each qualitative criterion;
+\item for each qualitative criterion, do peer-to-peer comparison with the groups A and B and the products ordered according to the lead time billing criterion, answering the following question: the degree of importance of the products of this group to the qualitative criterion is equivalent to what degree of importance of the other product evaluated according to the lead time billing criterion ?;
+\item assign to pa and pb the value of the lead time billing of the product with corresponding importance.
+\end{itemize}
+
+    \section{REFERENCES}
 

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
small changes

@@
             \begin{center}
-                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; np = net-profit; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
+                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; bl = billing; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
                     \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
@@
 						& \multicolumn{7}{c | }{$w=(0.35, 0.26, 0.18, 0.11, 0.05, 0.03, 0.01)$}  & \multicolumn{7}{c}{$w = (0.37, 0.26, 0.12, 0.12, 0.06, 0.05, 0.02)$} \\
-   						& sb & lt & rp & cr & ob & np & cm & sb & lt & rp & cr & ob & co & cm \\
+   						& sb & lt & rp & cr & ob & bl & cm & sb & lt & rp & cr & ob & co & cm \\
 						sb & 1.00 & 3.00 & 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 7.00 & 9.00 & 9.00 & 1.00 & 3.00 								& 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 7.00 & 9.00 & 9.00 \\
@@
   						& \multicolumn{7}{c | }{$w=(0.05, 0.10, 0.14, 0.21, 0.02, 0.45, 0.02\underline{})$}  & \multicolumn{7}{c}{$w = (0.07, 0.16, 0.25, 0.20, 0.02, 0.26, 0.03)$} \\
-   						& lt & sb & rp & cr & cm & np & ob & lt & sb & rp & cr & cm & np & ob \\
+   						& lt & sb & rp & cr & cm & bl & ob & lt & sb & rp & cr & cm & np & ob \\
 						lt & 1.00 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.20 & 7.00 & \cellcolor[HTML]{ACE600} 0.11 & 5.00 & 1.00 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 7.00 & \cellcolor[HTML]{ACE600} 0.20 & 5.00 \\
@@
    						& \multicolumn{7}{c | }{$w=(0.39, 0.10, 0.22, 0.09, 0.12, 0.07)$}  & \multicolumn{7}{c}{$w = (0.50, 0.18, 0.14, 0.06, 0.09, 0.03)$} \\
-   						& np & cr & lt & ob & sb & rp & & np & cr & lt & ob & sb & rp & \\
+   						& np & cr & lt & ob & sb & rp & & bl & cr & lt & ob & sb & rp & \\
 						np & 1.00 & 3.00 & 7.00 & \cellcolor[HTML]{ACE600} 7.00 & 5.00 & \cellcolor[HTML]{ACE600} 5.00 & & 1.00 & 3.00 & 7.00 & \cellcolor[HTML]{ACE600} 9.00 & 5.00 & \cellcolor[HTML]{ACE600} 9.00 \\
@@
 of these inconsistencies.
-For example, in the case of the plastic bag manufacturing company, the net profit criterion is more important than the criticality criterion and much more valuable than the lead time criterion.
+For example, in the case of the plastic bag manufacturing company, the billing criterion is more important than the criticality criterion and much more valuable than the lead time criterion.
 Also, the criticality criterion is more important than the lead time criterion.

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
multicriteria equation

@@
     \section{ALGORITHM FOR FORCING LOW CONSISTENCY RATE}
+
+    \section{ON MULTICRITERIA ABC CLASSIFICATION}
+
+In our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification.
+
+When we built the input data file, we considered three types of criteria for ABC analysis, cumulative sum (for billing and lead time criteria), qualitative, and binary criteria.
+While we were testing the solver, we noticed that an incorrect assignment of the weights can generate a strong bias in the multicriteria classification, since the criterion with the top percentage difference will always be dominant.
+
+Therefore, to assign the weights, three procedures were adopted, according to the different nature of each type of criterion used.
+
+In the case of the binary criteria, the choice of a binary parameters (0 and 1) results in a distribution of the percentage among the criteria that are critical.
+This seems to be consistent with the desired goal.
+However, in the case of the other criteria types, the consistency is no longer so clear.
+
+We can verify this inconsistency through a brief analysis of the two criteria classified according to the cumulative sum.
+For the data collected from the furniture trades company, the product with the highest billing (242,280.00 reais) has a billing corresponding to 12\% of the total amount; and a product with a longer lead time (30 days) represents 0.46\% of the total lead time, that is, a percentage 0.25\% higher than products with a lead time of 20 days (0.31\%) and 0.35\% higher than products with a lead time of 7 days (0.11\%).
+
+The question is: is the difference between the importance of a product with a 30-day lead time and a product with a 7-day lead time only 0.35\%?
+This value can only be appreciated when compared with the difference in importance of 12\% between the product with the highest and the product with the lowest billing.
+
+Make a multicriteria classification for the billing and lead time criteria based only on the accumulated sum is like calculate a weighted average of the annual sales of vehicles and bananas, hoping that this average will have some meaning.
+For there to be real meaning in the weighted average found by the multicriteria method, it is necessary to apply some procedure to balance the weights assigned to each criterion.
+
+	\citet{Odu2019} cites CRITIC as one of the methods applied for weight assignment in multicriteria classification. This method starts with normalizing the weights using the following equations:
+
+	\begin{equation}
+		\rho_{ij} = \frac{w_{ij} - w_{j}^{\min}}{w_{j}^{\max} - w_{j}^{\min}} \qquad i=1,...,m; j = 1, ..., n \qquad \textrm{for benefit criteria}
+	\end{equation}
+
+	\begin{equation}
+		\rho_{ij} = \frac{w_{j}^{\max} - w_{ij}}{w_{j}^{\max} - w_{j}^{\min}} \qquad i=1,...,m; j = 1, ..., n \qquad \textrm{for cost criteria}
+	\end{equation}
+
+	Where $w_{j}^{\min}$ and $w_{j}^{\max}$ are, respectively, the lowest and highest weights assigned to criterion $j$, $w_{ij}$ is the weight and $\rho_{ij}$ is the normalized weight of criteria $j$ for product $i$.
+
+	The problem with this normalization method is that the largest values of the different criteria will have exactly the same weight.
+In the case of the companies studied, this may not correspond to the assessment of experts.
+
+	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was based on the work of Willians.
+A single measure was adopted for these two criteria (lead time billing) dividing the billing by the lead time.
+
+In the case of qualitative criteria, the initial ABC classification was made using three weights, one weight assigned to products A, pa, a second weight assigned to products B, pb, and a third weight assigned to products C, pc, where pa > pb > pc.
+For qualitative criteria, pa, pb and pc must be assigned using the following steps:
+
+\begin{itemize}
+\item order the products, in descending order, according to their respective values for lead time billing;
+\item classify products into three groups, A, B and C, for each qualitative criterion;
+\item do pc = 0 for all group C products, for each qualitative criterion;
+\item for each qualitative criterion, do peer-to-peer comparison with the groups A and B and the products ordered according to the lead time billing criterion, answering the following question: the degree of importance of the products of this group to the qualitative criterion is equivalent to what degree of importance of the other product evaluated according to the lead time billing criterion ?;
+\item assign to pa and pb the value of the lead time billing of the product with corresponding importance.
+\end{itemize}
+
+Then, the equation can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:
+
+\begin{equation}
+	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum{w_{\sigma_q}*\frac{b_{e_p}}{lt_{e_p}}} + \sum{w_{\beta_b}*w_{p\beta_b}}
+\end{equation}
+
+where:
+
+$\textrm{NP}$ is the number of products;
+
+$\textrm{NQ}$ is the number of qualitative criteria;
+
+$\textrm{NB}$ is the number of binary criteria;
+
+$\Sigma$ is the set of qualitative criteria, \quad $\Sigma = \{\sigma_q\}_{q=1}^{NQ}$;
+
+$\textrm{B}$ is the set of binary criteria, \quad $\textrm{B} = \{\beta_b\}_{b=NQ+1}^{NQ+NB}$;
+
+$p$ is the index used to represent each product, \quad $p= 1,...,\textrm{NP}$;
+
+$e_p$ is the lead time billing equivalent to product $p$;
+
+$c$ is the index used to represent each criterion of qualitative or binary type , \quad $c \in \Sigma \cup \textrm{B}$;
+
+$b_p$ is the billing of product $p$;
+
+$lt_p$ is the lead time of product $p$;
+
+$\frac{b_p}{lt_p}$ is the lead time billing of product $p$;
+
+$w_{pc}$ is the weight of the product $p$ according to criterion $c$;
+
+$wb$ is the weight of criterion billing.
+
+$wlt$ is the weight of criterion lead time.
+
+$w_{c}$ is the weight of criterion $c$.
 
@@
 As we can see in the adjusted matrix, the algorithm quickly corrects these inconsistencies and then the weight vector.
-
-\subsection{On Multicriteria ABC Classification}
-
-In our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification.
-
-When we built the input data file, we considered three types of criteria for ABC analysis, cumulative sum (for billing and lead time criteria), qualitative, and binary criteria.
-While we were testing the solver, we noticed that an incorrect assignment of the weights can generate a strong bias in the multicriteria classification, since the criterion with the top percentage difference will always be dominant.
-
-Therefore, to assign the weights, three procedures were adopted, according to the different nature of each type of criterion used.
-
-In the case of the binary criteria, the choice of a binary parameters (0 and 1) results in a distribution of the percentage among the criteria that are critical.
-This seems to be consistent with the desired goal.
-However, in the case of the other criteria, the consistency is no longer so clear.
-
-We can verify this inconsistency through a brief analysis of the two criteria classified according to the cumulative sum.
-For the data collected from the furniture trades company, the product with the highest billing (242,280.00 reais) has a turnover corresponding to 12\% of the total turnover; and a product with a longer lead time (30 days) represents 0.46\% of the total lead time, that is, a percentage 0.25\% higher than products with a lead time of 20 days (0.31\%) and 0.35\% higher than products with a lead time of 7 days (0.11\%).
-
-The question is: is the difference between the importance of a product with a 30-day lead time and a product with a 7-day lead time only 0.35\%?
-This value can only be appreciated when compared with the difference in importance of 12\% between the product with the highest and the product with the lowest billing.
-
-Make a multicriteria classification for the billing and lead time criteria based only on the accumulated sum is like calculate a weighted average of the annual sales of vehicles and bananas, hoping that this average will have some meaning.
-For there to be real meaning in the weighted average found by the multicriteria method, it is necessary to apply some procedure to balance the weights assigned to each criterion.
-
-	\citet{Odu2019} cites CRITIC as one of the methods applied for weight assignment in multicriteria classification. This method starts with normalizing the weights using the following equations:
-
-	\begin{equation}
-		\rho_{ij} = \frac{w_{ij} - w_{j}^{\min}}{w_{j}^{\max} - w_{j}^{\min}} \qquad i=1,...,m; j = 1, ..., n \qquad \textrm{for benefit criteria}
-	\end{equation}
-
-	\begin{equation}
-		\rho_{ij} = \frac{w_{j}^{\max} - w_{ij}}{w_{j}^{\max} - w_{j}^{\min}} \qquad i=1,...,m; j = 1, ..., n \qquad \textrm{for cost criteria}
-	\end{equation}
-
-	Where $w_{j}^{\min}$ and $w_{j}^{\max}$ are, respectively, the lowest and highest weights assigned to criterion $j$, $w_{ij}$ is the weight and $\rho_{ij}$ is the normalized weight of criteria $j$ for product $i$.
-
-	The problem with this normalization method is that the largest values of the different criteria will have exactly the same weight.
-In the case of the companies studied, this may not correspond to the assessment of experts.
-
-	The solution that we adopted this work for multicriteria classification with lead time and billing criteria, was based on the work of Willians.
-A single measure was adopted for these two criteria (billing per lead time) dividing the billing by the lead time.
-
-In the case of qualitative criteria (substitutability, obsolescence and commonality), the initial ABC classification was made using three weights, one weight assigned to products A, pa, a second weight assigned to products B, pb, and a third weight assigned to products C, pc, where pa > pb > pc.
-For qualitative criteria, pa, pb and pc must be assigned using the following steps:
-
-\begin{itemize}
-\item order the products, in descending order, according to their respective values for lead time billing;
-\item classify products into three groups, A, B and C, for each qualitative criterion;
-\item do pc = 0 for all group C products, for each qualitative criterion;
-\item for each qualitative criterion, do peer-to-peer comparison with the groups A and B and the products ordered according to the lead time billing criterion, answering the following question: the degree of importance of the products of this group to the qualitative criterion is equivalent to what degree of importance of the other product evaluated according to the lead time billing criterion ?;
-\item assign to pa and pb the value of the lead time billing of the product with corresponding importance.
-\end{itemize}
 

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
multicriteria ABC classification

@@
 \def\shorttitle{ABC Multicriteria Classification with Analytical Hierarchy Process: How to Force Consistency of Paiwise Comparisons Matrix \textcolor[rgb]{0.98,0.00,0.00}}
+
+\usepackage{algpseudocode}
 
@@
 \begin{equation}
-	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum{w_{\sigma_q}*\frac{b_{e_p}}{lt_{e_p}}} + \sum{w_{\beta_b}*w_{p\beta_b}}
+	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{lt_{e_{p\sigma_q}}}} + \sum{w_{\beta_b}*w_{p\beta_b}}
 \end{equation}
@@
 
-$\textrm{B}$ is the set of binary criteria, \quad $\textrm{B} = \{\beta_b\}_{b=NQ+1}^{NQ+NB}$;
+$\textrm{B}$ is the set of binary criteria, \quad $\textrm{B} = \{\beta_b\}_{b=1}^{NB}$;
 
@@
 
-$e_p$ is the lead time billing equivalent to product $p$;
+$e_{p\sigma_q}$ is the product lead time billing equivalent to product $p$ on the criterion $\sigma_q$;
 

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
my beautiful equation :)

@@
 
-Then, the equation can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:
+Equation (\ref{eq:weight}) can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:
 
 \begin{equation}
-	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{lt_{e_{p\sigma_q}}}} + \sum{w_{\beta_b}*w_{p\beta_b}}
+	\label{eq:weight}
+	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum_{q=1}^{\textrm{NQ}}{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{lt_{e_{p\sigma_q}}}} + \sum_{b=1}^{\textrm{NB}}{w_{\beta_b}*w_{p\beta_b}}, \quad p= 1,...,\textrm{NP}
 \end{equation}

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
new beautiful multicriteria method - I belive it will work

@@
 
-	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was based on the work of Willians.
-A single measure was adopted for these two criteria (lead time billing) dividing the billing by the lead time.
+	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of Willians.
+A single measure was adopted for these two criteria (lead time billing) dividing the billing by the complement of the lead time percentage.
 
@@
 	\label{eq:weight}
-	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum_{q=1}^{\textrm{NQ}}{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{lt_{e_{p\sigma_q}}}} + \sum_{b=1}^{\textrm{NB}}{w_{\beta_b}*w_{p\beta_b}}, \quad p= 1,...,\textrm{NP}
+	\rho_{p} = (wb + wlt) * \frac{b_p}{1 + (lt^{\max} - lt_p)} + \sum_{q=1}^{\textrm{NQ}}{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{1 + (lt^{\max} - lt_{e_{p\sigma_q}})}} + \sum_{b=1}^{\textrm{NB}}{w_{\beta_b}*w_{p\beta_b}}, \quad p= 1,...,\textrm{NP}
 \end{equation}
@@
 
-$\frac{b_p}{lt_p}$ is the lead time billing of product $p$;
+$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing of product $p$;
 

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
percentage

@@
 
-$e_{p\sigma_q}$ is the product lead time billing equivalent to product $p$ on the criterion $\sigma_q$;
+$e_{p\sigma_q}$ is the product lead time billing weight percentage equivalent to product $p$ on the criterion $\sigma_q$;
 
@@
 
-$b_p$ is the billing of product $p$;
+$b_p$ is the billing weight percentage of product $p$;
 
-$lt_p$ is the lead time of product $p$;
+$lt_p$ is the lead time weight percentage of product $p$;
 
-$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing of product $p$;
+$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing weight percentage of product $p$;
 
-$w_{pc}$ is the weight of the product $p$ according to criterion $c$;
+$w_{pc}$ is the weight percentage of the product $p$ according to criterion $c$;
 
-$wb$ is the weight of criterion billing.
+$wb$ is the weight percentage of criterion billing.
 
-$wlt$ is the weight of criterion lead time.
+$wlt$ is the weight percentage of criterion lead time.
 
-$w_{c}$ is the weight of criterion $c$.
+$w_{c}$ is the weight percentage of criterion $c$.
 

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
complement

@@
 	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of Willians.
-A single measure was adopted for these two criteria (lead time billing) dividing the billing by the complement of the lead time percentage.
+A single measure was adopted for these two criteria (lead time billing weight complement) dividing the billing by the complement of the lead time percentage.
 
@@
 
-$e_{p\sigma_q}$ is the product lead time billing weight percentage equivalent to product $p$ on the criterion $\sigma_q$;
+$e_{p\sigma_q}$ is the product lead time billing weight percentage complement equivalent to product $p$ on the criterion $\sigma_q$;
 
@@
 
-$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing weight percentage of product $p$;
+$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing weight percentage complement for product $p$;
 

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
weight

@@
 	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of Willians.
-A single measure was adopted for these two criteria (lead time billing weight complement) dividing the billing by the complement of the lead time percentage.
+A single measure was adopted for these two criteria (lead time billing  weight) dividing the billing weight by the complement of the lead time weight.
 

### 2024-02-16 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating
work in progress - writing introduction

@@
 
-    \subsection{Pairwise Comparisons Matrix and Consistency Rate}
+	As stated by \cite{Kiran2019}, the "production planning and control (PP\&C) ...
+is responsible for ensuring the availability all materials, part of assembly at the right time, at the right place, and in right quantities in order to enable the progress of operations according to the predetermined schedules at the minimum possible costs." According to the author, factories producing large volumes of standardized products need very simple production control techniques.
+However factories producing a variety of products and product mix also need meticulous control with complex production control techniques.
+Therefore, in the latter case, a prior strategic planning becomes impressible for better use of the productive capacity as well as to avoid investment losses in materials that will not be used or will not bring significant profit to the company.
+Companies that market a wide variety of products and product mix should always use good strategic planning as a guide for sales and PP\&C anticipation strategies and it's really important to start any strategic planning by understanding the importance all products marked.
+
+	In this work we conducted a study with three companies from three different sectors, which market a wide variety of products, in some cases, highly personalized products.
+In view of the very high variety of products marketed by the companies studied, the interest of this study was to identify the main products, that is, the products that should be prioritized, so that this information could guide the strategic planning of the company.
+Also, we identified the need to consider several criteria for such a classification, therefore we used a multicriteria approach.
+
+	The importance of multicriteria classification for inventory management has been widely emphasized in scientific literature and several multicriteria methods have been used, being the ABC multicriteria classification with Analytical Hierarchy Process one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}.
+Few recent works talk about multicriteria classification applied to strategic planning \citep[\emph{e.g.},][]{BarbosaDePaula2022, Pereira2023, MarianoRibeiro2023}.
+
+	\citet{Odu2019} emphasize that, when aplying some multicriteria method, it is important to pay particular attention to the objectivity factors of criteria weights.
+The author provides an important overview of different weighting methods applicable to multicriteria techniques.
+In the present work, we opted for the multicriteria ABC classification and adopted the Analytic Hierarchy Process \citep{Saaty1987} to assign the weights to the different criteria.
+It is important to note that the Analytic Hierarchy Process derives the weights of the criteria based on the eigenvector of a pairwise comparison matrix which is constructed manually according to an empirical evaluation.
+According to \cite{Saaty1987}, this matrix must be antisymmetric and must have a consistency rate of less than 0.1.
+The autor reports that a software package supporting the AHP, called Expert Choice, for the IBM PC, was used in his work for making eigenvector calculations and guide the decision maker to improve matriz inconsistency if needed.
+During the execution of the work we present in this paper, we found that there is a strong difficulty in for calculation of the eigenvector, as well as for the construction of consistent pairwise comparison matrices and we had no access to the Expert Choice software package, so we developed an open source COPSolver library for Analitic Hierarch Process and multicriteria ABC classification based on a new a method for forcing the consistency of such matrices.
+We present this method in this paper.
+The Eigen library from eigen.tuxfamily.org was used for eigenvector calculation.
+Also we identified that the assignment of weights to ABC classification can be done using different criteria and we observed that such assignment generates a bias in the multicriteria ABC classification.
+Therefore we also developed a new methodology for assigning weights in a balanced way for ABC classification and we proposed a new multicriteria ABC classification method, that we aplyed on COPSolver library.
+We also presente both methods on this paper and an in-depth analysis of the results found by the library we developed for COPSolver.
 
@@
     \section{ON MULTICRITERIA ABC CLASSIFICATION}
+
+    Inventory classification problem is also a decision problem since we want to decide what is the better system and criteria for clustering the different inventory itens.
 

### 2024-02-16 accepted/CONEM2024/FCPCOM/CONEM2024.tex
work in progress - writing introduction - not finished yet

@@
 
+	\citet{Odu2019} emphasize that, when aplying some multicriteria method, it is important to pay particular attention to the objectivity factors of criteria weights.
+The author provides an important overview of different weighting methods applicable to multicriteria techniques.
 The importance of multicriteria classification for inventory management has been widely emphasized in scientific literature and several multicriteria methods have been used, being the ABC multicriteria classification with Analytical Hierarchy Process one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}.
@@
 
-	\citet{Odu2019} emphasize that, when aplying some multicriteria method, it is important to pay particular attention to the objectivity factors of criteria weights.
-The author provides an important overview of different weighting methods applicable to multicriteria techniques.
-In the present work, we opted for the multicriteria ABC classification and adopted the Analytic Hierarchy Process \citep{Saaty1987} to assign the weights to the different criteria.
+	In the present work, we opted for the multicriteria ABC classification and adopted the Analytic Hierarchy Process (AHP) \citep{Saaty1987} to assign the weights to the different criteria.
 It is important to note that the Analytic Hierarchy Process derives the weights of the criteria based on the eigenvector of a pairwise comparison matrix which is constructed manually according to an empirical evaluation.
@@
 The autor reports that a software package supporting the AHP, called Expert Choice, for the IBM PC, was used in his work for making eigenvector calculations and guide the decision maker to improve matriz inconsistency if needed.
-During the execution of the work we present in this paper, we found that there is a strong difficulty in for calculation of the eigenvector, as well as for the construction of consistent pairwise comparison matrices and we had no access to the Expert Choice software package, so we developed an open source COPSolver library for Analitic Hierarch Process and multicriteria ABC classification based on a new a method for forcing the consistency of such matrices.
-We present this method in this paper.
-The Eigen library from eigen.tuxfamily.org was used for eigenvector calculation.
+During the execution of the work we present in this paper, we found that there is a strong difficulty in calculation of the eigenvector, as well as for the construction of consistent pairwise comparison matrices and we had no access to the Expert Choice software package, so we developed an open source COPSolver library for Analitic Hierarch Process and multicriteria ABC classification based on a simple algorithm for forcing the consistency of such matrices.
+We present this algorithm in this paper.
+The Eigen library from eigen.tuxfamily.org was coupled to COPSolver for eigenvectors calculation of the matrices.
 Also we identified that the assignment of weights to ABC classification can be done using different criteria and we observed that such assignment generates a bias in the multicriteria ABC classification.
-Therefore we also developed a new methodology for assigning weights in a balanced way for ABC classification and we proposed a new multicriteria ABC classification method, that we aplyed on COPSolver library.
-We also presente both methods on this paper and an in-depth analysis of the results found by the library we developed for COPSolver.
+Therefore we also developed a new methodology for assigning weights in a balanced way for ABC classification and we proposed a new multicriteria weighting equation for the multicriteria classification COPSolver library.
+We also present both propositions on this paper and an in-depth analysis of the results found by the new library we developed for COPSolver.
 
@@
 
-    Inventory classification problem is also a decision problem since we want to decide what is the better system and criteria for clustering the different inventory itens.
-
-In our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification.
+As discussed earlier, in our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification.
 

### 2024-02-17 accepted/CONEM2024/FCPCOM/CONEM2024.tex
work in progress - improving introduction

--- 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
@@
 
-    \subsection{Pairwise Comparisons Matrix and Consistency Rate}
+	As stated by \cite{Kiran2019}, "production planning and control (PP\&C) ...
+is responsible for ensuring the availability \emph{of} all materials, part of assembly at the right time, at the right place, and in \emph{the} right quantities to enable the progress of operations according to the predetermined schedules at the minimum possible costs." The author warns that factories producing large volumes of standardized products need uncomplicated production control techniques, but factories producing a variety of products and product mixes also need meticulous control with complex production control techniques.
+In the latter case, prior strategic planning becomes impressible for better use of the productive capacity and to avoid investment losses in unnecessary or unprofitable material and, given the wide variety of products, it's crucial to start any strategic planning by understanding the importance of all products marked by the campany.
+
+	In this work, we present a study with three companies from three different sectors, which market a wide variety of products, in some cases, highly personalized products.
+The interest of this study is to identify the main products, that is, the products that company must prioritize, so that this information can guide the strategic planning.
+Also, we identify the need to consider several criteria for such a classification, therefore we used a multicriteria approach.
+
+	The importance of multicriteria classification for inventory management has been widely emphasized in scientific literature and several multicriteria methods have been used, being ABC multicriteria classification with Analytical Hierarchy Process one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}.
+But just a few recent works talk about multicriteria classification applied to strategic planning \citep[\emph{e.g.},][]{BarbosaDePaula2022, Pereira2023, MarianoRibeiro2023}, and the multicriteria methods applied are diverse.
+\citet{Odu2019} emphasize that, when applying some multicriteria method, it is important to pay particular attention to the objectivity factors of criteria weights.
+The author provides an important overview of different weighting methods applicable to multicriteria techniques.
+
+	In the present work, we opted for the multicriteria ABC classification and adopted the Analytic Hierarchy Process (AHP) \citep{Saaty1987} to assign the weights to the different criteria.
+It is important to note that the Analytic Hierarchy Process derives the weights of the criteria based on the eigenvector of a pairwise comparison matrix which is constructed manually according to an empirical evaluation.
+According to \cite{Saaty1987}, this matrix must be antisymmetric and must have a consistency rate of less than 0.1.
+The author reports that a software package supporting the AHP, called Expert Choice, for the IBM PC, was used in his work for making eigenvector calculations and guiding the decision maker to improve matrix inconsistency if needed.
+During the execution of the work we present in this paper, we found that there is a strong difficulty in the calculation of the eigenvector, as well as for the construction of consistent pairwise comparison matrices and we had no access to the Expert Choice software package, so we developed an open source COPSolver library for Analytic Hierarch Process and multicriteria ABC classification based on a simple algorithm for forcing the consistency of such matrices.
+We present this algorithm in this paper.
+The Eigen library from eigen.tuxfamily.org was coupled to COPSolver for eigenvectors calculation of the matrices.
+Also, we identified that the assignment of weights to ABC classification can be done using different criteria and we observed that such an assignment generates a bias in the multicriteria ABC classification.
+Therefore we also developed a new methodology for assigning weights in a balanced way for ABC classification and we proposed a new multicriteria weighting equation for the multicriteria classification COPSolver library.
+We also present both propositions in this paper and an in-depth analysis of the results found by the new library developed for COPSolver.
 
@@
 
-In our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification.
+As discussed earlier, in our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification.
 

### 2024-02-19 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating paper - introduction - almost finished

@@
 
-	As stated by \cite{Kiran2019}, "production planning and control (PP\&C) ...
-is responsible for ensuring the availability \emph{of} all materials, part of assembly at the right time, at the right place, and in \emph{the} right quantities to enable the progress of operations according to the predetermined schedules at the minimum possible costs." The author warns that factories producing large volumes of standardized products need uncomplicated production control techniques, but factories producing a variety of products and product mixes also need meticulous control with complex production control techniques.
-In the latter case, prior strategic planning becomes impressible for better use of the productive capacity and to avoid investment losses in unnecessary or unprofitable material and, given the wide variety of products, it's crucial to start any strategic planning by understanding the importance of all products marked by the campany.
+	"Manufacturing decisions can be classified into three categories: strategic, tactical and operational ...
+Operational decisions pertaining to issues such as order processing, detailed production scheduling, follow
+up, maintenance routines, and inventory control rules, drive the day to day activities" \citep{Singhal2013}.
+"In today’s competitive market the diversity in customer’s need have resulted in a high level of variability in the products which have to be manufactured" \citep{Ebrahimi2014}.
+Such diversity brings to light the need for the use of complex techniques for production management, especially at the oprational decision level \citep{Kiran2019}.
+In such a scenario prior strategic operational planning becomes impressible for better use of the productive capacity and to avoid investment losses in unnecessary or unprofitable material and, given the wide variety of products, it's crucial to start any strategic planning by understanding the importance of all products marked by the campany.
+
+	One of the approaches that has been widely applied to clustering products according to their importance is the multicriteria ABC classification.
+The importance of multicriteria ABC classification for inventory management has been widely emphasized in scientific literature and several multicriteria methods have been presented, being the Analytical Hierarchy Process one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}.
+Some recent studies also emphasize the importance of applying multicriteria analysis to strategic planning \citep[\emph{e.g.},][]{BarbosaDePaula2022, Pereira2023, MarianoRibeiro2023}.
+\citet{Odu2019} emphasize that, when applying some multicriteria method, it is important to pay particular attention to the objectivity factors of criteria weights.
+The author provides an important overview of different weighting methods applicable to multicriteria techniques.
 
@@
 The interest of this study is to identify the main products, that is, the products that company must prioritize, so that this information can guide the strategic planning.
-Also, we identify the need to consider several criteria for such a classification, therefore we used a multicriteria approach.
-
-	The importance of multicriteria classification for inventory management has been widely emphasized in scientific literature and several multicriteria methods have been used, being ABC multicriteria classification with Analytical Hierarchy Process one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}.
-But just a few recent works talk about multicriteria classification applied to strategic planning \citep[\emph{e.g.},][]{BarbosaDePaula2022, Pereira2023, MarianoRibeiro2023}, and the multicriteria methods applied are diverse.
-\citet{Odu2019} emphasize that, when applying some multicriteria method, it is important to pay particular attention to the objectivity factors of criteria weights.
-The author provides an important overview of different weighting methods applicable to multicriteria techniques.
-
-	In the present work, we opted for the multicriteria ABC classification and adopted the Analytic Hierarchy Process (AHP) \citep{Saaty1987} to assign the weights to the different criteria.
+We opted for the method ABC for multicriteria classification and adopted the Analytic Hierarchy Process (AHP) \citep{Saaty1987} to assign the weights to the different criteria.
 It is important to note that the Analytic Hierarchy Process derives the weights of the criteria based on the eigenvector of a pairwise comparison matrix which is constructed manually according to an empirical evaluation.
@@
 The Eigen library from eigen.tuxfamily.org was coupled to COPSolver for eigenvectors calculation of the matrices.
-Also, we identified that the assignment of weights to ABC classification can be done using different criteria and we observed that such an assignment generates a bias in the multicriteria ABC classification.
+Also, we identified that the assignment of weights to ABC classification can be done using different criteria types (cumulative sum, qualitative, and binary) depending on each specific criterion chosen, and we observed that such an assignment generates a bias in the multicriteria ABC classification.
 Therefore we also developed a new methodology for assigning weights in a balanced way for ABC classification and we proposed a new multicriteria weighting equation for the multicriteria classification COPSolver library.
 We also present both propositions in this paper and an in-depth analysis of the results found by the new library developed for COPSolver.
+
+		Seeking to present the scientific contributions and the results of this work, the next sections are organized as follows: Section 2 presents the algorithm developed to force the consistency of pairwise comparison matrices.
+Section 3 explains the proposed approach for assigning the weights for ABC classification and the equation for calculating the weights for the multicriteria classification.
+Section 4 gives a brief presentation of the COPSolver software and the new library developed for multicriteria classification.
+Section 5 presents the results as well as a brief analysis informing about the precautions that should be adopted in the construction of the COPSolver input file for multicritéria classification.
+Section 6 reports the credits in carrying out this work.
+Sections 7 and 8 conclude this article with the conclusions and acknowledgements, respectively.
 

### 2024-02-19 accepted/CONEM2024/FCPCOM/CONEM2024.tex
introduction - 99 overall score

@@
 up, maintenance routines, and inventory control rules, drive the day to day activities" \citep{Singhal2013}.
+Manufacturing decisions are closely related to sales decisions.
+Both have a significant impact on corporate benefits.
 "In today’s competitive market the diversity in customer’s need have resulted in a high level of variability in the products which have to be manufactured" \citep{Ebrahimi2014}.
-Such diversity brings to light the need for the use of complex techniques for production management, especially at the oprational decision level \citep{Kiran2019}.
-In such a scenario prior strategic operational planning becomes impressible for better use of the productive capacity and to avoid investment losses in unnecessary or unprofitable material and, given the wide variety of products, it's crucial to start any strategic planning by understanding the importance of all products marked by the campany.
+Such diversity brings to light the need for the use of complex techniques for production management, especially at the operational decision level \citep{Kiran2019}.
+In such a scenario, prior optimized operational planning becomes impressible for better use of the productive capacity and to avoid investment losses in unnecessary or unprofitable material.
+And, given the wide variety of products, it is crucial to start any planning by understanding the importance of all products marked by the company.
 
-	One of the approaches that has been widely applied to clustering products according to their importance is the multicriteria ABC classification.
-The importance of multicriteria ABC classification for inventory management has been widely emphasized in scientific literature and several multicriteria methods have been presented, being the Analytical Hierarchy Process one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}.
+	One of the approaches that widely applied to clustering products according to their importance is the multicriteria ABC classification.
+The scientific literature broadly emphasizes the value of multicriteria ABC classification for inventory management and presents several multicriteria methods.
+The Analytical Hierarchy Process is one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}.
 Some recent studies also emphasize the importance of applying multicriteria analysis to strategic planning \citep[\emph{e.g.},][]{BarbosaDePaula2022, Pereira2023, MarianoRibeiro2023}.
-\citet{Odu2019} emphasize that, when applying some multicriteria method, it is important to pay particular attention to the objectivity factors of criteria weights.
-The author provides an important overview of different weighting methods applicable to multicriteria techniques.
+\citet{Odu2019} emphasizes that, when applying some multicriteria methods, it is crucial to pay particular attention to the objectivity factors of criteria weights.
+The author provides a detailed overview of different weighting methods applicable to multicriteria techniques.
 
 		In this work, we present a study with three companies from three different sectors, which market a wide variety of products, in some cases, highly personalized products.
-The interest of this study is to identify the main products, that is, the products that company must prioritize, so that this information can guide the strategic planning.
+The interest of this study is to identify the principal products, that is, the products that each company must prioritize so that this information can guide the optimized operational planning.
 We opted for the method ABC for multicriteria classification and adopted the Analytic Hierarchy Process (AHP) \citep{Saaty1987} to assign the weights to the different criteria.
-It is important to note that the Analytic Hierarchy Process derives the weights of the criteria based on the eigenvector of a pairwise comparison matrix which is constructed manually according to an empirical evaluation.
-According to \cite{Saaty1987}, this matrix must be antisymmetric and must have a consistency rate of less than 0.1.
+It is important to note that the Analytic Hierarchy Process derives the weights of each criterion based on the eigenvector of a pairwise comparison matrix, which is constructed manually according to an empirical evaluation.
+According to \cite{Saaty1987}, this matrix must be antisymmetric and have a consistency rate of less than 0.1.
 The author reports that a software package supporting the AHP, called Expert Choice, for the IBM PC, was used in his work for making eigenvector calculations and guiding the decision maker to improve matrix inconsistency if needed.
-During the execution of the work we present in this paper, we found that there is a strong difficulty in the calculation of the eigenvector, as well as for the construction of consistent pairwise comparison matrices and we had no access to the Expert Choice software package, so we developed an open source COPSolver library for Analytic Hierarch Process and multicriteria ABC classification based on a simple algorithm for forcing the consistency of such matrices.
+During the execution of the work we present in this paper, we found that there is a substantial difficulty in the calculation of the eigenvector, as well as in the construction of consistent pairwise comparison matrices.
+Since we had no access to the Expert Choice software package, we developed an open-source COPSolver library for the Analytic Hierarchy Process and multicriteria ABC classification based on a simple algorithm for forcing the consistency of such matrices.
 We present this algorithm in this paper.
-The Eigen library from eigen.tuxfamily.org was coupled to COPSolver for eigenvectors calculation of the matrices.
-Also, we identified that the assignment of weights to ABC classification can be done using different criteria types (cumulative sum, qualitative, and binary) depending on each specific criterion chosen, and we observed that such an assignment generates a bias in the multicriteria ABC classification.
-Therefore we also developed a new methodology for assigning weights in a balanced way for ABC classification and we proposed a new multicriteria weighting equation for the multicriteria classification COPSolver library.
-We also present both propositions in this paper and an in-depth analysis of the results found by the new library developed for COPSolver.
+We coupled the Eigen library from eigen.tuxfamily.org to COPSolver for the eigenvectors calculation of the matrices.
+Also, we identified that it is possible to use different criteria types (cumulative sum, qualitative, and binary) when assigning weights to ABC classification, depending on each specific criterion chosen, and we observed that such an assignment generates a bias in the multicriteria ABC classification Therefore, we also developed a new methodology for assigning weights in a balanced way for ABC classification, and we proposed a new multicriteria weighting equation for the multicriteria classification COPSolver library.
+We also present both propositions in this paper, as well as an in-depth analysis of the results found by the new library developed for COPSolver.
 
-		Seeking to present the scientific contributions and the results of this work, the next sections are organized as follows: Section 2 presents the algorithm developed to force the consistency of pairwise comparison matrices.
-Section 3 explains the proposed approach for assigning the weights for ABC classification and the equation for calculating the weights for the multicriteria classification.
-Section 4 gives a brief presentation of the COPSolver software and the new library developed for multicriteria classification.
-Section 5 presents the results as well as a brief analysis informing about the precautions that should be adopted in the construction of the COPSolver input file for multicritéria classification.
+		The rest of this paper is structured as follows.
+Section 2 presents the algorithm developed to force the consistency of pairwise comparison matrices.
+Section 3 explains the proposed approach for assigning the weights for the ABC classification and the equation for calculating the weights for the multicriteria classification.
+Section 4 briefly exhibits COPSolver software and the new library developed for multicriteria classification.
+Section 5 presents the results and analysis informing about the precautions someone must have when elaborating the COPSolver input file for multicritéria classification.
 Section 6 reports the credits in carrying out this work.
-Sections 7 and 8 conclude this article with the conclusions and acknowledgements, respectively.
+Sections 7 and 8 conclude this article with conclusions and acknowledgments, respectively.
 
@@
 As we can see in the adjusted matrix, the algorithm quickly corrects these inconsistencies and then the weight vector.
+
+	\section{DISCUSSION AND FINAL REMARKS}
 

### 2024-02-19 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating introduction - small corrections

@@
 Manufacturing decisions are closely related to sales decisions.
-Both have a significant impact on corporate benefits.
-"In today’s competitive market the diversity in customer’s need have resulted in a high level of variability in the products which have to be manufactured" \citep{Ebrahimi2014}.
-Such diversity brings to light the need for the use of complex techniques for production management, especially at the operational decision level \citep{Kiran2019}.
+"In today’s competitive market the diversity in customer’s need have resulted in a high level of variability in the products which have to be manufactured" \citep{Ebrahimi2014} or acquired from other companies.
+Such diversity brings to light the need for the use of complex techniques for purchasing / production management, especially at the operational decision level \citep{Kiran2019}.
 In such a scenario, prior optimized operational planning becomes impressible for better use of the productive capacity and to avoid investment losses in unnecessary or unprofitable material.
@@
 We coupled the Eigen library from eigen.tuxfamily.org to COPSolver for the eigenvectors calculation of the matrices.
-Also, we identified that it is possible to use different criteria types (cumulative sum, qualitative, and binary) when assigning weights to ABC classification, depending on each specific criterion chosen, and we observed that such an assignment generates a bias in the multicriteria ABC classification Therefore, we also developed a new methodology for assigning weights in a balanced way for ABC classification, and we proposed a new multicriteria weighting equation for the multicriteria classification COPSolver library.
+Also, we identified that it is possible to use different criteria types (cumulative sum, qualitative, and binary) when assigning weights to ABC classification, depending on each specific criterion chosen, and we observed that such an assignment generates a bias in the multicriteria ABC classification.
+Therefore, we also developed a new methodology for assigning weights in a balanced way for ABC classification, and we proposed a new multicriteria weighting equation for the multicriteria classification COPSolver library.
 We also present both propositions in this paper, as well as an in-depth analysis of the results found by the new library developed for COPSolver.
@@
 Section 4 briefly exhibits COPSolver software and the new library developed for multicriteria classification.
-Section 5 presents the results and analysis informing about the precautions someone must have when elaborating the COPSolver input file for multicritéria classification.
+Section 5 presents the results and analysis informing about the precautions someone must have when elaborating the COPSolver input file for multicriteria classification.
 Section 6 reports the credits in carrying out this work.

### 2024-02-26 accepted/CONEM2024/FCPCOM/CONEM2024.tex
Algorithm for forcing low consistency rate

@@
 
+\usepackage{algorithm}
 \usepackage{algpseudocode}
@@
 
+    Algorithm (\ref{alg:forceConsistency}) illustrates the method developed to reduce the consistency rate ($CR$).
+This algorithm takes as input the pairwise comparison matrix ($M[m_{ij}]$) and the tolerance ($tol$) defined for the consistency rate and returns the matrix adjusted as well as the $CR$ of this new matrix (see \cite{Saaty1987} for more information on calculating the consistency rate).
+
+\begin{algorithm}
+\caption{forceConsistency($tol, M[m_{ij}]$)}\label{alg:forceConsistency}
+	\begin{algorithmic}
+	\Require $tol, M[m_{ij}]$
+	\Ensure $CR < tol$
+
+	\State $n \gets size(M[m_{ij}])$
+	\State $CR \gets$ consistencyRate($M[m_{ij}]$)
+
+	\State topLeftCorner( $CR, tol, M[m_{ij}]$)
+
+	\State bottomLeftCorner( $CR, tol, M[m_{ij}]$)
+
+	\State \textbf{return} $CR, tol, M[m_{ij}]$
+
+\end{algorithmic}
+\end{algorithm}
+
+The topLeftCorner() function (alg.
+\ref{alg:topLeftCorner}) performs a peer-to-peer comparison of each element of the pairwise matrix starting from the third row, $M[m_{\{sz\}j}]_{sz=3}^{n}$, with each element of the matrix $M[m_{jk}]_{j=1, k=j+1}^{n-1,n}$.
+In this comparison, the consistency of each pair is verified according to alg.
+(\ref{alg:consistencyCheck}).
+If any inconsistency is found, the value of one of the elements is reduced or increased, seeking to improve the consistency rate.
+Initially, the reduction of values is done through the reduce() function.
+If, after the reduction, the convergence rate is still greater than the tolerance, the increment of values is made through the increase() function.
+
+\begin{algorithm}
+\caption{consistency checking}\label{alg:consistencyCheck}
+	\begin{algorithmic}
+	\Require $M[m_{ij}]$
+
+	\If{$m_{\{sz\}j} * m_{jk} = m_{\{sz\}k}$}
+		\State $consistent \gets 1$ \Comment{values are consistent}
+	\Else
+		\State $consistent \gets 0$ \Comment{values are not consistent}
+	\EndIf
+
+	\State \textbf{return} $consistent$
+
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{topLeftCorner( $CR, tol, M[m_{ij}]$)}\label{alg:topLeftCorner}
+	\begin{algorithmic}
+	\Require $CR, tol, M[m_{ij}]$
+
+	\If{$CR \ge tol$}
+		\For{$sz \gets 3, n $}
+			\For{$j \gets 0, n-1 $}
+				\For{$k \gets j+1, n $}
+					\State $g \gets 0$
+					\State $s \gets 0$
+					\If{$m_{\{sz\}j}*m_{jk} > m_{\{sz\}k}$}
+						\State $g \gets j$
+						\State $s \gets k$
+					\ElsIf{$m_{\{sz\}j}*m_{jk} < m_{\{sz\}k}$}
+						\State $g \gets k$
+						\State $s \gets j$
+					\EndIf
+
+					\If{$g > 0 \textrm{ or } s > 0$}
+
+						\State reduce($CR, tol, sz, g, s, M[m_{ij}]$)
+
+						\If{$CR \le tol$}
+							\State \textbf{break}
+						\ElsIf{$m_{\{sz\}g} > m_{\{sz\}s}$}
+							\State increase(sz,g,s)
+							\If{$CR \le tol$}
+								\State \textbf{break}
+							\EndIf
+						\EndIf
+					\EndIf
+				\EndFor
+				\If{$CR \le tol$}
+					\State \textbf{break}
+				\EndIf
+			\EndFor
+				\If{$CR \le tol$}
+					\State \textbf{break}
+				\EndIf	
+		\EndFor
+	\EndIf
+
+	\State \textbf{return} $CR, tol, M[m_{ij}]$
+
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{reduce($CR, tol, n, g, s, M[m_{ij}]$)}\label{alg:reduce}
+	\begin{algorithmic}
+	\Require $CR, tol, n, g, s, M[m_{ij}]$
+
+	\While{$m_{ng}*m_{gs} > m_{ns} \textrm{ and } m_{ng} \neq 0$}
+		\State $auxCR \gets CR$
+		\State $m_{ng} ++$
+		\State $m_{gn} --$
+
+		\State $CR \gets$ consistencyRate($M[m_{ij}]$)
+
+		\If{$CR > auxCR$}
+			\State $m_{ng} --$
+			\State $m_{gn} ++$
+			\State $CR \gets$ consistencyRate($M[m_{ij}]$)
+			\State \textbf{break}
+
+		\ElsIf{$CR <= tol$}
+			\State \textbf{break}
+		\EndIf
+\EndWhile
+
+\State \textbf{return} $CR, tol, M[m_{ij}]$
+
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{increase($CR, tol, n, g, s, M[m_{ij}], it(M[m_{ij}])$)}\label{alg:increase}
+	\begin{algorithmic}
+	\Require $CR, tol, n, g, s, M[m_{ij}], it(M[m_{ij}])$
+
+	\While{$m_{ng}*m_{gs} < m_{ns} \textrm{ and } it(m_{ng}) \neq n-1$}
+		\State $auxCR \gets CR$
+		\State $m_{ns} ++$
+		\State $m_{sn} --$
+
+		\State $CR \gets$ consistencyRate($M[m_{ij}]$)
+
+		\If{$CR > auxCR$}
+			\State $m_{ns} --$
+			\State $m_{sn} ++$
+			\State $CR \gets$ consistencyRate($M[m_{ij}]$)
+			\State \textbf{break}
+
+		\ElsIf{$CR <= tol$}
+			\State \textbf{break}
+		\EndIf
+\EndWhile
+
+\State \textbf{return} $CR, tol, M[m_{ij}]$
+
+\end{algorithmic}
+\end{algorithm}
+
+The bottomLeftCorner() function is similar to the topLeftCorner() function.
+In the topLeftCorner() function, the peer-to-peer comparison starts with the elements of the third row ($M[m_{\{sz\}j}]_{sz=3}$), and then the elements of the next rows are evaluated, following the order from top to bottom.
+In the case of the bottomLeftCorner() function, on the other hand, the pair-by-pair comparison is made starting with the elements of the anti-penultimate row ($sz = n-3$), then the elements of the previous rows are evaluated, following the order from bottom to top.
+
+\begin{algorithm}
+\caption{bottomLeftCorner( $CR, tol, M[m_{ij}]$)}\label{alg:bottomLeftCorner}
+	\begin{algorithmic}
+	\Require $CR, tol, M[m_{ij}]$
+
+	\If{$CR \ge tol$}
+		\For{$sz \gets n-2, 1 $}
+			\For{$j \gets 0, n-3 $}
+				\For{$k \gets j+1, n-2 $}
+					\State $g \gets 0$
+					\State $s \gets 0$
+					\If{$m_{\{sz-1\}j}*m_{jk} > m_{\{sz-1\}k}$}
+						\State $g \gets j$
+						\State $s \gets k$
+					\ElsIf{$m_{\{sz-1\}j}*m_{jk} < m_{\{sz-1\}k}$}
+						\State $g \gets k$
+						\State $s \gets j$
+					\EndIf
+
+					\If{$g > 0 \textrm{ or } s > 0$}
+
+						\State reduce(sz-1,g,s)
+
+						\If{$CR <= tol$}
+							\State \textbf{break}
+						\ElsIf{$m_{\{sz-1\}g} > m_{\{sz-1\}s}$}
+							encrease(sz-1,g,s)
+							\If{$CR <= tol$}
+								\State \textbf{break}
+							\EndIf
+						\EndIf
+					\EndIf
+				\EndFor
+				\If{$CR <= tol$}
+					\State \textbf{break}
+				\EndIf
+			\EndFor
+				\If{$CR <= tol$}
+					\State \textbf{break}
+				\EndIf	
+		\EndFor
+	\EndIf
+
+	\State \textbf{return} $CR, tol, M[m_{ij}]$
+
+\end{algorithmic}
+\end{algorithm}
+
     \section{ON MULTICRITERIA ABC CLASSIFICATION}
@@
 	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of Willians.
-A single measure was adopted for these two criteria (lead time billing  weight) dividing the billing weight by the complement of the lead time weight.
+A single measure was adopted for these two criteria (lead time billing  weight) dividing the billing by the complement of the lead time for each product and then normalizing the weights.
 
@@
 
-Equation (\ref{eq:weight}) can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:
+Equations (\ref{eq:leadTimeBillingWeight}) and (\ref{eq:weight}) can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:
+
+\begin{equation}
+	\label{eq:leadTimeBillingWeight}
+	LtBW(p) = \frac{\frac{b_p}{1 + (lt^{\max} - lt_p)}}{\sum_{p=1}^{\textrm{NP}}{ \{ \frac{b_p}{1 + (lt^{\max} - lt_p)} \} }}, \quad p= 1,...,\textrm{NP}
+\end{equation}
 
@@
 	\label{eq:weight}
-	\rho_{p} = (wb + wlt) * \frac{b_p}{1 + (lt^{\max} - lt_p)} + \sum_{q=1}^{\textrm{NQ}}{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{1 + (lt^{\max} - lt_{e_{p\sigma_q}})}} + \sum_{b=1}^{\textrm{NB}}{w_{\beta_b}*w_{p\beta_b}}, \quad p= 1,...,\textrm{NP}
+	\rho_{p} = (wb + wlt) * LtBW(p) + \sum_{q=1}^{\textrm{NQ}}{w_{\sigma_q}* LtBW(e_{p\sigma_q})} + \sum_{b=1}^{\textrm{NB}}{w_{\beta_b}*w_{p\beta_b}}, \quad p= 1,...,\textrm{NP}
 \end{equation}
@@
 
-$e_{p\sigma_q}$ is the product lead time billing weight percentage complement equivalent to product $p$ on the criterion $\sigma_q$;
-
 $c$ is the index used to represent each criterion of qualitative or binary type , \quad $c \in \Sigma \cup \textrm{B}$;
 
-$b_p$ is the billing weight percentage of product $p$;
+$LtBW(p)$ is the lead time billing weight of product $p$;
 
-$lt_p$ is the lead time weight percentage of product $p$;
+$b_p$ is the billing of product $p$;
 
-$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing weight percentage complement for product $p$;
+$lt_p$ is the of product $p$;
+
+$wb$ is the multicriteria weight of criterion billing.
+
+$wlt$ is the multicriteria weight of criterion lead time.
+
+$w_{c}$ is the multicriteria weight of criterion $c$.
 
 $w_{pc}$ is the weight percentage of the product $p$ according to criterion $c$;
-
-$wb$ is the weight percentage of criterion billing.
-
-$wlt$ is the weight percentage of criterion lead time.
-
-$w_{c}$ is the weight percentage of criterion $c$.
 

### 2024-02-26 accepted/CONEM2024/FCPCOM/CONEM2024.tex
improving abstract

@@
     \abstract{\textbf{Resumo:} Multicriteria classification is usually a crucial step in the decision-making in the manufacturing management process.
-For such classification, the attribution of weights to the criteria strongly influences the coherence of the categorization.
+For such classification, the attribution of weights to the criteria, as well as the attribution of weights for the products according to each criterion, strongly influences the coherence of the categorization.
 Saaty's Analytic Hierarchy Process (AHP) is an eminent method for assigning weights to multiple criteria.
@@
 However, since criteria's pairwise comparison matrices are usually generated manually and based only on some employee know-how, there is high complexity in elaborating a consistent pairwise matrix, especially when comparing several criteria.
-This paper presents a constructive algorithm that can adjust inconsistent matrices, forcing such matrices to have a better consistency rate.
-We tested this algorithm by applying the AHP method for ABC multicriteria classification to companies in three sectors.
-As a result, we observed that the algorithm adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours, then showing that it is an essential resource for applying the AHP method.}\\
+This paper presents a constructive algorithm that can adjust inconsistent matrices, forcing such matrices to have a better consistency rate, and a new procedure and equation for ABC multicriteria classification.
+We tested the proposed solutions by applying the AHP method for ABC multicriteria classification to companies in three sectors.
+As a result, we observed that the algorith for forcing consistency adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours, and that the procedures develop for multicriteria classification provided consistent results according to analysis of company managers, showing to be essential resources for applying the AHP and ABC multicriteria classification methods.}\\
     %
@@
 \begin{algorithm}
-\caption{forceConsistency($tol, M[m_{ij}]$)}\label{alg:forceConsistency}
+\caption{forceConsistency()}\label{alg:forceConsistency}
 	\begin{algorithmic}
@@
 \ref{alg:topLeftCorner}) performs a peer-to-peer comparison of each element of the pairwise matrix starting from the third row, $M[m_{\{sz\}j}]_{sz=3}^{n}$, with each element of the matrix $M[m_{jk}]_{j=1, k=j+1}^{n-1,n}$.
-In this comparison, the consistency of each pair is verified according to alg.
+In this comparison, the consistency of each pair is verified according to Alg.
 (\ref{alg:consistencyCheck}).
@@
 \begin{algorithm}
-\caption{topLeftCorner( $CR, tol, M[m_{ij}]$)}\label{alg:topLeftCorner}
+\caption{topLeftCorner()}\label{alg:topLeftCorner}
 	\begin{algorithmic}
@@
 \begin{algorithm}
-\caption{reduce($CR, tol, n, g, s, M[m_{ij}]$)}\label{alg:reduce}
+\caption{reduce()}\label{alg:reduce}
 	\begin{algorithmic}
@@
 \begin{algorithm}
-\caption{increase($CR, tol, n, g, s, M[m_{ij}], it(M[m_{ij}])$)}\label{alg:increase}
+\caption{increase()}\label{alg:increase}
 	\begin{algorithmic}
@@
 \begin{algorithm}
-\caption{bottomLeftCorner( $CR, tol, M[m_{ij}]$)}\label{alg:bottomLeftCorner}
+\caption{bottomLeftCorner()}\label{alg:bottomLeftCorner}
 	\begin{algorithmic}

### 2024-02-26 accepted/CONEM2024/FCPCOM/CONEM2024.tex
improving abstract

@@
     % Digitar o resumo
-    \abstract{\textbf{Resumo:} Multicriteria classification is usually a crucial step in the decision-making in the manufacturing management process.
-For such classification, the attribution of weights to the criteria, as well as the attribution of weights for the products according to each criterion, strongly influences the coherence of the categorization.
+    \abstract{\textbf{Resumo:} Multicriteria classification is usually a crucial step in the decision-making in the manufacturing and purchasing management process.
+For such classification, the attribution of weights to the criteria, as well as the attribution of weights to the products according to each criterion, strongly influences the coherence of the categorization.
 Saaty's Analytic Hierarchy Process (AHP) is an eminent method for assigning weights to multiple criteria.
@@
 However, since criteria's pairwise comparison matrices are usually generated manually and based only on some employee know-how, there is high complexity in elaborating a consistent pairwise matrix, especially when comparing several criteria.
-This paper presents a constructive algorithm that can adjust inconsistent matrices, forcing such matrices to have a better consistency rate, and a new procedure and equation for ABC multicriteria classification.
+This paper presents a constructive algorithm that can adjust inconsistent matrices, forcing such matrices to have a better consistency rate and a new procedure and equation for ABC multicriteria classification.
 We tested the proposed solutions by applying the AHP method for ABC multicriteria classification to companies in three sectors.
-As a result, we observed that the algorith for forcing consistency adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours, and that the procedures develop for multicriteria classification provided consistent results according to analysis of company managers, showing to be essential resources for applying the AHP and ABC multicriteria classification methods.}\\
+As a result, we observed that the algorithm for forcing consistency adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours and that the procedures developed for multicriteria classification provided consistent results according to the analysis of company managers, showing to be essential resources for applying the AHP and ABC multicriteria classification methods.}\\
     %

### 2024-02-29 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating

@@
     % Digitar o título
-    \title{CONEM2024-0025\\ ABC  MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX} 
+    \title{CONEM2024-0025\\ NEW ABC  MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX} 
     %
@@
 We tested the proposed solutions by applying the AHP method for ABC multicriteria classification to companies in three sectors.
-As a result, we observed that the algorithm for forcing consistency adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours and that the procedures developed for multicriteria classification provided consistent results according to the analysis of company managers, showing to be essential resources for applying the AHP and ABC multicriteria classification methods.}\\
+As a result, we observed that the algorithm for forcing consistency adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours and that the new solution method developed for multicriteria classification provided consistent results according to the analysis of company managers, showing to be essential resources for applying the AHP and ABC multicriteria classification methods.}\\
     %
@@
                     \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
+                    	\multicolumn{7}{c}{original data} & & \multicolumn{7}{c}{adjusted} \\
+   						\cline {1-15} \\
 						\multicolumn{14}{l}{car mechanics company} \\
@@
 						\cline {1-15} \\
-  						& \multicolumn{7}{c | }{CR = 0.151}  & \multicolumn{7}{c}{CR = 0.096} \\
-  						& \multicolumn{7}{c | }{$w=(0.05, 0.10, 0.14, 0.21, 0.02, 0.45, 0.02\underline{})$}  & \multicolumn{7}{c}{$w = (0.07, 0.16, 0.25, 0.20, 0.02, 0.26, 0.03)$} \\
-   						& lt & sb & rp & cr & cm & bl & ob & lt & sb & rp & cr & cm & np & ob \\
-						lt & 1.00 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.20 & 7.00 & \cellcolor[HTML]{ACE600} 0.11 & 5.00 & 1.00 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 7.00 & \cellcolor[HTML]{ACE600} 0.20 & 5.00 \\
-						sb & 5.00 & 1.00 & 0.33 & \cellcolor[HTML]{ACE600} 0.33 & 5.00 &\cellcolor[HTML]{ACE600}  0.14 & 7.00 & 5.00 & 1.00 & 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 5.00 & \cellcolor[HTML]{ACE600} 0.33 & 7.00 \\
-						rp & 7.00 & 3.00 & 1.00 & \cellcolor[HTML]{ACE600} 0.33 & 5.00 & \cellcolor[HTML]{ACE600} 0.14 & 3.00 & 7.00 & 3.00 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 7.00 & \cellcolor[HTML]{ACE600} 1.00 & 3.00 \\
-						cr & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]		{ACE600} 3.00 & 1.00 & \cellcolor[HTML]{ACE600} 9.00 & \cellcolor[HTML]{ACE600} 0.33 & 9.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 \\
-						cm & 0.14 & 0.20 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.11 & 1.00 & 0.11 & 1.00 & 0.14 & 0.20 & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 0.14 & 1.00 & 0.11 & 1.00 \\
-						np & \cellcolor[HTML]{ACE600} 9.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 3.00 & 9.00 & 1.00 & 9.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 & 1.00 & 9.00 \\
-						ob & 0.20 & 0.14 & 0.33 & 0.11 & 1.00 & 0.11 & 1.00 & 0.20 & 0.14 & 0.33 & 0.11 & 1.00 & 0.11 & 1.00 \\
+  						& \multicolumn{7}{c | }{CR = 0.136}  & \multicolumn{7}{c}{CR = 0.096} \\
+  						& \multicolumn{7}{c | }{$w=(0.07, 0.13, 0.26, 0.03, 0.48, 0.03)$}  & \multicolumn{7}{c}{$w = (0.09, 0.16, 0.35, 0.03, 0.35, 0.03)$} \\
+   						& lt & rp & cr & cm & bl & ob & & lt & rp & cr & cm & bl & ob \\
+						lt & 1.00 & 0.20 & 0.14 & 7.00 & \cellcolor[HTML]{ACE600} 0.11 & 5.00 & & 1.00 & 0.20 & 0.14 & 7.00 & \cellcolor[HTML]{ACE600} 0.14 & 5.00 \\
+						rp & 5.00 & 1.00 & 0.33 & 5.00 & \cellcolor[HTML]{ACE600} 0.14 & 3.00 & & 5.00 & 1.00 & 0.33 & 5.00 & \cellcolor[HTML]{ACE600} 0.33 & 3.00 \\
+						cr & 7.00 & 3.00 & 1.00 & 9.00 & \cellcolor[HTML]{ACE600} 0.33 & 9.00 & & 7.00 & 3.00 & 1.00 & 9.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 \\
+						cm & 0.14 & 0.20 & 0.11 & 1.00 & 0.11 & 1.00 & & 0.14 & 0.20 & 0.11 & 1.00 & 0.11 & 1.00 \\
+						bl & \cellcolor[HTML]{ACE600} 9.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 3.00 & 9.00 & 1.00 & 9.00 & & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 & 1.00 & 9.00 \\
+						ob & 0.20 & 0.33 & 0.11 & 1.00 & 0.11 & 1.00 & & 0.20 & 0.33 & 0.11 & 1.00 & 0.11 & 1.00 \\
 						\cline {1-15} \\
+
 						\multicolumn{14}{l}{plastic packaging manufacturing company} \\
@@
 So, it is more likely that the algorithm changes the weights related to the fourth criterion and the next ones.
-Therefore, the ordering of criteria in the matrix must follow the following rules:
+Therefore, in the preparation of the input file the data of the criteria must be informed in such a way that the criteria are ordered in descending order according to their respective relevance.
 
-\begin{itemize}
-\item the three most relevant criteria for the company are among the first;
-\item the other criteria are ordered from the last to fourth position, in descending order of relevance.
-\end{itemize}
+For the data presented in Table \ref{tab:pairwiseMatrix}, there was no concern with the correct ordering of the criteria.
+Based on the results and previous observations, we have reordered the criteria using their respective weights, initially defined by the normalized eigenvector of the original pairwise comparisons matrix ($w$ in Tab.
+\ref{tab:pairwiseMatrix}).
+Table \ref{tab:pairwiseMatrixReordered} presents the modification of results after altering the criteria ordination on the input data.
 
-For the data presented in Table 1, there was no concern with the correct ordering of the criteria.
-Based on the results and previous observations,  we requested the criteria classification according to its relevance to each company.
-Table 2 presents the modification of results after altering the criteria ordination on the input data.
+\begin{table}[ht]
+            \begin{center}
+                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; bl = billing; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
+                    \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
+   						\multicolumn{7}{c}{original data reordered} & & \multicolumn{7}{c}{adjusted} \\
+   						\cline {1-15} \\
+						\multicolumn{14}{l}{car mechanics company} \\
+						\cline {1-15} \\
+						& \multicolumn{7}{c | }{CR = 0.216}  & \multicolumn{7}{c}{CR = 0.085} \\
+						& \multicolumn{7}{c | }{$w=(0.35, 0.26, 0.18, 0.11, 0.05, 0.03, 0.01)$}  & \multicolumn{7}{c}{$w = (0.37, 0.26, 0.12, 0.12, 0.06, 0.05, 0.02)$} \\
+   						& sb & lt & rp & cr & ob & bl & cm & sb & lt & rp & cr & ob & co & cm \\
+						sb & 1.00 & 3.00 & 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 7.00 & 9.00 & 9.00 & 1.00 & 3.00 								& 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 7.00 & 9.00 & 9.00 \\
+						lt & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 7.00 & 9.00 & 9.00 & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 9.00 & 9.00 \\
+						rp & 0.33 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 9.00 & \cellcolor[HTML]{ACE600} 9.00 & 9.00 & 0.33 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 9.00 \\
+						cr & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 5.00 & \cellcolor[HTML]{ACE600} 9.00 & 9.00 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 9.00 \\
+						ob & 0.14 & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & \cellcolor[HTML]{ACE600} 5.00 & 9.00 & 0.14 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 9.00 \\
+						np & 0.11 & 0.11 & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & 9.00 & 0.11 & 0.11 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & 9.00 \\
+						cm & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 1.00 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 0.11 & 1.00 \\
+						\cline {1-15} \\
+						\multicolumn{14}{l}{furniture trades company} \\
+						\cline {1-15} \\
+  						& \multicolumn{7}{c | }{CR = 0.136}  & \multicolumn{7}{c}{CR = 0.082} \\
+  						& \multicolumn{7}{c | }{$w=(0.48, 0.26, 0.13, 0.07, 0.03, 0.03)$}  & \multicolumn{7}{c}{$w = (0.49, 0.27, 0.11, 0.06, 0.05, 0.03)$} \\
+   						& bl & cr & rp & lt & ob & cm & & bl & cr & rp & lt & ob & cm \\        
+						bl & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 & & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 \\
+						cr & 0.33 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & & 0.33 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 \\
+						rp & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 5.00 & 3.00 & 5.00 & & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & 3.00 & 5.00 \\
+						lt & 0.11 & 0.14 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & \cellcolor[HTML]{ACE600} 5.00 & 7.00 & & 0.11 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 7.00 \\
+						ob & 0.11 & 0.11 & 0.33 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & & 0.11 & 0.11 & 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 \\
+						sb & 0.11 & 0.11 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & & 0.11 & 0.11 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 \\
+						\cline {1-15} \\
+
+						\multicolumn{14}{l}{plastic packaging manufacturing company} \\
+						\cline {1-15} \\
+   						& \multicolumn{7}{c | }{CR = 0.625}  & \multicolumn{7}{c}{CR = 0.094} \\
+   						& \multicolumn{7}{c | }{$w=(0.40, 0.22, 0.12, 0.07, 0.10, 0.10)$}  & \multicolumn{7}{c}{$w = (0.56, 0.21, 0.08, 0.07, 0.07, 0.02)$} \\
+   						& bl & lt & sb & rp & ob & cr & & bl & lt & sb & rp & ob & cr & \\
+						bl & 1.00 & 7.00 & 5.00 & \cellcolor[HTML]{ACE600} 5.00 & 7.00 & \cellcolor[HTML]{ACE600} 3.00 & & 1.00 & 7.00 & 5.00 & \cellcolor[HTML]{ACE600} 9.00 & 7.00 & \cellcolor[HTML]{ACE600} 9.00 \\
+						lt & 0.14 & 1.00 & \cellcolor[HTML]{ACE600} 7.00 & \cellcolor[HTML]{ACE600} 7.00 & 5.00 & \cellcolor[HTML]{ACE600} 0.33 & & 0.14 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 5.00 & \cellcolor[HTML]{ACE600} 9.00 \\
+						sb & 0.20 & \cellcolor[HTML]{ACE600} 0.14 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 3.00 & 5.00 & & 0.20 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 5.00 \\
+						rp & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 0.33 & 5.00 & & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 5.00 \\
+						ob & 0.14 & 0.20 & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 3.00 & 1.00 & 5.00 & & 0.14 & 0.20 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & 5.00 \\
+						cr & \cellcolor[HTML]{ACE600} 0.33 & \cellcolor[HTML]{ACE600} 3.00 & 0.20 & 0.20 & 0.20 & 1.00 & & \cellcolor[HTML]{ACE600} 0.11 & \cellcolor[HTML]{ACE600} 0.11 & 0.20 & 0.20 & 0.20 & 1.00 \\
+				\end{tabular} \label{tab:pairwiseMatrixReordered}
+            \end{center}
+\end{table}
+
+a Tab.
+\ref{tab:pairwiseMatrixAdjusted} apresenta uma comparação dos resultados usando diferentes métodos.
+Na matrix PCM 02, o método para forçar consistência foi aplicado antes da reordenação dos critérios antes.
+Já no caso da matrix PCM 03, o método para forçar consistência foi aplicado após a reordenação dos critérios.
+Esta tabela também mostra a matrix PCM 04 com os ajustes realizados pelo dono da empresa na matrix PCM 01 após verificar os resultados encontrados pelo COPSolver.
+Conforme podemos verificar, o software COPSolver provê uma importante ajuda na elaboração de tabelas de comparação por pares consistentes.
+Verificamos também que é importante realizar a ordenação dos critérios antes de ajustar a matriz buscando uma melhor consistência, pois os pesos atribuídos para os critérios mais relevantes devem ser preferencialmente mantidos.
+Finalmente, observamos que a ordenação dos critérios também ajuda no ajuste manual das matrizes de comparação por pares, já que a apresentação destas tabelas com os critérios ordenados facilita a análise dos pesos.
+Para classificação multicritério dos itens foi utilizada a matriz de comparação por pares PCM 04, tendo em vista a importância da avaliação final realizada pelo funcionário responsável ou dono da empresa.
+
+\begin{table}[ht]
+            \begin{center}
+                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; bl = billing; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
+                    \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
+                        \\
+   						\multicolumn{14}{c}{furniture trades company} \\
+   						\cline {1-15} \\
+   						\multicolumn{7}{l}{PCM 01 - original data reordered} & & \multicolumn{7}{l}{PCM 02 - PCM 01 adjusted and than reordered} \\
+						\cline {1-15} \\
+  						& \multicolumn{7}{c | }{CR = 0.136}  & \multicolumn{7}{c}{CR = 0.096} \\
+  						& \multicolumn{7}{c | }{$w=(0.48, 0.26, 0.13, 0.07, 0.03, 0.03)$}  & \multicolumn{7}{c}{$w = (0.35, 0.35, 0.16, 0.09, 0.03, 0.03)$} \\
+   						& bl & cr & rp & lt & ob & cm & & bl & cr & rp & lt & ob & cm \\        
+						bl & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 & & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 7.00 & 9.00 & 9.00 \\
+						cr & 0.33 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 \\
+						rp & 0.14 & 0.33 & 1.00 & 5.00 & 3.00 & 5.00 & & \cellcolor[HTML]{ACE600} 0.33 & 0.33 & 1.00 & 5.00 & 3.00 & 5.00 \\
+						lt & 0.11 & 0.14 & 0.20 & 1.00 & 5.00 & 7.00 & & \cellcolor[HTML]{ACE600} 0.14 & 0.14 & 0.20 & 1.00 & 5.00 & 7.00 \\
+						ob & 0.11 & 0.11 & 0.33 & 0.20 & 1.00 & 1.00 & & 0.11 & 0.11 & 0.33 & 0.20 & 1.00 & 1.00 \\
+						sb & 0.11 & 0.11 & 0.20 & 0.14 & 1.00 & 1.00 & & 0.11 & 0.11 & 0.20 & 0.14 & 1.00 & 1.00 \\
+						\cline {1-15} \\
+						\multicolumn{7}{l}{PCM 03 - PCM 01 reordered and than adjusted} & & \multicolumn{7}{l}{PCM 01 - manually adjusted based on COPSolver results} \\
+						\cline {1-15} \\
+  						& \multicolumn{7}{c | }{CR = 0.082}  & \multicolumn{7}{c}{CR = 0.082} \\
+  						& \multicolumn{7}{c | }{$w=(0.49, 0.27, 0.11, 0.06, 0.05, 0.03)$}  & \multicolumn{7}{c}{$w = (0.50, 0.25, 0.12, 0.08, 0.03, 0.03)$} \\
+   						& bl & cr & rp & lt & ob & cm & & bl & cr & rp & lt & ob & cm \\        
+						bl & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 & & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & 9.00 \\
+						cr & 0.33 & 1.00 & 3.00 & 7.00 & 9.00 & 9.00 & & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 9.00 & 9.00 \\
+						rp & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & 3.00 & 5.00 & & 0.14 & 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 5.00 & 5.00 \\
+						lt & 0.11 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & \cellcolor[HTML]{ACE600} 1.00 & 7.00 & & 0.11 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & 5.00 & \cellcolor[HTML]{ACE600} 5.00 \\
+						ob & 0.11 & 0.11 & 0.33 & \cellcolor[HTML]{ACE600} 1.00 & 1.00 & \cellcolor[HTML]{ACE600} 3.00 & & 0.11 & 0.11 & \cellcolor[HTML]{ACE600}  0.20 & 0.20 & 1.00 & 1.00 \\
+						sb & 0.11 & 0.11 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & & 0.11 & 0.11 & 0.20 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & 1.00 \\
+						\cline {1-15} \\
+				\end{tabular} \label{tab:pairwiseMatrixAdjusted}
+            \end{center}
+	\end{table}
 
@@
 
-	\section{DISCUSSION AND FINAL REMARKS}
+\subsection{Analysis on the New ABC Multicriteria Classification Method}
 
-    \section{REFERENCES}
+\begin{table}[h!]
+\begin{center}
+\begin{small}
+\begin{tabular}[c]{l r r | l r r r r}
+\multicolumn{8}{l}{car mechanics company} \\
+\cline {1-8} \\
+\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
+\multicolumn{3}{c |}{cutoff}  & \multicolumn{5}{c}{75 sales between October 2020 and July 2023} \\
+\multicolumn{3}{c |}{0.35 \%; 0.70 \%} & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
+A &  10 & 23.81 \% & smooth & 18.75 \% &  20.00 \% & 16.67 \% & 0 \%\\
+B &  15 & 35.71 \% & slow-moving & 6.25 \% & 10.00 \% & 0.00 \% & 0 \%\\
+C &  17 & 40.48 \% & sporadic & 75.00 \% & 70.00 \% & 83.33 \% & 0 \% \\
+\cline {1-8} \\
+\multicolumn{8}{l}{furniture trades company} \\
+\cline {1-8} \\
+\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
+\multicolumn{3}{c |}{cutoff:} &\\
+\multicolumn{3}{c |}{0.35 \%; 0.70 \%}& & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
+A &  26 & 10.24 \% & smooth & 31.58 \% &  73.08 \% & 30.00 \% & 24.82 \%\\
+B &  80 & 31.50 \% & slow-moving & 18.62 \% & 19.23 \% & 33.75 \% & 9.93 \%\\
+C & 148 & 58.27 \% & sporadic & 49.80 \% & 7.69 \% & 36.25 \% & 65.25 \% \\
+\cline {1-8} \\
+ \multicolumn{8}{l}{plastic packaging manufacturing company}\\
+\cline {1-8} \\
+\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
+\multicolumn{3}{c |}{cutoff:} & \multicolumn{5}{c}{5,967 sales between November 2019 and February 2023}\\
+\multicolumn{3}{c |}{0.35 \%; 0.70 \%} & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
+A &   128 &  5.49 \% & smooth & 15.31 \% & 22.66 \% & 23.97 \% & 10.42 \%\\
+B &   726 & 31.12 \% & slow-moving & 5.53 \% & 1.56 \% & 8.68 \% & 4.33 \%\\
+C & 1,479 & 63.39 \% & sporadic & 79.16 \% & 75.78 \% & 67.36 \% & 85.25 \% \\
+\cline {1-8} \\
 
-    \section{INTRODUÇÃO}
-
-        O objetivo destas instruções é servir de guia para a formatação dos trabalhos a serem publicados nos anais. Os anais do XII CONEM serão publicados no formato Adobe$^{\small{TM}}$ PDF.
-
-        Os artigos \textcolor{red}{\underline{\textbf{DEVEM}}} ser formatados de acordo com estas instruções.
-O presente arquivo pode ser usado como modelo por usuários do \LaTeX.
-Além disso, pode ser usado como um guia de formatação para usuários de outros processadores de texto.
-
-        Os trabalhos (\textit{draft} e \textit{final paper}) estão limitados a no mínimo \textcolor{red}{\underline{\textbf{6 páginas}}} e no máximo \textcolor{red}{\underline{\textbf{10 páginas}}}, incluindo tabelas e figuras.
-O arquivo final em formato PDF não deve exceder 2 MB.
-
-        A língua oficial do congresso é o português; entretanto serão aceitos manuscritos em espanhol ou em inglês.
-Se o trabalho não for escrito em inglês, o autor deverá incluir o título, os nomes dos autores e afiliações, o resumo e as palavras-chave, traduzidos para o inglês, após a lista de referências, no fim do artigo.
-
-    \section{FORMATO DO TEXTO}
-
-        O artigo deve ser digitado no \textit{template} ``CONEM2024.tex'' e as principais configurações (ex.: formato do papel, tipo e tamanho da fonte do título/Seção/Subseção, espaços, margens, alinhamentos, indentação, etc.) já estão previamente configuradas no arquivo ``abcm.sty''.
-Título, nomes dos autores, instituição, endereço, resumo e palavras-chave devem ser recuados 0,1 cm da margem esquerda e marcados por uma linha preta na borda esquerda com largura de 2$\frac{1}{4}$ pontos.
-
-        Informações suficientes devem ser fornecidas diretamente no texto, ou por referência a trabalhos publicados disponíveis. Notas de rodapé devem ser evitadas.
-
-        Todos os símbolos e notações devem ser definidos no texto.
-As grandezas físicas devem ser expressas no Sistema Internacional de Unidades.
-Os símbolos matemáticos que aparecem no texto devem ser digitados em itálico.
-As unidades devem ser digitadas no estilo romano (ex.: kg, m, MJ, kW/m$^2$, em vez de $kg$, $m$, $MJ$, $kW/m^2$).
-
-        As referências bibliográficas devem ser citadas no texto dando o sobrenome do(s) autor(es) e o ano de publicação, conforme os seguintes exemplos: ``...
-conforme apresentado \citep{MinwooShamim13}.'' ou ``Recentemente, \citet{MinwooShamim13} demonstraram que …''.
-No caso de três ou mais autores, deve ser utilizada a expressão ``\textit{et al.}'', como segue: ``...
-conforme já relatado \citep{Bordalo89}'' e ``Recentemente, \citet{Bordalo89} demonstraram que …''.
-Duas ou mais referências com os mesmos autores e ano de publicação devem ser distinguidas acrescentando ``a'', ``b'', etc., ao ano de publicação.
-No caso da necessidade de citar vários trabalhos em uma mesma chamada, o seguinte formato pode ser utilizado: ``...já se encontra consolidado na literatura (\citeauthor{Coimbra78}, \citeyear{Coimbra78}; \citeauthor{Clark86}, \citeyear{Clark86} e \citeauthor{Sparrow80},  \citeyear{Sparrow80})''.
-
-        As referências devem ser listadas no final do manuscrito de acordo com as instruções fornecidas na Seção 4.
-
-        \textbf{\textcolor[rgb]{0.98,0.00,0.00}{\underline{NÃO NUMERAR AS PÁGINAS.}}}
-
-    \subsection{Títulos e Subtítulos das Seções }
-
-        Os títulos das seções são com letras maiúsculas (Exemplo: \textbf{MODELO MATEMÁTICO}), enquanto os subtítulos só têm as primeiras letras maiúsculas de cada palavra (Exemplo: \textbf{Modelo Matemático}).
-Eles devem ser numerados, usando numerais arábicos separados por pontos, até o máximo de 3 subníveis.
-Uma linha em branco de espaçamento simples deve ser incluída acima e abaixo de cada título ou subtítulo.
-
-    \subsection{Corpo do Texto}
-
-        Conforme já se encontra definido no arquivo ``abcm.sty'', o corpo do texto é justificado e com espaçamento simples.
-A primeira linha de cada parágrafo tem recuo de 0,5 cm a partir da margem esquerda.
-
-        As equações matemáticas são alinhadas à esquerda com recuo de 0,5 cm.
-Elas são referidas como ``Eq.
-(\ref{eq:equation1})'' no meio de uma frase, ou ``Equação (\ref{eq:equation1})'' quando usada no início de uma sentença.
-Os números das equações são numerais arábicos colocados entre parênteses, e alinhados à direita, como mostrado na Eq.
-(\ref{eq:equation1}).
-Os símbolos usados nas equações devem ser definidos imediatamente antes ou depois de sua primeira ocorrência no texto.
-
-        O tamanho da fonte usado nas equações deve ser compatível com o utilizado no texto.
-Todas as grandezas físicas devem ter suas unidades expressas no Sistema Internacional de Unidades, como já mencionado.
-
-        \begin{equation}
-        \sigma = E \cdot \epsilon. \label{eq:equation1}
-        \end{equation}
-
-    	\noindent
-    	onde: $\sigma$ é a tensão, $E$ é o módulo de elasticidade longitudinal (ou Módulo de Young) e $\epsilon$ é a deformação longitudinal.
-
-        As figuras e tabelas devem ser colocadas no texto o mais próximo possível do ponto em que foram mencionadas pela primeira vez e devem ser numeradas consecutivamente em algarismos arábicos.
-As tabelas devem ser centralizadas e referidas por ``Tab.
-\ref{tab:tabexemplo}'' no meio de uma frase, ou por ``Tabela \ref{tab:tabexemplo}'' quando usada no início de uma sentença.
-Uma linha em branco, em espaço simples, deve ser introduzida entre a tabela e o texto subsequente.
-
-        Anotações e valores numéricos incluídos na tabela devem ter tamanhos compatíveis com a fonte usada no texto do trabalho e todas as unidades devem ser expressas no Sistema Internacional de Unidades.
-As unidades são incluídas apenas na primeira linha ou primeira coluna de cada tabela, conforme for apropriado.
-O estilo de borda é livre.
-As explicações, se houver, devem ser fornecidas ao pé das tabelas e não dentro das mesmas.
-
-        \begin{table}[ht]
-            \begin{center}
-                \caption{\textbf{Exemplo de tabela.}}
-                    \begin{tabular}{c|c|c}
-                    \hline
-                    Propriedades do compósito       & CFRC-TWILL        & CFRC-4HS         \\
-                    \hline
-                    Resistência à Flexão  (MPa)     & 209.0 $\pm$ 10.0       & 180.0 $\pm$  15.0    \\
-                    \hline
-                    Módulo de Flexão  (GPa)         & 57.0 $\pm$ 2.8    & 18.0 $\pm$  1.3  \\
-                    \hline
-                    \end{tabular} \label{tab:tabexemplo}
+\end{tabular}
+\caption{ABC multicriteria and demand pattern classifications for three companies (results found by COPSolver)}
+\label{tab:results}
+\end{small}
 \end{center}
@@
 
-        As figuras devem ser centralizadas.
-Elas são referenciadas por ``Fig.
-\ref{fig:figexemplo}'' no meio de uma frase ou por ``Figura \ref{fig:figexemplo}'' quando usada no início de uma sentença.
-Sua legenda deve ser centralizada e localizada imediatamente abaixo da figura.
-As anotações e numerações devem ter tamanhos compatíveis com a fonte usada no texto e todas as unidades devem ser expressas no Sistema Internacional de Unidades.
-As figuras devem ser colocadas o mais próximo possível de sua primeira citação no texto.
-Deve ser deixada uma linha em branco, de espaçamento simples, entre a figura e o texto subsequente.
-
-        \begin{figure}[h]
-            \begin{center}
-                \includegraphics[angle=0, scale=.8]{figura.png}
-            \end{center}
-            \caption{\textbf{Exemplo de figura.}}
-            \label{fig:figexemplo}
-        \end{figure}
-
-        Figuras coloridas e fotografias de alta qualidade podem ser incluídas no trabalho.
-Para reduzir o tamanho do arquivo e preservar a resolução gráfica, os arquivos das imagens podem ser convertidos para o formato GIF (para figuras com até 16 cores) ou para o formato JPEG (alta densidade de cores), antes de serem inseridos no trabalho.
+	\section{DISCUSSION AND FINAL REMARKS}
 
@@
     % REFERÊNCIAS
-    \section{REFERÊNCIAS}
+    \section{REFERENCES}
 
@@
 
-        Referências aceitas incluem: artigos de periódicos, dissertações, teses, artigos publicados em anais de congressos, livros, comunicações privadas e artigos submetidos e aceitos (com fonte identificada) e citações a páginas da internet.
-
-        A lista de referências deve ser uma seção específica denominada Referências, localizada no fim do artigo.
-
-        A primeira linha de cada referência deve ser alinhada à esquerda, sendo que as demais terão recuo já configurado a partir da margem esquerda.
-Todas as referências incluídas na lista devem aparecer como citações no texto do trabalho.
-
-        As referências devem ser postas em ordem alfabética, usando o último nome do primeiro autor, seguida do ano da publicação. Exemplo da lista de referências é apresentado abaixo.
-
         \bibliographystyle{abcm}
         \bibliography{bibliografia}
+
+        \section{CRediT authorship contribution statement} 
+		\label{sec:contributions}
+
+		T.B.
+Fraga: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing – original draft, Writing – review \& editing, Supervision, Project administration.
+B.M.
+Cavalcanti: Investigation.
+A.M.D.Silva: Investigation.
+E.L.R.
+Silva: Investigation.
 
@@
 
- % RESUMO EM INGLES
-
-\noindent{
-   \\ 
-    \begin{tabular}{||p{\textwidth}}
-    \begin{center}
-    \vspace{-.6cm}
-    \title{AFTER FULL PAPER IN PORTUGUESE OR SPANISH, IT IS NECESSARY THE ABSTRACT IN ENGLISH}
-    \end{center}
-    \authors{First Author’s Name, e-mail1$^1$} \\
-    \authors{Second Author’s Name, e-mail$^2$} \\
-    \authors{Third Author’s Name, e-mail$^2$} \\\\
-    \institution{$^1$Institution and address for first author} \\
-    \institution{$^2$Institution and address for second and third authors} \\
-    \\
-    \authors{\textcolor[rgb]{0.98,0.00,0.00}{Same format for other authors and institutions, if any. (\textit{This guidance should be removed from the final paper.})}} \\
-    \\
-    \abstract{\textbf{Abstract:} The purpose of these instructions is to serve as a guide for formatting papers to be published in the Proceedings of the XII CONEM.
-The abstract must describe the objectives, methodology and main conclusions of the article, containing between 300 and 400 words in a single paragraph.
-It should not contain either formulae or bibliographic references.
-The full paper will be published in the proceedings of the event.}\\
-    \\
-    \keywords{\textbf{Keywords:} keyword 1, keyword 2, keyword 3 (up to 5 keywords) }\\
-    \end{tabular}
-}
-
 \end{document}

### 2024-03-12 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating data - small corrections

@@
 
-	One of the approaches that widely applied to clustering products according to their importance is the multicriteria ABC classification.
+	One of the approaches that is widely applied to clustering products according to their importance is the multicriteria ABC classification.
 The scientific literature broadly emphasizes the value of multicriteria ABC classification for inventory management and presents several multicriteria methods.
@@
 In the topLeftCorner() function, the peer-to-peer comparison starts with the elements of the third row ($M[m_{\{sz\}j}]_{sz=3}$), and then the elements of the next rows are evaluated, following the order from top to bottom.
-In the case of the bottomLeftCorner() function, on the other hand, the pair-by-pair comparison is made starting with the elements of the anti-penultimate row ($sz = n-3$), then the elements of the previous rows are evaluated, following the order from bottom to top.
+In the case of the bottomLeftCorner() function, on the other hand, the pair-by-pair comparison is made starting with the elements of the anti-penultimate row ($sz = n-2$), then the elements of the previous rows are evaluated, following the order from bottom to top.
 
@@
 
-As discussed earlier, in our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification.
+As discussed earlier, in our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification, that is, assign weights to each product according to each criterion.
 
@@
 
-	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of Willians.
+The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of \cite{Williams1984}.
 A single measure was adopted for these two criteria (lead time billing  weight) dividing the billing by the complement of the lead time for each product and then normalizing the weights.
 
-In the case of qualitative criteria, the initial ABC classification was made using three weights, one weight assigned to products A, pa, a second weight assigned to products B, pb, and a third weight assigned to products C, pc, where pa > pb > pc.
-For qualitative criteria, pa, pb and pc must be assigned using the following steps:
+In the case of qualitative criteria, the initial ABC classification was made using three weights, one weight assigned to group A products, $w(A)$, a second weight assigned to group B products, $w(B)$, and a third weight assigned to products C, $w(C)$, where $w(A) > w(B) > w(C)$.
+For qualitative criteria, $w(A)$, $w(B)$ and $w(C)$ must be assigned using the following steps:
 
@@
 \item classify products into three groups, A, B and C, for each qualitative criterion;
-\item do pc = 0 for all group C products, for each qualitative criterion;
-\item for each qualitative criterion, do peer-to-peer comparison with the groups A and B and the products ordered according to the lead time billing criterion, answering the following question: the degree of importance of the products of this group to the qualitative criterion is equivalent to what degree of importance of the other product evaluated according to the lead time billing criterion ?;
-\item assign to pa and pb the value of the lead time billing of the product with corresponding importance.
+\item do $w(C)$ = 0 for all group C products, for each qualitative criterion;
+\item for each qualitative criterion, do peer-to-peer comparison with the groups A and B products and the products ordered according to the lead time billing criterion, answering the following question: the degree of importance of the products of this group to the qualitative criterion is equivalent to what degree of importance of the other product evaluated according to the lead time billing criterion ?;
+\item assign to $w(A)$ and $w(B)$ the value of the lead time billing of the product with corresponding importance; 
 \end{itemize}
 
-Equations (\ref{eq:leadTimeBillingWeight}) and (\ref{eq:weight}) can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:
+After the correct assignment of the weights for each product according to each criterion, Eqs.
+(\ref{eq:leadTimeBillingWeight}) and (\ref{eq:weight}) can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:
 
@@
 
-$w_{pc}$ is the weight percentage of the product $p$ according to criterion $c$;
+$w_{pc}$ is the normalized weight percentage of the product $p$ according to criterion $c$;
 
@@
     Table \ref{tab:pairwiseMatrix} presents the modifications made by the software 'COPSolver: library for solving the multicriteria classification problem' in the pairwise comparisons matrix and the consequent changes in the consistency rate (CR) for the data collected from the three companies selected for this study.
+
+    Speaking about the CR, Tab.
+1 clearly shows the inconsistencies before the modification and how the weight modifications made by the algorithm reflect the adjustments of these inconsistencies.
+For example, in the case of the plastic bag manufacturing company, the billing criterion is more important than the criticality criterion and much more valuable than the lead time criterion.
+Also, the criticality criterion is more important than the lead time criterion.
+These statements are coherent.
+However, the vector of the weights of this matrix clearly shows that the criticality criterion is less relevant than the lead time criterion, which is inconsistent with the two first statements.
+The assignment of the other weights related to criteria criticality and lead time causes this inconsistency.
+We can see from the input data matrix that the obsolescence, replaceability, and repairability criteria are more important than the criticality criterion but less valuable than the lead-time criterion.
+According to the initial statement (that criticality is more relevant than lead time), this new statement generates the inconsistency of the pairwise comparisons matrix.
+As we can see in the adjusted matrix, the algorithm quickly corrects these inconsistencies and then the weight vector.
 
@@
 
-As we can see in this table, the pairwise comparison weights are adjusted primarily according to the weights assigned to the first three criteria.
+As we can see in Tab.
+\ref{tab:pairwiseMatrix}, the pairwise comparison weights are adjusted primarily according to the weights assigned to the first three criteria.
 Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria are preserved.
@@
 
-a Tab.
-\ref{tab:pairwiseMatrixAdjusted} apresenta uma comparação dos resultados usando diferentes métodos.
-Na matrix PCM 02, o método para forçar consistência foi aplicado antes da reordenação dos critérios antes.
-Já no caso da matrix PCM 03, o método para forçar consistência foi aplicado após a reordenação dos critérios.
-Esta tabela também mostra a matrix PCM 04 com os ajustes realizados pelo dono da empresa na matrix PCM 01 após verificar os resultados encontrados pelo COPSolver.
-Conforme podemos verificar, o software COPSolver provê uma importante ajuda na elaboração de tabelas de comparação por pares consistentes.
-Verificamos também que é importante realizar a ordenação dos critérios antes de ajustar a matriz buscando uma melhor consistência, pois os pesos atribuídos para os critérios mais relevantes devem ser preferencialmente mantidos.
-Finalmente, observamos que a ordenação dos critérios também ajuda no ajuste manual das matrizes de comparação por pares, já que a apresentação destas tabelas com os critérios ordenados facilita a análise dos pesos.
-Para classificação multicritério dos itens foi utilizada a matriz de comparação por pares PCM 04, tendo em vista a importância da avaliação final realizada pelo funcionário responsável ou dono da empresa.
+Table 3 presents a comparison of the results using different methods on the data provided by the furniture trading company.
+In matrix PCM 02, the method used to force consistency was applied before the reordering of the criteria.
+In the case of matrix PCM 03, the same method was applied after reordering the criteria.
+This table also shows the matrix PCM 04 with adjustments made manually to the matrix PCM 01 after verifying the results found by COPSolver.
+As we can see, the COPSolver software provides an important help in the preparation of consistent pairwise comparison matrices.
+We also found that it is important to perform the ordering of the criteria before adjusting the matrix seeking better consistency, since the weights assigned to the most relevant criteria should preferably be maintained.
+It is possible to verify in these tables that the reordering before the application of the method to force consistency causes the changes to be more distributed and are carried out in the weights relative to the least important criteria.
+Finally, we observe that the ordering of the criteria also helps in the manual adjustment of the pairwise comparison matrices, since the presentation of these tables with the ordered criteria facilitates the analysis of the weights.
+For multicriteria classification of items, the pairwise comparison matrix PCM 03 was used.
+However, in practical cases it is important to have a final assessment of the responsible employee and the matrix used for ABC classification can be a final matrix manually updated by the employee based on the results found by COPSolver.
 
@@
                 \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; bl = billing; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
-                    \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
+                    \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.1cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
                         \\
    						\multicolumn{14}{c}{furniture trades company} \\
-   						\cline {1-15} \\
-   						\multicolumn{7}{l}{PCM 01 - original data reordered} & & \multicolumn{7}{l}{PCM 02 - PCM 01 adjusted and than reordered} \\
-						\cline {1-15} \\
-  						& \multicolumn{7}{c | }{CR = 0.136}  & \multicolumn{7}{c}{CR = 0.096} \\
-  						& \multicolumn{7}{c | }{$w=(0.48, 0.26, 0.13, 0.07, 0.03, 0.03)$}  & \multicolumn{7}{c}{$w = (0.35, 0.35, 0.16, 0.09, 0.03, 0.03)$} \\
+   						\cline {1-14} \\
+   						& \multicolumn{6}{l}{PCM 01 - original data reordered} & & \multicolumn{6}{l}{PCM 02 - PCM 01 adjusted and than reordered} \\
+						\cline {1-14} \\
+  						& \multicolumn{6}{c}{CR = 0.136}  & & \multicolumn{6}{c}{CR = 0.096} \\
+  						& \multicolumn{6}{c}{$w=(0.48, 0.26, 0.13, 0.07, 0.03, 0.03)$} & & \multicolumn{6}{c}{$w = (0.35, 0.35, 0.16, 0.09, 0.03, 0.03)$} \\
    						& bl & cr & rp & lt & ob & cm & & bl & cr & rp & lt & ob & cm \\        
@@
 						sb & 0.11 & 0.11 & 0.20 & 0.14 & 1.00 & 1.00 & & 0.11 & 0.11 & 0.20 & 0.14 & 1.00 & 1.00 \\
-						\cline {1-15} \\
-						\multicolumn{7}{l}{PCM 03 - PCM 01 reordered and than adjusted} & & \multicolumn{7}{l}{PCM 01 - manually adjusted based on COPSolver results} \\
-						\cline {1-15} \\
-  						& \multicolumn{7}{c | }{CR = 0.082}  & \multicolumn{7}{c}{CR = 0.082} \\
-  						& \multicolumn{7}{c | }{$w=(0.49, 0.27, 0.11, 0.06, 0.05, 0.03)$}  & \multicolumn{7}{c}{$w = (0.50, 0.25, 0.12, 0.08, 0.03, 0.03)$} \\
+						\cline {1-14} \\
+						& \multicolumn{6}{l}{PCM 03 - PCM 01 reordered and than adjusted} & & \multicolumn{6}{l}{PCM 01 - manually adjusted based on COPSolver results} \\
+						\cline {1-14} \\
+  						& \multicolumn{6}{c}{CR = 0.082}  & & \multicolumn{6}{c}{CR = 0.082} \\
+  						& \multicolumn{6}{c}{$w=(0.49, 0.27, 0.11, 0.06, 0.05, 0.03)$} & & \multicolumn{6}{c}{$w = (0.50, 0.25, 0.12, 0.08, 0.03, 0.03)$} \\
    						& bl & cr & rp & lt & ob & cm & & bl & cr & rp & lt & ob & cm \\        
@@
 						sb & 0.11 & 0.11 & 0.20 & 0.14 & \cellcolor[HTML]{ACE600} 0.33 & 1.00 & & 0.11 & 0.11 & 0.20 & \cellcolor[HTML]{ACE600} 0.20 & 1.00 & 1.00 \\
-						\cline {1-15} \\
+						\cline {1-14} \\
 				\end{tabular} \label{tab:pairwiseMatrixAdjusted}
@@
 
-Speaking about the CR, Tab. 1 clearly shows the inconsistencies before the modification and how the weight modifications made by the algorithm reflect the adjustments
-of these inconsistencies.
-For example, in the case of the plastic bag manufacturing company, the billing criterion is more important than the criticality criterion and much more valuable than the lead time criterion.
-Also, the criticality criterion is more important than the lead time criterion.
-These statements are coherent.
-However, the vector of the weights of this matrix clearly shows that the criticality criterion is less relevant than the lead time criterion, which is inconsistent with the two first statements.
-The assignment of the other weights related to criteria criticality and lead time causes this inconsistency.
-We can see from the input data matrix that the obsolescence, replaceability, and repairability criteria are more important than the criticality criterion but less valuable than the lead-time criterion.
-According to the initial statement (that criticality is more relevant than lead time), this new statement generates the inconsistency of the pairwise comparisons matrix.
-As we can see in the adjusted matrix, the algorithm quickly corrects these inconsistencies and then the weight vector.
-
-\subsection{Analysis on the New ABC Multicriteria Classification Method}
+\subsection{Analysis On The New ABC Multicriteria Classification Method}
 
@@
 \begin{center}
-\begin{small}
-\begin{tabular}[c]{l r r | l r r r r}
-\multicolumn{8}{l}{car mechanics company} \\
-\cline {1-8} \\
-\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
-\multicolumn{3}{c |}{cutoff}  & \multicolumn{5}{c}{75 sales between October 2020 and July 2023} \\
-\multicolumn{3}{c |}{0.35 \%; 0.70 \%} & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
-A &  10 & 23.81 \% & smooth & 18.75 \% &  20.00 \% & 16.67 \% & 0 \%\\
-B &  15 & 35.71 \% & slow-moving & 6.25 \% & 10.00 \% & 0.00 \% & 0 \%\\
-C &  17 & 40.48 \% & sporadic & 75.00 \% & 70.00 \% & 83.33 \% & 0 \% \\
-\cline {1-8} \\
-\multicolumn{8}{l}{furniture trades company} \\
-\cline {1-8} \\
-\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
-\multicolumn{3}{c |}{cutoff:} &\\
-\multicolumn{3}{c |}{0.35 \%; 0.70 \%}& & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
-A &  26 & 10.24 \% & smooth & 31.58 \% &  73.08 \% & 30.00 \% & 24.82 \%\\
-B &  80 & 31.50 \% & slow-moving & 18.62 \% & 19.23 \% & 33.75 \% & 9.93 \%\\
-C & 148 & 58.27 \% & sporadic & 49.80 \% & 7.69 \% & 36.25 \% & 65.25 \% \\
-\cline {1-8} \\
- \multicolumn{8}{l}{plastic packaging manufacturing company}\\
-\cline {1-8} \\
-\multicolumn{3}{l |}{multc. ABC clssf.} & \multicolumn{5}{c}{demand pattern classification}\\
-\multicolumn{3}{c |}{cutoff:} & \multicolumn{5}{c}{5,967 sales between November 2019 and February 2023}\\
-\multicolumn{3}{c |}{0.35 \%; 0.70 \%} & & \multicolumn{1}{c}{total} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{C}\\
-A &   128 &  5.49 \% & smooth & 15.31 \% & 22.66 \% & 23.97 \% & 10.42 \%\\
-B &   726 & 31.12 \% & slow-moving & 5.53 \% & 1.56 \% & 8.68 \% & 4.33 \%\\
-C & 1,479 & 63.39 \% & sporadic & 79.16 \% & 75.78 \% & 67.36 \% & 85.25 \% \\
-\cline {1-8} \\
+\begin{tabular}[c]{c r r r}
+\multicolumn{4}{c}{new ABC Multcriteria Classification with AHP} \\
+\\
+\multicolumn{4}{l}{car mechanics company} \\
+\cline {1-4} \\
+\multicolumn{4}{c}{75 sales between October 2020 and July 2023} \\
+\\
+  &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\
+A &  10 & 23.81 \% &  80 \% \\
+B &  15 & 35.71 \% &  95 \% \\
+C &  17 & 40.48 \% & 100 \% \\
+\cline {1-4} \\
+\multicolumn{4}{l}{furniture trades company} \\
+\cline {1-4} \\
+\multicolumn{4}{c}{254 sales between } \\
+\\
+ &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\
+
+A &  59 & 23.23 \% &  79.78 \%  \\
+B &  56 & 22.05 \% &  94.81 \% \\
+C & 139 & 54.72 \% & 100.00 \% \\
+\cline {1-4} \\
+
+ \multicolumn{4}{l}{plastic packaging manufacturing company}\\
+\cline {1-4} \\
+\multicolumn{4}{c}{5,967 sales between November 2019 and February 2023} \\
+\\
+ &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\
+
+A &   128 &  5.49 \% & \\
+B &   726 & 31.12 \% & \\
+C & 1,479 & 63.39 \% & \\
+\cline {1-4} \\
 
 \end{tabular}
-\caption{ABC multicriteria and demand pattern classifications for three companies (results found by COPSolver)}
+\caption{ABC multicriteria classifications for three companies (results found by COPSolver)}
 \label{tab:results}
-\end{small}
 \end{center}
@@
 
-        \section{CRediT authorship contribution statement} 
+        \section{CRediT AUTHORSHIP CONTRIBUTION STATEMENT} 
 		\label{sec:contributions}
@@
 
-        Os trabalhos escritos em português ou espanhol devem incluir (após direitos autorais) título, os nomes dos autores e afiliações, o resumo e as palavras-chave, traduzidos para o inglês e a declaração a seguir, devidamente adaptada para o número de autores.
-
-        O(s) autor(es) é(são) o(s) único(s) responsável(is) pelo conteúdo deste trabalho.
+        Os autores são os únicos responsávelis pelo conteúdo deste trabalho.
 

### 2024-03-13 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating

@@
 
+	\section{COPSOLVER}
+
+	COPSolver is a software originally developed by Fraga (2024) to solve several decision and optimization problems, especially in the area of combinatorial optimization.
+The software works with a modular system of libraries, in which each library is developed to solve a single type of specific problem, which makes the software very efficient and robust.
+The structure of the software allows high flexibility in the reuse of already developed codes, as is characteristic of the C++ language.
+The main difference is that in the case of COPSolver, objects are defined as problems, hence the term problem-oriented programming.
+Currently, the configuration file, config.txt, should be used to define the type of problem and the solution methodology addressed, as well as the values of the parameters that must be informed by the user.
+COPSolver software libraries usually use two input files which are config.txt and data.txt.
+For the software to work properly both files must be built following the predefined formats for each specific library.
+
+	To apply the methodology proposed in this article, the module 'COPSolver: library for solving the multicriteria classification problem' is being developed.
+In the case of this library, the configuration file must be prepared according to the template available at https://tbfraga.github.io/COPSolver/benchmarks/clssp/config.txt.
+A model for preparing the data.txt file for this same library is available at https://tbfraga.github.io/COPSolver/benchmarks/clssp/alexia/original-data/data.txt.
+
 	\section{RESULTS AND DISCUSSIONS}
+
+    \subsection{Data Collected}
+
+    To test the methodology proposed in this article, data were collected from three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing.
+Based on the data collected, three benchmarks were developed.
+The date.txt files corresponding to these three benchmarks are available at https://tbfraga.github.io/COPSolver/ benchmarks/.
 
@@
 
-    Speaking about the CR, Tab.
-1 clearly shows the inconsistencies before the modification and how the weight modifications made by the algorithm reflect the adjustments of these inconsistencies.
-For example, in the case of the plastic bag manufacturing company, the billing criterion is more important than the criticality criterion and much more valuable than the lead time criterion.
-Also, the criticality criterion is more important than the lead time criterion.
+    This table clearly shows the inconsistencies before the modification and how the weight modifications made by the algorithm reflect the adjustments of these inconsistencies.
+For example, in the case of the plastic bag manufacturing company, the billing criterion has moderate importance over criticality criterion and very strong importance over lead time criterion.
+Also, the criticality criterion has moderate importance over lead time criterion.
 These statements are coherent.
@@
    						& \multicolumn{7}{c | }{$w=(0.39, 0.10, 0.22, 0.09, 0.12, 0.07)$}  & \multicolumn{7}{c}{$w = (0.50, 0.18, 0.14, 0.06, 0.09, 0.03)$} \\
-   						& np & cr & lt & ob & sb & rp & & bl & cr & lt & ob & sb & rp & \\
-						np & 1.00 & 3.00 & 7.00 & \cellcolor[HTML]{ACE600} 7.00 & 5.00 & \cellcolor[HTML]{ACE600} 5.00 & & 1.00 & 3.00 & 7.00 & \cellcolor[HTML]{ACE600} 9.00 & 5.00 & \cellcolor[HTML]{ACE600} 9.00 \\
+   						& bl & cr & lt & ob & sb & rp & & bl & cr & lt & ob & sb & rp & \\
+						bl & 1.00 & 3.00 & 7.00 & \cellcolor[HTML]{ACE600} 7.00 & 5.00 & \cellcolor[HTML]{ACE600} 5.00 & & 1.00 & 3.00 & 7.00 & \cellcolor[HTML]{ACE600} 9.00 & 5.00 & \cellcolor[HTML]{ACE600} 9.00 \\
 						cr & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.20 & \cellcolor[HTML]{ACE600} 0.20 & & 0.33 & 1.00 & 3.00 & \cellcolor[HTML]{ACE600} 3.00 & \cellcolor[HTML]{ACE600} 1.00 & \cellcolor[HTML]{ACE600} 5.00 \\
@@
 
-As we can see in Tab.
-\ref{tab:pairwiseMatrix}, the pairwise comparison weights are adjusted primarily according to the weights assigned to the first three criteria.
+Table \ref{tab:pairwiseMatrix} also shows that the pairwise comparison weights are adjusted by the solver primarily according to the weights assigned to the first three criteria.
 Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria are preserved.
@@
 
-For the data presented in Table \ref{tab:pairwiseMatrix}, there was no concern with the correct ordering of the criteria.
-Based on the results and previous observations, we have reordered the criteria using their respective weights, initially defined by the normalized eigenvector of the original pairwise comparisons matrix ($w$ in Tab.
-\ref{tab:pairwiseMatrix}).
+For the data presented in Tab.
+\ref{tab:pairwiseMatrix}, there was no concern with the correct ordering of the criteria.
+Based on the results and previous observations, we have reordered the criteria using their respective weights, initially defined by the normalized eigenvector of the original pairwise comparisons matrix, $w$.
 Table \ref{tab:pairwiseMatrixReordered} presents the modification of results after altering the criteria ordination on the input data.
@@
 We also found that it is important to perform the ordering of the criteria before adjusting the matrix seeking better consistency, since the weights assigned to the most relevant criteria should preferably be maintained.
-It is possible to verify in these tables that the reordering before the application of the method to force consistency causes the changes to be more distributed and are carried out in the weights relative to the least important criteria.
+It is possible to verify in these tables that the reordering before the application of the method to force consistency to be carried out in the weights relative to the least important criteria.
 Finally, we observe that the ordering of the criteria also helps in the manual adjustment of the pairwise comparison matrices, since the presentation of these tables with the ordered criteria facilitates the analysis of the weights.
+This is because, when ordered according to the relevance of the criteria, the elements of the pairwise comparison matrix have a trend of increasing order from left to right and decreasing order from top to bottom.
 For multicriteria classification of items, the pairwise comparison matrix PCM 03 was used.

### 2024-03-13 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating

@@
 \usetikzlibrary{shapes.geometric,shapes.misc,shapes.symbols,arrows.meta,graphs,fit,positioning,shadows}
+
+\usepackage[toc,page]{appendix}
+\usepackage{verbatim}
+\usepackage{etoolbox}
+
+\makeatletter
+\patchcmd{\verbatim@input}{\@verbatim}{\scriptsize\@verbatim}{}{}
+\makeatother
 
@@
 
-    To test the methodology proposed in this article, data were collected from three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing.
+    To test the methodology proposed in this article, data were collected for constriction of the pairwise comparison matrix and for ABC classification, using the billing (bl) criterion and other criteria suggested by \cite{FloresWhybark1986}: lead-time (lt); criticality (cr); obsolescence (ob); commonality (cm); substitutability (sb); and repairability (rp).
+To collect the data, we partnered with three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing.
 Based on the data collected, three benchmarks were developed.
@@
 
+For analysis of the proposed new methodology for ABC muticriteria classification, we will be focusing on the presentation and analysis of the data provided by the furniture trades company.
+
+The Tab.
+2 presents a comparison of the results obtained for the data described above, by ABC classification for the criteria billing and lead time billing.
+Appendice A presents the file AHP\_Solution.txt, that presents the results found by the module 'COPSolver: library for solving the multicriteria classification problem' - the results generated from the new ABC multicriteria classification with Analitic Hierarch Process and compare it to the ABC classifications of each criterion, for the items ordered in descending order according to the ABC multicriteria classification.
+
+Based on the results presented in these tables, we can verify that the ABC classification, considering only the billing criterion, does not follow the normal pattern defined by the Pareto rule.
+However, when we use the lead time add-on billing criterion, it is possible to verify that the values are close to what is expected.
+It is also possible to verify in a very clear way that the approach used to measure the weights of the products produces much more relevant results than the simple random assignment of weights.
+This approach reduces the viez effect caused by the imbalance of weights and makes the final result carry important qualitative information provided by the responsible official, assigning the appropriate relevance of the different products, as well as the criteria analyzed.
+
+Based on an evaluation of the final results by the participating company, it was possible to verify that these results were very coherent, offering the company very relevant information for the identification of products whose inventory must be maintained, receiving greater attention from the company, as well as for the adoption of more appropriate procedures for the correct control of the different items marketed by the company.
+
 \begin{table}[h!]
@@
 
+        \begin{appendices}
+		\setcounter{section}{0}
+		\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
+		\makeatletter
+		\addtocontents{toc}{%
+		\begingroup
+		\let\protect\l@section\protect\l@subsection
+}
+
+	\section{AHP\_solution.txt}
+
+	\verbatiminput{files/AHP_solution.txt}
+
+	\addtocontents{toc}{\endgroup}
+	\end{appendices}
+
 \end{document}

### 2024-03-13 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating

@@
 \usepackage{etoolbox}
+
+\usepackage{pdfpages}
+
+\usepackage{graphicx}
 
@@
 The date.txt files corresponding to these three benchmarks are available at https://tbfraga.github.io/COPSolver/ benchmarks/.
+Appendice A presents the data.txt file elaborated with the data provided by the furniture trades company.
 
@@
 
-The Tab.
-2 presents a comparison of the results obtained for the data described above, by ABC classification for the criteria billing and lead time billing.
-Appendice A presents the file AHP\_Solution.txt, that presents the results found by the module 'COPSolver: library for solving the multicriteria classification problem' - the results generated from the new ABC multicriteria classification with Analitic Hierarch Process and compare it to the ABC classifications of each criterion, for the items ordered in descending order according to the ABC multicriteria classification.
+Figure \ref{fig:results} presents part of a comparison of the results obtained for the data described above, by ABC classification for the criteria billing and the new ABC multicriteria with Analytic Hierarch Process.
+Appendice A shows the file AHP\_Solution.txt, that presents the complete results found by the module 'COPSolver: library for solving the multicriteria classification problem'.
 
-Based on the results presented in these tables, we can verify that the ABC classification, considering only the billing criterion, does not follow the normal pattern defined by the Pareto rule.
-However, when we use the lead time add-on billing criterion, it is possible to verify that the values are close to what is expected.
+\begin{figure}[ht]
+	\includegraphics[width=\linewidth]{files/0001.jpg}
+  	\caption{Comparison between the ABC classification for the billing criterion and the ABC multicriteria classification}
+  	\label{fig:results}
+\end{figure}
+
+Based on the results found by COPSolver, we can verify that the ABC classification, considering only the billing criterion, does not follow the normal pattern defined by the Pareto's rule.
+However, when we use the new ABC multicriteria classification, it is possible to verify that the values are close to what is expected.
 It is also possible to verify in a very clear way that the approach used to measure the weights of the products produces much more relevant results than the simple random assignment of weights.
@@
 
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}[c]{c r r r}
-\multicolumn{4}{c}{new ABC Multcriteria Classification with AHP} \\
-\\
-\multicolumn{4}{l}{car mechanics company} \\
-\cline {1-4} \\
-\multicolumn{4}{c}{75 sales between October 2020 and July 2023} \\
-\\
-  &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\
-A &  10 & 23.81 \% &  80 \% \\
-B &  15 & 35.71 \% &  95 \% \\
-C &  17 & 40.48 \% & 100 \% \\
-\cline {1-4} \\
-\multicolumn{4}{l}{furniture trades company} \\
-\cline {1-4} \\
-\multicolumn{4}{c}{254 sales between } \\
-\\
- &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\
+	\section{CONCLUSIONS AND FURTHER WORK}
 
-A &  59 & 23.23 \% &  79.78 \%  \\
-B &  56 & 22.05 \% &  94.81 \% \\
-C & 139 & 54.72 \% & 100.00 \% \\
-\cline {1-4} \\
+    In this article we present a new methodology for multicriteria ABC classification as an analytical hierarchy process which includes a procedure to force the consitences of the pairwise comparison matrices, as well as a procedure for assigning weights to the products evaluated according to qualitative criteria and a new equation for calculating the weights of the products in the multicriteria classification.
+This methodology was tested using data provided by three companies, from three different sectors.
+As a result, we verified the importance and efficiency of the method developed to force the consistency of the Matrix.
+We also verified that the new methodology proposed for multicriteria ABC classification generated very coherent results, giving the appropriate importance to the products, according to all the evaluated criteria.
 
- \multicolumn{4}{l}{plastic packaging manufacturing company}\\
-\cline {1-4} \\
-\multicolumn{4}{c}{5,967 sales between November 2019 and February 2023} \\
-\\
- &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\
-
-A &   128 &  5.49 \% & \\
-B &   726 & 31.12 \% & \\
-C & 1,479 & 63.39 \% & \\
-\cline {1-4} \\
-
-\end{tabular}
-\caption{ABC multicriteria classifications for three companies (results found by COPSolver)}
-\label{tab:results}
-\end{center}
-\end{table}
-
-	\section{DISCUSSION AND FINAL REMARKS}
+The methodologies developed and results found will be used as a basis for building a portfolio with the identification of product demand pattern and, subsequently, for the development of a combined methodology for demand forecasting.
+These will be the next works that we will be developing.
 
@@
         Se houver, esta seção deve ser colocada antes da lista de referências.
+
+        \section{CRediT AUTHORSHIP CONTRIBUTION STATEMENT} 
+		\label{sec:contributions}
+
+		T.B.
+Fraga: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing – original draft, Writing – review \& editing, Supervision, Project administration.
+B.M.
+Cavalcanti: Investigation.
+A.M.D.Silva: Investigation.
+E.L.R.
+Silva: Investigation.
+
+    \section{COPYRIGHT LIABILITY}
+
+        The authors are uniquely responsible for the content of this work.
 
@@
 
-        \section{CRediT AUTHORSHIP CONTRIBUTION STATEMENT} 
-		\label{sec:contributions}
-
-		T.B.
-Fraga: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing – original draft, Writing – review \& editing, Supervision, Project administration.
-B.M.
-Cavalcanti: Investigation.
-A.M.D.Silva: Investigation.
-E.L.R.
-Silva: Investigation.
-
-    \section{RESPONSABILIDADE AUTORAIS}
-
-        Os autores são os únicos responsávelis pelo conteúdo deste trabalho.
-
+        \newpage
         \begin{appendices}
@@
 }
+	\section{data.txt}
+
+	\verbatiminput{files/data.txt}
 

### 2024-03-14 accepted/CONEM2024/FCPCOM/CONEM2024.tex
In the middle of the stones flowers are born

@@
 
-	\section{CONCLUSIONS AND FURTHER WORK}
+	\section{CONCLUSIONS AND FURTHER WORKS}
 
-    In this article we present a new methodology for multicriteria ABC classification as an analytical hierarchy process which includes a procedure to force the consitences of the pairwise comparison matrices, as well as a procedure for assigning weights to the products evaluated according to qualitative criteria and a new equation for calculating the weights of the products in the multicriteria classification.
+    In this article we present a new methodology for multicriteria ABC classification with Analytical Hierarchy Process which includes a procedure to force the consitences of the pairwise comparisons matrices, as well as a procedure for assigning weights to the products evaluated according to qualitative criteria and a new equation for calculating the weights of the products in the multicriteria classification.
 This methodology was tested using data provided by three companies, from three different sectors.
-As a result, we verified the importance and efficiency of the method developed to force the consistency of the Matrix.
+As a result, we verified the importance and efficiency of the method developed to force the matrices consistency.
 We also verified that the new methodology proposed for multicriteria ABC classification generated very coherent results, giving the appropriate importance to the products, according to all the evaluated criteria.
 
-The methodologies developed and results found will be used as a basis for building a portfolio with the identification of product demand pattern and, subsequently, for the development of a combined methodology for demand forecasting.
-These will be the next works that we will be developing.
+As further works, the methodologies developed and results found will be used as a basis for building a portfolio with the identification of product demand patterns and, subsequently, for the development of a combined methodology for demand forecasting of small companies.
 
-    \section{AGRADECIMENTOS}
+    \section{ACKNOWLEDGEMENTS}
+
+Huge thanks to the teams responsible for developing elementary OS, as well as yandex translator, grammarly, duckduckgo, gummi, CodeBlocks, git, GitHub, gcc, and TeXLive libraries.
+Without the availability of these tools, the 'COPSolver's library for solving the multicriteria classification problem' could never have been developed.
+I am also very grateful to my co-workers Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique for their constant support to the projects I develop and to my dear advisees , among others, for having participated so enthusiastically in the projects that gave rise to this software, in particular for having made the effort to describe real processes in such detail.
+I would also like to thank the company in the plastic bag sector and other companies that made the studies possible as well as the identification of the new optimization problem addressed in COPSolver\_1.0-1.
+\\
 

### 2024-03-15 accepted/CONEM2024/FCPCOM/CONEM2024.tex
ACKNOWLEDGEMENTS revised

@@
 
-Huge thanks to the teams responsible for developing elementary OS, as well as yandex translator, grammarly, duckduckgo, gummi, CodeBlocks, git, GitHub, gcc, and TeXLive libraries.
-Without the availability of these tools, the 'COPSolver's library for solving the multicriteria classification problem' could never have been developed.
-I am also very grateful to my co-workers Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique for their constant support to the projects I develop and to my dear advisees , among others, for having participated so enthusiastically in the projects that gave rise to this software, in particular for having made the effort to describe real processes in such detail.
-I would also like to thank the company in the plastic bag sector and other companies that made the studies possible as well as the identification of the new optimization problem addressed in COPSolver\_1.0-1.
+Huge thanks to the teams responsible for developing elementary OS, CodeBlocks, git, GitHub, gcc, TeXLive libraries, duckduckgo, gummi, Yandex translator, and Grammarly.
+Without the availability of these tools, this paper and the "COPSolver's library for solving the multicriteria classification problem" could never have been developed.
+I am also very grateful to my co-workers Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique for their constant support for my projects and to my dear advisees Betriz Marinho Cavalcanti, Alexia Maria Duque Silva and Erika Leticia Rodrigues Silva for having participated so enthusiastically in this project, in particular for having made such effort to collect all the necessary data for this study.
+I would also like to thank the three companies that provided all the essential information we needed for the correct development of this work.
 \\
-
-        Se houver, esta seção deve ser colocada antes da lista de referências.
 

### 2024-03-18 accepted/CONEM2024/FCPCOM/CONEM2024.tex
improving the introduction's text

@@
 \def\shortauthor{T. B. Fraga, B. M. Cavalcanti, A. M. D. Silva e E. L. R. Silva \textcolor[rgb]{0.98,0.00,0.00}}
-\def\shorttitle{ABC Multicriteria Classification with Analytical Hierarchy Process: How to Force Consistency of Paiwise Comparisons Matrix \textcolor[rgb]{0.98,0.00,0.00}}
+\def\shorttitle{A New Effective ABC Multicriteria Classification with AHP: How to Force Consistency of Paiwise Comparisons Matrix. \textcolor[rgb]{0.98,0.00,0.00}}
 
@@
     % Digitar o título
-    \title{CONEM2024-0025\\ NEW ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX} 
+    \title{CONEM2024-0025\\ A NEW EFFECTIVE ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX} 
     %
@@
     \authors{Erika Leticia Rodrigues Silva, erika.leticias@ufpe.br$^1$} \\\\
-    \institution{$^1$Nome da instituição, endereço para correspondência (institucional, se houver)} \\
+    \institution{$^1$Centro Acadêmico do Agreste, Universidade Federal de Pernambuco, Avenida Marielle Franco, Bairro Nova Caruaru, Caruaru, PE, BR, CEP: 55014-900} \\
     \\
@@
 AHP's logic is not complicated at all.
-However, since criteria's pairwise comparison matrices are usually generated manually and based only on some employee know-how, there is high complexity in elaborating a consistent pairwise matrix, especially when comparing several criteria.
+However, since criteria's pairwise comparisons matrices are usually generated manually and based only on some employee know-how, there is high complexity in elaborating a consistent pairwise matrix, especially when comparing several criteria.
 This paper presents a constructive algorithm that can adjust inconsistent matrices, forcing such matrices to have a better consistency rate and a new procedure and equation for ABC multicriteria classification.
 We tested the proposed solutions by applying the AHP method for ABC multicriteria classification to companies in three sectors.
-As a result, we observed that the algorithm for forcing consistency adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours and that the new solution method developed for multicriteria classification provided consistent results according to the analysis of company managers, showing to be essential resources for applying the AHP and ABC multicriteria classification methods.}\\
+As a result, we observed that the algorithm for forcing consistency adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours and that the new solution method developed for multicriteria classification provided consistent results according to the analysis of company managers, both showing to be essential resources for applying the AHP and ABC multicriteria classification methods.}\\
     %
@@
 
-	"Manufacturing decisions can be classified into three categories: strategic, tactical and operational ...
-Operational decisions pertaining to issues such as order processing, detailed production scheduling, follow
-up, maintenance routines, and inventory control rules, drive the day to day activities" \citep{Singhal2013}.
+	According to \cite{Singhal2013}, the manufacturing decisions can be classified into three categories: strategic, tactical and operational.
+As explained by the authors, the operational decisions pertaining to issues such as order processing, detailed production scheduling, follow up, maintenance routines, and inventory control rules, drive the day to day activities.
 Manufacturing decisions are closely related to sales decisions.
-"In today’s competitive market the diversity in customer’s need have resulted in a high level of variability in the products which have to be manufactured" \citep{Ebrahimi2014} or acquired from other companies.
-Such diversity brings to light the need for the use of complex techniques for purchasing / production management, especially at the operational decision level \citep{Kiran2019}.
+\cite{Ebrahimi2014} warn that in today’s competitive market the diversity in customer’s need have resulted in a high level of variability in the products which have to be manufactured and this statement is also valid for the products acquired from other companies.
+Such complication brings to light the need for the use of complex techniques for purchasing / production management, especially at the operational decision level \citep{Kiran2019}.
 In such a scenario, prior optimized operational planning becomes impressible for better use of the productive capacity and to avoid investment losses in unnecessary or unprofitable material.
@@
 We opted for the method ABC for multicriteria classification and adopted the Analytic Hierarchy Process (AHP) \citep{Saaty1987} to assign the weights to the different criteria.
-It is important to note that the Analytic Hierarchy Process derives the weights of each criterion based on the eigenvector of a pairwise comparison matrix, which is constructed manually according to an empirical evaluation.
-According to \cite{Saaty1987}, this matrix must be antisymmetric and have a consistency rate of less than 0.1.
+It is important to note that the AHP derives the weights of each criterion based on the eigenvector of a pairwise comparisons matrix, which is constructed manually according to an empirical evaluation.
+According to \cite{Saaty1987}, this matrix must be positive reciprocal and have a consistency rate of less than 0.1.
 The author reports that a software package supporting the AHP, called Expert Choice, for the IBM PC, was used in his work for making eigenvector calculations and guiding the decision maker to improve matrix inconsistency if needed.
-During the execution of the work we present in this paper, we found that there is a substantial difficulty in the calculation of the eigenvector, as well as in the construction of consistent pairwise comparison matrices.
-Since we had no access to the Expert Choice software package, we developed an open-source COPSolver library for the Analytic Hierarchy Process and multicriteria ABC classification based on a simple algorithm for forcing the consistency of such matrices.
+During the execution of the work we present in this paper, we found that there is a substantial difficulty in the calculation of the eigenvector, as well as in the construction of consistent pairwise comparisons matrices.
+Since we had no access to the Expert Choice software package, we developed an open-source COPSolver's library for solving the multicriteria classification problem, which applies a simple algorithm for forcing the consistency of such matrices when applying the AHP.
 We present this algorithm in this paper.
@@
 Also, we identified that it is possible to use different criteria types (cumulative sum, qualitative, and binary) when assigning weights to ABC classification, depending on each specific criterion chosen, and we observed that such an assignment generates a bias in the multicriteria ABC classification.
-Therefore, we also developed a new methodology for assigning weights in a balanced way for ABC classification, and we proposed a new multicriteria weighting equation for the multicriteria classification COPSolver library.
+Therefore, we also developed a new methodology for assigning weights in a balanced way for ABC classification, and we proposed a new multicriteria weighting equation for the multicriteria classification COPSolver's library.
 We also present both propositions in this paper, as well as an in-depth analysis of the results found by the new library developed for COPSolver.

### 2024-03-18 accepted/CONEM2024/FCPCOM/CONEM2024.tex
final version - missing only last revision of the complete work

@@
     Algorithm (\ref{alg:forceConsistency}) illustrates the method developed to reduce the consistency rate ($CR$).
-This algorithm takes as input the pairwise comparison matrix ($M[m_{ij}]$) and the tolerance ($tol$) defined for the consistency rate and returns the matrix adjusted as well as the $CR$ of this new matrix (see \cite{Saaty1987} for more information on calculating the consistency rate).
+This algorithm takes as input the pairwise comparisons matrix ($M[m_{ij}]$) and the tolerance ($tol$) defined for the consistency rate and returns the matrix adjusted as well as the $CR$ of this new matrix (see \cite{Saaty1987} for more information on calculating the consistency rate).
 
@@
 The topLeftCorner() function (alg.
-\ref{alg:topLeftCorner}) performs a peer-to-peer comparison of each element of the pairwise matrix starting from the third row, $M[m_{\{sz\}j}]_{sz=3}^{n}$, with each element of the matrix $M[m_{jk}]_{j=1, k=j+1}^{n-1,n}$.
+\ref{alg:topLeftCorner}) performs a peer-to-peer comparison of each element of the pairwise matrix starting from the fourth row, $M[m_{\{sz\}j}]_{sz=4}^{n}$, with each element of the matrix $M[m_{jk}]_{j=1, k=j+1 \land k \neq sz}^{n-1,n}$.
 In this comparison, the consistency of each pair is verified according to Alg.
@@
 	\If{$CR \ge tol$}
-		\For{$sz \gets 3, n $}
-			\For{$j \gets 0, n-1 $}
+		\For{$sz \gets 4, n $}
+			\For{$j \gets 1, n-1 $}
 				\For{$k \gets j+1, n $}
+					\If{$k \neq sz $}
 						\State $g \gets 0$
@@
 									\State \textbf{break}
+								\EndIf
 							\EndIf
@@
 
-The bottomLeftCorner() function is similar to the topLeftCorner() function.
-In the topLeftCorner() function, the peer-to-peer comparison starts with the elements of the third row ($M[m_{\{sz\}j}]_{sz=3}$), and then the elements of the next rows are evaluated, following the order from top to bottom.
-In the case of the bottomLeftCorner() function, on the other hand, the pair-by-pair comparison is made starting with the elements of the anti-penultimate row ($sz = n-2$), then the elements of the previous rows are evaluated, following the order from bottom to top.
-
 \begin{algorithm}
@@
 		\For{$sz \gets n-2, 1 $}
-			\For{$j \gets 0, n-3 $}
-				\For{$k \gets j+1, n-2 $}
+			\For{$j \gets 1, n-1 $}
+				\For{$k \gets j+1, n $}
+					\If{$sz \neq k $}
 						\State $g \gets 0$
@@
 						\EndIf
+					\EndIf
 				\EndFor
@@
 
+The bottomLeftCorner() function is similar to the topLeftCorner() function.
+In the topLeftCorner() function, the peer-to-peer comparison starts with the elements of the fourth row ($M[m_{\{sz\}j}]_{sz=4}^{n}$), and then the elements of the next rows are evaluated, following the order from top to bottom.
+In the case of the bottomLeftCorner() function, on the other hand, the pair-by-pair comparison is made starting with the elements of the anti-penultimate row ($sz = n-2$), then the elements of the previous rows are evaluated, following the order from bottom to top.
+
     \section{ON MULTICRITERIA ABC CLASSIFICATION}
@@
 As discussed earlier, in our study, we observed that one of the crucial points for correctly applying multicriteria ABC classification is correctly attributing the weights for the initial ABC classification, that is, assign weights to each product according to each criterion.
-
 When we built the input data file, we considered three types of criteria for ABC analysis, cumulative sum (for billing and lead time criteria), qualitative, and binary criteria.
 While we were testing the solver, we noticed that an incorrect assignment of the weights can generate a strong bias in the multicriteria classification, since the criterion with the top percentage difference will always be dominant.
-
 Therefore, to assign the weights, three procedures were adopted, according to the different nature of each type of criterion used.
-
 In the case of the binary criteria, the choice of a binary parameters (0 and 1) results in a distribution of the percentage among the criteria that are critical.
@@
 However, in the case of the other criteria types, the consistency is no longer so clear.
-
 We can verify this inconsistency through a brief analysis of the two criteria classified according to the cumulative sum.
 For the data collected from the furniture trades company, the product with the highest billing (242,280.00 reais) has a billing corresponding to 12\% of the total amount; and a product with a longer lead time (30 days) represents 0.46\% of the total lead time, that is, a percentage 0.25\% higher than products with a lead time of 20 days (0.31\%) and 0.35\% higher than products with a lead time of 7 days (0.11\%).
-
 The question is: is the difference between the importance of a product with a 30-day lead time and a product with a 7-day lead time only 0.35\%?
 This value can only be appreciated when compared with the difference in importance of 12\% between the product with the highest and the product with the lowest billing.
-
 Make a multicriteria classification for the billing and lead time criteria based only on the accumulated sum is like calculate a weighted average of the annual sales of vehicles and bananas, hoping that this average will have some meaning.
@@
 In the case of the companies studied, this may not correspond to the assessment of experts.
-
 The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of \cite{Williams1984}.
-A single measure was adopted for these two criteria (lead time billing  weight) dividing the billing by the complement of the lead time for each product and then normalizing the weights.
-
-In the case of qualitative criteria, the initial ABC classification was made using three weights, one weight assigned to group A products, $w(A)$, a second weight assigned to group B products, $w(B)$, and a third weight assigned to products C, $w(C)$, where $w(A) > w(B) > w(C)$.
+A single measure was adopted for these two criteria (lead time billing  weight) dividing the billing by the complement of the lead time for each product and then normalizing the results.
+In the case of qualitative criteria, the initial ABC classification was made using three weights, one weight assigned to group A products, $w(A)$, a second weight assigned to group B products, $w(B)$, and a third weight assigned to group C products, $w(C)$, where $w(A) > w(B) > w(C)$.
 For qualitative criteria, $w(A)$, $w(B)$ and $w(C)$ must be assigned using the following steps:
@@
 
+$e_{p\sigma_q}$ is the product lead time billing equivalent of product $p$ for criteria $\sigma_q$;
+
 $b_p$ is the billing of product $p$;
@@
 
-	COPSolver is a software originally developed by Fraga (2024) to solve several decision and optimization problems, especially in the area of combinatorial optimization.
-The software works with a modular system of libraries, in which each library is developed to solve a single type of specific problem, which makes the software very efficient and robust.
+	COPSolver is a software originally developed by \cite{Fraga2023} to solve several decision and optimization problems, especially in the area of combinatorial optimization.
+The software works with a modular system of libraries, in which each library is developed to solve a single type of a specific problem, which makes the software very efficient and robust.
 The structure of the software allows high flexibility in the reuse of already developed codes, as is characteristic of the C++ language.
@@
 A model for preparing the data.txt file for this same library is available at https://tbfraga.github.io/COPSolver/benchmarks/clssp/alexia/original-data/data.txt.
+For more details about this library see \cite{Fraga2024}.
 
@@
 
-    To test the methodology proposed in this article, data were collected for constriction of the pairwise comparison matrix and for ABC classification, using the billing (bl) criterion and other criteria suggested by \cite{FloresWhybark1986}: lead-time (lt); criticality (cr); obsolescence (ob); commonality (cm); substitutability (sb); and repairability (rp).
+    To test the methodology proposed in this article, data were collected for construction of the pairwise comparison matrix and for ABC classification, using the billing (bl) criterion and other criteria suggested by \cite{FloresWhybark1986}: lead-time (lt); criticality (cr); obsolescence (ob); commonality (cm); substitutability (sb); and repairability (rp).
 To collect the data, we partnered with three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing.
@@
 For the data presented in Tab.
-\ref{tab:pairwiseMatrix}, there was no concern with the correct ordering of the criteria.
-Based on the results and previous observations, we have reordered the criteria using their respective weights, initially defined by the normalized eigenvector of the original pairwise comparisons matrix, $w$.
+\ref{tab:pairwiseMatrix}, with the exception of the car mechanics company, there was no concern with the correct ordering of the criteria.
+Based on the results and previous observations, we have computationally reordered the criteria using their respective weights, initially defined by the normalized eigenvector of the original pairwise comparisons matrix, $w$.
 Table \ref{tab:pairwiseMatrixReordered} presents the modification of results after altering the criteria ordination on the input data.
@@
 Appendice A shows the file AHP\_Solution.txt, that presents the complete results found by the module 'COPSolver: library for solving the multicriteria classification problem'.
+We can see in this figure that the multicriteria classification includes in the group A all products previously classified as A according to the billing criterion, however the order of relevance of the products is changed.
+Additionally, we can verify that other products, previously classified as C and B were included in the list of group A products because it is necessary to give due attention also to these products, due to their relevance according to other criteria.
+As an example, we can cite the product 2500, which is a 30-centimeter fan.
+In the evaluated period, this product had a turnover of 1,620.00 reais.
+Although the billing of this product was not significant when compared to the billing of the other products classified as A, this is a product that is hardly repairable, with high obsolescence and that serves several purposes.
+Therefore, in the multicriteria rating, this product took 13th place in terms of importance, therefore it is classified as A.
+This change shows the importance of the multicriteria classification.
 
@@
 
-Based on the results found by COPSolver, we can verify that the ABC classification, considering only the billing criterion, does not follow the normal pattern defined by the Pareto's rule.
-However, when we use the new ABC multicriteria classification, it is possible to verify that the values are close to what is expected.
+Based on the results found by COPSolver, we can verify that the ABC classification, considering only the billing criterion, does not follow the normal pattern defined by the Pareto's rule (where 20\% of the causes generate around 80\% of the result).
+However, when we use the new ABC multicriteria classification, the values are close to what is expected.
 It is also possible to verify in a very clear way that the approach used to measure the weights of the products produces much more relevant results than the simple random assignment of weights.
-This approach reduces the viez effect caused by the imbalance of weights and makes the final result carry important qualitative information provided by the responsible official, assigning the appropriate relevance of the different products, as well as the criteria analyzed.
+This approach reduces the viez effect caused by the imbalance of weights and makes the final result carry important qualitative information provided by the responsible employee, assigning the appropriate relevance of the different products, as well as the criteria analyzed.
 
@@
 
-As further works, the methodologies developed and results found will be used as a basis for building a portfolio with the identification of product demand patterns and, subsequently, for the development of a combined methodology for demand forecasting of small companies.
+As further works, the methodologies developed and results found will be used as a basis for building a portfolio with the identification of product demand patterns and, subsequently, for the development of a combined methodology for demand forecasting in small companies.
 
@@
 
-Huge thanks to the teams responsible for developing elementary OS, CodeBlocks, git, GitHub, gcc, TeXLive libraries, duckduckgo, gummi, Yandex translator, and Grammarly.
+Huge thanks to the teams responsible for developing elementary OS, CodeBlocks, git, GitHub, gcc, Eigen library, TeXLive libraries, duckduckgo, gummi, Yandex translator, and Grammarly.
 Without the availability of these tools, this paper and the "COPSolver's library for solving the multicriteria classification problem" could never have been developed.

### 2024-03-18 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating

@@
    \\
-    \keywords{\textbf{Palavras-chave:} ABC multicriteria classification, analytic hierarchy process, consistency rate,  constructive algorithm, COPSolver library}\\
+    \keywords{\textbf{Palavras-chave:} ABC multicriteria classification, Analytic Hierarchy Process, consistency rate, multicriteria equation, COPSolver library}\\
     %

### 2024-03-18 accepted/CONEM2024/FCPCOM/CONEM2024.tex
small correction

@@
 The topLeftCorner() function (alg.
-\ref{alg:topLeftCorner}) performs a peer-to-peer comparison of each element of the pairwise matrix starting from the fourth row, $M[m_{\{sz\}j}]_{sz=4}^{n}$, with each element of the matrix $M[m_{jk}]_{j=1, k=j+1 \land k \neq sz}^{n-1,n}$.
+\ref{alg:topLeftCorner}) performs a peer-to-peer comparison of each element of the pairwise matrix starting from the fourth row, $M[m_{\{sz\}j}]_{sz=4}$, with each element of the matrix $M[m_{jk}]_{j=1, k=j+1 \land k \neq sz}^{n-1,n}$.
 In this comparison, the consistency of each pair is verified according to Alg.

### 2024-03-18 accepted/CONEM2024/FCPCOM/CONEM2024.tex
minor correction

@@
 
-    To test the methodology proposed in this article, data were collected for construction of the pairwise comparison matrix and for ABC classification, using the billing (bl) criterion and other criteria suggested by \cite{FloresWhybark1986}: lead-time (lt); criticality (cr); obsolescence (ob); commonality (cm); substitutability (sb); and repairability (rp).
+    To test the methodology proposed in this article, data were collected for construction of the pairwise comparisons matrix and for ABC classification, using the billing (bl) criterion and other criteria suggested by \cite{FloresWhybark1986}: lead-time (lt); criticality (cr); obsolescence (ob); commonality (cm); substitutability (sb); and repairability (rp).
 To collect the data, we partnered with three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing.

### 2024-03-24 accepted/CONEM2024/MBPTMP/CONEM2024.tex
updating paper

@@
 \def\shorttitle{Versão Reduzida do Título do Artigo \textcolor[rgb]{0.98,0.00,0.00}{(Letras Iniciais em Caixa Alta, certifique que não ultrapasse uma linha)}}
+
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{rotating}
+\usepackage{multirow}
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{lemma}[theorem]{Lemma}
+\usepackage{enumitem}
+\usepackage{amsfonts}
+
+\usepackage{array, makecell}
+
+\usepackage{xcolor}
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric,shapes.misc,shapes.symbols,arrows.meta,graphs,fit,positioning,shadows}
 
@@
 
-    \section{INTRODUÇÃO}
+    \section{INTRODUCTION}
+	\label{sec:intro}
 
-        O objetivo destas instruções é servir de guia para a formatação dos trabalhos a serem publicados nos anais. Os anais do XII CONEM serão publicados no formato Adobe$^{\small{TM}}$ PDF.
+The term multi-product batch production is usually applied to designate an intermittent production system in which batches of different products and sizes are processed one at a time, sharing the same production facilities.
+A multi-product batch plant basically consists of one or more production units, grouped into one or more stages, and possibly, intermediate storage locations.
+At each stage some distinct operations are performed and the batches are processed sequentially over the stages (serial batching).
+As stated by \cite{PetkovMaranas1998} the batch plant can operate under a single-product campaign (SPC) production mode, where all the batches of a given product are manufactured before production of the next product begins, or under mixed-product campaign (MPC) production modes where more batches are produced per unit time at the expense of increased changeover times and cleanup costs.
+Also the plant layout can take on different formats, such as: single unit, where all operations needed to process the batches are performed by a single processor; serial flowshop plant, in which all products follow the same linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{ShiEtAll2017}; and convergent and/or divergent networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
 
-        Os artigos \textcolor{red}{\underline{\textbf{DEVEM}}} ser formatados de acordo com estas instruções.
-O presente arquivo pode ser usado como modelo por usuários do \LaTeX.
-Além disso, pode ser usado como um guia de formatação para usuários de outros processadores de texto.
+The scientific literature address many different problems related to such industrial enviroment, including the design, planning, sizing, scheduling and balancing problems.
+The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
+The configuration of the plant basically consists of defining the number of stages, the number of units and their capacity per stage, and the capacity for intermediate storages, as well as the best factory layout.
+The multi-product batch planning problem is basically determining the quantities to be produced, the number of batches and their sizes, the needs of materials and the total sales during each time period \citep{FumeroEtAl2016}.
 
-        Os trabalhos (\textit{draft} e \textit{final paper}) estão limitados a no mínimo \textcolor{red}{\underline{\textbf{6 páginas}}} e no máximo \textcolor{red}{\underline{\textbf{10 páginas}}}, incluindo tabelas e figuras.
-O arquivo final em formato PDF não deve exceder 2 MB.
+Since a single batch is processed at a time, it is necessary that the batches are dimensioned in such a way that the quantity produced of each product is sufficient to meet the demand during the period in which other batches are being processed \citep{Eilon1985}.
+This problem is named multi-product batch sizing.
+\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production, and \cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product serial batching sizing problem in a divergent networked plant of a steel industry (Fig.
+\ref{fig:networkdPlantSteelIndustry}).
 
-        A língua oficial do congresso é o português; entretanto serão aceitos manuscritos em espanhol ou em inglês.
-Se o trabalho não for escrito em inglês, o autor deverá incluir o título, os nomes dos autores e afiliações, o resumo e as palavras-chave, traduzidos para o inglês, após a lista de referências, no fim do artigo.
+\begin{figure}[h]
+\label{fig:networkdPlantSteelIndustry}
+\begin{center}
+\begin{tikzpicture}[font=\sffamily,every label/.append style={font=\small\sffamily,align=center}]
+
+\node[cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP00){};
+\node[rectangle, draw, right=0.5cm of WIP00, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit00){};
+\node[draw,dashed,rounded corners,fit=(WIP00) (unit00),inner sep=25pt,label={above:{stage (0,0)}}](stage00){};
+
+\node[above right=2cm and 4cm of WIP00, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP11){};
+\node[rectangle, draw, right=0.5cm of WIP11, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit11){};
+\node[draw,dashed,rounded corners,fit=(WIP11) (unit11),inner sep=25pt,label={above:{stage (1,1)}}](stage11){};
+
+\draw[-latex] (stage00.east) -- (stage11.west);
+
+\node[right=2.5cm of stage00, minimum width=1cm, minimum height=1.4cm](WIP1){.....};
+
+\node[right=0.3cm of WIP1, minimum width=1cm, minimum height=1.4cm](WIP1a){};
+
+\draw[-latex] (stage00.east) -- (WIP1.west);
+
+\node[below right=2cm and 4cm of WIP00, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIPp1){};
+\node[rectangle, draw, right=0.5cm of WIPp1, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unitp1){};
+\node[draw,dashed,rounded corners,fit=(WIPp1) (unitp1),inner sep=25pt,label={above:{stage (p,1)}}](stagep1){};
+
+\draw[-latex] (stage00.east) -- (stagep1.west);
+
+\node[right=4cm of WIP11, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP1m){};
+\node[rectangle, draw, right=0.5cm of WIP1m, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit1m){};
+\node[draw,dashed,rounded corners,fit=(WIP1m) (unit1m),inner sep=25pt,label={above:{stage (1,m$_1$)}}](stage1m){};
+
+\draw[-latex] (stage11.east) -- (stage1m.west);
+
+\node[right=4cm of WIPp1, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIPpm){};
+\node[rectangle, draw, right=0.5cm of WIPpm, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unitpm){};
+\node[draw,dashed,rounded corners,fit=(WIPpm) (unitpm),inner sep=25pt,label={above:{stage (p,m$_p$)}}](stagepm){};
+
+\draw[-latex] (stagep1.east) -- (stagepm.west);
+
+\node[right=3.5cm of WIP1, minimum width=1cm, minimum height=1.4cm](WIPm){.....};
+
+\node[left=0.5cm of WIPm, minimum width=1cm, minimum height=1.4cm](WIPma){};
+
+\draw[-latex] (WIP1a.east) -- (WIPma.west);
+
+\end{tikzpicture}
+\end{center}
+\caption{Multi-product serial batching divergent networked plant of a steel industry. Source: adapted from \cite{LiuEtAl2020} * stage $(i, j)$ means stage $j$ of production line $i$.}
+\end{figure}
+
+In multi-product batch scheduling (MBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the batches based on the known demand.
+Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
+Some cientific works impose additional constraints on the MBS problem - such as release times and due dates for each batch, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
+Also, some cientific works consider MBS problems within different layouts as well as dinamic and multiperiod scenarios.
+In parallel MBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
+Many cientifc works propose mixed-integer linear programming (MILP) formulations to solve MBS problems.
+As example, we can mention the work of \cite{MendezEtAll2000} that presents a MILP continuous-time model and a two-step systematic methodology for a single stage multi-product batch scheduling problem with different due-dates.
+Later, \cite{MendezCerda2003} also proposed another MILP formulation for reactive scheduling.
+As observerd by \cite{HeHui2008}, with the problem size increasing, the computational effort of MILP increases greatly so it is very difﬁcult for MILP to obtain acceptable solutions to large-size problems within reasonable time.
+Citing some works that use other approaches, \cite {KimEtAl1996} propose a Gantt chart mapping method and a modified genetic algorithm for solving a networked flowshop multi-product batch scheduling problem as well as a rule-based reactive rescheduling scheme for dinamicaly overcoming in-process deviation from the initial optimized schedule and \cite{HeHui2008} present a rule-based genetic algorithm for the scheduling of single stage multi-product batch plants with parallel units.
+
+It is importante to note that some production units are capable of processing multiple jobs at the same time.
+In such a case batches of different products and sizes can be grouped and processed by these units as a single batch.
+It is therefore necessary to determine the set of "batches" that each new compounded batch will contain.
+The multi-product balancing problem consists of determining these groupings, seeking to minimize the overall makespan.
+\cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.
+\cite{FowlerMonch2022} present a taxonomy and an extensive literature review for the p-batch problems.
+According to the authors, a p-batch problem can be classified as compatible setting - where there is no restriction on which jobs can be used to form a batch - and incompatible family case - where only jobs belonging to the same family can be used to form a batch.
+Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product p-batch problem involving identical parallel units, capacity constraints, and incompatible families with different job sizes.
+
+In a real production environment, some of these problems arise in a connected way, so many cientific works adress mixed multi-product batch problems.
+As example, \cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.
+Also, the work of \cite{MendezEtAll2000}, previously mentioned, considers planning as an integrated part of solution in real-world multi-product batch plant scheduling and therefore includes the product batching problem in its proposed MILP continuous-time models and two-step systematic methodology.
+
+\subsection{Taxonomy and Notation}
+
+In short, based on the bibliographic survey conducted for the preparation of this paper, we identify that the multi-product batch problems can differentiate with the following aspects:
+
+\begin{enumerate}[label=\arabic*)]
+\item \textbf{number of stages ($\sigma$)}: single stage ($SS$) or multistage ($MS$);
+\item \textbf{layout($\lambda$)}: single unit ($SU$), flowshop ($Fl$), parallel ($Pl$), or networked ($Nt$) (convergent ($CNt$) and /or divergent ($DNt$));
+\item \textbf{production mode ($\mu$)}: single-product campaing ($SPC$), mixed-product campaign ($MPC$), serial batching ($s\textrm{-}batch$) and/or parallel batching ($p\textrm{-}batch$);
+\item \textbf{problem:($\pi$)}  : design ($D$), planning ($P$), sizing ($Sz$), scheduling ($Sc$) and/or balancing ($B$); 
+\item \textbf{time horizon ($\eta$)}: single period ($SP$), multiperiod ($MP$) or cyclic ($Cc$);
+\item \textbf{scenario ($\gamma$)}: static ($St$) or dynamic ($Dn$);
+\item \textbf{input ($\iota$)}: deterministic ($Dt$) and/or stochastic ($St$);
+\item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), customer satisfaction($CS$), plant performance ($PP$) and/or processing time ($PT$);
+\item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$), sequencing constraints($SqC$).
+\end{enumerate}
+
+So, to describe a speciﬁc multi-product batch problem, we propose the notation $\sigma|\lambda|\mu|\pi|\eta|\gamma|\iota|\delta|\rho$.
+Some of the multi-product batch problems and solution approaches discussed in the references cited in this paper are summarized in Tab.
+\ref{tab:review}.
+
+\begin{table}[h!]
+\begin{center}
+\begin{small}
+\begin{tabular}[c]{l l l}
+reference & problem & contributions  \\
+\cline {1-3} \\
+\cite{Eilon1985} & $SS|SU|s\textrm{-}batch|Sc|SP$ &  analysis of the effect\\
+& $St|Dt|SC, HC|-$  & of splitting batches \\
+\cline {1-3} \\
+Ravemark and & $MS|Pl|SPC|D|Cc|$ & convex MILP model \\
+Rippin (1998) & $St|Dt|C|WIP$ & solved with DICOPT++ \\
+\cline {1-3} \\
+Petkov and & $MS|Pl|SPC|D|Cc|$ & exact method\\
+Maranas (1998)  & $St|St|NP|-$ & \\
+\cline {1-3} \\
+\cite{MendezEtAll2000} & $SS|Pl|MPC|P,Sc|SP|St|$ & MILP continuous-time  \\
+& $Dt|WIPC|RT, DD$ & model and a two-step  \\
+& & systematic methodology \\
+\cline {1-3} \\
+Méndez and & $SS|Pl|MPC|Sc|SP|Dn|Dt|$ & MIPL model and \\
+Cerdá (2003) &$wE/T|RT, DD, SDST$ & a rescheduling algorithm\\
+\cline {1-3} \\
+\cite{HeHui2008} & $SS|Pl|MPC|Sc|SP|$ & rule-based genetic \\
+& $St|Dt|C_{max}, TT|LCU, DD$ & algorithm \\
+\cline {1-3} \\
+\cite{FumeroEtAl2016} & $MS|Pl|MPC|D,P,Sc|Cc|$ & MILP model \\
+& $St|Dt|NP|LCU,USC$ & solved with CPLEX \\
+\cline {1-3} \\
+\cite{LiuEtAl2020} & $MS|DNt|s\textrm{-}batch|Sz|MP|St|$ & mixed-integer quadratic \\
+& $Dt|SC,WIPC|LCU,WIP$ & programming model  \\
+& & and exact algorithm \\
+\cline {1-3} \\
+\cite{LiEtAl2022} & $SS|Pl|p\textrm{-}batch|Sc,B|SP|$ & MILP model \\
+& $St|Dt|C_{max}|LCU, RT, IF$ & and a constraint-guided \\
+ & & artificial immune \\
+ & & system based algorithm \\ 
+\cline {1-3} \\
+\end{tabular}
+\caption{Some contributions on the multi-product batch problems}
+\label{tab:review}
+\end{small}
+\end{center}
+\end{table}
+
+\subsection{Contributions of this Paper}
+
+In this work we are interested in the multiperiod multi-product batch scheduling problem that arises in a networked plant of a plastic bag industry.
+The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020} (Fig.
+\ref{fig:networkdPlantSteelIndustry}), however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
+Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}.
+Thus, part of the problem solving process consists of solving a multi-product p-batch scheduling problem into extruders.
+Also, in the problem we study, in addition to demand, we must consider the factory and outlets' storage capacity, which is individually defined for products, but also for the set of products.
+
+When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product p-batches, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
+Using the notation presented before, this problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ problem.
+For simplification purposes, we named this problem multi-product p-batch processing time maximization (MBPTM) problem.
+
+It is important to note that, since the MBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product p-batch s-batch problem in the plastic bag networked plant of the industry studied.
+In a future work, we intend to present the mathematical model and a Particle Collison based solution algorithm we are developing for this last problem.
+As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MBPTM problem.
+
+The rest of the paper is organized as follows.
+In the next sections, the MBPTM problem is presented.
+Section \ref{sec:mathModel} presents an interger mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution.
+Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
+Section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.
+Finally, in sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions to this work are informed and acknowledgments are given, respectively.
+
+\section{MULTI-PRODUCT P-BATCH PROCESSING TIME MAXIMIZATION PROBLEM}
+\label{sec:MBPTMP}
+
+The multi-product p-batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
+In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product.
+In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set.
+The production quantity of each product is mainly defined according to the demand for the product.
+However, it is still possible to stock the products and/or send them to the outlets.
+In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch.
+Also, there is a time limit available for processing the batch.
+About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.
+
+\subsection{Mathematical Model}
+\label{sec:mathModel}
+
+Given that:
+
+$\textrm{UD}_i$ is the demand for the product $i$;
+
+$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch;
+
+$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory;
+
+$\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets;
+
+$\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets;
+
+$\textrm{p}_i$ is the production rate of product $i$;
+
+$\textrm{Z}$ is the timeout for batch processing;
+
+$P_i$ is the amount of product $i$ produced;
+
+$D_i$ is the amount of product $i$ delivered for the demand;
+
+$O_i$ amount of product $i$ shipped to factory outlets;
+
+$I_i$ is the amount of product $i$ that will be stored at the factory;
+
+$T$ is the batch processing time;
+
+We have the problem:
+
+\begin{equation}
+\label{MBPTMP01}
+max \quad T
+\end{equation}
+
+$s.t.$
+
+\begin{equation}
+P_i - \textrm{p}_i * T  = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+P_i - D_i - O_i - I_i = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+\label{MBPTMP04}
+D_i \leq \textrm{UD}_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+O_i \leq \textrm{UO}_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+\sum_i{O_i} \leq \textrm{O}
+\end{equation}
+
+\begin{equation}
+I_i \leq \textrm{UI}_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+\sum_i{I_i} \leq \textrm{I}
+\end{equation}
+
+\begin{equation}
+T \leq \textrm{Z}
+\end{equation}
+
+\begin{equation}
+\min \{\textrm{UD}_i - D_i, O_i + I_i\} = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+\min\{\textrm{O} - \sum_i\{ O_i\}, \textrm{UO}_i - O_i, I_i\} = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+\label{MBPTMP10}
+T, D_i, O_i, I_i \in  \mathbb{Z}^ + \quad \forall i
+\end{equation}
+
+where:
+
+Constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$.
+Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$.
+Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the outlets, and the factory-stocked quantity of each product must be less than their respective known limits.
+Constraints (6) and (8) state that both the sum of product quantities sent to the outlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values.
+The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
+Equations in (10) and (11) define the production distribution priority.
+And finally, the constraints in (12) inform the nature of the decision variables.
+
+\section{ANALYTICAL SOLUTION}
+\label{sec:analyticalSol}
+
+The method proposed in this paper for solution of the MBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the part of the production used to meet demand, the part of the production sent to outlets and the part of the production stocked in factory.
+Next, we explain each of these parts in detail.
+\\
+
+\noindent \emph{Calculation of maximum p-batch processing time:} \\
+
+It is possible to split the batch processing time into two time slots:
+
+\begin{equation}
+T = T' + T''
+\end{equation}
+
+\noindent where $T'$ is the maximum processing time whose production will be used exclusively to meet the demand.
+
+Then, being $D_{i}^{'}$ the quantity produced of the product $i$ after $T'$ units of processing time, we have:
+
+\begin{equation}
+\label{eq:s02}
+D_{i}^{'} - \textrm{p}_i * T'  = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+\label{eq:s03}
+D_{i}^{'} \in Z \quad \forall i
+\end{equation}
+
+\noindent and, as $D_{i}^{'} \leq D_i$, $\forall i$, we have:
+
+\begin{equation}
+\label{eq:s04}
+D_{i}^{'} \leq \textrm{UD}_i\quad \forall i
+\end{equation}
+
+From the equations in (\ref{eq:s02}) and the restrictions in (\ref{eq:s03}) and (\ref{eq:s04}), we have:
+
+\begin{equation}
+\label{eq:s05}
+T' \leq \lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor \quad \forall i
+\end{equation}
+
+And, as we wish maximum value to $T'$, from (\ref{eq:s05}) we have:
+
+\begin{equation}
+\label{eq:s06}
+T' = \min_i\{\lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor\}
+\end{equation}
+
+Observe that there may be a leftover corresponding to the demand not met by the production in the first part of the processing time, $T'$.
+This leftover, $S_i$, will be defined according to the equations in (\ref{eq:s07}):
+
+\begin{equation}
+\label{eq:s07}
+S_i = \textrm{UD}_i - D_{i}^{'} \quad \forall i
+\end{equation}
+
+It is also possible to consider that outlets are extensions of the factory stock.
+Therefore, it is possible to consider the factory stock of product $i$ and the outlets stock $i$ as single stock for the product $i$, $E_i$, so that:
+
+\begin{equation}
+\label{eq:s08}
+E_i = O_i + I_i
+\end{equation}
+
+\begin{equation}
+\label{eq:s09}
+E_i \leq \textrm{UO}_i + \textrm{UI}_i
+\end{equation}
+
+\begin{equation}
+\label{eq:s10}
+\sum_i {E_i} \leq \textrm{O} + \textrm{I}
+\end{equation}
+
+\begin{equation}
+\label{eq:s11}
+E_i \in Z \quad \forall i
+\end{equation}
+
+As the time $T'$ was used only for production that will meet the demand, $T''$  will be the remaining processing time, \emph{i.e.} the maximum processing time used for production that will meet the leftover of demand, sent to the outlets and stored in factory.
+So we have:
+
+\begin{equation}
+\label{eq:s12}
+E_i + S_i - \textrm{p}_i * T''  = 0 \quad \forall i
+\end{equation}
+
+\noindent Thus, after replacing (\ref{eq:s12}) in (\ref{eq:s09}) and applying some algebra, we have:
+
+\begin{equation}
+\label{eq:s13}
+T''  \leq (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i \quad \forall i
+\end{equation}
+
+\noindent And, after replacing (\ref{eq:s12}) in (\ref{eq:s10}) and applying some algebra, we have:
+
+\begin{equation}
+\label{eq:s14}
+ T'' \leq (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i
+\end{equation}
+
+Finally, as $T''$  is an integer value and we want to maximize this value, then:
+
+\begin{equation}
+\label{eq:s15}
+ T'' = \lfloor\min\{\min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor
+\end{equation}
+
+So, the analytical method for finding maximum $T$ can be decomposed into 4 steps:
+
+step 1: find $T'$, where:
+\begin{equation}
+T' = \lfloor{\min_{i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
+\end{equation}
+
+step 2: calculate $S_i$ for all products.
+\begin{equation}
+\label{eq:unmet}
+S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
+\end{equation}
+
+step 3: find $T''$, where:
+\begin{equation}
+T'' = \lfloor{\min \{\min_{i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
+\end{equation}
+
+step 4: calculate $T$, where: 
+\begin{equation}
+T^* = T' + T''
+\end{equation}
+\begin{equation}
+T = \min \{T^* , \textrm{Z}\}
+\end{equation}
+
+Note that, as we reduce the value of $T'$, the consequent reduction of $D_{i}^{'}$ will be directly attributed to the leftover of demand $S_i$ and, therefore, there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1.
+Thus it is possible to use a simplification of the method presented, making $T' = 0$.
+In this case $S_i = \textrm{UD}_i, \forall i$.
+The simplified version of the method is presented below:
+
+step 1: find $T^*$, where:
+\begin{equation}
+T^* = \lfloor{\min \{\min_{i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
+\end{equation}
+
+step 2: calculate $T$, where:
+
+\begin{equation}
+T = \min \{T^* , \textrm{Z}\}
+\end{equation}
+
+This simplification of the method demonstrates that the value calculated to $T$ does not depend on the way the production of the product $i$, $P_i$, is distributed between service to demand, $D_i$, outlets, $O_i$, and  factory's stock, $I_i$.
+
+\noindent \emph{Full solution:}
+
+We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply attending the priorities for distribution. The following three algorithms can be used to find a complete solution.
+
+The Algorithm (\ref{alg:part01}) is used for finding an optimimal value for $T$.
+
+\begin{algorithm}
+\caption{Solving MBPTM problem | Part 01 - find an optimal $T$ to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}).}\label{alg:part01}
+\begin{algorithmic}
+	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}$
+	\State $T^* \gets \lfloor{\min \{\min_{i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor$
+	\State $T \gets \min \{T^* , \textrm{Z}\}$
+\State \textbf{Return:} $T$.
+\end{algorithmic}
+\end{algorithm}
+
+Then an initial production distribution can be done by the Algorithm (\ref{alg:part02}).
+This distribution is made without considering the restrictions defined for the set of products.
+$SO$ and $SI$ represent, respectively, the total amount that can be sent to the outlets and the total amount that can be stocked in factory after the initial distribution.
+If this values are negative, this indicates that the proposed initial distribution is not a feasible distribution.
+
+\begin{algorithm}
+\caption{Solving MBPTM problem | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions for the set of products of the batch.}\label{alg:part02}
+\begin{algorithmic}
+	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}, T$.
+	\For{all i}
+		\State $E_i \gets T * \textrm{p}_i$
+		\State $D_i \gets \min \{\textrm{UD}_i, E_i\}$
+		\State $E_i \gets E_i - D_i$
+		\State $O_i \gets \min \{\textrm{UO}_i, E_i\}$
+		\State $E_i = E_i - O_i$
+		\State $\textrm{UO}_i = \textrm{UO}_i - O_i$
+		\State $I_i = E_i$
+		\State $\textrm{UI}_i = \textrm{UI}_i - I_i$
+	\EndFor
+	\State $SO = \textrm{O} - \sum_i{O_i}$
+	\State $SI = \textrm{I} - \sum_i{I_i}$
+	\State \textbf{Return:} $D_i, O_i, I_i, E_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
+\end{algorithmic}
+\end{algorithm}
+
+So, after applying Algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
+However, if $SO < 0$ or $SI <0$, solution is not yet feasible.
+But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements:
+
+$if \quad SO < 0 \quad then \quad SI > 0 \quad and  \quad |SO| < SI$
+
+$if \quad SI < 0 \quad then \quad SO > 0 \quad and  \quad |SI| < SO$
+
+Therefore it is possible to meet the restrictions by applying the Agorithm (\ref{alg:part03}).
+This algorithm redistributes the production of factory's stock to the outlets or vice versa, respectively, due to having a $SI$ or $SO$ negative.
+
+\begin{algorithm}
+\caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch set.}\label{alg:part03}
+\begin{algorithmic}
+\Require $O_i, I_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
+\If{$SO < 0$}
+\For{all $i$}
+	\State $O_i \gets O_i - \min\{ O_i, UI_i, |SO|\}$
+	\State $I_i \gets I_i + \min\{ O_i, UI_i, |SO|\}$
+	\State $SO \gets SO + \min\{ O_i, UI_i, |SO|\}$
+	\If{$SO = 0$}
+		break looping for;
+	\EndIf
+\EndFor
+\EndIf
+
+\If{$SI < 0$}
+\For{all $i$}
+	\State $I_i \gets I_i - \min\{ I_i, UO_i, |SI|\}$
+	\State $O_i \gets O_i + \min\{ I_i, UO_i, |SI|\}$
+	\State $SI \gets SI + \min\{ I_i, UO_i, |SI|\}$
+	\If{$SI = 0$}
+		break looping for;
+	\EndIf
+\EndFor
+\EndIf
+\State \textbf{Return:} $O_i, I_i, \forall i$.
+\end{algorithmic}
+\end{algorithm}
+
+\section{TESTS AND RESULTS}
+\label{sec:results}
+
+To test the developed model and analytical solution method, we created a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem and also a solver in LINGO named MBPTM.lng both available at codeocean and GitHub \citep{COPSolver2023}.
+A brief explanation of the software can be found in the paper of \cite{Fraga2023}.
+The tests were performed on a notebook with an Intel i7 processor.
+We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\
+
+\begin{equation}
+\textrm{p}_i = \textrm{rand}()\%30 + 10
+\end{equation}
+
+\begin{equation}
+\textrm{UD}_i = \textrm{rand}()\%3000 + 800;
+\end{equation}
+
+\begin{equation}
+ \textrm{seed1} = \textrm{rand}()\%3000 + 500;
+\end{equation}
+
+\begin{equation}
+\textrm{seed2} = \textrm{rand}()\%5000 + 1000;
+\end{equation}
+
+\begin{equation}
+\textrm{O} = \textrm{N}/2*\textrm{seed1};
+\end{equation}
+
+\begin{equation}
+\textrm{UO}_i = \textrm{rand}()\%(\textrm{seed1}-500) + 500;
+\end{equation}
+
+\begin{equation}
+\textrm{I} = \textrm{N}/2*\textrm{seed2};
+\end{equation}
+
+\begin{equation}
+\textrm{UI}_i = \textrm{rand}()\%(\textrm{seed2}-1000) + 1000;
+\end{equation}
+
+\begin{equation}
+\textrm{Z} = 100;
+\end{equation}
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}[c]{c r r r}
+$i$ & 1 & 2 & total \\
+\cline {1-4} \\
+$\textrm{p}_i$ & 60 & 40 & \\
+$\textrm{UD}_i$ & 1000 & 500 & \\
+$\textrm{UO}_i$ & 600 & 600 & 1000 \\
+$\textrm{UI}_i$ & 3000 & 2000 & 3000 \\
+\cline {1-4} \\
+& & $\textrm{Z}$ & 100 \\
+\end{tabular}
+\caption{Benchmark MBPTM 2}
+\label{tab:MBPTMP001}
+\end{center}
+\end{table}
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}[c]{c r r r r}
+$i$ & 1 & 2 & 3 & total \\
+\cline {1-5} \\
+$\textrm{p}_i$ & 60 & 40 & 50 \\
+$\textrm{UD}_i$ & 1000 & 500 & 800 \\
+$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 \\
+$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 3500 \\
+\cline {1-5} \\
+& & & $\textrm{Z}$ & 100 \\
+\end{tabular}
+\caption{Benchmark MBPTM 3}
+\label{tab:MBPTMP002}
+\end{center}
+\end{table}
+
+\begin{table}[h]
+\begin{center}
+\begin{small}
+\begin{tabular}[c]{c r r r r r r r r r r r }
+$i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
+\cline {1-12} \\
+$\textrm{p}_i$ & 60 & 40 & 50 & 40 & 30 & 50 & 60 & 10 & 20 & 40\\
+$\textrm{UD}_i$ & 1000 & 500 & 800 & 500 & 400 & 500 & 2000 & 300 & 500 & 1000 \\
+$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 & 300 & 200 & 500 & 800 & 0 & 200 & 3000 \\
+$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 800 & 3000 & 1000 & 400 & 300 & 200 & 0 & 5000 \\
+\cline {1-12} \\
+& & & & & & & & & & $\textrm{Z}$ & 100 \\
+\end{tabular}
+\caption{Benchmark MBPTM 10}
+\label{tab:MBPTMP003}
+\end{small}
+\end{center}
+\end{table}
+
+Randomly generated benchmarks were named RMBPTM $\textrm{N}$, being $\textrm{N}$ the number of products.
+Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
+To build the results presented in this work, we used source=0.
+The benchmarks used for the tests performed can be consulted at github.com/tbfraga/COPSolver.
+
+Table \ref{tab:results} presents the results obtained by applying the analytical method (COPSolver) and the LINGO solver for the solution of the previously presented benchmarks.
+
+\begin{table}[h]
+\begin{center}
+\begin{footnotesize}
+\begin{tabular}[c]{l r r r r}
+problem & LINGO solver & time (s) & analytical method & time (s) \\
+\cline {1-5} \\
+MBPTM 2 & 55 & 0.03 & 55 & $<$ 0.01 \\
+MBPTM 3 & 48 & 0.03 & 48 & $<$ 0.01 \\
+MBPTM 10 & 30 & 0.05 & 30 & $<$ 0.01 \\
+RMBPTM 20 & 100 & 0.06 & 100 & $<$ 0.01 \\
+RMBPTM 50 & 98 & 0.08 & 98 & $<$ 0.01 \\
+RMBPTM 100 & 98 & 0.11 & 98 & $<$ 0.01 \\
+RMBPTM 1,000 & 78 & 1.20 & 78 & $<$ 0.01 \\
+RMBPTM 2,000 & 70 & 3.25 & 70 & $<$ 0.01 \\
+RMBPTM 5,000 & 70 & 15.12 & 70 & $<$ 0.02 \\
+RMBPTM 10,000 & 70 & 55.19 & 70 & $<$ 0.04 \\
+\cline {1-5} \\
+\end{tabular}
+\caption{Results obtained with the LINGO solver and the analytical method}
+\label{tab:results}
+\end{footnotesize}
+\end{center}
+\end{table}
+
+Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MBPTM 3 and 10 found by both COPSolver and LINGO solver.
+Files containing all results can be found at github.com/tbfraga/COPSolver.
+
+\begin{table}[h]
+\begin{center}
+\begin{footnotesize}
+\begin{tabular}[c]{l r r r r}
+product & production & delivered (s) & send to outlets & stocked in factory \\
+\cline {1-5} \\
+P1 & 2,880 & 1,000 & 300 & 1,580 \\
+P2 & 1,920 & 500 & 600 & 820 \\
+P3 & 2,400 & 800 & 600 & 1,000 \\
+\cline {1-5} \\
+\end{tabular}
+\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 3}
+\label{tab:compResultsMBPTMP2}
+\end{footnotesize}
+\end{center}
+\end{table}
+
+\begin{table}[h]
+\begin{center}
+\begin{footnotesize}
+\begin{tabular}[c]{l r r r r}
+product & production & delivered (s) & send to outlets & stocked in factory \\
+\cline {1-5} \\
+P1 & 1,800 & 1,000 & 400 & 400 \\
+P2 & 1,200 & 500 & 600 & 100 \\
+P3 & 1,500 & 800 & 600 & 100 \\
+P4 & 1,200 & 500 & 700 & 0 \\
+P5 & 900 & 400 & 300 & 200 \\
+P6 & 1,500 & 500 & 200 & 800 \\
+P7 & 1,800 & 1800 & 0 & 0 \\
+P8 & 300 & 300 & 0 & 0 \\
+P9 & 600 & 500 & 0 & 100 \\
+P10 & 1,200 & 1000 & 200 & 0 \\
+\cline {1-5} \\
+\end{tabular}
+\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 10}
+\label{tab:compResultsMBPTMP3}
+\end{footnotesize}
+\end{center}
+\end{table}
+
+It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
+As the analytical method is a polynomial time complexity method, we did not intend to compare computational costs, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
+
+We have considered here a static problem, so in a future work we will study the complexities of solving the problem dynamically and try to propose new solution methods if needed.
+
+\section{CONCLUSIONS AND SUGGESTIONS FOR FUTURE WORKS}
+\label{sec:conclusions}
+
+In this paper we presented the multi-product p-batch processing time maximization problem, as well as a mathematical model and an exact analytical solution method for this problem.
+The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO software, from LINDO Systems, and with a solver developed in C++ language.
+Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large problems, which demonstrates the efficiency of the proposed method.
+As in this paper we considered a static problem, in a future work we will study the complexities that arise when considering the same problem in a dinamic scenario.
+We will also verify if there is the possibility of extending the proposed analytical method to solve a class of integer programming problems with similar characteristics to the studied problem.
+
+\section{CRediT AUTHORSHIP CONTRIBUTION STATEMENT} 
+\label{sec:contributions}
+
+T.B.
+Fraga: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing – original draft, Writing – review \& editing, Supervision, Project administration.
+Í.R.B.
+Aquino: Investigation.
+R.C.S.
+Menêzes: Investigation.
+
+\section{ACKNOWLEDGMENTS}
+\label{sec:acknowledgments}
+
+We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects.
+We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process.
+Finally, we would like to thank Pró-reitoria de Extensão e Cultura da UFPE (PROExC) and the Research Director of Propesqi (Pró-reitoria de Pesquisa e Inovação da UFPE) for their support and recognition of our work, and dear Professors Antônio José da Silva Neto and João Flávio Vieira de Vasconcellos from IPRJ/UERJ, who contributed significantly to the formation of essential skills for the development of our projects.
+We also thank my co-worker Marcos Luiz Henrique, for having helped by evaluating the mathematical model and solution method proposed in this paper.
 

### 2024-03-24 accepted/CONEM2024/MBPTMP/CONEM2024.tex
updating paper

@@
 \usepackage{abcm}
-\def\shortauthor{P. Autor, S. Autor e T. Autor \textcolor[rgb]{0.98,0.00,0.00}{(Atualize o cabeçalho de acordo)}}
-\def\shorttitle{Versão Reduzida do Título do Artigo \textcolor[rgb]{0.98,0.00,0.00}{(Letras Iniciais em Caixa Alta, certifique que não ultrapasse uma linha)}}
+\def\shortauthor{T.B. Fraga, I.R.B. de Aquino and R.C.S. Menêzes}
+\def\shorttitle{An Exact Method for the Multi-product P-batch Processing Time Maximization Problem}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \label{fig:networkdPlantSteelIndustry}
@@
 \end{center}
-\caption{Multi-product serial batching divergent networked plant of a steel industry. Source: adapted from \cite{LiuEtAl2020} * stage $(i, j)$ means stage $j$ of production line $i$.}
+\caption{\textbf{Multi-product serial batching divergent networked plant of a steel industry. Source: adapted from \cite{LiuEtAl2020} * stage $(i, j)$ means stage $j$ of production line $i$.}}
 \end{figure}
@@
 
-\begin{table}[h!]
+\begin{table}[ht]
 \begin{center}
+\caption{\textbf{Some contributions on the multi-product batch problems.}}
 \begin{small}
 \begin{tabular}[c]{l l l}
+\\
 reference & problem & contributions  \\
@@
 \end{tabular}
-\caption{Some contributions on the multi-product batch problems}
 \label{tab:review}
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \begin{center}
+\caption{\textbf{Benchmark MBPTM 2.}}
 \begin{tabular}[c]{c r r r}
+\\
 $i$ & 1 & 2 & total \\
@@
 \end{tabular}
-\caption{Benchmark MBPTM 2}
 \label{tab:MBPTMP001}
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \begin{center}
+\caption{\textbf{Benchmark MBPTM 3.}}
 \begin{tabular}[c]{c r r r r}
+\\
 $i$ & 1 & 2 & 3 & total \\
@@
 \end{tabular}
-\caption{Benchmark MBPTM 3}
 \label{tab:MBPTMP002}
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \begin{center}
+\caption{\textbf{Benchmark MBPTM 10.}}
 \begin{small}
 \begin{tabular}[c]{c r r r r r r r r r r r }
+\\
 $i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
@@
 \end{tabular}
-\caption{Benchmark MBPTM 10}
 \label{tab:MBPTMP003}
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \begin{center}
+\caption{\textbf{Results obtained with the LINGO solver and the analytical method.}}
 \begin{footnotesize}
 \begin{tabular}[c]{l r r r r}
+\\
 problem & LINGO solver & time (s) & analytical method & time (s) \\
@@
 \end{tabular}
-\caption{Results obtained with the LINGO solver and the analytical method}
 \label{tab:results}
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \begin{center}
+\caption{\textbf{Results obtained with the LINGO solver and COPSolver for the MBPTM 3.}}
 \begin{footnotesize}
 \begin{tabular}[c]{l r r r r}
+\\
 product & production & delivered (s) & send to outlets & stocked in factory \\
@@
 \end{tabular}
-\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 3}
 \label{tab:compResultsMBPTMP2}
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \begin{center}
+\caption{\textbf{Results obtained with the LINGO solver and COPSolver for the MBPTM 10.}}
 \begin{footnotesize}
 \begin{tabular}[c]{l r r r r}
+\\
 product & production & delivered (s) & send to outlets & stocked in factory \\
@@
 \end{tabular}
-\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 10}
 \label{tab:compResultsMBPTMP3}
@@
 
-    \section{FORMATO DO TEXTO}
-
-        O artigo deve ser digitado no \textit{template} ``CONEM2024.tex'' e as principais configurações (ex.: formato do papel, tipo e tamanho da fonte do título/Seção/Subseção, espaços, margens, alinhamentos, indentação, etc.) já estão previamente configuradas no arquivo ``abcm.sty''.
-Título, nomes dos autores, instituição, endereço, resumo e palavras-chave devem ser recuados 0,1 cm da margem esquerda e marcados por uma linha preta na borda esquerda com largura de 2$\frac{1}{4}$ pontos.
-
-        Informações suficientes devem ser fornecidas diretamente no texto, ou por referência a trabalhos publicados disponíveis. Notas de rodapé devem ser evitadas.
-
-        Todos os símbolos e notações devem ser definidos no texto.
-As grandezas físicas devem ser expressas no Sistema Internacional de Unidades.
-Os símbolos matemáticos que aparecem no texto devem ser digitados em itálico.
-As unidades devem ser digitadas no estilo romano (ex.: kg, m, MJ, kW/m$^2$, em vez de $kg$, $m$, $MJ$, $kW/m^2$).
-
-        As referências bibliográficas devem ser citadas no texto dando o sobrenome do(s) autor(es) e o ano de publicação, conforme os seguintes exemplos: ``...
-conforme apresentado \citep{MinwooShamim13}.'' ou ``Recentemente, \citet{MinwooShamim13} demonstraram que …''.
-No caso de três ou mais autores, deve ser utilizada a expressão ``\textit{et al.}'', como segue: ``...
-conforme já relatado \citep{Bordalo89}'' e ``Recentemente, \citet{Bordalo89} demonstraram que …''.
-Duas ou mais referências com os mesmos autores e ano de publicação devem ser distinguidas acrescentando ``a'', ``b'', etc., ao ano de publicação.
-No caso da necessidade de citar vários trabalhos em uma mesma chamada, o seguinte formato pode ser utilizado: ``...já se encontra consolidado na literatura (\citeauthor{Coimbra78}, \citeyear{Coimbra78}; \citeauthor{Clark86}, \citeyear{Clark86} e \citeauthor{Sparrow80},  \citeyear{Sparrow80})''.
-
-        As referências devem ser listadas no final do manuscrito de acordo com as instruções fornecidas na Seção 4.
-
-        \textbf{\textcolor[rgb]{0.98,0.00,0.00}{\underline{NÃO NUMERAR AS PÁGINAS.}}}
-
-    \subsection{Títulos e Subtítulos das Seções }
-
-        Os títulos das seções são com letras maiúsculas (Exemplo: \textbf{MODELO MATEMÁTICO}), enquanto os subtítulos só têm as primeiras letras maiúsculas de cada palavra (Exemplo: \textbf{Modelo Matemático}).
-Eles devem ser numerados, usando numerais arábicos separados por pontos, até o máximo de 3 subníveis.
-Uma linha em branco de espaçamento simples deve ser incluída acima e abaixo de cada título ou subtítulo.
-
-    \subsection{Corpo do Texto}
-
-        Conforme já se encontra definido no arquivo ``abcm.sty'', o corpo do texto é justificado e com espaçamento simples.
-A primeira linha de cada parágrafo tem recuo de 0,5 cm a partir da margem esquerda.
-
-        As equações matemáticas são alinhadas à esquerda com recuo de 0,5 cm.
-Elas são referidas como ``Eq.
-(\ref{eq:equation1})'' no meio de uma frase, ou ``Equação (\ref{eq:equation1})'' quando usada no início de uma sentença.
-Os números das equações são numerais arábicos colocados entre parênteses, e alinhados à direita, como mostrado na Eq.
-(\ref{eq:equation1}).
-Os símbolos usados nas equações devem ser definidos imediatamente antes ou depois de sua primeira ocorrência no texto.
-
-        O tamanho da fonte usado nas equações deve ser compatível com o utilizado no texto.
-Todas as grandezas físicas devem ter suas unidades expressas no Sistema Internacional de Unidades, como já mencionado.
-
-        \begin{equation}
-        \sigma = E \cdot \epsilon. \label{eq:equation1}
-        \end{equation}
-
-    	\noindent
-    	onde: $\sigma$ é a tensão, $E$ é o módulo de elasticidade longitudinal (ou Módulo de Young) e $\epsilon$ é a deformação longitudinal.
-
-        As figuras e tabelas devem ser colocadas no texto o mais próximo possível do ponto em que foram mencionadas pela primeira vez e devem ser numeradas consecutivamente em algarismos arábicos.
-As tabelas devem ser centralizadas e referidas por ``Tab.
-\ref{tab:tabexemplo}'' no meio de uma frase, ou por ``Tabela \ref{tab:tabexemplo}'' quando usada no início de uma sentença.
-Uma linha em branco, em espaço simples, deve ser introduzida entre a tabela e o texto subsequente.
-
-        Anotações e valores numéricos incluídos na tabela devem ter tamanhos compatíveis com a fonte usada no texto do trabalho e todas as unidades devem ser expressas no Sistema Internacional de Unidades.
-As unidades são incluídas apenas na primeira linha ou primeira coluna de cada tabela, conforme for apropriado.
-O estilo de borda é livre.
-As explicações, se houver, devem ser fornecidas ao pé das tabelas e não dentro das mesmas.
-
-        \begin{table}[ht]
-            \begin{center}
-                \caption{\textbf{Exemplo de tabela.}}
-                    \begin{tabular}{c|c|c}
-                    \hline
-                    Propriedades do compósito       & CFRC-TWILL        & CFRC-4HS         \\
-                    \hline
-                    Resistência à Flexão  (MPa)     & 209.0 $\pm$ 10.0       & 180.0 $\pm$  15.0    \\
-                    \hline
-                    Módulo de Flexão  (GPa)         & 57.0 $\pm$ 2.8    & 18.0 $\pm$  1.3  \\
-                    \hline
-                    \end{tabular} \label{tab:tabexemplo}
-            \end{center}
-        \end{table}
-
-        As figuras devem ser centralizadas.
-Elas são referenciadas por ``Fig.
-\ref{fig:figexemplo}'' no meio de uma frase ou por ``Figura \ref{fig:figexemplo}'' quando usada no início de uma sentença.
-Sua legenda deve ser centralizada e localizada imediatamente abaixo da figura.
-As anotações e numerações devem ter tamanhos compatíveis com a fonte usada no texto e todas as unidades devem ser expressas no Sistema Internacional de Unidades.
-As figuras devem ser colocadas o mais próximo possível de sua primeira citação no texto.
-Deve ser deixada uma linha em branco, de espaçamento simples, entre a figura e o texto subsequente.
-
-        \begin{figure}[h]
-            \begin{center}
-                \includegraphics[angle=0, scale=.8]{figura.png}
-            \end{center}
-            \caption{\textbf{Exemplo de figura.}}
-            \label{fig:figexemplo}
-        \end{figure}
-
-        Figuras coloridas e fotografias de alta qualidade podem ser incluídas no trabalho.
-Para reduzir o tamanho do arquivo e preservar a resolução gráfica, os arquivos das imagens podem ser convertidos para o formato GIF (para figuras com até 16 cores) ou para o formato JPEG (alta densidade de cores), antes de serem inseridos no trabalho.
-
-    \section{AGRADECIMENTOS}
-
-        Se houver, esta seção deve ser colocada antes da lista de referências.
-
     % REFERÊNCIAS
-    \section{REFERÊNCIAS}
+   \section{REFERENCES}
 
@@
 
-        Referências aceitas incluem: artigos de periódicos, dissertações, teses, artigos publicados em anais de congressos, livros, comunicações privadas e artigos submetidos e aceitos (com fonte identificada) e citações a páginas da internet.
-
-        A lista de referências deve ser uma seção específica denominada Referências, localizada no fim do artigo.
-
-        A primeira linha de cada referência deve ser alinhada à esquerda, sendo que as demais terão recuo já configurado a partir da margem esquerda.
-Todas as referências incluídas na lista devem aparecer como citações no texto do trabalho.
-
-        As referências devem ser postas em ordem alfabética, usando o último nome do primeiro autor, seguida do ano da publicação. Exemplo da lista de referências é apresentado abaixo.
-
         \bibliographystyle{abcm}
@@
 
-    \section{RESPONSABILIDADE AUTORAIS}
+\section{COPYRIGHT LIABILITY}
 
-        Os trabalhos escritos em português ou espanhol devem incluir (após direitos autorais) título, os nomes dos autores e afiliações, o resumo e as palavras-chave, traduzidos para o inglês e a declaração a seguir, devidamente adaptada para o número de autores.
-
-        O(s) autor(es) é(são) o(s) único(s) responsável(is) pelo conteúdo deste trabalho.
-
- % RESUMO EM INGLES
-
-\noindent{
-   \\ 
-    \begin{tabular}{||p{\textwidth}}
-    \begin{center}
-    \vspace{-.6cm}
-    \title{AFTER FULL PAPER IN PORTUGUESE OR SPANISH, IT IS NECESSARY THE ABSTRACT IN ENGLISH}
-    \end{center}
-    \authors{First Author’s Name, e-mail1$^1$} \\
-    \authors{Second Author’s Name, e-mail$^2$} \\
-    \authors{Third Author’s Name, e-mail$^2$} \\\\
-    \institution{$^1$Institution and address for first author} \\
-    \institution{$^2$Institution and address for second and third authors} \\
-    \\
-    \authors{\textcolor[rgb]{0.98,0.00,0.00}{Same format for other authors and institutions, if any. (\textit{This guidance should be removed from the final paper.})}} \\
-    \\
-    \abstract{\textbf{Abstract:} The purpose of these instructions is to serve as a guide for formatting papers to be published in the Proceedings of the XII CONEM.
-The abstract must describe the objectives, methodology and main conclusions of the article, containing between 300 and 400 words in a single paragraph.
-It should not contain either formulae or bibliographic references.
-The full paper will be published in the proceedings of the event.}\\
-    \\
-    \keywords{\textbf{Keywords:} keyword 1, keyword 2, keyword 3 (up to 5 keywords) }\\
-    \end{tabular}
-}
+        The authors are uniquely responsible for the content of this work.
 

### 2024-05-22 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating files

@@
     % Digitar o resumo
-    \abstract{\textbf{Resumo:} Multicriteria classification is usually a crucial step in the decision-making in the manufacturing and purchasing management process.
+    \abstract{\textbf{Resumo:} Currently, most companies produce and market a wide variety of products.
+Because of this, clustering items has become a crucial step in the decision-making for manufacturing and purchasing management processes.
+ABC multicriteria classification is a technique commonly used for clustering items.
 For such classification, the attribution of weights to the criteria, as well as the attribution of weights to the products according to each criterion, strongly influences the coherence of the categorization.
-Saaty's Analytic Hierarchy Process (AHP) is an eminent method for assigning weights to multiple criteria.
+Saaty's Analytic Hierarchy Process (AHP) is an eminent method for assigning weights to multiple criteria, and so it is broadly used in multicriteria classification.
 AHP's logic is not complicated at all.
-However, since criteria's pairwise comparisons matrices are usually generated manually and based only on some employee know-how, there is high complexity in elaborating a consistent pairwise matrix, especially when comparing several criteria.
-This paper presents a constructive algorithm that can adjust inconsistent matrices, forcing such matrices to have a better consistency rate and a new procedure and equation for ABC multicriteria classification.
-We tested the proposed solutions by applying the AHP method for ABC multicriteria classification to companies in three sectors.
+However, since criteria's pairwise comparison matrices are usually generated manually and based only on some employee know-how, there is high complexity in elaborating a consistent pairwise matrix, especially when comparing several criteria.
+The attribution of weights to the products according to each criterion is also a difficult task cause there is a need for balancing all the quantitative values and the empirical values defined for the qualitative criteria.
+This paper presents a constructive algorithm that can adjust inconsistent pairwise comparison matrices, forcing such matrices to have a better consistency rate, and a balancing procedure for attributing weights to the products according to qualitative criteria as well as a new equation for ABC multicriteria classification.
+We developed a new library for the COPSolver software by applying this new AHP method for the ABC multicriteria classification.
+We tested the proposed solutions to companies in three sectors.
 As a result, we observed that the algorithm for forcing consistency adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours and that the new solution method developed for multicriteria classification provided consistent results according to the analysis of company managers, both showing to be essential resources for applying the AHP and ABC multicriteria classification methods.}\\
@@
 I would also like to thank the three companies that provided all the essential information we needed for the correct development of this work.
-\\
 
-        \section{CRediT AUTHORSHIP CONTRIBUTION STATEMENT} 
+        \section{CREDIT AUTHORSHIP CONTRIBUTION STATEMENT} 
 		\label{sec:contributions}
@@
 
-        \newpage
-        \begin{appendices}
-		\setcounter{section}{0}
-		\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
-		\makeatletter
-		\addtocontents{toc}{%
-		\begingroup
-		\let\protect\l@section\protect\l@subsection
-}
-	\section{data.txt}
-
-	\verbatiminput{files/data.txt}
-
-	\section{AHP\_solution.txt}
-
-	\verbatiminput{files/AHP_solution.txt}
-
-	\addtocontents{toc}{\endgroup}
-	\end{appendices}
-
 \end{document}

### 2024-05-22 accepted/CONEM2024/MBPTMP/CONEM2024.tex
updating paper
updating files

@@
 \documentclass[10pt,fleqn,a4paper,twoside]{article}
-\usepackage{abcm}
-\def\shortauthor{T.B. Fraga, I.R.B. de Aquino and R.C.S. Menêzes}
-\def\shorttitle{An Exact Method for the Multi-product P-batch Processing Time Maximization Problem}
 
@@
 
+\usepackage{abcm}
+\def\shortauthor{T.B. Fraga, I.R.B. de Aquino and R.C.S. Menêzes}
+\def\shorttitle{An Exact Method for the Multi-product P-batch Processing Time Maximization Problem}
+
 \begin{document}
@@
     % Digitar o título
-    \title{CONEM2024-XXXX \\ AN EXACT METHOD FOR THE MULTI-PRODUCT P-BATCH PROCESSING TIME MAXIMIZATION PROBLEM}
+    \title{CONEM2024-0014 \\ AN EXACT METHOD FOR THE MULTI-PRODUCT P-BATCH PROCESSING TIME MAXIMIZATION PROBLEM}
     %
@@
 When applying some local search heuristics to solve a MPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products.
-In this paper we name this problem multi-product p-batch processing time maximization (MPBPTM) problem.
+We name this problem multi-product p-batch processing time maximization (MPBPTM) problem.
 Once a MPBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPBS problems.
 In addition, for some industries, efficiently solving a MPBPTM problem can have a significant impact on storage costs and customer satisfaction.
-In this paper we present a mathematical model and an exact method with polynomial time complexity for the MBPTM problem.
-We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method.
+In this paper we present a mathematical model and an exact method with polynomial time complexity for the MPBPTM problem.
+We developed a LINGO solver for solving the mathematic model, and a C++ solver for application of the proposed exact method.
 We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small and very large.
@@
    \\
-    \keywords{\textbf{Palavras-chave:} palavra 1, palavra 2, palavra 3 (até 5 palavras, separadas  por vírgulas) }\\
-    %
+    \keywords{\textbf{Palavras-chave:} multi-product p-batch problem, processing time maximization, integer programming model, analytical solution, COPSolver}\\
+
     \end{tabular}
@@
 \item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), customer satisfaction($CS$), plant performance ($PP$) and/or processing time ($PT$);
-\item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$), sequencing constraints($SqC$).
+\item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$), sequencing constraints ($SqC$).
 \end{enumerate}
@@
 
-\subsection{Contributions of this Paper}
+\subsection{Contributions of this Article}
 
-In this work we are interested in the multiperiod multi-product batch scheduling problem that arises in a networked plant of a plastic bag industry.
-The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020} (Fig.
-\ref{fig:networkdPlantSteelIndustry}), however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
+The work presented in this article is part of a project in which we propose the modeling and solution of a multiperiod multi-product batch scheduling problem that arises in a networked plant of a plastic bag industry.
+The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020} and illustrated in Fig.
+(\ref{fig:networkdPlantSteelIndustry} ), however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
 Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}.
@@
 When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product p-batches, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
-Using the notation presented before, this problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU, PSC, SC, DPR$ problem.
-For simplification purposes, we named this problem multi-product p-batch processing time maximization (MBPTM) problem.
+Using the notation presented before, this problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU,$ $PSC, SC, DPR$ problem.
+For simplification purposes, we named this problem multi-product p-batch processing time maximization (MPBPTM) problem.
 
-It is important to note that, since the MBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product p-batch s-batch problem in the plastic bag networked plant of the industry studied.
+It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product p-batch s-batch problem in the plastic bag networked plant of the industry studied.
 In a future work, we intend to present the mathematical model and a Particle Collison based solution algorithm we are developing for this last problem.
-As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MBPTM problem.
+As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPBPTM problem.
 
 The rest of the paper is organized as follows.
-In the next sections, the MBPTM problem is presented.
-Section \ref{sec:mathModel} presents an interger mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution.
-Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
-Section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.
-Finally, in sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions to this work are informed and acknowledgments are given, respectively.
+In the next sections, the MPBPTM problem is introduced.
+Section 2.1 describes an interger mathematical model for the problem and section 3 shows an analytical method for its solution.
+Section 4 displays the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
+Section 5 presents the paper's conclusions and suggestions for future works.
+Finally, in sections 6 and 7, the contributions to this work are informed and acknowledgments are given, respectively.
 
@@
 The production quantity of each product is mainly defined according to the demand for the product.
-However, it is still possible to stock the products and/or send them to the outlets.
-In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch.
+However, it is still possible to stock the products and / or send them to the outlets.
+In both cases, there is a stocking / shipping limit for each product and a stocking / shipping limit for the set of products in the batch.
 Also, there is a time limit available for processing the batch.
@@
 
-$T$ is the batch processing time;
+$T$ is the batch processing time; \\
 
@@
 
-where:
-
-Constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$.
+where constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$.
 Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$.
@@
 
-The method proposed in this paper for solution of the MBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the part of the production used to meet demand, the part of the production sent to outlets and the part of the production stocked in factory.
+The method proposed in this paper for solution of the MPBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the part of the production used to meet demand, the part of the production sent to outlets and the part of the production stocked in factory.
 Next, we explain each of these parts in detail.
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem and also a solver in LINGO named MBPTM.lng both available at codeocean and GitHub \citep{COPSolver2023}.
-A brief explanation of the software can be found in the paper of \cite{Fraga2023}.
+To test the developed model and analytical solution method, we created a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem and also a solver in LINGO named MBPTM.lng both available at codeocean and GitHub.
+A brief explanation of the software and links for downloads can be found in the paper of \cite{Fraga2023}.
 The tests were performed on a notebook with an Intel i7 processor.
@@
 \begin{center}
-\caption{\textbf{Benchmark MBPTM 2.}}
+\caption{\textbf{Benchmark MPBPTM 2.}}
 \begin{tabular}[c]{c r r r}
@@
 \begin{center}
-\caption{\textbf{Benchmark MBPTM 3.}}
+\caption{\textbf{Benchmark MPBPTM 3.}}
 \begin{tabular}[c]{c r r r r}
@@
 \begin{center}
-\caption{\textbf{Benchmark MBPTM 10.}}
+\caption{\textbf{Benchmark MPBPTM 10.}}
 \begin{small}
@@
 
-Randomly generated benchmarks were named RMBPTM $\textrm{N}$, being $\textrm{N}$ the number of products.
+Randomly generated benchmarks were named RMPBPTM $\textrm{N}$, being $\textrm{N}$ the number of products.
 Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
@@
 \cline {1-5} \\
-MBPTM 2 & 55 & 0.03 & 55 & $<$ 0.01 \\
-MBPTM 3 & 48 & 0.03 & 48 & $<$ 0.01 \\
-MBPTM 10 & 30 & 0.05 & 30 & $<$ 0.01 \\
-RMBPTM 20 & 100 & 0.06 & 100 & $<$ 0.01 \\
-RMBPTM 50 & 98 & 0.08 & 98 & $<$ 0.01 \\
-RMBPTM 100 & 98 & 0.11 & 98 & $<$ 0.01 \\
-RMBPTM 1,000 & 78 & 1.20 & 78 & $<$ 0.01 \\
-RMBPTM 2,000 & 70 & 3.25 & 70 & $<$ 0.01 \\
-RMBPTM 5,000 & 70 & 15.12 & 70 & $<$ 0.02 \\
-RMBPTM 10,000 & 70 & 55.19 & 70 & $<$ 0.04 \\
+MPBPTM 2 & 55 & 0.03 & 55 & $<$ 0.01 \\
+MPBPTM 3 & 48 & 0.03 & 48 & $<$ 0.01 \\
+MPBPTM 10 & 30 & 0.05 & 30 & $<$ 0.01 \\
+RMPBPTM 20 & 100 & 0.06 & 100 & $<$ 0.01 \\
+RMPBPTM 50 & 98 & 0.08 & 98 & $<$ 0.01 \\
+RMPBPTM 100 & 98 & 0.11 & 98 & $<$ 0.01 \\
+RMPBPTM 1,000 & 78 & 1.20 & 78 & $<$ 0.01 \\
+RMPBPTM 2,000 & 70 & 3.25 & 70 & $<$ 0.01 \\
+RMPBPTM 5,000 & 70 & 15.12 & 70 & $<$ 0.02 \\
+RMPBPTM 10,000 & 70 & 55.19 & 70 & $<$ 0.04 \\
 \cline {1-5} \\
@@
 \begin{center}
-\caption{\textbf{Results obtained with the LINGO solver and COPSolver for the MBPTM 3.}}
+\caption{\textbf{Results obtained with the LINGO solver and COPSolver for the MPBPTM 3.}}
 \begin{footnotesize}
@@
 
-\begin{table}[ht]
+\begin{table}[h!]
 \begin{center}
-\caption{\textbf{Results obtained with the LINGO solver and COPSolver for the MBPTM 10.}}
+\caption{\textbf{Results obtained with the LINGO solver and COPSolver for the MPBPTM 10.}}
 \begin{footnotesize}
@@
 
+\section{COPYRIGHT LIABILITY}
+
+        The authors are uniquely responsible for the content of this work.
+
     % REFERÊNCIAS
@@
 
-\section{COPYRIGHT LIABILITY}
-
-        The authors are uniquely responsible for the content of this work.
-
 \end{document}

### 2024-05-22 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating article

@@
     % Digitar o título
-    \title{CONEM2024-0025\\ A NEW EFFECTIVE ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX} 
+    \title{CONEM2024-0025\\ A NEW EFFECTIVE ABC MULTICRITERIA CLASSIFICATION WITH ANALYTIC HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX} 
     %
@@
     \abstract{\textbf{Resumo:} Currently, most companies produce and market a wide variety of products.
-Because of this, clustering items has become a crucial step in the decision-making for manufacturing and purchasing management processes.
+Because of this, clustering items has become a crucial step in the decision-making for manufacturing and purchasing management processes, making it possible to apply different policies to each product's group, reducing the cost necessary for managing inventory.
 ABC multicriteria classification is a technique commonly used for clustering items.
@@
 However, since criteria's pairwise comparison matrices are usually generated manually and based only on some employee know-how, there is high complexity in elaborating a consistent pairwise matrix, especially when comparing several criteria.
-The attribution of weights to the products according to each criterion is also a difficult task cause there is a need for balancing all the quantitative values and the empirical values defined for the qualitative criteria.
-This paper presents a constructive algorithm that can adjust inconsistent pairwise comparison matrices, forcing such matrices to have a better consistency rate, and a balancing procedure for attributing weights to the products according to qualitative criteria as well as a new equation for ABC multicriteria classification.
+The attribution of weights to the products according to each criterion is also a difficult task cause there is a need to balance all the quantitative values and the empirical values defined for the qualitative criteria.
+This paper presents a constructive algorithm that can adjust inconsistent pairwise comparison matrices, forcing such matrices to have a better consistency rate, a balancing procedure for attributing weights to the products according to qualitative criteria, and a new equation for ABC multicriteria classification.
 We developed a new library for the COPSolver software by applying this new AHP method for the ABC multicriteria classification.
@@
 The scientific literature broadly emphasizes the value of multicriteria ABC classification for inventory management and presents several multicriteria methods.
-The Analytical Hierarchy Process is one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}.
+The Analytic Hierarchy Process is one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}.
 Some recent studies also emphasize the importance of applying multicriteria analysis to strategic planning \citep[\emph{e.g.},][]{BarbosaDePaula2022, Pereira2023, MarianoRibeiro2023}.
@@
 
-	\State $n \gets size(M[m_{ij}])$
 	\State $CR \gets$ consistencyRate($M[m_{ij}]$)
@@
 If, after the reduction, the convergence rate is still greater than the tolerance, the increment of values is made through the increase() function.
-
-\begin{algorithm}
-\caption{consistency checking}\label{alg:consistencyCheck}
-	\begin{algorithmic}
-	\Require $M[m_{ij}]$
-
-	\If{$m_{\{sz\}j} * m_{jk} = m_{\{sz\}k}$}
-		\State $consistent \gets 1$ \Comment{values are consistent}
-	\Else
-		\State $consistent \gets 0$ \Comment{values are not consistent}
-	\EndIf
-
-	\State \textbf{return} $consistent$
-
-\end{algorithmic}
-\end{algorithm}
+The bottomLeftCorner() function is similar to the topLeftCorner() function.
+In the topLeftCorner() function, the peer-to-peer comparison starts with the elements of the fourth row ($M[m_{\{sz\}j}]_{sz=4}^{n}$), and then the elements of the next rows are evaluated, following the order from top to bottom.
+In the case of the bottomLeftCorner() function, on the other hand, the pair-by-pair comparison is made starting with the elements of the anti-penultimate row ($sz = n-2$), then the elements of the previous rows are evaluated, following the order from bottom to top.
 
@@
 
-The bottomLeftCorner() function is similar to the topLeftCorner() function.
-In the topLeftCorner() function, the peer-to-peer comparison starts with the elements of the fourth row ($M[m_{\{sz\}j}]_{sz=4}^{n}$), and then the elements of the next rows are evaluated, following the order from top to bottom.
-In the case of the bottomLeftCorner() function, on the other hand, the pair-by-pair comparison is made starting with the elements of the anti-penultimate row ($sz = n-2$), then the elements of the previous rows are evaluated, following the order from bottom to top.
+\begin{algorithm}
+\caption{consistency checking}\label{alg:consistencyCheck}
+	\begin{algorithmic}
+	\Require $M[m_{ij}]$
+
+	\If{$m_{\{sz\}j} * m_{jk} = m_{\{sz\}k}$}
+		\State $consistent \gets 1$ \Comment{values are consistent}
+	\Else
+		\State $consistent \gets 0$ \Comment{values are not consistent}
+	\EndIf
+
+	\State \textbf{return} $consistent$
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 
-$lt_p$ is the of product $p$;
+$lt_p$ is the lead time of product $p$;
 
@@
 The date.txt files corresponding to these three benchmarks are available at https://tbfraga.github.io/COPSolver/ benchmarks/.
-Appendice A presents the data.txt file elaborated with the data provided by the furniture trades company.
 
@@
 
-For analysis of the proposed new methodology for ABC muticriteria classification, we will be focusing on the presentation and analysis of the data provided by the furniture trades company.
+After an extensive search of the scientific literature, we did not find benchmarks or numerical tests considering binary and qualitative criteria in the literature.
+Then, for analyzing the proposed new methodology for ABC multicriteria classification, we will focus on the presentation and analysis of the data provided by the furniture trades company.
 
 Figure \ref{fig:results} presents part of a comparison of the results obtained for the data described above, by ABC classification for the criteria billing and the new ABC multicriteria with Analytic Hierarch Process.
-Appendice A shows the file AHP\_Solution.txt, that presents the complete results found by the module 'COPSolver: library for solving the multicriteria classification problem'.
+The file AHP\_Solution.txt, that presents the complete results found by the module 'COPSolver: library for solving the multicriteria classification problem' can be found at https://tbfraga.github.io/COPSolver/benchmarks/clssp/alexia/adjusted-data/results/AHP\_solution.txt.
 We can see in this figure that the multicriteria classification includes in the group A all products previously classified as A according to the billing criterion, however the order of relevance of the products is changed.
@@
 
-    In this article we present a new methodology for multicriteria ABC classification with Analytical Hierarchy Process which includes a procedure to force the consitences of the pairwise comparisons matrices, as well as a procedure for assigning weights to the products evaluated according to qualitative criteria and a new equation for calculating the weights of the products in the multicriteria classification.
+    In this article we present a new methodology for multicriteria ABC classification with Analytic Hierarchy Process which includes a procedure to force the consitences of the pairwise comparisons matrices, as well as a procedure for assigning weights to the products evaluated according to qualitative criteria and a new equation for calculating the weights of the products in the multicriteria classification.
 This methodology was tested using data provided by three companies, from three different sectors.

### 2024-05-22 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating final version

@@
     \abstract{\textbf{Resumo:} Currently, most companies produce and market a wide variety of products.
-Because of this, clustering items has become a crucial step in the decision-making for manufacturing and purchasing management processes, making it possible to apply different policies to each product's group, reducing the cost necessary for managing inventory.
+Because of this, clustering items has become a crucial step in the decision-making for manufacturing and purchasing management processes, making it possible to apply different policies to each group, reducing the cost necessary for managing inventory.
 ABC multicriteria classification is a technique commonly used for clustering items.
@@
 This paper presents a constructive algorithm that can adjust inconsistent pairwise comparison matrices, forcing such matrices to have a better consistency rate, a balancing procedure for attributing weights to the products according to qualitative criteria, and a new equation for ABC multicriteria classification.
-We developed a new library for the COPSolver software by applying this new AHP method for the ABC multicriteria classification.
+We developed a new library for the COPSolver software by applying this new ABC multicriteria classification with AHP.
 We tested the proposed solutions to companies in three sectors.
-As a result, we observed that the algorithm for forcing consistency adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours and that the new solution method developed for multicriteria classification provided consistent results according to the analysis of company managers, both showing to be essential resources for applying the AHP and ABC multicriteria classification methods.}\\
+As a result, we observed that the algorithm for forcing consistency adjusts the pairwise matrices in just a few seconds, avoiding the manual work of several hours and that the new solution method developed for multicriteria classification provided consistent results, according to the analysis of the company managers, when compared to the ABC classification using only the billing criterion, showing to be essential resources for applying the AHP and ABC multicriteria classification methods.}\\
     %

### 2024-05-28 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - review - size and abstract ok
The abstract was rewritten to meet the defined number of words.

--- 2024-05-22 accepted/CONEM2024/MBPTMP/CONEM2024.tex
@@
     % Digitar o resumo
-    \abstract{\textbf{Resumo:} Among the most complex multi-product batch problems are the multi-product p-batch scheduling (MPBS) problems, where jobs must be scheduled on parallel batch processing machines.
-When applying some local search heuristics to solve a MPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products.
-We name this problem multi-product p-batch processing time maximization (MPBPTM) problem.
-Once a MPBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPBS problems.
-In addition, for some industries, efficiently solving a MPBPTM problem can have a significant impact on storage costs and customer satisfaction.
-In this paper we present a mathematical model and an exact method with polynomial time complexity for the MPBPTM problem.
-We developed a LINGO solver for solving the mathematic model, and a C++ solver for application of the proposed exact method.
-We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small and very large.
-As result, we find that the exact method can obtain optimal solutions in a very short time (just few seconds), even when solving very large instances.}\\
+    \abstract{\textbf{Resumo:} Multi-product batch (MPB) problems arise in manufacturing environments where several batches of products are processed sequentially, sharing the same set of production units.
+Among the most well-known MPB problems stands out the multi-product batch scheduling (MPBS) problems, whose objective is to find one of the feasible batch processing schedules that best meets a set of objectives predefined by the company.
+Along with the most complex MPBS problems are the multi-product p-batch scheduling (MPpBS) problems, where the schedule occurs on parallel batch processing machines.
+When applying some local search heuristics to solve the MPpBS problem, it can be necessary to iteratively solve a single-stage multi-product p-batch sizing problem with different processing rates for each product, limited capacity units, and storage capacity defined both for each product and for all products (named in this article multi-product p-batch processing time maximization (MPpBPTM) problem).
+Then, the efficiency of the method developed for solving an MPpBPTM problem exerts a decisive influence on the computational cost of the local search algorithm applied to solve some MPpBS problems.
+In addition, the efficiency of solving an MPpBPTM problem can significantly impact storage costs and customer satisfaction.
+This article presents a mathematical model and an exact method with polynomial time complexity for the MPpBPTM problem.
+We developed a LINGO solver for solving the mathematical model and a C++ COPSolver library for applying the proposed exact method.
+We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small-scale and very large-scale.
+As a result, we found that both solvers can obtain optimal solutions in just a few seconds, even when solving very large-scale instances.
+However, the exact method is much more efficient since it solves the problem in polynomial time.
+In addition, the modular structure of the library developed for COPSolver allows the easy application of the proposed solution method when developing new heuristics for solving MPpBS problems, making this tool a significant technological contribution to the production management of some industries as well as for researchers in the area.}\\
     %
@@
 This problem is named multi-product batch sizing.
-\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production, and \cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product serial batching sizing problem in a divergent networked plant of a steel industry (Fig.
-\ref{fig:networkdPlantSteelIndustry}).
-
-\begin{figure}[ht]
-\label{fig:networkdPlantSteelIndustry}
-\begin{center}
-\begin{tikzpicture}[font=\sffamily,every label/.append style={font=\small\sffamily,align=center}]
-
-\node[cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP00){};
-\node[rectangle, draw, right=0.5cm of WIP00, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit00){};
-\node[draw,dashed,rounded corners,fit=(WIP00) (unit00),inner sep=25pt,label={above:{stage (0,0)}}](stage00){};
-
-\node[above right=2cm and 4cm of WIP00, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP11){};
-\node[rectangle, draw, right=0.5cm of WIP11, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit11){};
-\node[draw,dashed,rounded corners,fit=(WIP11) (unit11),inner sep=25pt,label={above:{stage (1,1)}}](stage11){};
-
-\draw[-latex] (stage00.east) -- (stage11.west);
-
-\node[right=2.5cm of stage00, minimum width=1cm, minimum height=1.4cm](WIP1){.....};
-
-\node[right=0.3cm of WIP1, minimum width=1cm, minimum height=1.4cm](WIP1a){};
-
-\draw[-latex] (stage00.east) -- (WIP1.west);
-
-\node[below right=2cm and 4cm of WIP00, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIPp1){};
-\node[rectangle, draw, right=0.5cm of WIPp1, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unitp1){};
-\node[draw,dashed,rounded corners,fit=(WIPp1) (unitp1),inner sep=25pt,label={above:{stage (p,1)}}](stagep1){};
-
-\draw[-latex] (stage00.east) -- (stagep1.west);
-
-\node[right=4cm of WIP11, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIP1m){};
-\node[rectangle, draw, right=0.5cm of WIP1m, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unit1m){};
-\node[draw,dashed,rounded corners,fit=(WIP1m) (unit1m),inner sep=25pt,label={above:{stage (1,m$_1$)}}](stage1m){};
-
-\draw[-latex] (stage11.east) -- (stage1m.west);
-
-\node[right=4cm of WIPp1, cylinder, cylinder uses custom fill, minimum width=0.8cm, minimum height=1.4cm, shape border rotate=90, aspect=0.5, draw, label={below:{work-in-progress}}](WIPpm){};
-\node[rectangle, draw, right=0.5cm of WIPpm, minimum width=1cm, minimum height=1cm, label={above:{unit}}](unitpm){};
-\node[draw,dashed,rounded corners,fit=(WIPpm) (unitpm),inner sep=25pt,label={above:{stage (p,m$_p$)}}](stagepm){};
-
-\draw[-latex] (stagep1.east) -- (stagepm.west);
-
-\node[right=3.5cm of WIP1, minimum width=1cm, minimum height=1.4cm](WIPm){.....};
-
-\node[left=0.5cm of WIPm, minimum width=1cm, minimum height=1.4cm](WIPma){};
-
-\draw[-latex] (WIP1a.east) -- (WIPma.west);
-
-\end{tikzpicture}
-\end{center}
-\caption{\textbf{Multi-product serial batching divergent networked plant of a steel industry. Source: adapted from \cite{LiuEtAl2020} * stage $(i, j)$ means stage $j$ of production line $i$.}}
-\end{figure}
+\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production, and \cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product serial batching sizing problem in a divergent networked plant of a steel industry.
 

### 2024-05-28 accepted/CONEM2024/MBPTMP/Review/Template-Latex-CONEM2024/CONEM2024.tex
updating article - review - size and abstract ok
The abstract was rewritten to meet the defined number of words.

% MODELO CONEM 2022 - Obs. Adequado para o CONEM 2024.
%
% Date: January 12, 2024
%
\documentclass[10pt,fleqn,a4paper,twoside]{article}
\usepackage{abcm}
\def\shortauthor{P. Autor, S. Autor e T. Autor \textcolor[rgb]{0.98,0.00,0.00}{(Atualize o cabeçalho de acordo)}}
\def\shorttitle{Versão Reduzida do Título do Artigo \textcolor[rgb]{0.98,0.00,0.00}{(Letras Iniciais em Caixa Alta, certifique que não ultrapasse uma linha)}}

\begin{document}

    % CABEÇALHO
    \thispagestyle{empty}
    \begin{figure}[h]
        \begin{center}
            \includegraphics[angle=0, width=\textwidth]{Logo_template.png}
        \end{center}
    \end{figure}
    \vspace{-.5cm}
    \hspace{-.8cm}
    \begin{tabular}{||p{\textwidth}}
    \begin{center}
    \vspace{-.6cm}
    %
    % Digitar o título
    \title{CONEM2024-XXXX \textcolor{red}{(XXXX é a identificação do artigo final)} \\ INSTRUÇÕES PARA A FORMATAÇÃO DE TRABALHOS SUBMETIDOS PARA PUBLICAÇÃO NOS ANAIS DO XII CONGRESSO NACIONAL DE ENGENHARIA MECÂNICA}
    %
    \end{center}
	%
	% Digitar os nomes dos autores/instituição
    \authors{Nome do primeiro autor, e-mail$^1$} \\
    \authors{Nome do segundo autor, e-mail$^1$} \\
    \authors{Nome do terceiro autor, e-mail$^2$} \\\\
    \institution{$^1$Nome da instituição, endereço para correspondência (institucional, se houver)} \\
    \institution{$^2$Nome da instituição, endereço para correspondência (institucional, se houver)} \\
    \\
    \authors{\textcolor[rgb]{0.98,0.00,0.00}{Mesmo  formato para outros autores e instituições, se houver. (\textit{Esta orientação deve ser retirada no texto final.})}} \\
    \\
    %
    % Digitar o resumo
    \abstract{\textbf{Resumo:} O resumo deve descrever os objetivos, o contexto e a importância da pesquisa, os métodos, os resultados e as principais conclusões do artigo. {\bf Não deve conter} fórmulas nem referências bibliográficas. Deve ser escrito em apenas um parágrafo e conter de 300 a 400 palavras.}\\
    %
    % Digitar as palavras-chave
   \\
    \keywords{\textbf{Palavras-chave:} palavra 1, palavra 2, palavra 3 (até 5 palavras, separadas  por vírgulas) }\\
    %
    \end{tabular}

    \section{INTRODUÇÃO}

        O objetivo destas instruções é servir de guia para a formatação dos trabalhos a serem publicados nos anais. Os anais do XII CONEM serão publicados no formato Adobe$^{\small{TM}}$ PDF.

        Os artigos \textcolor{red}{\underline{\textbf{DEVEM}}} ser formatados de acordo com estas instruções. O presente arquivo pode ser usado como modelo por usuários do \LaTeX. Além disso, pode ser usado como um guia de formatação para usuários de outros processadores de texto.

        Os trabalhos (\textit{draft} e \textit{final paper}) estão limitados a no mínimo \textcolor{red}{\underline{\textbf{6 páginas}}} e no máximo \textcolor{red}{\underline{\textbf{10 páginas}}}, incluindo tabelas e figuras. O arquivo final em formato PDF não deve exceder 2 MB.

        A língua oficial do congresso é o português; entretanto serão aceitos manuscritos em espanhol ou em inglês. Se o trabalho não for escrito em inglês, o autor deverá incluir o título, os nomes dos autores e afiliações, o resumo e as palavras-chave, traduzidos para o inglês, após a lista de referências, no fim do artigo.

    \section{FORMATO DO TEXTO}

        O artigo deve ser digitado no \textit{template} ``CONEM2024.tex'' e as principais configurações (ex.: formato do papel, tipo e tamanho da fonte do título/Seção/Subseção, espaços, margens, alinhamentos, indentação, etc.) já estão previamente configuradas no arquivo ``abcm.sty''. Título, nomes dos autores, instituição, endereço, resumo e palavras-chave devem ser recuados 0,1 cm da margem esquerda e marcados por uma linha preta na borda esquerda com largura de 2$\frac{1}{4}$ pontos.

        Informações suficientes devem ser fornecidas diretamente no texto, ou por referência a trabalhos publicados disponíveis. Notas de rodapé devem ser evitadas.

        Todos os símbolos e notações devem ser definidos no texto. As grandezas físicas devem ser expressas no Sistema Internacional de Unidades. Os símbolos matemáticos que aparecem no texto devem ser digitados em itálico. As unidades devem ser digitadas no estilo romano (ex.: kg, m, MJ, kW/m$^2$, em vez de $kg$, $m$, $MJ$, $kW/m^2$).

        As referências bibliográficas devem ser citadas no texto dando o sobrenome do(s) autor(es) e o ano de publicação, conforme os seguintes exemplos: ``... conforme apresentado \citep{MinwooShamim13}.'' ou ``Recentemente, \citet{MinwooShamim13} demonstraram que …''. No caso de três ou mais autores, deve ser utilizada a expressão ``\textit{et al.}'', como segue: ``... conforme já relatado \citep{Bordalo89}'' e ``Recentemente, \citet{Bordalo89} demonstraram que …''. Duas ou mais referências com os mesmos autores e ano de publicação devem ser distinguidas acrescentando ``a'', ``b'', etc., ao ano de publicação. No caso da necessidade de citar vários trabalhos em uma mesma chamada, o seguinte formato pode ser utilizado: ``...já se encontra consolidado na literatura (\citeauthor{Coimbra78}, \citeyear{Coimbra78}; \citeauthor{Clark86}, \citeyear{Clark86} e \citeauthor{Sparrow80},  \citeyear{Sparrow80})''.

        As referências devem ser listadas no final do manuscrito de acordo com as instruções fornecidas na Seção 4.

        \textbf{\textcolor[rgb]{0.98,0.00,0.00}{\underline{NÃO NUMERAR AS PÁGINAS.}}}

    \subsection{Títulos e Subtítulos das Seções }

        Os títulos das seções são com letras maiúsculas (Exemplo: \textbf{MODELO MATEMÁTICO}), enquanto os subtítulos só têm as primeiras letras maiúsculas de cada palavra (Exemplo: \textbf{Modelo Matemático}). Eles devem ser numerados, usando numerais arábicos separados por pontos, até o máximo de 3 subníveis. Uma linha em branco de espaçamento simples deve ser incluída acima e abaixo de cada título ou subtítulo.

    \subsection{Corpo do Texto}

        Conforme já se encontra definido no arquivo ``abcm.sty'', o corpo do texto é justificado e com espaçamento simples. A primeira linha de cada parágrafo tem recuo de 0,5 cm a partir da margem esquerda.

        As equações matemáticas são alinhadas à esquerda com recuo de 0,5 cm.  Elas são referidas como ``Eq. (\ref{eq:equation1})'' no meio de uma frase, ou ``Equação (\ref{eq:equation1})'' quando usada no início de uma sentença. Os números das equações são numerais arábicos colocados entre parênteses, e alinhados à direita, como mostrado na Eq. (\ref{eq:equation1}). Os símbolos usados nas equações devem ser definidos imediatamente antes ou depois de sua primeira ocorrência no texto.

        O tamanho da fonte usado nas equações deve ser compatível com o utilizado no texto. Todas as grandezas físicas devem ter suas unidades expressas no Sistema Internacional de Unidades, como já mencionado.

        \begin{equation}
        \sigma = E \cdot \epsilon. \label{eq:equation1}
        \end{equation}

    	\noindent
    	onde: $\sigma$ é a tensão, $E$ é o módulo de elasticidade longitudinal (ou Módulo de Young) e $\epsilon$ é a deformação longitudinal.

        As figuras e tabelas devem ser colocadas no texto o mais próximo possível do ponto em que foram mencionadas pela primeira vez e devem ser numeradas consecutivamente em algarismos arábicos. As tabelas devem ser centralizadas e referidas por ``Tab. \ref{tab:tabexemplo}'' no meio de uma frase, ou por ``Tabela \ref{tab:tabexemplo}'' quando usada no início de uma sentença. Uma linha em branco, em espaço simples, deve ser introduzida entre a tabela e o texto subsequente.

        Anotações e valores numéricos incluídos na tabela devem ter tamanhos compatíveis com a fonte usada no texto do trabalho e todas as unidades devem ser expressas no Sistema Internacional de Unidades. As unidades são incluídas apenas na primeira linha ou primeira coluna de cada tabela, conforme for apropriado. O estilo de borda é livre. As explicações, se houver, devem ser fornecidas ao pé das tabelas e não dentro das mesmas.

        \begin{table}[ht]
            \begin{center}
                \caption{\textbf{Exemplo de tabela.}}
                    \begin{tabular}{c|c|c}
                    \hline
                    Propriedades do compósito       & CFRC-TWILL        & CFRC-4HS         \\
                    \hline
                    Resistência à Flexão  (MPa)     & 209.0 $\pm$ 10.0       & 180.0 $\pm$  15.0    \\
                    \hline
                    Módulo de Flexão  (GPa)         & 57.0 $\pm$ 2.8    & 18.0 $\pm$  1.3  \\
                    \hline
                    \end{tabular} \label{tab:tabexemplo}
            \end{center}
        \end{table}

        As figuras devem ser centralizadas. Elas são referenciadas por ``Fig. \ref{fig:figexemplo}'' no meio de uma frase ou por ``Figura \ref{fig:figexemplo}'' quando usada no início de uma sentença. Sua legenda deve ser centralizada e localizada imediatamente abaixo da figura. As anotações e numerações devem ter tamanhos compatíveis com a fonte usada no texto e todas as unidades devem ser expressas no Sistema Internacional de Unidades. As figuras devem ser colocadas o mais próximo possível de sua primeira citação no texto. Deve ser deixada uma linha em branco, de espaçamento simples, entre a figura e o texto subsequente.

        \begin{figure}[h]
            \begin{center}
                \includegraphics[angle=0, scale=.8]{figura.png}
            \end{center}
            \caption{\textbf{Exemplo de figura.}}
            \label{fig:figexemplo}
        \end{figure}

        Figuras coloridas e fotografias de alta qualidade podem ser incluídas no trabalho. Para reduzir o tamanho do arquivo e preservar a resolução gráfica, os arquivos das imagens podem ser convertidos para o formato GIF (para figuras com até 16 cores) ou para o formato JPEG (alta densidade de cores), antes de serem inseridos no trabalho.

    \section{AGRADECIMENTOS}

        Se houver, esta seção deve ser colocada antes da lista de referências.

    % REFERÊNCIAS
    \section{REFERÊNCIAS}

         %   \citet{key} ==>>                Jones et al. (1990)
         %   \citet*{key} ==>>               Jones, Baker, and Smith (1990)
         %   \citep{key} ==>>                (Jones et al., 1990)
         %   \citep*{key} ==>>               (Jones, Baker, and Smith, 1990)
         %   \citep[chap. 2]{key} ==>>       (Jones et al., 1990, chap. 2)
         %   \citep[e.g.][]{key} ==>>        (e.g. Jones et al., 1990)
         %   \citep[e.g.][p. 32]{key} ==>>   (e.g. Jones et al., p. 32)
         %   \citeauthor{key} ==>>           Jones et al.
         %   \citeauthor*{key} ==>>          Jones, Baker, and Smith
         %   \citeyear{key} ==>>             1990

        Referências aceitas incluem: artigos de periódicos, dissertações, teses, artigos publicados em anais de congressos, livros, comunicações privadas e artigos submetidos e aceitos (com fonte identificada) e citações a páginas da internet.

        A lista de referências deve ser uma seção específica denominada Referências, localizada no fim do artigo.

        A primeira linha de cada referência deve ser alinhada à esquerda, sendo que as demais terão recuo já configurado a partir da margem esquerda. Todas as referências incluídas na lista devem aparecer como citações no texto do trabalho.

        As referências devem ser postas em ordem alfabética, usando o último nome do primeiro autor, seguida do ano da publicação. Exemplo da lista de referências é apresentado abaixo.

        \bibliographystyle{abcm}
        \bibliography{bibliografia}

    \section{RESPONSABILIDADE AUTORAIS}

        Os trabalhos escritos em português ou espanhol devem incluir (após direitos autorais) título, os nomes dos autores e afiliações, o resumo e as palavras-chave, traduzidos para o inglês e a declaração a seguir, devidamente adaptada para o número de autores.

        O(s) autor(es) é(são) o(s) único(s) responsável(is) pelo conteúdo deste trabalho.

 % RESUMO EM INGLES

\noindent{
   \\ 
    \begin{tabular}{||p{\textwidth}}
    \begin{center}
    \vspace{-.6cm}
    \title{AFTER FULL PAPER IN PORTUGUESE OR SPANISH, IT IS NECESSARY THE ABSTRACT IN ENGLISH}
    \end{center}
    \authors{First Author’s Name, e-mail1$^1$} \\
    \authors{Second Author’s Name, e-mail$^2$} \\
    \authors{Third Author’s Name, e-mail$^2$} \\\\
    \institution{$^1$Institution and address for first author} \\
    \institution{$^2$Institution and address for second and third authors} \\
    \\
    \authors{\textcolor[rgb]{0.98,0.00,0.00}{Same format for other authors and institutions, if any. (\textit{This guidance should be removed from the final paper.})}} \\
    \\
    \abstract{\textbf{Abstract:} The purpose of these instructions is to serve as a guide for formatting papers to be published in the Proceedings of the XII CONEM. The abstract must describe the objectives, methodology and main conclusions of the article, containing between 300 and 400 words in a single paragraph.  It should not contain either formulae or bibliographic references. The full paper will be published in the proceedings of the event.}\\
    \\
    \keywords{\textbf{Keywords:} keyword 1, keyword 2, keyword 3 (up to 5 keywords) }\\
    \end{tabular}
}

\end{document}

### 2024-05-28 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating paper - review - number of pages
Figure 1 was removed so that the number of pages of the article was reduced.
section 3, 4 and 5
3) Trocar item "2. MULTI-PRODUCT P-BATCH PROCESSING TIME MAXIMIZATION PROBLEM" por "2. MATERIALS AND METHODS" para fins de melhor organização do trabalho; 4) Trocar item "3. ANALYTICAL SOLUTION" por "3. RESULTS AND DISCUSSION";

Foi criada uma seção "MATERIALS AND METHODS". As seções anteriores foram inseridas dentro desta como sub-seções.

O título da seção "TETS AND RESULTS" foi substituído por "RESULTS AND DISCUSSION"

--- 2024-05-28 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
@@
 
-\section{MULTI-PRODUCT P-BATCH PROCESSING TIME MAXIMIZATION PROBLEM}
+\section{MATERIALS AND METHODS}
+\subsection{Multi-product p-Batch Processing Time Maximization Problem}
 \label{sec:MBPTMP}
@@
 
-\section{ANALYTICAL SOLUTION}
+\subsection{Analytical Solution}
 \label{sec:analyticalSol}
@@
 The Algorithm (\ref{alg:part01}) is used for finding an optimimal value for $T$.
+Then an initial production distribution can be done by the Algorithm (\ref{alg:part02}).
+This distribution is made without considering the restrictions defined for the set of products.
+$SO$ and $SI$ represent, respectively, the total amount that can be sent to the outlets and the total amount that can be stocked in factory after the initial distribution.
+If this values are negative, this indicates that the proposed initial distribution is not a feasible distribution.
 
-\begin{algorithm}
+\begin{algorithm}[h!]
 \caption{Solving MBPTM problem | Part 01 - find an optimal $T$ to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}).}\label{alg:part01}
@@
 \end{algorithm}
-
-Then an initial production distribution can be done by the Algorithm (\ref{alg:part02}).
-This distribution is made without considering the restrictions defined for the set of products.
-$SO$ and $SI$ represent, respectively, the total amount that can be sent to the outlets and the total amount that can be stocked in factory after the initial distribution.
-If this values are negative, this indicates that the proposed initial distribution is not a feasible distribution.
 
@@
 However, if $SO < 0$ or $SI <0$, solution is not yet feasible.
-But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements:
+But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements: \\
 
-$if \quad SO < 0 \quad then \quad SI > 0 \quad and  \quad |SO| < SI$
+$if \quad SO < 0 \quad then \quad SI > 0 \quad and  \quad |SO| < SI$ \\
 
-$if \quad SI < 0 \quad then \quad SO > 0 \quad and  \quad |SI| < SO$
+$if \quad SI < 0 \quad then \quad SO > 0 \quad and  \quad |SI| < SO$ \\
 
@@
 
-\begin{algorithm}
+\begin{algorithm}[h!]
 \caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch set.}\label{alg:part03}
@@
 
-\section{TESTS AND RESULTS}
+\section{RESULTS AND DISCUSSION}
 \label{sec:results}
@@
 
-\section{COPYRIGHT LIABILITY}
-
-        The authors are uniquely responsible for the content of this work.
-
     % REFERÊNCIAS
@@
 
+\section{COPYRIGHT LIABILITY}
+
+        The authors are uniquely responsible for the content of this work.
+
 \end{document}

### 2024-05-29 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article
1) Corrigir tamanho e tipo de fonte colocadas no cabeçalho, usando como base o template fornecido por este congresso;

Estou usando o template fornecido pelo congresso.

6) Colocar todas as letras do item 6 em maiúsculas;

feito

7) Apenas uma linha em branco, em espaço simples, deve ser introduzida entre as tabelas/figuras/equações e o texto subsequente;

Texto escrito em latex. Asando arquivo abcm.sty e modelos disponibilizados. Deixando apenas uma linha entre textos e figuras / equações / tabelas. Formatação é feita automaticamente conforme definido no arquivo abcm.sty.
upd

@@
 The scientific literature address many different problems related to such industrial enviroment, including the design, planning, sizing, scheduling and balancing problems.
-The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
+The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.
 The configuration of the plant basically consists of defining the number of stages, the number of units and their capacity per stage, and the capacity for intermediate storages, as well as the best factory layout.
@@
 The work presented in this article is part of a project in which we propose the modeling and solution of a multiperiod multi-product batch scheduling problem that arises in a networked plant of a plastic bag industry.
-The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020} and illustrated in Fig.
-(\ref{fig:networkdPlantSteelIndustry} ), however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
+The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020}, however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
 Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}.
@@
 Also, in the problem we study, in addition to demand, we must consider the factory and outlets' storage capacity, which is individually defined for products, but also for the set of products.
-
 When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product p-batches, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
@@
 For simplification purposes, we named this problem multi-product p-batch processing time maximization (MPBPTM) problem.
-
 It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product p-batch s-batch problem in the plastic bag networked plant of the industry studied.
@@
 
-where constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$.
-Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$.
-Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the outlets, and the factory-stocked quantity of each product must be less than their respective known limits.
-Constraints (6) and (8) state that both the sum of product quantities sent to the outlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values.
-The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
-Equations in (10) and (11) define the production distribution priority.
-And finally, the constraints in (12) inform the nature of the decision variables.
+where constraints in Eq.
+(2) relate the quantity produced, $P_i$, to batch processing time $T$.
+Constraints in Eq.
+(3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$.
+Constraints in Eq.
+(4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the outlets, and the factory-stocked quantity of each product must be less than their respective known limits.
+Constraints deined by Eq.
+(6) and (8) state that both the sum of product quantities sent to the outlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values.
+The restriction in Eq.
+(9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
+Equations (10) and (11) define the production distribution priority.
+And finally, the constraints in Eq.
+(12) inform the nature of the decision variables.
 
@@
 
-From the equations in (\ref{eq:s02}) and the restrictions in (\ref{eq:s03}) and (\ref{eq:s04}), we have:
+From the Eq. (\ref{eq:s02}) and the restrictions in Eq. (\ref{eq:s03}) and (\ref{eq:s04}), we have:
 
@@
 
-And, as we wish maximum value to $T'$, from (\ref{eq:s05}) we have:
+And, as we wish maximum value to $T'$, from Eq. (\ref{eq:s05}) we have:
 
@@
 Observe that there may be a leftover corresponding to the demand not met by the production in the first part of the processing time, $T'$.
-This leftover, $S_i$, will be defined according to the equations in (\ref{eq:s07}):
+This leftover, $S_i$, will be defined according to the equations in Eq.
+(\ref{eq:s07}):
 
@@
 
-\noindent Thus, after replacing (\ref{eq:s12}) in (\ref{eq:s09}) and applying some algebra, we have:
+\noindent Thus, after replacing Eq. (\ref{eq:s12}) in Eq. (\ref{eq:s09}) and applying some algebra, we have:
 
@@
 
-\noindent And, after replacing (\ref{eq:s12}) in (\ref{eq:s10}) and applying some algebra, we have:
+\noindent And, after replacing Eq. (\ref{eq:s12}) in Eq. (\ref{eq:s10}) and applying some algebra, we have:
 
@@
 
-We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply attending the priorities for distribution. The following three algorithms can be used to find a complete solution.
-
-The Algorithm (\ref{alg:part01}) is used for finding an optimimal value for $T$.
+We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply attending the priorities for distribution.
+The following three algorithms can be used to find a complete solution: The Algorithm (\ref{alg:part01}) is used for finding an optimimal value for $T$.
 Then an initial production distribution can be done by the Algorithm (\ref{alg:part02}).
@@
 If this values are negative, this indicates that the proposed initial distribution is not a feasible distribution.
+So, after applying Algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
+However, if $SO < 0$ or $SI <0$, solution is not yet feasible.
+But as the solution found to $T$ is feasible to the problem defined in Eq.
+(\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements: \\
+
+$if \quad SO < 0 \quad then \quad SI > 0 \quad and  \quad |SO| < SI$ \\
+
+$if \quad SI < 0 \quad then \quad SO > 0 \quad and  \quad |SI| < SO$ \\
 
@@
 \end{algorithm}
-
-So, after applying Algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
-However, if $SO < 0$ or $SI <0$, solution is not yet feasible.
-But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements: \\
-
-$if \quad SO < 0 \quad then \quad SI > 0 \quad and  \quad |SO| < SI$ \\
-
-$if \quad SI < 0 \quad then \quad SO > 0 \quad and  \quad |SI| < SO$ \\
 
@@
 The tests were performed on a notebook with an Intel i7 processor.
-We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\
+We tested the solvers developed for the benchmarks presented on Tab.
+\ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\
 
@@
 Table \ref{tab:results} presents the results obtained by applying the analytical method (COPSolver) and the LINGO solver for the solution of the previously presented benchmarks.
+Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MBPTM 3 and 10 found by both COPSolver and LINGO solver.
+Files containing all results can be found at github.com/tbfraga/COPSolver.
+It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
+It is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large-scale problems.
+However, as the analytical method is a polynomial time complexity method, it is much more efficient.
+In addition, the modular structure of the library developed for COPSolver allows the easy application of the proposed solution method when developing new heuristics for solving MPpBS problems, making this tool a significant technological contribution to the production management of some industries as well as for researchers in the area.
+Since we have considered here a static problem, in a future work we will study the complexities of solving the problem dynamically and try to propose new solution methods if needed.
 
@@
 \end{table}
-
-Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MBPTM 3 and 10 found by both COPSolver and LINGO solver.
-Files containing all results can be found at github.com/tbfraga/COPSolver.
 
@@
 
-It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
-As the analytical method is a polynomial time complexity method, we did not intend to compare computational costs, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
-
-We have considered here a static problem, so in a future work we will study the complexities of solving the problem dynamically and try to propose new solution methods if needed.
-
 \section{CONCLUSIONS AND SUGGESTIONS FOR FUTURE WORKS}
@@
 
-\section{CRediT AUTHORSHIP CONTRIBUTION STATEMENT} 
+\section{CREDIT AUTHORSHIP CONTRIBUTION STATEMENT} 
 \label{sec:contributions}

### 2024-05-29 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - improving text

@@
 Using the notation presented before, this problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU,$ $PSC, SC, DPR$ problem.
-For simplification purposes, we named this problem multi-product p-batch processing time maximization (MPBPTM) problem.
+For simplification purposes, we named this problem multi-product p-batch processing time maximization (MPpBPTM) problem.
 It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product p-batch s-batch problem in the plastic bag networked plant of the industry studied.
 In a future work, we intend to present the mathematical model and a Particle Collison based solution algorithm we are developing for this last problem.
-As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPBPTM problem.
+As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPpBPTM problem.
 
 The rest of the paper is organized as follows.
-In the next sections, the MPBPTM problem is introduced.
+In the next sections, the MPpBPTM problem is introduced.
 Section 2.1 describes an interger mathematical model for the problem and section 3 shows an analytical method for its solution.
@@
 \section{MATERIALS AND METHODS}
+
+The method applied in this work consists of identifying new optimization problems, and mathematically modeling as well as proposing a new solution methodology for the identified problems.
+The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, as cited in this article.
+The following sections present the new interger programming problem identified (MPpBPTM) and an exact analytical method developed for solving it.
+
 \subsection{Multi-product p-Batch Processing Time Maximization Problem}
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem and also a solver in LINGO named MBPTM.lng both available at codeocean and GitHub.
+To test the developed model and analytical solution method, we created a solver in LINGO named MBPTM.lng and also a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem, both available at codeocean and GitHub.
 A brief explanation of the software and links for downloads can be found in the paper of \cite{Fraga2023}.
@@
 \begin{center}
-\caption{\textbf{Benchmark MPBPTM 2.}}
+\caption{\textbf{Benchmark MPpBPTM 2.}}
 \begin{tabular}[c]{c r r r}
@@
 \begin{center}
-\caption{\textbf{Benchmark MPBPTM 3.}}
+\caption{\textbf{Benchmark MPpBPTM 3.}}
 \begin{tabular}[c]{c r r r r}
@@
 \begin{center}
-\caption{\textbf{Benchmark MPBPTM 10.}}
+\caption{\textbf{Benchmark MPpBPTM 10.}}
 \begin{small}
@@
 
-Randomly generated benchmarks were named RMPBPTM $\textrm{N}$, being $\textrm{N}$ the number of products.
+Randomly generated benchmarks were named RMPpBPTM $\textrm{N}$, being $\textrm{N}$ the number of products.
 Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
 To build the results presented in this work, we used source=0.
-The benchmarks used for the tests performed can be consulted at github.com/tbfraga/COPSolver.
+Files containing benchmarks used for the tests performed and all results can be found at tbfraga.github.io/COPSolver/benchmarks.
 
 Table \ref{tab:results} presents the results obtained by applying the analytical method (COPSolver) and the LINGO solver for the solution of the previously presented benchmarks.
-Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MBPTM 3 and 10 found by both COPSolver and LINGO solver.
-Files containing all results can be found at github.com/tbfraga/COPSolver.
+Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MPpBPTM 3 and 10 found by both COPSolver and LINGO solver.
 It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
@@
 \cline {1-5} \\
-MPBPTM 2 & 55 & 0.03 & 55 & $<$ 0.01 \\
-MPBPTM 3 & 48 & 0.03 & 48 & $<$ 0.01 \\
-MPBPTM 10 & 30 & 0.05 & 30 & $<$ 0.01 \\
-RMPBPTM 20 & 100 & 0.06 & 100 & $<$ 0.01 \\
-RMPBPTM 50 & 98 & 0.08 & 98 & $<$ 0.01 \\
-RMPBPTM 100 & 98 & 0.11 & 98 & $<$ 0.01 \\
-RMPBPTM 1,000 & 78 & 1.20 & 78 & $<$ 0.01 \\
-RMPBPTM 2,000 & 70 & 3.25 & 70 & $<$ 0.01 \\
-RMPBPTM 5,000 & 70 & 15.12 & 70 & $<$ 0.02 \\
-RMPBPTM 10,000 & 70 & 55.19 & 70 & $<$ 0.04 \\
+MPpBPTM 2 & 55 & 0.03 & 55 & $<$ 0.01 \\
+MPpBPTM 3 & 48 & 0.03 & 48 & $<$ 0.01 \\
+MPpBPTM 10 & 30 & 0.05 & 30 & $<$ 0.01 \\
+RMPpBPTM 20 & 100 & 0.06 & 100 & $<$ 0.01 \\
+RMPpBPTM 50 & 98 & 0.08 & 98 & $<$ 0.01 \\
+RMPpBPTM 100 & 98 & 0.11 & 98 & $<$ 0.01 \\
+RMPpBPTM 1,000 & 78 & 1.20 & 78 & $<$ 0.01 \\
+RMPpBPTM 2,000 & 70 & 3.25 & 70 & $<$ 0.01 \\
+RMPpBPTM 5,000 & 70 & 15.12 & 70 & $<$ 0.02 \\
+RMPpBPTM 10,000 & 70 & 55.19 & 70 & $<$ 0.04 \\
 \cline {1-5} \\
@@
 \begin{center}
-\caption{\textbf{Results obtained with the LINGO solver and COPSolver for the MPBPTM 3.}}
+\caption{\textbf{Results obtained with the LINGO solver and COPSolver for the MPpBPTM 3.}}
 \begin{footnotesize}
@@
 \\
-product & production & delivered (s) & send to outlets & stocked in factory \\
+product & production & delivered & send to outlets & stocked in factory \\
 \cline {1-5} \\
@@
 \begin{center}
-\caption{\textbf{Results obtained with the LINGO solver and COPSolver for the MPBPTM 10.}}
+\caption{\textbf{Results obtained with the LINGO solver and COPSolver for the MPpBPTM 10.}}
 \begin{footnotesize}
@@
 The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO software, from LINDO Systems, and with a solver developed in C++ language.
-Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large problems, which demonstrates the efficiency of the proposed method.
+Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large-scale problems, which demonstrates the efficiency of the proposed method.
 As in this paper we considered a static problem, in a future work we will study the complexities that arise when considering the same problem in a dinamic scenario.

### 2024-05-29 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - improving

@@
 For simplification purposes, we named this problem multi-product p-batch processing time maximization (MPpBPTM) problem.
-It is important to note that, since the MPBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product p-batch s-batch problem in the plastic bag networked plant of the industry studied.
+It is important to note that, since the MPpBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product p-batch s-batch problem in the plastic bag networked plant of the industry studied.
 In a future work, we intend to present the mathematical model and a Particle Collison based solution algorithm we are developing for this last problem.
@@
 In the next sections, the MPpBPTM problem is introduced.
-Section 2.1 describes an interger mathematical model for the problem and section 3 shows an analytical method for its solution.
-Section 4 displays the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
-Section 5 presents the paper's conclusions and suggestions for future works.
-Finally, in sections 6 and 7, the contributions to this work are informed and acknowledgments are given, respectively.
+Section 2.2 describes an interger mathematical model for the problem and section 2.3 shows an analytical method for its solution.
+Section 3 displays the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
+Section 4 presents the paper's conclusions and suggestions for future works.
+Finally, in sections 5 and 6, the contributions to this work are informed and acknowledgments are given, respectively.
 

### 2024-05-29 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - improving text

@@
 
-The multi-product p-batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
+The MPpBPTM problem arises when a set of different products are processed simultaneously in a same production batch.
 In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product.
@@
 About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.
+The problem is to identify the maximum feasible time for the multi-product p-batch processing.
 
@@
 
-The method proposed in this paper for solution of the MPBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the part of the production used to meet demand, the part of the production sent to outlets and the part of the production stocked in factory.
+The method proposed in this paper for solution of the MPpBPTM problem is composed of two distinct parts, which are: a) calculation of the maximum processing time of the predefined multi-product p-batch; and b) calculation of the part of the production used to meet demand, the part of the production sent to outlets and the part of the production stocked in factory.
 Next, we explain each of these parts in detail.
@@
 \begin{algorithm}[h!]
-\caption{Solving MBPTM problem | Part 01 - find an optimal $T$ to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}).}\label{alg:part01}
+\caption{Solving MPpBPTM problem | Part 01 - find an optimal $T$ to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}).}\label{alg:part01}
 \begin{algorithmic}
@@
 \begin{algorithm}
-\caption{Solving MBPTM problem | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions for the set of products of the batch.}\label{alg:part02}
+\caption{Solving MPpBPTM problem | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions for the set of products of the batch.}\label{alg:part02}
 \begin{algorithmic}
@@
 \begin{algorithm}[h!]
-\caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch set.}\label{alg:part03}
+\caption{Solving MPpBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch set.}\label{alg:part03}
 \begin{algorithmic}
@@
 
-To test the developed model and analytical solution method, we created a solver in LINGO named MBPTM.lng and also a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem, both available at codeocean and GitHub.
+To test the developed model and analytical solution method, we created a solver in LINGO named MPpBPTM.lng and also a solver in C++ named COPSolver: library for solving the multi-product p-batch processing time maximization problem, both available at codeocean and GitHub.
 A brief explanation of the software and links for downloads can be found in the paper of \cite{Fraga2023}.
@@
 We tested the solvers developed for the benchmarks presented on Tab.
-\ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\
+\ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions:
 
@@
 
-\begin{table}[ht]
+Randomly generated benchmarks were named RMPpBPTM $\textrm{N}$, being $\textrm{N}$ the number of products.
+Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
+To build the results presented in this work, we used source=0.
+Files containing benchmarks used for the tests performed and all results can be found at tbfraga.github.io/COPSolver/benchmarks.
+
+\begin{table}[h!]
 \begin{center}
@@
 
-\begin{table}[ht]
+\begin{table}[h!]
 \begin{center}
@@
 
-Randomly generated benchmarks were named RMPpBPTM $\textrm{N}$, being $\textrm{N}$ the number of products.
-Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
-To build the results presented in this work, we used source=0.
-Files containing benchmarks used for the tests performed and all results can be found at tbfraga.github.io/COPSolver/benchmarks.
-
 Table \ref{tab:results} presents the results obtained by applying the analytical method (COPSolver) and the LINGO solver for the solution of the previously presented benchmarks.

### 2024-05-29 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - improving text

@@
 
-In multi-product batch scheduling (MBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the batches based on the known demand.
+In multi-product batch scheduling (MPBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the batches based on the known demand.
 Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
-Some cientific works impose additional constraints on the MBS problem - such as release times and due dates for each batch, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
-Also, some cientific works consider MBS problems within different layouts as well as dinamic and multiperiod scenarios.
-In parallel MBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
-Many cientifc works propose mixed-integer linear programming (MILP) formulations to solve MBS problems.
+Some cientific works impose additional constraints on the MPBS problems - such as release times and due dates for each batch, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
+Also, some cientific works consider MPBS problems within different layouts as well as dinamic and multiperiod scenarios.
+In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
+Many cientifc works propose mixed-integer linear programming (MILP) formulations to solve MPBS problems.
 As example, we can mention the work of \cite{MendezEtAll2000} that presents a MILP continuous-time model and a two-step systematic methodology for a single stage multi-product batch scheduling problem with different due-dates.

### 2024-05-29 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - improving text

@@
 The method applied in this work consists of identifying new optimization problems, and mathematically modeling as well as proposing a new solution methodology for the identified problems.
-The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, as cited in this article.
+This work was developed following a practice-based learning approach, as described in the work of \cite{Fraga2022}.
+The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, and technological tools, such as LINGO, CodeBlocks, Gummi, LaTeX software, as well as platforms for the development of group work, such as GitHub and Google Classroom.
 The following sections present the new interger programming problem identified (MPpBPTM) and an exact analytical method developed for solving it.

### 2024-05-29 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - improving text

@@
 
-The method applied in this work consists of identifying new optimization problems, and mathematically modeling as well as proposing a new solution methodology for the identified problems.
+The method applied in this work consists of identifying new optimization problems, and mathematically modeling as well as proposing new solution methodologies for the identified problems.
 This work was developed following a practice-based learning approach, as described in the work of \cite{Fraga2022}.

### 2024-05-29 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - improving text

@@
 
-The method applied in this work consists of identifying new optimization problems, and mathematically modeling as well as proposing new solution methodologies for the identified problems.
 This work was developed following a practice-based learning approach, as described in the work of \cite{Fraga2022}.
+The method applied consists of identifying new optimization problems, and mathematically modeling as well as proposing new solution methodologies for the identified problems.
 The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, and technological tools, such as LINGO, CodeBlocks, Gummi, LaTeX software, as well as platforms for the development of group work, such as GitHub and Google Classroom.

### 2024-05-29 manuscript/evaluation/cover.tex
Practical Based Learning - Students Evaluation - new idea for working with

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

\documentclass[
  fontsize=11pt,
  paper=a4,
  parskip=half,
  enlargefirstpage=on,    % More space on first page
  fromalign=right,        % PLacement of name in letter head
  fromphone=off,          % Turn on phone number of sender
  fromrule=aftername,     % Rule after sender name in letter head
  addrfield=on,           % Adress field for envelope with window
  backaddress=on,         % Sender address in this window
  subject=beforeopening,  % Placement of subject
  locfield=narrow,        % Additional field for sender
  foldmarks=on,           % Print foldmarks
]{scrlttr2}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{blindtext}

\setkomafont{fromname}{\sffamily \LARGE}
\setkomafont{fromaddress}{\sffamily}%% statt \small
\setkomafont{pagenumber}{\sffamily}
\setkomafont{subject}{\bfseries}
\setkomafont{backaddress}{\mdseries}

\LoadLetterOption{DIN}
\setkomavar{fromname}{Tatiana Balbi Fraga}
\setkomavar{fromaddress}{Avenida Marielle Franco, Bairro Nova Caruaru, Caruaru, PE, Brazil}
\setkomavar{fromphone}{+55 (81)  9\,8947\,9100}
\setkomavar{fromemail}{tatiana.balbi@ufpe.br}
\setkomavar{backaddressseparator}{\enspace\textperiodcentered\enspace}
\setkomavar{signature}{Tatiana Balbi Fraga \\ 
Founding leader of the Systems Analysis, Modeling and Optimization Group \\
and Professor of the Production Engineering Course \\
at the Academic Center of Agreste - Federal University of Pernambuco}
\setkomavar{place}{Caruaru}
\setkomavar{date}{\today}
\setkomavar{enclseparator}{: }

\begin{document}

\begin{letter}{Computers \& Industrial Engineering}
    \setkomavar{subject}{Cover letter}
    \opening{Dear editor,}

	Along with this letter, I am sending a paper in which I present the Multi-product Batch Processing Time Maximization (MBPTM) problem, as well as a mathematical model and an analytical solution method with polynomial time complexity.

MBPTM is a combinatorial optimization problem. The complexity of MBPTM is mainly attributed to the fact that there is a production limit for the set of products and not just for each product. This restriction causes the problem to be defined as a non-polynomial problem.

The problem was identified by me during the development of a solver for production planning in extruders. As I am applying a local search heuristic, at each iteration I need to generate a new solution, and therefore I need to solve the MBPTM problem.

However, MBPTM is also a practical problem and its solution directly influences the efficiency of inventory control in some industries, as is the case of industries in the plastic bag sector.

As is widely known, there are few combinatorial optimization problems that can be solved using exact methods. In this paper we present an exact optimization method for solving the MBPTM problem, based on the idea of partitioning the problem into two smaller problems.

I had a vague idea about the proposed method while I was presenting the problem to my co-workers, and I managed to develop the method the same day before going to sleep, as I was really engaged about the idea of the method and about the impact that this method would generate for the performance of the solver I'm developing for production planning in extruders.

According to the bibliographic research carried out by the authors, the problem and exact method proposed in this paper has not yet been presented in the scientific literature.

Also, the language used in the paper is simple, so that many researchers can easily understand the work.

I am then waiting for your final decision with great expectation of approval of the work for publication in this journal.	
    \closing{Sincerely,}
  \end{letter}
\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

### 2024-05-29 manuscript/evaluation/manuscript.tex
Practical Based Learning - Students Evaluation - new idea for working with

--- 2024-01-23 accepted/CONEM2024/MBPTMP/MBPTMP/manuscript.tex
@@
 
-\journal{Computers \& Industrial Engineering}
+\journal{XXX}
 
@@
 
-\title{An exact method for the multi-product p-batch processing time maximization problem}
+\title{Um novo modelo de avaliação para o curso de Engenharia de Produção}
 
@@
 \begin{abstract} 
-Among the most complex multi-product batch problems are the multi-product p-batch scheduling (MPBS) problems, where jobs must be scheduled on parallel batch processing machines.
-When applying some local search heuristics to solve a MPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products.
-In this paper we name this problem multi-product p-batch processing time maximization (MBPTM) problem.
-Once a MBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPPBS problems.
-In addition, for some industries, efficiently solving a MBPTM problem can have a significant impact on storage costs and customer satisfaction.
-In this paper we present a mathematical model and an exact method with polynomial time complexity for the MBPTM problem.
-We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method.
-We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small and very large.
-As result, we find that the exact method can obtain optimal solutions in a very short time (just few seconds), even when solving very large instances.
+Este artigo apresenta um modelo de avaliação semestral baseado no processo seletivo de empresas multinacionais a na abordagem metodologica Aprendizado Baseado na Prática. 
 \end{abstract}
@@
 \begin{highlights}
-\item taxonomy and notation for the multi-product batch problems;
-\item multi-product p-batch processing time maximization (MBPTM) problem definition;
-\item integer programming model for the MBPTM problem;
-\item exact optimization method for solving the MBPTM problem;
-\item important inventory control support for some industries.
+\item xxx
 \end{highlights}

### 2024-05-30 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - final version

@@
 The method applied consists of identifying new optimization problems, and mathematically modeling as well as proposing new solution methodologies for the identified problems.
-The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, and technological tools, such as LINGO, CodeBlocks, Gummi, LaTeX software, as well as platforms for the development of group work, such as GitHub and Google Classroom.
+The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, and technological tools, such as LINGO, CodeBlocks, Gummi, LaTeX, as well as platforms for the development of group work, such as GitHub and Google Classroom.
 The following sections present the new interger programming problem identified (MPpBPTM) and an exact analytical method developed for solving it.

### 2024-05-30 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - final version

@@
 \item \textbf{input ($\iota$)}: deterministic ($Dt$) and/or stochastic ($St$);
-\item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), customer satisfaction($CS$), plant performance ($PP$) and/or processing time ($PT$);
+\item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), customer satisfaction ($CS$), plant performance ($PP$) and/or processing time ($PT$);
 \item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$), sequencing constraints ($SqC$).

### 2024-06-07 accepted/CONEM2024/FCPCOM/review/CONEM2024.tex
updating

--- 2024-05-22 accepted/CONEM2024/FCPCOM/CONEM2024.tex
@@
     % Digitar o resumo
-    \abstract{\textbf{Resumo:} Currently, most companies produce and market a wide variety of products.
+    \abstract{\textbf{Resumo:} Most companies produce and market a wide variety of products.
 Because of this, clustering items has become a crucial step in the decision-making for manufacturing and purchasing management processes, making it possible to apply different policies to each group, reducing the cost necessary for managing inventory.
@@
 
-	\State $CR \gets$ consistencyRate($M[m_{ij}]$)
-
 	\State topLeftCorner( $CR, tol, M[m_{ij}]$)
@@
 The topLeftCorner() function (alg.
-\ref{alg:topLeftCorner}) performs a peer-to-peer comparison of each element of the pairwise matrix starting from the fourth row, $M[m_{\{sz\}j}]_{sz=4}$, with each element of the matrix $M[m_{jk}]_{j=1, k=j+1 \land k \neq sz}^{n-1,n}$.
-In this comparison, the consistency of each pair is verified according to Alg.
-(\ref{alg:consistencyCheck}).
+\ref{alg:topLeftCorner}) performs a peer-to-peer comparison of each element of the pairwise matrix starting from the fourth row, $M[m_{\{sz\}j}]_{sz=4}^{n}$, with each element of the matrix $M[m_{jk}]_{j=1, k=j+1 \land k \neq sz}^{n-1,n}$.
+In this comparison, the consistency of each pair is verified.
 If any inconsistency is found, the value of one of the elements is reduced or increased, seeking to improve the consistency rate.
@@
 The bottomLeftCorner() function is similar to the topLeftCorner() function.
-In the topLeftCorner() function, the peer-to-peer comparison starts with the elements of the fourth row ($M[m_{\{sz\}j}]_{sz=4}^{n}$), and then the elements of the next rows are evaluated, following the order from top to bottom.
+In the topLeftCorner() function, the peer-to-peer comparison starts with the elements of the fourth row, and then the elements of the next rows are evaluated, following the order from top to bottom.
 In the case of the bottomLeftCorner() function, on the other hand, the pair-by-pair comparison is made starting with the elements of the anti-penultimate row ($sz = n-2$), then the elements of the previous rows are evaluated, following the order from bottom to top.
@@
 
-\begin{algorithm}
-\caption{consistency checking}\label{alg:consistencyCheck}
-	\begin{algorithmic}
-	\Require $M[m_{ij}]$
-
-	\If{$m_{\{sz\}j} * m_{jk} = m_{\{sz\}k}$}
-		\State $consistent \gets 1$ \Comment{values are consistent}
-	\Else
-		\State $consistent \gets 0$ \Comment{values are not consistent}
-	\EndIf
-
-	\State \textbf{return} $consistent$
-
-\end{algorithmic}
-\end{algorithm}
-
     \section{ON MULTICRITERIA ABC CLASSIFICATION}
@@
 	Where $w_{j}^{\min}$ and $w_{j}^{\max}$ are, respectively, the lowest and highest weights assigned to criterion $j$, $w_{ij}$ is the weight and $\rho_{ij}$ is the normalized weight of criteria $j$ for product $i$.
-
 The problem with this normalization method is that the largest values of the different criteria will have exactly the same weight.
@@
 In the case of qualitative criteria, the initial ABC classification was made using three weights, one weight assigned to group A products, $w(A)$, a second weight assigned to group B products, $w(B)$, and a third weight assigned to group C products, $w(C)$, where $w(A) > w(B) > w(C)$.
-For qualitative criteria, $w(A)$, $w(B)$ and $w(C)$ must be assigned using the following steps:
-
-\begin{itemize}
-\item order the products, in descending order, according to their respective values for lead time billing;
-\item classify products into three groups, A, B and C, for each qualitative criterion;
-\item do $w(C)$ = 0 for all group C products, for each qualitative criterion;
-\item for each qualitative criterion, do peer-to-peer comparison with the groups A and B products and the products ordered according to the lead time billing criterion, answering the following question: the degree of importance of the products of this group to the qualitative criterion is equivalent to what degree of importance of the other product evaluated according to the lead time billing criterion ?;
-\item assign to $w(A)$ and $w(B)$ the value of the lead time billing of the product with corresponding importance; 
-\end{itemize}
-
-After the correct assignment of the weights for each product according to each criterion, Eqs.
-(\ref{eq:leadTimeBillingWeight}) and (\ref{eq:weight}) can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:
+For qualitative criteria, $w(A)$, $w(B)$ and $w(C)$ must be assigned using the following steps: i) order the products, in descending order, according to their respective values for lead time billing; ii) classify products into three groups, A, B and C, for each qualitative criterion; iii) do $w(C)$ = 0 for all group C products, for each qualitative criterion; iv) for each qualitative criterion, do peer-to-peer comparison with the groups A and B products and the products ordered according to the lead time billing criterion, answering the following question: the degree of importance of the products of this group to the qualitative criterion is equivalent to what degree of importance of the other product evaluated according to the lead time billing criterion ?; and v) assign to $w(A)$ and $w(B)$ the value of the lead time billing of the product with corresponding importance.
+After steps (i) to (iv), Eqs (\ref{eq:leadTimeBillingWeight}) and (\ref{eq:weight}) can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:
 
@@
 
-where:
-
-$\textrm{NP}$ is the number of products;
-
-$\textrm{NQ}$ is the number of qualitative criteria;
-
-$\textrm{NB}$ is the number of binary criteria;
-
-$\Sigma$ is the set of qualitative criteria, \quad $\Sigma = \{\sigma_q\}_{q=1}^{NQ}$;
-
-$\textrm{B}$ is the set of binary criteria, \quad $\textrm{B} = \{\beta_b\}_{b=1}^{NB}$;
-
-$p$ is the index used to represent each product, \quad $p= 1,...,\textrm{NP}$;
-
-$c$ is the index used to represent each criterion of qualitative or binary type , \quad $c \in \Sigma \cup \textrm{B}$;
-
-$LtBW(p)$ is the lead time billing weight of product $p$;
-
-$e_{p\sigma_q}$ is the product lead time billing equivalent of product $p$ for criteria $\sigma_q$;
-
-$b_p$ is the billing of product $p$;
-
-$lt_p$ is the lead time of product $p$;
-
-$wb$ is the multicriteria weight of criterion billing.
-
-$wlt$ is the multicriteria weight of criterion lead time.
-
-$w_{c}$ is the multicriteria weight of criterion $c$.
-
-$w_{pc}$ is the normalized weight percentage of the product $p$ according to criterion $c$;
+Where: $\textrm{NP}$ is the number of products; $\textrm{NQ}$ is the number of qualitative criteria; $\textrm{NB}$ is the number of binary criteria; $\Sigma$ is the set of qualitative criteria, $\Sigma = \{\sigma_q\}_{q=1}^{NQ}$; $\textrm{B}$ is the set of binary criteria, $\textrm{B} = \{\beta_b\}_{b=1}^{NB}$; $p$ is the index used to represent each product, $p= 1,...,\textrm{NP}$; $c$ is the index used to represent each criterion of qualitative or binary type, $c \in \Sigma \cup \textrm{B}$; $LtBW(p)$ is the lead time billing weight of product $p$; $e_{p\sigma_q}$ is the product lead time billing equivalent of product $p$ for criteria $\sigma_q$; $b_p$ is the billing of product $p$; $lt_p$ is the lead time of product $p$; $wb$ is the multicriteria weight of criterion billing; $wlt$ is the multicriteria weight of criterion lead time; $w_{c}$ is the multicriteria weight of criterion $c$; and $w_{pc}$ is the normalized weight percentage of the product $p$ according to criterion $c$.
 
@@
 For the software to work properly both files must be built following the predefined formats for each specific library.
-
 To apply the methodology proposed in this article, the module 'COPSolver: library for solving the multicriteria classification problem' is being developed.
@@
     Table \ref{tab:pairwiseMatrix} presents the modifications made by the software 'COPSolver: library for solving the multicriteria classification problem' in the pairwise comparisons matrix and the consequent changes in the consistency rate (CR) for the data collected from the three companies selected for this study.
-
 This table clearly shows the inconsistencies before the modification and how the weight modifications made by the algorithm reflect the adjustments of these inconsistencies.
@@
 As we can see in the adjusted matrix, the algorithm quickly corrects these inconsistencies and then the weight vector.
+Also the pairwise comparison weights are adjusted by the solver primarily according to the weights assigned to the first three criteria.
+Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria are preserved.
+The algorithm will change the weights of the other criteria to force the consistency of the pairwise comparisons matrix.
+Another significant observation is that the algorithm stops when it reaches the desired consistency rate.
+So, it is more likely that the algorithm changes the weights related to the fourth criterion and the next ones.
+Therefore, in the preparation of the input file the data of the criteria must be informed in such a way that the criteria are ordered in descending order according to their respective relevance.
+For the data presented in Tab.
+\ref{tab:pairwiseMatrix}, with the exception of the car mechanics company, there was no concern with the correct ordering of the criteria.
+Based on the results and previous observations, we have computationally reordered the criteria using their respective weights, initially defined by the normalized eigenvector of the original pairwise comparisons matrix, $w$.
+Table \ref{tab:pairwiseMatrixReordered} presents the modification of results after altering the criteria ordination on the input data.
+Table 3 presents a comparison of the results using different methods on the data provided by the furniture trading company.
+In matrix PCM 02, the method used to force consistency was applied before the reordering of the criteria.
+In the case of matrix PCM 03, the same method was applied after reordering the criteria.
+This table also shows the matrix PCM 04 with adjustments made manually to the matrix PCM 01 after verifying the results found by COPSolver.
+As we can see, the COPSolver software provides an important help in the preparation of consistent pairwise comparison matrices.
+We also found that it is important to perform the ordering of the criteria before adjusting the matrix seeking better consistency, since the weights assigned to the most relevant criteria should preferably be maintained.
+It is possible to verify in these tables that the reordering before the application of the method to force consistency to be carried out in the weights relative to the least important criteria.
+Finally, we observe that the ordering of the criteria also helps in the manual adjustment of the pairwise comparison matrices, since the presentation of these tables with the ordered criteria facilitates the analysis of the weights.
+This is because, when ordered according to the relevance of the criteria, the elements of the pairwise comparison matrix have a trend of increasing order from left to right and decreasing order from top to bottom.
+For multicriteria classification of items, the pairwise comparison matrix PCM 03 was used.
+However, in practical cases it is important to have a final assessment of the responsible employee and the matrix used for ABC classification can be a final matrix manually updated by the employee based on the results found by COPSolver.
 
@@
                 \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; bl = billing; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
+                    \begin{small}
                     \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
@@
 				\end{tabular} \label{tab:pairwiseMatrix}
+				\end{small}
             \end{center}
 	\end{table}
-
-Table \ref{tab:pairwiseMatrix} also shows that the pairwise comparison weights are adjusted by the solver primarily according to the weights assigned to the first three criteria.
-Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria are preserved.
-The algorithm will change the weights of the other criteria to force the consistency of the pairwise comparisons matrix.
-Another significant observation is that the algorithm stops when it reaches the desired consistency rate.
-So, it is more likely that the algorithm changes the weights related to the fourth criterion and the next ones.
-Therefore, in the preparation of the input file the data of the criteria must be informed in such a way that the criteria are ordered in descending order according to their respective relevance.
-
-For the data presented in Tab.
-\ref{tab:pairwiseMatrix}, with the exception of the car mechanics company, there was no concern with the correct ordering of the criteria.
-Based on the results and previous observations, we have computationally reordered the criteria using their respective weights, initially defined by the normalized eigenvector of the original pairwise comparisons matrix, $w$.
-Table \ref{tab:pairwiseMatrixReordered} presents the modification of results after altering the criteria ordination on the input data.
 
@@
 				\end{tabular} \label{tab:pairwiseMatrixReordered}
+				\end{small}
             \end{center}
@@
 
-Table 3 presents a comparison of the results using different methods on the data provided by the furniture trading company.
-In matrix PCM 02, the method used to force consistency was applied before the reordering of the criteria.
-In the case of matrix PCM 03, the same method was applied after reordering the criteria.
-This table also shows the matrix PCM 04 with adjustments made manually to the matrix PCM 01 after verifying the results found by COPSolver.
-As we can see, the COPSolver software provides an important help in the preparation of consistent pairwise comparison matrices.
-We also found that it is important to perform the ordering of the criteria before adjusting the matrix seeking better consistency, since the weights assigned to the most relevant criteria should preferably be maintained.
-It is possible to verify in these tables that the reordering before the application of the method to force consistency to be carried out in the weights relative to the least important criteria.
-Finally, we observe that the ordering of the criteria also helps in the manual adjustment of the pairwise comparison matrices, since the presentation of these tables with the ordered criteria facilitates the analysis of the weights.
-This is because, when ordered according to the relevance of the criteria, the elements of the pairwise comparison matrix have a trend of increasing order from left to right and decreasing order from top to bottom.
-For multicriteria classification of items, the pairwise comparison matrix PCM 03 was used.
-However, in practical cases it is important to have a final assessment of the responsible employee and the matrix used for ABC classification can be a final matrix manually updated by the employee based on the results found by COPSolver.
-
 \begin{table}[ht]
             \begin{center}
-                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for three companies 					(results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; bl = billing; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
+                \caption{\textbf{Pairwise comparisons matrix and consistency rate changes for furniture trades company (results found by COPSolver) - legend: sb = substitutability; lt = lead-time; rp = repairability; cr = criticality; ob = obsolescence; bl = billing; cm = commonality; CR = consistence rate; w = normalized weights vector.}}
+                    \begin{small}
                     \begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.1cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
                         \\
-   						\multicolumn{14}{c}{furniture trades company} \\
-   						\cline {1-14} \\
    						& \multicolumn{6}{l}{PCM 01 - original data reordered} & & \multicolumn{6}{l}{PCM 02 - PCM 01 adjusted and than reordered} \\
@@
 				\end{tabular} \label{tab:pairwiseMatrixAdjusted}
+				\end{small}
             \end{center}
@@
 
-After an extensive search of the scientific literature, we did not find benchmarks or numerical tests considering binary and qualitative criteria in the literature.
-Then, for analyzing the proposed new methodology for ABC multicriteria classification, we will focus on the presentation and analysis of the data provided by the furniture trades company.
-
+For analyzing the proposed new methodology for ABC multicriteria classification, we will focus on the presentation and analysis of the data provided by the furniture trades company.
 Figure \ref{fig:results} presents part of a comparison of the results obtained for the data described above, by ABC classification for the criteria billing and the new ABC multicriteria with Analytic Hierarch Process.
-The file AHP\_Solution.txt, that presents the complete results found by the module 'COPSolver: library for solving the multicriteria classification problem' can be found at https://tbfraga.github.io/COPSolver/benchmarks/clssp/alexia/adjusted-data/results/AHP\_solution.txt.
 We can see in this figure that the multicriteria classification includes in the group A all products previously classified as A according to the billing criterion, however the order of relevance of the products is changed.
@@
 This change shows the importance of the multicriteria classification.
-
-\begin{figure}[ht]
-	\includegraphics[width=\linewidth]{files/0001.jpg}
-  	\caption{Comparison between the ABC classification for the billing criterion and the ABC multicriteria classification}
-  	\label{fig:results}
-\end{figure}
-
 Based on the results found by COPSolver, we can verify that the ABC classification, considering only the billing criterion, does not follow the normal pattern defined by the Pareto's rule (where 20\% of the causes generate around 80\% of the result).
@@
 This approach reduces the viez effect caused by the imbalance of weights and makes the final result carry important qualitative information provided by the responsible employee, assigning the appropriate relevance of the different products, as well as the criteria analyzed.
+Based on an evaluation of the final results by the participating company, it was possible to verify that these results were very coherent, offering the company very relevant information for the identification of products whose inventory must be maintained, receiving greater attention from the company, as well as for the adoption of more appropriate procedures for the correct control of the different items marketed by the company.
+The file AHP\_Solution.txt, that presents the complete results found by the module 'COPSolver: library for solving the multicriteria classification problem' can be found at tbfraga.github.io/COPSolver/benchmarks/clssp/alexia/adjusted-data/results/AHP\_solution.txt.
 
-Based on an evaluation of the final results by the participating company, it was possible to verify that these results were very coherent, offering the company very relevant information for the identification of products whose inventory must be maintained, receiving greater attention from the company, as well as for the adoption of more appropriate procedures for the correct control of the different items marketed by the company.
+\begin{figure}[ht]
+	\includegraphics[width=\linewidth]{files/0001.jpg}
+  	\caption{\textbf{Comparison between the ABC classification for the billing criterion and the ABC multicriteria classification.}}
+  	\label{fig:results}
+\end{figure}
 
@@
 We also verified that the new methodology proposed for multicriteria ABC classification generated very coherent results, giving the appropriate importance to the products, according to all the evaluated criteria.
-
 As further works, the methodologies developed and results found will be used as a basis for building a portfolio with the identification of product demand patterns and, subsequently, for the development of a combined methodology for demand forecasting in small companies.
@@
 
-    \section{COPYRIGHT LIABILITY}
-
-        The authors are uniquely responsible for the content of this work.
-
     % REFERÊNCIAS
@@
 
+ \section{COPYRIGHT LIABILITY}
+
+        The authors are uniquely responsible for the content of this work.
+
 \end{document}

### 2024-06-12 accepted/CONEM2024/FCPCOM/review/CONEM2024.tex
updating article - final version
updating article - latest fixes

@@
 \usepackage{graphicx}
+\usepackage{times}
 
@@
 The attribution of weights to the products according to each criterion is also a difficult task cause there is a need to balance all the quantitative values and the empirical values defined for the qualitative criteria.
-This paper presents a constructive algorithm that can adjust inconsistent pairwise comparison matrices, forcing such matrices to have a better consistency rate, a balancing procedure for attributing weights to the products according to qualitative criteria, and a new equation for ABC multicriteria classification.
+This article presents a constructive algorithm that can adjust inconsistent pairwise comparison matrices, forcing such matrices to have a better consistency rate, a balancing procedure for attributing weights to the products according to qualitative criteria, and a new equation for ABC multicriteria classification.
 We developed a new library for the COPSolver software by applying this new ABC multicriteria classification with AHP.
@@
 
+	\begin{figure}[h!]
+	\includegraphics[width=\linewidth, height=0.65\textwidth]{files/0001.jpg}
+  	\caption{\textbf{Comparison between the ABC classification for the billing criterion and the ABC multicriteria classification.}}
+  	\label{fig:results}
+\end{figure}
+
 \subsection{Analysis On The New ABC Multicriteria Classification Method}
@@
 The file AHP\_Solution.txt, that presents the complete results found by the module 'COPSolver: library for solving the multicriteria classification problem' can be found at tbfraga.github.io/COPSolver/benchmarks/clssp/alexia/adjusted-data/results/AHP\_solution.txt.
-
-\begin{figure}[ht]
-	\includegraphics[width=\linewidth]{files/0001.jpg}
-  	\caption{\textbf{Comparison between the ABC classification for the billing criterion and the ABC multicriteria classification.}}
-  	\label{fig:results}
-\end{figure}
 

### 2024-06-12 accepted/MDPI/MDPI_template/manuscript.tex
updating MDPI article and files

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi}

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2024}
\copyrightyear{2024}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ } 
\daterevised{ } % Comment out if no revised date
\dateaccepted{ } 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org
%\CorrStatement{yes}  % For updates

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{A New Effective ABC Multicriteria Classification with AHP: How to Force Consistency of Paiwise Comparisons Matrix.}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Tatiana Fraga $^{1,\dagger,}$*\orcidA{}, Beatriz Cavacanti $^{2}$, Alexia Maria Silva $^{3}$ and Erika Leticia Silva $^{4}$}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address[1]{%
$^{1}$ \quad Federal University of Pernambuco; tatiana.balbi@ufpe.br\\
$^{2}$ \quad Federal University of Pernambuco; beatriz.marinhocavalcanti@ufpe.br\\
$^{3}$ \quad Federal University of Pernambuco; alexia.duque@ufpe.br\\
$^{4}$ \quad Federal University of Pernambuco; erika.leticias@ufpe.br}

% Contact information of the corresponding author
\corres{Correspondence: tatiana.balbi@ufpe.br}

% Current address and/or shared authorship
\firstnote{Current address: Centro Acadêmico do Agreste, Avenida Marielle Franco, Bairro Nova Caruaru, Caruaru - PE. CEP: 55014-900.}  % Current address should not be the same as any items in the Affiliation section.
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Multicriteria classification is usually a crucial step in the decision-making in manufacturing and purchasing management processes. But in such classification, both the attribution of weights to the criteria and the attribution of weights to the products according to each criterion strongly influence the coherence of the categorization.   Saaty's Analytic Hierarchy Process (AHP) is an eminent method for assigning weights to multiple criteria. Yet, since criteria's pairwise comparison matrices are usually generated manually and based only on some employee know-how, there is high complexity in elaborating a consistent pairwise matrix, especially when comparing several criteria. The attribution of weights to the products according to each criterion is also a difficult task cause there is a need to balance all the quantitative values and the empirical values defined for the qualitative criteria. This article presents an efficient algorithm that can adjust inconsistent pairwise comparison matrices, a balancing procedure for attributing weights to the products according to qualitative criteria, and a new equation for ABC multicriteria classification. We tested the proposed solutions to companies in three sectors, demonstrating that this approach provided consistent results, according to the analysis of the company managers, being an essential resource for decision-making.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Advances in Respiratory Medicine
%\addhighlights{yes}
%\renewcommand{\addhighlights}{%

%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars. Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it. Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
%\textbf{What are the main findings?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}\vspace{3pt}
%\textbf{What is the implication of the main finding?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.

% The order of the section titles is different for some journals. Please refer to the "Instructions for Authors” on the journal homepage.

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}   
\unskip

\begin{table}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data \textsuperscript{1}\\
\bottomrule
\end{tabularx}
\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

The text continues here (Figure~\ref{fig2} and Table~\ref{tab2}).

% Example of a figure that spans the whole page width. The same concept works for tables, too.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=15.5cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

\begin{table}[H]
\caption{This is a wide table.\label{tab2}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{CCCC}
			\toprule
			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
			\midrule
\multirow[m]{3}{*}{Entry 1 *}	& Data			& Data			& Data\\
			  	                   & Data			& Data			& Data\\
			             	      & Data			& Data			& Data\\
                   \midrule
\multirow[m]{3}{*}{Entry 2}    & Data			& Data			& Data\\
			  	                  & Data			& Data			& Data\\
			             	     & Data			& Data			& Data\\
                   \midrule
\multirow[m]{3}{*}{Entry 3}    & Data			& Data			& Data\\
			  	                 & Data			& Data			& Data\\
			             	    & Data			& Data			& Data\\
                  \midrule
\multirow[m]{3}{*}{Entry 4}   & Data			& Data			& Data\\
			  	                 & Data			& Data			& Data\\
			             	    & Data			& Data			& Data\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{* Tables may have a footer.}}
\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{linenomath}
\begin{equation}
a = 1,
\end{equation}
\end{linenomath}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

% Example of a page in landscape format (with table and table footnote).
%\startlandscape
%\begin{table}[H] %% Table in wide page
%\caption{This is a very wide table.\label{tab3}}
%	\begin{tabularx}{\textwidth}{CCCC}
%		\toprule
%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
%		\midrule
%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
%		\bottomrule
%	\end{tabularx}
%	\begin{adjustwidth}{+\extralength}{0cm}
%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
%	\end{adjustwidth}
%\end{table}
%\finishlandscape

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

% Only for journal Hardware:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.\vspace{6pt}\\
%\begin{tabularx}{\textwidth}{lll}
%\toprule
%\textbf{Name} & \textbf{Type} & \textbf{Description} \\
%\midrule
%S1 & Python script (.py) & Script of python source code used in XX \\
%S2 & Text (.txt) & Script of modelling code used to make Figure X \\
%S3 & Text (.txt) & Raw data from experiment X \\
%S4 & Video (.mp4) & Video demonstrating the hardware in use \\
%... & ... & ... \\
%\bottomrule
%\end{tabularx}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval. Please note that the Editorial Office might ask you for further information. Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans. OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals. OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}

\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{We encourage all authors of articles published in MDPI journals to share their research data. In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Where no new data were created, or where data is unavailable due to privacy or ethical restrictions, a statement is still required. Suggested Data Availability Statements are available in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}.}

% Only for journal Nursing Reports
%\publicinvolvement{Please describe how the public (patients, consumers, carers) were involved in the research. Consider reporting against the GRIPP2 (Guidance for Reporting Involvement of Patients and the Public) checklist. If the public were not involved in any aspect of the research add: ``No public involvement in any aspect of this research''.}

% Only for journal Nursing Reports
%\guidelinesstandards{Please add a statement indicating which reporting guideline was used when drafting the report. For example, ``This manuscript was drafted against the XXX (the full name of reporting guidelines and citation) for XXX (type of research) research''. A complete list of reporting guidelines can be accessed via the equator network: \url{https://www.equator-network.org/}.}

% Only for journal Nursing Reports
%\useofartificialintelligence{Please describe in detail any and all uses of artificial intelligence (AI) or AI-assisted tools used in the preparation of the manuscript. This may include, but is not limited to, language translation, language editing and grammar, or generating text. Alternatively, please state that “AI or AI-assisted tools were not used in drafting any aspect of this manuscript”.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflicts of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional

%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & Linear dichroism
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}
\subsection[\appendixname~\thesubsection]{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\begin{table}[H] 
\caption{This is a table caption.\label{tab5}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}

\section[\appendixname~\thesection]{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book1}
Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
\bibitem[Author3(year)]{ref-book2}
Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
\bibitem[Author4(year)]{ref-unpublish}
Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
% Reference 5
\bibitem[Author5(year)]{ref-communication}
Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
\bibitem[Author6(year)]{ref-proceeding}
Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
% Reference 7
\bibitem[Author7(year)]{ref-thesis}
Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
\bibitem[Author8(year)]{ref-url}
Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\PublishersNote{}
\end{adjustwidth}
\end{document}

### 2024-06-12 accepted/MDPI/MDPI_template/manuscript.tex
updating

@@
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}
+\keyword{ABC multicriteria classification; Analytic Hierarchy Process; consistency rate; multicriteria equation; COPSolver library.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\setcounter{section}{-1} %% Remove this when starting to work on the template.
-\section{How to Use this Template}
-
-The template details the sections that can be used in a manuscript.
-Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
-Please check the instructions on the authors' page of the journal to verify the correct order and names.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References).
-Only journal Laws uses \footnote.
+%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.
 
@@
 
-The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
-Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
+According to \cite{Singhal2013}, the manufacturing decisions can be classified into three categories: strategic, tactical and operational.
+As explained by the authors, the operational decisions pertaining to issues such as order processing, detailed production scheduling, follow up, maintenance routines, and inventory control rules, drive the day to day activities.
+Manufacturing decisions are closely related to sales decisions.
+\cite{Ebrahimi2014} warn that in today’s competitive market the diversity in customer’s need have resulted in a high level of variability in the products which have to be manufactured and this statement is also valid for the products acquired from other companies.
+Such complication brings to light the need for the use of complex techniques for purchasing / production management, especially at the operational decision level \citep{Kiran2019}.
+In such a scenario, prior optimized operational planning becomes impressible for better use of the productive capacity and to avoid investment losses in unnecessary or unprofitable material.
+And, given the wide variety of products, it is crucial to start any planning by understanding the importance of all products marked by the company.
+
+One of the approaches that is widely applied to clustering products according to their importance is the multicriteria ABC classification.
+The scientific literature broadly emphasizes the value of multicriteria ABC classification for inventory management and presents several multicriteria methods.
+The Analytic Hierarchy Process is one of the most common techniques applied for this purpose \citep{Flores1992, AltayGuvenir1998, Lolli2014, Balaji2014}.
+Some recent studies also emphasize the importance of applying multicriteria analysis to strategic planning \citep[\emph{e.g.},][]{BarbosaDePaula2022, Pereira2023, MarianoRibeiro2023}.
+\citet{Odu2019} emphasizes that, when applying some multicriteria methods, it is crucial to pay particular attention to the objectivity factors of criteria weights.
+The author provides a detailed overview of different weighting methods applicable to multicriteria techniques.
+
+In this work, we present a study with three companies from three different sectors, which market a wide variety of products, in some cases, highly personalized products.
+The interest of this study is to identify the principal products, that is, the products that each company must prioritize so that this information can guide the optimized operational planning.
+We opted for the method ABC for multicriteria classification and adopted the Analytic Hierarchy Process (AHP) \citep{Saaty1987} to assign the weights to the different criteria.
+It is important to note that the AHP derives the weights of each criterion based on the eigenvector of a pairwise comparisons matrix, which is constructed manually according to an empirical evaluation.
+According to \cite{Saaty1987}, this matrix must be positive reciprocal and have a consistency rate of less than 0.1.
+The author reports that a software package supporting the AHP, called Expert Choice, for the IBM PC, was used in his work for making eigenvector calculations and guiding the decision maker to improve matrix inconsistency if needed.
+During the execution of the work we present in this paper, we found that there is a substantial difficulty in the calculation of the eigenvector, as well as in the construction of consistent pairwise comparisons matrices.
+Since we had no access to the Expert Choice software package, we developed an open-source COPSolver's library for solving the multicriteria classification problem, which applies a simple algorithm for forcing the consistency of such matrices when applying the AHP.
+We present this algorithm in this paper.
+We coupled the Eigen library from eigen.tuxfamily.org to COPSolver for the eigenvectors calculation of the matrices.
+Also, we identified that it is possible to use different criteria types (cumulative sum, qualitative, and binary) when assigning weights to ABC classification, depending on each specific criterion chosen, and we observed that such an assignment generates a bias in the multicriteria ABC classification.
+Therefore, we also developed a new methodology for assigning weights in a balanced way for ABC classification, and we proposed a new multicriteria weighting equation for the multicriteria classification COPSolver's library.
+We also present both propositions in this paper, as well as an in-depth analysis of the results found by the new library developed for COPSolver.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %=====================================
-%\bibliography{your_external_BibTeX_file}
+%\bibliography{lib.bib}
 
@@
 \begin{thebibliography}{999}
+
+% Reference 1
+\bibitem[Singhal et al.(2013)]{Singhal2013}
+Singhal, J.; Bitran, G.R.; Dasu, S.
+Production Management.
+In {\em Encyclopedia of Operations Research and Management Science}; Gass, S.I., Fu, M.C., Eds.; Springer US: Boston, United States, 2013; pp.
+1173--1182.
+% Reference 2
+\bibitem[Ebrahimi et al.(2014)]{Ebrahimi2014}
+Ebrahimi, A.H.; Johansson, P.E.C.; Bengtsson, K.; Åkesson, K. Managing Product and Production Variety – A Language Workbench Approach. {\em Procedia CIRP} {\bf 2014}, {\em 17}, 338--344.
+% Reference 3
+\bibitem[Kiran(2019)]{Kiran2019}
+Kiran, D.R. \textit{Production Planning and Control: A Comprehensive Approach}, 1rd ed.; Butterworth-Heinemann: Cambridge, United States, 2019.
+
 % Reference 1

### 2024-07-16 manuscript/MPMPBPTMP/CONEM2024.tex
MPMPpBPTM problem

--- 2024-05-30 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
@@
 \usetikzlibrary{shapes.geometric,shapes.misc,shapes.symbols,arrows.meta,graphs,fit,positioning,shadows}
+\usepackage{times}
 
@@
 \def\shortauthor{T.B. Fraga, I.R.B. de Aquino and R.C.S. Menêzes}
-\def\shorttitle{An Exact Method for the Multi-product P-batch Processing Time Maximization Problem}
+\def\shorttitle{Multi-period, Multi-product P-batch Processing Time Maximization Problem}
 
@@
     % CABEÇALHO
-    \thispagestyle{empty}
-    \begin{figure}[h]
-        \begin{center}
-            \includegraphics[angle=0, width=\textwidth]{Logo_template.png}
-        \end{center}
-    \end{figure}
-    \vspace{-.5cm}
-    \hspace{-.8cm}
-    \begin{tabular}{||p{\textwidth}}
-    \begin{center}
-    \vspace{-.6cm}
-    %
-    % Digitar o título
-    \title{CONEM2024-0014 \\ AN EXACT METHOD FOR THE MULTI-PRODUCT P-BATCH PROCESSING TIME MAXIMIZATION PROBLEM}
-    %
-    \end{center}
-	%
-	% Digitar os nomes dos autores/instituição
-    \authors{Tatiana Balbi Fraga, tatiana.balbi@ufpe.br$^1$} \\
-    \authors{Ítalo Ruan Barbosa de Aquino, italo\_ruan\_@hotmail.com$^1$} \\
-    \authors{Regilda da Costa e Silva Menêzes, regilda.smenezes@ufpe.br$^1$} \\\\
-    \institution{$^1$Centro Acadêmico do Agreste, Universidade Federal de Pernambuco, Avenida Marielle Franco, Bairro Nova Caruaru, Caruaru - PE, CEP: 55014-900} \\
-    \\
-    %
-    % Digitar o resumo
-    \abstract{\textbf{Resumo:} Multi-product batch (MPB) problems arise in manufacturing environments where several batches of products are processed sequentially, sharing the same set of production units.
-Among the most well-known MPB problems stands out the multi-product batch scheduling (MPBS) problems, whose objective is to find one of the feasible batch processing schedules that best meets a set of objectives predefined by the company.
-Along with the most complex MPBS problems are the multi-product p-batch scheduling (MPpBS) problems, where the schedule occurs on parallel batch processing machines.
-When applying some local search heuristics to solve the MPpBS problem, it can be necessary to iteratively solve a single-stage multi-product p-batch sizing problem with different processing rates for each product, limited capacity units, and storage capacity defined both for each product and for all products (named in this article multi-product p-batch processing time maximization (MPpBPTM) problem).
-Then, the efficiency of the method developed for solving an MPpBPTM problem exerts a decisive influence on the computational cost of the local search algorithm applied to solve some MPpBS problems.
-In addition, the efficiency of solving an MPpBPTM problem can significantly impact storage costs and customer satisfaction.
-This article presents a mathematical model and an exact method with polynomial time complexity for the MPpBPTM problem.
-We developed a LINGO solver for solving the mathematical model and a C++ COPSolver library for applying the proposed exact method.
-We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small-scale and very large-scale.
-As a result, we found that both solvers can obtain optimal solutions in just a few seconds, even when solving very large-scale instances.
-However, the exact method is much more efficient since it solves the problem in polynomial time.
-In addition, the modular structure of the library developed for COPSolver allows the easy application of the proposed solution method when developing new heuristics for solving MPpBS problems, making this tool a significant technological contribution to the production management of some industries as well as for researchers in the area.}\\
-    %
-    % Digitar as palavras-chave
-   \\
-    \keywords{\textbf{Palavras-chave:} multi-product p-batch problem, processing time maximization, integer programming model, analytical solution, COPSolver}\\
 
-    \end{tabular}
-
-    \section{INTRODUCTION}
-	\label{sec:intro}
-
-The term multi-product batch production is usually applied to designate an intermittent production system in which batches of different products and sizes are processed one at a time, sharing the same production facilities.
-A multi-product batch plant basically consists of one or more production units, grouped into one or more stages, and possibly, intermediate storage locations.
-At each stage some distinct operations are performed and the batches are processed sequentially over the stages (serial batching).
-As stated by \cite{PetkovMaranas1998} the batch plant can operate under a single-product campaign (SPC) production mode, where all the batches of a given product are manufactured before production of the next product begins, or under mixed-product campaign (MPC) production modes where more batches are produced per unit time at the expense of increased changeover times and cleanup costs.
-Also the plant layout can take on different formats, such as: single unit, where all operations needed to process the batches are performed by a single processor; serial flowshop plant, in which all products follow the same linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{ShiEtAll2017}; and convergent and/or divergent networked processes, in which units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.
-
-The scientific literature address many different problems related to such industrial enviroment, including the design, planning, sizing, scheduling and balancing problems.
-The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.
-The configuration of the plant basically consists of defining the number of stages, the number of units and their capacity per stage, and the capacity for intermediate storages, as well as the best factory layout.
-The multi-product batch planning problem is basically determining the quantities to be produced, the number of batches and their sizes, the needs of materials and the total sales during each time period \citep{FumeroEtAl2016}.
-
-Since a single batch is processed at a time, it is necessary that the batches are dimensioned in such a way that the quantity produced of each product is sufficient to meet the demand during the period in which other batches are being processed \citep{Eilon1985}.
-This problem is named multi-product batch sizing.
-\cite{Eilon1985} gives a detailed explanation of the inadequacy of the use of the well-know EBQ (economic batch quantity) square-root formula for multi-product batch production, and \cite{LiuEtAl2020} present a mixed-integer quadratic programming model and an exact optimization algorithm for a multi-stage multi-product serial batching sizing problem in a divergent networked plant of a steel industry.
-
-In multi-product batch scheduling (MPBS) problems it is necessary to determine the ideal batch size for each product and also the production sequence of the batches based on the known demand.
-Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}.
-Some cientific works impose additional constraints on the MPBS problems - such as release times and due dates for each batch, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}.
-Also, some cientific works consider MPBS problems within different layouts as well as dinamic and multiperiod scenarios.
-In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.
-Many cientifc works propose mixed-integer linear programming (MILP) formulations to solve MPBS problems.
-As example, we can mention the work of \cite{MendezEtAll2000} that presents a MILP continuous-time model and a two-step systematic methodology for a single stage multi-product batch scheduling problem with different due-dates.
-Later, \cite{MendezCerda2003} also proposed another MILP formulation for reactive scheduling.
-As observerd by \cite{HeHui2008}, with the problem size increasing, the computational effort of MILP increases greatly so it is very difﬁcult for MILP to obtain acceptable solutions to large-size problems within reasonable time.
-Citing some works that use other approaches, \cite {KimEtAl1996} propose a Gantt chart mapping method and a modified genetic algorithm for solving a networked flowshop multi-product batch scheduling problem as well as a rule-based reactive rescheduling scheme for dinamicaly overcoming in-process deviation from the initial optimized schedule and \cite{HeHui2008} present a rule-based genetic algorithm for the scheduling of single stage multi-product batch plants with parallel units.
-
-It is importante to note that some production units are capable of processing multiple jobs at the same time.
-In such a case batches of different products and sizes can be grouped and processed by these units as a single batch.
-It is therefore necessary to determine the set of "batches" that each new compounded batch will contain.
-The multi-product balancing problem consists of determining these groupings, seeking to minimize the overall makespan.
-\cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.
-\cite{FowlerMonch2022} present a taxonomy and an extensive literature review for the p-batch problems.
-According to the authors, a p-batch problem can be classified as compatible setting - where there is no restriction on which jobs can be used to form a batch - and incompatible family case - where only jobs belonging to the same family can be used to form a batch.
-Not mentioned by \cite{FowlerMonch2022}, \cite{LiEtAl2022} deal with a multi-product p-batch problem involving identical parallel units, capacity constraints, and incompatible families with different job sizes.
-
-In a real production environment, some of these problems arise in a connected way, so many cientific works adress mixed multi-product batch problems.
-As example, \cite{FumeroEtAl2016} developed a multi-period mixed-integer linear programming model for MPCs multistage multi-product batch problems, which integrates design, production planning, and scheduling decisions.
-Also, the work of \cite{MendezEtAll2000}, previously mentioned, considers planning as an integrated part of solution in real-world multi-product batch plant scheduling and therefore includes the product batching problem in its proposed MILP continuous-time models and two-step systematic methodology.
-
-\subsection{Taxonomy and Notation}
-
-In short, based on the bibliographic survey conducted for the preparation of this paper, we identify that the multi-product batch problems can differentiate with the following aspects:
-
-\begin{enumerate}[label=\arabic*)]
-\item \textbf{number of stages ($\sigma$)}: single stage ($SS$) or multistage ($MS$);
-\item \textbf{layout($\lambda$)}: single unit ($SU$), flowshop ($Fl$), parallel ($Pl$), or networked ($Nt$) (convergent ($CNt$) and /or divergent ($DNt$));
-\item \textbf{production mode ($\mu$)}: single-product campaing ($SPC$), mixed-product campaign ($MPC$), serial batching ($s\textrm{-}batch$) and/or parallel batching ($p\textrm{-}batch$);
-\item \textbf{problem:($\pi$)}  : design ($D$), planning ($P$), sizing ($Sz$), scheduling ($Sc$) and/or balancing ($B$); 
-\item \textbf{time horizon ($\eta$)}: single period ($SP$), multiperiod ($MP$) or cyclic ($Cc$);
-\item \textbf{scenario ($\gamma$)}: static ($St$) or dynamic ($Dn$);
-\item \textbf{input ($\iota$)}: deterministic ($Dt$) and/or stochastic ($St$);
-\item \textbf{performance measure ($\delta$)}: capital cost ($C$), setup cost ($SC$), holding cost ($HC$), work-in-process cost ($WIPC$), net profit ($NP$), makespan ($C_{max}$), total completion time ($TC$), weighted completion time ($TWC$), maximum lateness ($L_{max}$), maximal tardiness ($T_{max}$), total tardiness (TT), total weighted tardiness ($TWT$), the number of tardy jobs ($NTJ$), weighted number of tardy jobs ($WNTJ$), earliness/tardiness ($E/T$), weighted $E/T$ ($wE/T$), customer satisfaction($CS$), plant performance ($PP$) and/or processing time ($PT$);
-\item \textbf{others ($\rho$)}: limited capacity units ($LCU$), storage capacity by product ($PSC$), storage capacity ($SC$), work-in-process storage ($WIP$), release time ($RT$), due dates ($DD$), incompatible families ($IF$), different processing rates ($DPR$), sequence-dependent setup times ($SDST$), sequencing constraints ($SqC$).
-\end{enumerate}
-
-So, to describe a speciﬁc multi-product batch problem, we propose the notation $\sigma|\lambda|\mu|\pi|\eta|\gamma|\iota|\delta|\rho$.
-Some of the multi-product batch problems and solution approaches discussed in the references cited in this paper are summarized in Tab.
-\ref{tab:review}.
-
-\begin{table}[ht]
-\begin{center}
-\caption{\textbf{Some contributions on the multi-product batch problems.}}
-\begin{small}
-\begin{tabular}[c]{l l l}
-\\
-reference & problem & contributions  \\
-\cline {1-3} \\
-\cite{Eilon1985} & $SS|SU|s\textrm{-}batch|Sc|SP$ &  analysis of the effect\\
-& $St|Dt|SC, HC|-$  & of splitting batches \\
-\cline {1-3} \\
-Ravemark and & $MS|Pl|SPC|D|Cc|$ & convex MILP model \\
-Rippin (1998) & $St|Dt|C|WIP$ & solved with DICOPT++ \\
-\cline {1-3} \\
-Petkov and & $MS|Pl|SPC|D|Cc|$ & exact method\\
-Maranas (1998)  & $St|St|NP|-$ & \\
-\cline {1-3} \\
-\cite{MendezEtAll2000} & $SS|Pl|MPC|P,Sc|SP|St|$ & MILP continuous-time  \\
-& $Dt|WIPC|RT, DD$ & model and a two-step  \\
-& & systematic methodology \\
-\cline {1-3} \\
-Méndez and & $SS|Pl|MPC|Sc|SP|Dn|Dt|$ & MIPL model and \\
-Cerdá (2003) &$wE/T|RT, DD, SDST$ & a rescheduling algorithm\\
-\cline {1-3} \\
-\cite{HeHui2008} & $SS|Pl|MPC|Sc|SP|$ & rule-based genetic \\
-& $St|Dt|C_{max}, TT|LCU, DD$ & algorithm \\
-\cline {1-3} \\
-\cite{FumeroEtAl2016} & $MS|Pl|MPC|D,P,Sc|Cc|$ & MILP model \\
-& $St|Dt|NP|LCU,USC$ & solved with CPLEX \\
-\cline {1-3} \\
-\cite{LiuEtAl2020} & $MS|DNt|s\textrm{-}batch|Sz|MP|St|$ & mixed-integer quadratic \\
-& $Dt|SC,WIPC|LCU,WIP$ & programming model  \\
-& & and exact algorithm \\
-\cline {1-3} \\
-\cite{LiEtAl2022} & $SS|Pl|p\textrm{-}batch|Sc,B|SP|$ & MILP model \\
-& $St|Dt|C_{max}|LCU, RT, IF$ & and a constraint-guided \\
- & & artificial immune \\
- & & system based algorithm \\ 
-\cline {1-3} \\
-\end{tabular}
-\label{tab:review}
-\end{small}
-\end{center}
-\end{table}
-
-\subsection{Contributions of this Article}
-
-The work presented in this article is part of a project in which we propose the modeling and solution of a multiperiod multi-product batch scheduling problem that arises in a networked plant of a plastic bag industry.
-The industrial plant of this company is very similar to the multi-product s-batch networked plant of the steel industry presented by \cite{LiuEtAl2020}, however, the production process in this plastic bags industry begins in extruders, which are production units capable of processing different batches simultaneously.
-Therefore the problem we are interested is a multi-product \emph{p-batch} \emph{s-batch} problem in a networked plant close to the problem addressed by \cite{LiEtAl2022}.
-Thus, part of the problem solving process consists of solving a multi-product p-batch scheduling problem into extruders.
-Also, in the problem we study, in addition to demand, we must consider the factory and outlets' storage capacity, which is individually defined for products, but also for the set of products.
-When we began to propose an algorithm to solve the studied problem through a local search method, we identified the need to determine, at each iteration, a maximum processing time for predefined multi-product p-batches, based on known restrictions, so that the new solution built was a feasible solution and at the same time with the best fitness.
-Using the notation presented before, this problem can be classified as a multi-product $SS|SU|p\textrm{-}batch|Sz|SP|St|Dt|PT|LCU,$ $PSC, SC, DPR$ problem.
-For simplification purposes, we named this problem multi-product p-batch processing time maximization (MPpBPTM) problem.
-It is important to note that, since the MPpBPTM problem need to be solved at each iteration, it has a direct impact on the overall efficiency of the local search method proposed for solving the multi-product p-batch s-batch problem in the plastic bag networked plant of the industry studied.
-In a future work, we intend to present the mathematical model and a Particle Collison based solution algorithm we are developing for this last problem.
-As scientific contributions of this paper, we present a mathematical model and a very efficient polynomial optmization method for solving the MPpBPTM problem.
-
-The rest of the paper is organized as follows.
-In the next sections, the MPpBPTM problem is introduced.
-Section 2.2 describes an interger mathematical model for the problem and section 2.3 shows an analytical method for its solution.
-Section 3 displays the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
-Section 4 presents the paper's conclusions and suggestions for future works.
-Finally, in sections 5 and 6, the contributions to this work are informed and acknowledgments are given, respectively.
-
-\section{MATERIALS AND METHODS}
-
-This work was developed following a practice-based learning approach, as described in the work of \cite{Fraga2022}.
-The method applied consists of identifying new optimization problems, and mathematically modeling as well as proposing new solution methodologies for the identified problems.
-The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, and technological tools, such as LINGO, CodeBlocks, Gummi, LaTeX, as well as platforms for the development of group work, such as GitHub and Google Classroom.
-The following sections present the new interger programming problem identified (MPpBPTM) and an exact analytical method developed for solving it.
-
-\subsection{Multi-product p-Batch Processing Time Maximization Problem}
+\section{Multi-period, Multi-product p-Batch Processing Time Maximization Problem}
 \label{sec:MBPTMP}
@@
 About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.
-The problem is to identify the maximum feasible time for the multi-product p-batch processing.
+
+The Multi-period, Multi-product p-Batch Processing Time Maximization (MPMPpBPTM) problem é uma versão mais complexa do MPpBPTM na qual considera-se um horizonte de planejamento contendo mais do que um único período (dias, semanas, etc).
+Neste caso as decisões devem ser tomadas para cada período.
+
+O MPMPpBPTM é mais complexo do que o MPpBPTM porque, no caso do primeiro, a decisão sobre a produção de determinado produto em determinado período pode influir fortemente nos limites permitidos para produção do mesmo produto e de outros produtos em outros períodos.
+
+Para melhor compreensão do problema MPMPpBPTM e de sua complexidade, considere o problema MPpBPTM com dois produtos e um único período de planejamento (1 dia) apresentado na Tab.
+1, e o problema MPMPpBPTM com dois produtos e um horizonte de planejamento de dois dias, conforme apresentado na Tab.
+2, onde: $\textrm{p}_i$ is the production rate of product $i$; $\textrm{UD}_i$ is the demand for the product $i$; $\textrm{UD}_{id}$ is the demand for the product $i$ on day $d$; $\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets; $\textrm{UI}_i$ é o limite de estoque para o produto $i$ in the factory on the first day de planejamento; $\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets; $\textrm{I}$ é o limite de estoque in the factory para all products in the batch, on the first day de planejamento; $\textrm{Z}$ is the timeout for batch processing; $\textrm{Z}_d$ is the timeout for batch processing on day $d$.
+
+\begin{table}[h!]
+\begin{center}
+\caption{\textbf{Benchmark MPpBPTM 02.}}
+\begin{tabular}[c]{c r r c r}
+\\
+$i$ & 1 & 2 & & total \\
+\cline {1-5} \\
+$\textrm{p}_i$ & 60 & 40 & \\
+$\textrm{UD}_i$ & 1000 & 500 & \\
+$\textrm{UO}_i$ & 600 & 600 & $\textrm{O}$ & 1000 \\
+$\textrm{UI}_i$ & 3000 & 2000 & $\textrm{I}$ & 3000 \\
+\cline {1-5} \\
+& & & $\textrm{Z}$ & 100 \\
+\end{tabular}
+\label{tab:MBPTMP001}
+\end{center}
+\end{table}
+
+\begin{table}[h!]
+\begin{center}
+\caption{\textbf{Benchmark MPMPpBPTM 02.}}
+\begin{tabular}[c]{c r r c r}
+\\
+$i$ & 1 & 2 & & total \\
+\cline {1-5} \\
+$\textrm{p}_i$ & 60 & 40 & \\
+$\textrm{UD}_{i1}$ & 1000 & 500 & \\
+$\textrm{UD}_{i2}$ &  500 & 500 & \\
+$\textrm{UO}_i$ & 600 & 600 & $\textrm{O}$ & 1000 \\
+$\textrm{UI}_i$ & 3000 & 2000 & $\textrm{I}$ & 3000 \\
+\cline {1-5} \\
+& & & $\textrm{Z}_1$ & 100 \\
+& & & $\textrm{Z}_1$ &  50 \\
+\end{tabular}
+\label{tab:MBPTMP001}
+\end{center}
+\end{table}
+
+No caso do problema MPpBPTM 02, desejamos encontrar o tempo máximo de planejamento em um único período para o lote contendo os produtos 1 e 2.
+Neste caso, podemos encontrar T, aplicando as equações matemáticas (\ref{eq:01}) e (\ref{eq:02}) propostas por Fraga (2024) para solução deste problema:
+
+\begin{equation}
+\label{eq:01}
+T^* = \lfloor{\min \{\min_{i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
+\end{equation}
+
+\begin{equation}
+\label{eq:02}
+T = \min \{T^* , \textrm{Z}\}
+\end{equation}
 

### 2024-07-16 manuscript/MPMPBPTMP/CONEM2024.tex
MPMPpBPTM problem
DMPMPpBPTM

@@
 
-\section{Multi-period, Multi-product p-Batch Processing Time Maximization Problem}
+\section{Dinamic Multi-period, Multi-product p-Batch Processing Time Maximization Problem}
 \label{sec:MBPTMP}
@@
 
-The Multi-period, Multi-product p-Batch Processing Time Maximization (MPMPpBPTM) problem é uma versão mais complexa do MPpBPTM na qual considera-se um horizonte de planejamento contendo mais do que um único período (dias, semanas, etc).
+The Dinâmic Multi-period, Multi-product p-Batch Processing Time Maximization (DMPMPpBPTM) problem é uma versão mais complexa do MPpBPTM na qual considera-se um horizonte de planejamento contendo mais do que um único período (dias, semanas, etc).
 Neste caso as decisões devem ser tomadas para cada período.
+Adicionamente, em um cenário dinâmico, consideramos que já existe um planejamento prévio para produção e entregas.
+Neste caso o objetivo consiste em definir um encaixe de produção para atender às novas demandas.
 
-O MPMPpBPTM é mais complexo do que o MPpBPTM porque, no caso do primeiro, a decisão sobre a produção de determinado produto em determinado período pode influir fortemente nos limites permitidos para produção do mesmo produto e de outros produtos em outros períodos.
+O DMPMPpBPTM é mais complexo do que o MPpBPTM porque, no caso do primeiro, a decisão sobre a produção de determinado produto em determinado período pode influir fortemente nos limites permitidos para produção do mesmo produto e de outros produtos em outros períodos.
+E o mesmo é válido para os limites de estocagem definidos em cada período.
 
-Para melhor compreensão do problema MPMPpBPTM e de sua complexidade, considere o problema MPpBPTM com dois produtos e um único período de planejamento (1 dia) apresentado na Tab.
-1, e o problema MPMPpBPTM com dois produtos e um horizonte de planejamento de dois dias, conforme apresentado na Tab.
-2, onde: $\textrm{p}_i$ is the production rate of product $i$; $\textrm{UD}_i$ is the demand for the product $i$; $\textrm{UD}_{id}$ is the demand for the product $i$ on day $d$; $\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets; $\textrm{UI}_i$ é o limite de estoque para o produto $i$ in the factory on the first day de planejamento; $\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets; $\textrm{I}$ é o limite de estoque in the factory para all products in the batch, on the first day de planejamento; $\textrm{Z}$ is the timeout for batch processing; $\textrm{Z}_d$ is the timeout for batch processing on day $d$.
+Para melhor compreensão do problema DMPMPpBPTM e de sua complexidade, considere o problema MPpBPTM com dois produtos e um único período de planejamento (1 dia) apresentado na Tab.
+1, e o problema DMPMPpBPTM com dois produtos e um horizonte de planejamento de dois dias, conforme apresentado na Tab.
+2, onde: $\textrm{p}_i$ is the production rate of product $i$; $\textrm{UD}_i$ is the demand for the product $i$; $\textrm{UD}_{id}$ is the demand for the product $i$ on day $d$; $\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets; $\textrm{UI}_i$ é o limite de estoque para o produto $i$; $\textrm{UI}_{id}$ é o limite de estoque para o produto $i$ no dia $d$; $\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets; $\textrm{I}$ é o limite de estoque in the factory para all products in the batch, on the first day de planejamento; $\textrm{Z}$ is the timeout for batch processing; $\textrm{Z}_d$ is the timeout for batch processing on day $d$.
 
@@
 \begin{center}
-\caption{\textbf{Benchmark MPMPpBPTM 02.}}
+\caption{\textbf{Benchmark DMPMPpBPTM 02.}}
 \begin{tabular}[c]{c r r c r}
@@
 $\textrm{UD}_{i1}$ & 1000 & 500 & \\
-$\textrm{UD}_{i2}$ &  500 & 500 & \\
+$\textrm{UD}_{i2}$ &  200 & 500 & \\
 $\textrm{UO}_i$ & 600 & 600 & $\textrm{O}$ & 1000 \\
-$\textrm{UI}_i$ & 3000 & 2000 & $\textrm{I}$ & 3000 \\
+$\textrm{UI}_{i1}$ & 3000 & 2000 & $\textrm{I}_1$ & 3000 \\
+$\textrm{UI}_{i2}$ & 1500 & 2000 & $\textrm{I}_2$ & 1500 \\
 \cline {1-5} \\
 & & & $\textrm{Z}_1$ & 100 \\
-& & & $\textrm{Z}_1$ &  50 \\
+& & & $\textrm{Z}_2$ &  50 \\
 \end{tabular}
@@
 
-No caso do problema MPpBPTM 02, desejamos encontrar o tempo máximo de planejamento em um único período para o lote contendo os produtos 1 e 2.
-Neste caso, podemos encontrar T, aplicando as equações matemáticas (\ref{eq:01}) e (\ref{eq:02}) propostas por Fraga (2024) para solução deste problema:
+No caso do problema MPpBPTM 02, desejamos encontrar o tempo máximo de planejamento em um único período, T, para o lote contendo os produtos 1 e 2.
+Neste caso, podemos encontrar T aplicando as equações matemáticas (\ref{eq:01}) e (\ref{eq:02}) propostas por Fraga (2024) para solução deste problema:
 
@@
 \end{equation}
+
+Aplicando estas fórmulas, teremos a solução T = 55. A produção e a distribuição desta produção para atendimento à demanda, envio para outlets e estoque em fábrica são apresentados na Tab. 3.
+
+\begin{table}[h!]
+\begin{center}
+\caption{\textbf{Results obtained for the MPpBPTM 02.}}
+\begin{footnotesize}
+\begin{tabular}[c]{c r r r r}
+\\
+product & production & delivered & send to outlets & stocked in factory \\
+\cline {1-5} \\
+1 & 3,300 & 1,000 & 400 & 1,900 \\
+2 & 2,200 &   500 & 600 & 1,100 \\
+\cline {1-5} \\
+\end{tabular}
+\label{tab:compResultsMBPTMP2}
+\end{footnotesize}
+\end{center}
+\end{table}
+
+Já no caso do problema DMPMPpBPTM 02, apresentado na Tab.
+2, é necessário considerar um planejamento para um segundo período, com nova demanda, novos limites de estocagem, e um novo limite para tempo de processamento do mesmo lote.
+Ademais, o planejamento de cada período deve ainda considerar o planejamento e as informações referentes aos outros períodos.
+
+Por exemplo, no caso do problema apresentado na Tab.
+2, antes de considerar qualquer planejamento, temos um limite de estocagem para o produto 2 de 3000 unidade no primeiro dia.
+Contudo este limite é reduzido para 1500 unidade no segundo dia.
+Isso poderia ser justificado, por exemplo, caso houvesse uma produção previamente planejada de 1500 unidados do produto 1 para o segundo dia.
+
+A Tab.
+4 apresenta uma atualização dos dados do problema DMPMPpBPTM 02, após o primeiro período, considerando a solução apresentada para o problema MPpBPTM 02, $T_1 = 55$, e usando a produção do primeiro período para atender a demanda do segundo período.
+
+\begin{table}[h!]
+\begin{center}
+\caption{\textbf{Atualização das informação do DMPMPpBPTM 02, após primeiro período com $T_1 = 55$.}}
+\begin{tabular}[c]{c r r c r}
+\\
+$i$ & 1 & 2 & & total \\
+\cline {1-5} \\
+$\textrm{p}_i$ & 60 & 40 & \\
+$\textrm{UD}_{i1}$ & 0 & 0 & \\
+$\textrm{UD}_{i2}$ &  0 & 0 & \\
+$\textrm{UO}_i$ & 100 & 100 & $\textrm{O}$ & 0 \\
+$\textrm{UI}_{i1}$ & 1,100 & 900 & $\textrm{I}_1$ & 0 \\
+$\textrm{UI}_{i2}$ & - 200 &  1400 & $\textrm{I}_2$ & -1,000 \\
+\cline {1-5} \\
+& & & $\textrm{T}_1$ &  55 \\
+& & & $\textrm{Z}_2$ &  50 \\
+\end{tabular}
+\label{tab:MBPTMP001}
+\end{center}
+\end{table}
+
+Conforme é possível verificar na Tab.
+4, considerando $T_1 = 55$, teríamos um excesso de estoque para o segundo período.
+Isso conmprova que a determinação do tempo máximo de produção do lote no primeiro período deve levar em conta as informações relativas aos outros períodos.
+Outra questão relevante a ser considerada é o melhor momento para produção.
+Isso é válido para todos os períodos considerados.
+É importante aqui também ressaltar que estoque implica em custos, portanto é sempre melhor produzir no momento mais tarde possível.
+
+A seção à seguir apresenta uma adaptação do modelo matemático proposto por Fraga(2024), para solução do DMPMPpBPTM.
 

### 2024-07-16 manuscript/MPMPBPTMP/CONEM2024.tex
DMPMPPBPTM problem - problem definition

@@
 4, considerando $T_1 = 55$, teríamos um excesso de estoque para o segundo período.
-Isso conmprova que a determinação do tempo máximo de produção do lote no primeiro período deve levar em conta as informações relativas aos outros períodos.
-Outra questão relevante a ser considerada é o melhor momento para produção.
-Isso é válido para todos os períodos considerados.
-É importante aqui também ressaltar que estoque implica em custos, portanto é sempre melhor produzir no momento mais tarde possível.
+Este resultado comprova que a determinação do tempo máximo de produção do lote no primeiro período deve levar em conta as informações relativas aos outros períodos.
+É possível demonstrar que isso é válido para todos os períodos considerados.
+Contudo tal demonstração não será apresentada neste artigo.
+Tendo em vista que as decisões de produção em cada períodos implicam em restrições de produção para outros períodos, outra questão relevante a ser considerada é o melhor momento para produção.
+Como estoque implica em custos, consideramos que é sempre melhor produzir no momento mais tarde possível.
 
-A seção à seguir apresenta uma adaptação do modelo matemático proposto por Fraga(2024), para solução do DMPMPpBPTM.
+O problema DMPMPpBPTM portanto, consiste em definir o tempo máximo de produção para lotes multi-produtos paralelos, para cade período considerado, tendo como base os seguintes aspectos:
+
+\begin{itemize}
+\item são considerados $N$ produtos, $i=1,...,N$, que devem ser processados simultaneamente em um único lote;
+\item cada produto é produzido de acordo com uma taxa de produção conhecida, $p_i$, a qual pode variar de um produto para outro;
+\item é considerado um horizonte de planejamento com $D$ períodos, $d=1,...,D$;
+\item existe uma demanda conhecida para cada produto em cada período, $\textrm{UD}_{id}$;
+\item existe um limite conhecido para a quantidade enviada de cada produto para os outlets, $\textrm{UO}_i$; 
+\item existe um limite conhecido para a quantidade enviada do conjunto de produtos para os outlets, $\textrm{O}$;
+\item as quantidades de cada produto solicitadas diretamente pelos outlets são entendidas como demanda e não influem nos limites anteriormente definidos;
+\item existe um limite conhecido para a quantidade de cada produto que pode ser estocada em fábrica, $\textrm{UI}_{id}$, sendo que estes limites podem variar de um período para outro;
+\item existe um limite conhecido para a quantidade total do conjunto de produtos que pode ser estocada em fábrica, $\textrm{U}_{d}$, sendo que este limite também pode variar de um período para outro;
+\item não é atriuída nenhuma prioridade para quais produtos devem ser estocados em fábrica ou enviados para os outlets;
+\item existe um tempo máximo para processamento do lote, $Z_d$, o qual pode variar de um período para outro;
+\item a produção deve prioritariamente atender à demanda, depois ser enviada para os outlets e, a quantidade restante estocada em fábrica, de acordo com as restrições conhecidas;
+\item deve-se produzir de acordo com a demanda e os limites de estoque e restrições de envio para os outlets, dando prioridade à produção no momento mais tarde possível;
+\item contudo a demanda deve ser atendida tão logo quanto possível;
+\item existe um planejamento prévio, o qual não pode ser alterado, todas as variáveis do problema são definidas como resultados deste planejamento prévio junto com novas informações, a demanda informada é a demanda não atendida pelo planejamento prévio;
+\item o tempo máximo de processamento para o lote de produtos em cada período, $T_d$, deve ser definido de forma que as restrições acima elencadas sejam todas respeitadas.
+\end{itemize}
+
+A seção à seguir um modelo metemático para o problema DMPMPpBPTM.
 

### 2024-07-17 manuscript/DMPMPBPTMP/CONEM2024.tex
DMPMPpBPTM problem - updating definition

--- 2024-07-16 manuscript/MPMPBPTMP/CONEM2024.tex
@@
 
-\section{Dinamic Multi-period, Multi-product p-Batch Processing Time Maximization Problem}
+\section{Dinamic Multi-period, Multi-product p-Batch Processing Time Maximization Problem - not finished yet}
 \label{sec:MBPTMP}
 
-The MPpBPTM problem arises when a set of different products are processed simultaneously in a same production batch.
+The Multi-product p-Batch Processing Time Maximization Problem (MPpBPTM) problem arises when a set of different products are processed simultaneously in a same production batch.
 In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product.
@@
 The Dinâmic Multi-period, Multi-product p-Batch Processing Time Maximization (DMPMPpBPTM) problem é uma versão mais complexa do MPpBPTM na qual considera-se um horizonte de planejamento contendo mais do que um único período (dias, semanas, etc).
-Neste caso as decisões devem ser tomadas para cada período.
+Neste caso é necessário definir o tempo máximo de processamento de cada lote para o período atual, mas considerando um horizonte de planejamento contendo vários períodos.
 Adicionamente, em um cenário dinâmico, consideramos que já existe um planejamento prévio para produção e entregas.
@@
 \cline {1-5} \\
-& & & $\textrm{Z}_1$ & 100 \\
-& & & $\textrm{Z}_2$ &  50 \\
+& & & $\textrm{Z}$ & 100 \\
 \end{tabular}
@@
 Já no caso do problema DMPMPpBPTM 02, apresentado na Tab.
-2, é necessário considerar um planejamento para um segundo período, com nova demanda, novos limites de estocagem, e um novo limite para tempo de processamento do mesmo lote.
-Ademais, o planejamento de cada período deve ainda considerar o planejamento e as informações referentes aos outros períodos.
+2, é necessário considerar que existe um planejamento prévio para o segundo período, o qual não pode ser alterado e, portanto, variação nos limites de estocagem.
+Há ainda uma demanda prevista adicional com previsão de entrega para o segundo período.
 
@@
 Contudo este limite é reduzido para 1500 unidade no segundo dia.
-Isso poderia ser justificado, por exemplo, caso houvesse uma produção previamente planejada de 1500 unidados do produto 1 para o segundo dia.
+Isso pode ser justificado, por exemplo, com uma produção previamente planejada de 1500 unidados do produto 1 para o segundo período.
 
 A Tab.
-4 apresenta uma atualização dos dados do problema DMPMPpBPTM 02, após o primeiro período, considerando a solução apresentada para o problema MPpBPTM 02, $T_1 = 55$, e usando a produção do primeiro período para atender a demanda do segundo período.
+4 apresenta uma atualização dos dados do problema DMPMPpBPTM 02, considerando a solução apresentada para o problema MPpBPTM 02, $T_1 = 55$, e usando a produção do primeiro período para atender a demanda do segundo período.
 
@@
 Contudo tal demonstração não será apresentada neste artigo.
-Tendo em vista que as decisões de produção em cada períodos implicam em restrições de produção para outros períodos, outra questão relevante a ser considerada é o melhor momento para produção.
-Como estoque implica em custos, consideramos que é sempre melhor produzir no momento mais tarde possível.
 
-O problema DMPMPpBPTM portanto, consiste em definir o tempo máximo de produção para lotes multi-produtos paralelos, para cade período considerado, tendo como base os seguintes aspectos:
+O problema DMPMPpBPTM portanto, consiste em definir o tempo máximo de produção para um lote multi-produtos paralelos, tendo como base os seguintes aspectos:
 
@@
 \item é considerado um horizonte de planejamento com $D$ períodos, $d=1,...,D$;
+\item o lote será processado no primeiro período;
 \item existe uma demanda conhecida para cada produto em cada período, $\textrm{UD}_{id}$;
@@
 \item não é atriuída nenhuma prioridade para quais produtos devem ser estocados em fábrica ou enviados para os outlets;
-\item existe um tempo máximo para processamento do lote, $Z_d$, o qual pode variar de um período para outro;
+\item existe um tempo máximo para processamento do lote, $Z$;
 \item a produção deve prioritariamente atender à demanda, depois ser enviada para os outlets e, a quantidade restante estocada em fábrica, de acordo com as restrições conhecidas;
-\item deve-se produzir de acordo com a demanda e os limites de estoque e restrições de envio para os outlets, dando prioridade à produção no momento mais tarde possível;
-\item contudo a demanda deve ser atendida tão logo quanto possível;
-\item existe um planejamento prévio, o qual não pode ser alterado, todas as variáveis do problema são definidas como resultados deste planejamento prévio junto com novas informações, a demanda informada é a demanda não atendida pelo planejamento prévio;
 \item o tempo máximo de processamento para o lote de produtos em cada período, $T_d$, deve ser definido de forma que as restrições acima elencadas sejam todas respeitadas.
@@
 
-\subsection{Mathematical Model}
+\subsection{Mathematical Model - not finished yet}
 \label{sec:mathModel}

### 2024-07-17 manuscript/DMPMPBPTMP/CONEM2024.tex
DMPMPpBPTM problem solved

@@
 Já no caso do problema DMPMPpBPTM 02, apresentado na Tab.
-2, é necessário considerar que existe um planejamento prévio para o segundo período, o qual não pode ser alterado e, portanto, variação nos limites de estocagem.
+2, é necessário considerar que existe um planejamento prévio para o segundo período e, portanto, variação nos limites de estocagem.
 Há ainda uma demanda prevista adicional com previsão de entrega para o segundo período.
@@
 Contudo este limite é reduzido para 1500 unidade no segundo dia.
-Isso pode ser justificado, por exemplo, com uma produção previamente planejada de 1500 unidados do produto 1 para o segundo período.
+Isso pode ser justificado, por exemplo, com uma ordem de produção já lançada 1500 unidados do produto 1 para o segundo período.
 
@@
 
-O problema DMPMPpBPTM portanto, consiste em definir o tempo máximo de produção para um lote multi-produtos paralelos, tendo como base os seguintes aspectos:
+O problema DMPMPpBPTM pode, portanto, ser definido como base os seguintes aspectos:
 
@@
 \item a produção deve prioritariamente atender à demanda, depois ser enviada para os outlets e, a quantidade restante estocada em fábrica, de acordo com as restrições conhecidas;
-\item o tempo máximo de processamento para o lote de produtos em cada período, $T_d$, deve ser definido de forma que as restrições acima elencadas sejam todas respeitadas.
+\item o problema consiste em definir o máximo tempo viável de processamento para o lote, $T$, e a distribuição da produção resultante, entre atendimento à demanda, envio para outlets e estocagem em fábrica, com base nas restrições acima elencadas;
 \end{itemize}
@@
 A seção à seguir um modelo metemático para o problema DMPMPpBPTM.
+
+\section{Solving - not finished yet}
+
+No caso de um DMPMPpBPTM, a produção é limitada de acordo com a demanda, o limite da quantidade de cada produto e do cunjunto de produtos que pode ser enviada para os outlets e o limite da quantidade de cada produto e do cunjunto de produtos que pode ser estocada em fábrica.
+
+Observe que, no caso de um DMPMPpBPTM, os dados relativos ao primeiro período estipulam um tempo máximo para processamento do lote, o qual não poderá ser ultrapassado, independente das demandas futuras.
+Isso porque, apesar de existir a possibilidade de atendimento das demandas futuras com a produção do primeiro período, esta produção deverá ser estocada, respeitando os limites definidos.
+
+Portanto, basicamente, a diferença entre o MPpBPTM e o DMPMPpBPTM está no fato de que poderá haver uma redução no limite considerado para estocagem em fábrica no primeiro período.
+
+Observe que, parte da quantidade estocada em fábrica no primeiro período será utilizada para atendimento à demanda no segundo período, e a quantidade restante, se houver, será mantida em estoque no segundo período.
+Portanto, podemos definir um novo limite para estocagem em fábrica no primeiro período, $UI_{i1}$, usando a equação:
+
+\begin{equation}
+UI_{i1}^* \leq min \{\textrm{UI}_{i1}, \textrm{UI}_{i2} + \textrm{UD}_{i2} \} \quad \forall i
+\end{equation}
+
+No caso de considerarmos um terceiro período, a quantidade limite para estoque em fábrica no segundo período seria também afetada pelo terceiro período, assim, a equação (3) pode ser reescrita como:
+
+\begin{equation}
+UI_{i1}^* \leq min \{\textrm{UI}_{i1},  UI_{i2}^* +  \textrm{UD}_{i2}\} \quad \forall i
+\end{equation}
+
+Estendedo a observação apresentada para um terceiro período, parte da quantidade estocada em fábrica no segundo período será utilizada para atendimento à demanda no terceiro período, e a quantidade restante, se houver, será mantida em estoque no terceiro período.
+Assim, temos:
+
+\begin{equation}
+UI_{i2}^* \leq min \{\textrm{UI}_{i2}, \textrm{UI}_{i3} + \textrm{UD}_{i3} \} \quad \forall i
+\end{equation}
+
+Substituindo (5) em (4), temos:
+
+\begin{equation}
+UI_{i1}^* \leq min \{\textrm{UI}_{i1},  min \{\textrm{UI}_{i2}, \textrm{UI}_{i3} + \textrm{UD}_{i3} \} +  \textrm{UD}_{i2}\} \quad \forall i
+\end{equation}
+
+Usando um pouco de álgebra, temos:
+
+\begin{equation}
+UI_{i1}^* \leq min \{\textrm{UI}_{i1}, \textrm{UI}_{i2} + \textrm{UD}_{i2}, \textrm{UI}_{i3} + \textrm{UD}_{i3} +  \textrm{UD}_{i2}\} \quad \forall i
+\end{equation}
+
+Assim, generaliznaod para $n$ períodos, teremos a seguinte restrição:
+
+\begin{equation}
+UI_{i1}^* \leq min \{\textrm{UI}_{i1}, \min_{d \in \mathbb{Z} , 1 \leq d \leq n} \{\textrm{UI}_{i1}, \textrm{UI}_{id} + \sum_{k=2}^{d} {\textrm{UD}_{ik}}\} \} \quad \forall i
+\end{equation}
 
